### 2023-12-25 paper.qmd
metadata

---
title: ""
abstract: "Abstract goes here"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

# Introduction

### 2023-12-25 index.qmd
break

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
---

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**

![](pngs/md.png)

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("dplyr")
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
```

```{webr-r}
ballcastsim <- function(
	dfm=app0,
	probw=c(0.5,0), 	
	probva=c(0.7,0.2,0.03,0.00), 				
	probvb=c(0.7,0.2,0.03,0.00), 
	ztech=c(0,0)
			){

  # Simulate prob
  probvrnd <<- dfm |>
    dplyr::mutate(ZV=rnorm(dplyr::n(),probw[1],probw[2])) |>
    dplyr::mutate(N=runif(dplyr::n(),ztech[1],ztech[2])) |>
    dplyr::mutate(p3=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probva[1],probva[3]))))) |>
    dplyr::mutate(p6=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probvb[1],probvb[3]))))) |>
    dplyr::mutate(p2=(1-p3)*pmax(0, pmin(1,rnorm(dplyr::n(),probva[2],probva[4])))) |>
    dplyr::mutate(p5=(1-p6)*pmax(0, pmin(1,rnorm(dplyr::n(),probvb[2],probvb[4])))) |>
    dplyr::mutate(p1=1-p2-p3) |>
    dplyr::mutate(p4=1-p5-p6) |>
    dplyr::select(P,ZV,N,p1,p2,p3,p4,p5,p6)

  #ballcodf <- dfm |> dplyr::left_join(probvrnd,by='P') |> base::split(.$P) |>
  #     purrr::map(function(x){
  ## Assigning voters in each precinct
  #cp <- stats::rbinom(x$R,1,x$ZV) 
  ### Setting up vector frame
  #dc <- data.frame(P=x$P,ZV=x$ZV,R=x$R,C=cp,p1=x$p1,p2=x$p2,p3=x$p3,p4=x$p4,p5=x$p5,p6=x$p6) |>
  #  dplyr::mutate(Id=row_number()) |> 
  #  dplyr::relocate(Id,.before=P)  |>
  #  dplyr::group_by(Id) |> 
  #  dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(p1,p2,p3)),sample(4:6,1,prob=c(p4,p5,p6)))) |>
  #  dplyr::ungroup() 
  #})  |>
  #dplyr::bind_rows(.) |>
  #dplyr::mutate(Id=row_number(P)) |> 
  #dplyr::relocate(Id,.before=P) |> 
  #dplyr::mutate(S=ifelse(V==1,1,0)) |> 
  #dplyr::mutate(T=ifelse(V==4,1,0)) |>  
  #dplyr::mutate(U=ifelse(V==2,1,0)) |>
  #dplyr::mutate(V=ifelse(V==5,1,0)) |>
  #dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
  #dplyr::select(c('P','R','S','T','U','V')) |>
  #dplyr::mutate(S=sum(S),T=sum(T),U=sum(U),V=sum(V)) |>
  #dplyr::distinct() |> 
  #dplyr::mutate(Z=sum(S+T+U+V)) |>
  #dplyr::ungroup() 
}
print(ballcastsim())
```

```{r, echo=F}
knitr::knit_exit()
```

[From Bard:](https://g.co/bard/share/37bfadf733c5)

Published July 22, 2023 at 05:37 AM

> The first problem is that the proportion of votes cast by mail (w) is nearly constant across all precincts. This is not what we would expect to see in a fair election, where the proportion of votes cast by mail would vary depending on the demographics of the precinct. For example, we would expect to see a higher proportion of votes cast by mail in precincts with a higher population of elderly people.

> The second problem is that we can calculate D knowing only K and A. This is also not possible in a fair election, as D should be determined by the number of ballots cast by mail, which is not known until after all ballots have been cast.

> The third problem is that n decreases rapidly over the quantiles of z, meaning that Democrats are more likely to cast their ballots by mail as Republicans perform better overall. This is not what we would expect to see in a fair election, as we would expect the proportion of Democrats and Republicans who vote by mail to be relatively constant.

> The fourth problem is that the difference between x and y diverges rapidly over the quantiles of z, meaning that as Republican do better in the early vote, the more they suffer in the mail-in vote. This is also not what we would expect to see in a fair election, as we would expect the two types of votes to be relatively correlated.

```{webr-r}
webr::install("ManifoldDestinyWASM", repos = "https://lotariohw26.github.io/ManifoldDestinyWASM/repo")
library(ManifoldDestinyWASM)
ls(package:ManifoldDestinyWASM)
```

### 2023-12-26 presentation.qmd
makefile

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
```

# `r #metad$toc$sec1$nmn`

```{r}
knitr::knit_exit()
```

 Ed. Solomon

> "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.

## `r metad$toc$sec1$unm[1]`

- Two candidates: A, B
- County with three precincts: 1, 2, 3
- Two modes of voting
  - Number of ballots mode 1: S, T
  - Number of ballots mode 2: U, V

##

```{r, echo=F, caption="Example 1"}
## Tower 1
ex1m <- as.matrix(cbind(S,T,U,V))
towi <- as.data.frame(ex1m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))

towi[3:4,1] <- ""
towi[4,2] <- ""
lego_hux_nor_i <- hux(towi[,1:3]) 
lego_hux_nor_i 
```

```{r, echo=F, caption="Example 2"}
## Tower 2
ex2m <- as.matrix(cbind(S,T,Up,Vp))
towii <- as.data.frame(ex2m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))
towii[3:4,1] <- ""
towii[4,2] <- ""
lego_hux_nor_ii <- hux(towii[,1:3]) 
lego_hux_nor_ii 
```

## `r metad$toc$sec1$unm[2]`

```{r, echo=F}
lego_hux_nor <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
  set_background_color(1, 1:2, "black") %>% 
  set_background_color(2, 1:2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_nor %>% set_caption("")
```

Parameters: ** $x$, $y$, $\zeta$, $\alpha$, $\lambda$ **
\begin{equation*}
x=`r modlat$x_s[1]` \text{, }y=`r modlat$y_s[1]`
\end{equation*}
\begin{equation*}
\zeta=`r modlat$zeta_s[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lamda_s[1]`=`r modlat$lamda_s[2]`
\end{equation*}

##

```{r, echo=F}
ctone_sf <- 'Election results applying standard form on case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

Numerical calculation of candidate one total percentage
- Precinct 1
 - $\alpha=\frac{`r cx[1]`+`r cy[1]`\cdot `r czeta[1]`}{1+`r czeta[1]`}=`r calpha[1]`$
- Precinct 2
 - $\alpha=\frac{`r cx[2]`+`r cy[2]`\cdot `r czeta[2]`}{1+`r czeta[2]`}=`r calpha[2]`$
- Precinct 3
 - $\alpha=\frac{`r cx[3]`+`r cy[3]`\cdot `r czeta[3]`}{1+`r czeta[3]`}=`r calpha[3]`$

## `r metad$toc$sec1$unm[3]`

```{r, echo=F}
lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(1:2, 1, "black") %>% 
  set_background_color(1:2, 2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_imp %>% set_caption("")
```

Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
\begin{equation*}
g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
\end{equation*}

##

```{r, echo=F}
ctone_hf <- 'Election results applying hybrid form case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

Numerical calculation of candidate one total percentage
- Precinct 1
 - $\alpha=\frac{`r cg[1]`+`r ch[1]`\cdot `r cGamma[1]`}{1+`r cGamma[1]`}=`r calpha[1]`$
- Precinct 2
 - $\alpha=\frac{`r cg[2]`+`r ch[2]`\cdot `r cGamma[2]`}{1+`r cGamma[2]`}=`r calpha[2]`$
- Precinct 3
 - $\alpha=\frac{`r cg[3]`+`r ch[3]`\cdot `r cGamma[3]`}{1+`r cGamma[3]`}=`r calpha[3]`$

```{r, echo=F}
ctone_hf <- 'Election results applying hybrid form case II'
stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

## `r metad$toc$sec1$unm[4]`

```{r, echo=F}
lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(c(1),c(1), "black") %>% 
  set_background_color(c(2),c(2), "black") %>% 
  set_background_color(c(1),c(2), "grey") %>% 
  set_background_color(c(2),c(1), "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_opo %>% set_caption("")
```
Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$
\begin{equation*}
n=`r modlat$n_o[1]` \text{ , } m=`r modlat$m_o[1]`
\end{equation*}
\begin{equation*}
\xi=`r modlat$xi_o[1]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_o[1]`=`r modlat$Omega_o[2]`
\end{equation*}
\begin{equation*}
\lambda=`r modlat$lamda_o[1]`=`r modlat$lamda_o[2]`
\end{equation*}

##

```{r, echo=F}
ctone_of <- 'Election results applying opposition form'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
kableExtra::kbl(format(stfo_sel,digits=4), caption=ctone_of) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

## `r metad$toc$sec1$unm[5]`

- **Step 1:** Each registered voter assign themself (independent of voting technology) to either candidate A or candidate B
- **Step 2:** Voting technology realized
- **Step 3:** Registered voters determine whether to vote or not to vote 
- **Step 4:** If voting, do this by either mode 1 or by mode 2.

```{mermaid}
  flowchart LR
  A[Candidate A or B] --> R[A]
  R --> RV[Vote]
  RV --> RVE[Non-Mail]
  RV --> RVM[Mail]
  R --> RN[Not Vote]
  DV --> DVE[Non-Mail]
  DV --> DVM[Mail]
  A --> D[B]
  D --> DV[Vote]
  D --> Dn[Not Vote]
```

##

- Probability of assigning oneself to candidate A in precinct $i$
  - $p_{w,i} \sim N(\alpha_i,\sigma^2_{w,i})$
- Voting technology
  - $z_i \sim U(0,1)$
- Probability of not voting in precinct $i$
  - Candidate A, $p_{nz,a,i}=(1-z_i)p_{n,a,i}\sim N(\alpha_{a,n},\sigma^2_{a,n})$ <br>
  - Candidate B, $p_{nz,b,i}=(1-z_i)p_{n,b,i}\sim N(\alpha_{b,n},\sigma^2_{b,n})$
- Probability of voting by mode 2 in precinct $i$
  - Candidate A, $p_{m2,a,i}=(1-p_{nv,a,i})p_{a,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
  - Candidate B, $p_{m2,b,i}=(1-p_{nv,b,i})p_{b,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
- Probability of voting by mode 1 in precinct $i$
  - Candidate A, $p_{m1,a,i}=1-p_{m2,a,i}-p_{nz,a,i}$ 
  - Candidate B, $p_{m1,b,i}=1-p_{m2,b,i}-p_{nz,b,i}$

Neutral-voting assumption:

- Decission to vote or not to vote is independent of voting preferences:
  - $p_{nz,a,i}=p_{nz,a,i}$ 
- If voting, decission to vote by mode 1 or by mode 2 independent of voting preferences: 
  - $p_{m2,a,i}=p_{m2,a,i}$

Note: As we will investigate later, this condition might be needed in order to restore a rigged election to its original form.

## `r metad$toc$sec1$unm[6]`

1. Differences in the cost of voting (e.g., topology, voting rules, dropboxes etc.) across precincts $\Rightarrow$
1. Changes to the likelihood of voting $\Rightarrow$ 
1. Simplify so that changes in the likelihood of voting only impact Mode 2 $\Rightarrow$ 
1. Higher $\zeta_i$ $\Rightarrow$
1. Which changes the total election outcome through $\alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}$

##

The impact on the election outcome, however, would be small or close to non-existens if the conditions
of the existance of a *trivial* Manifold occuranse related to normal form are not satisfied:

- Proportion of mail-in-votes to election day vote is already high (Aggregate convergence lemma)
  - Note: $\lim_{\zeta_i \rightarrow \infty} \alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}=y_i$
- Correlation between $x$ and $y$ is very high (Twixt lemma)
  - Note: If correlation is 1, we can set $x_i=\rho_s y_i$ so that $\alpha_i(y_i,\zeta_i)=\frac{\rho_s y_i+\zeta_i y_i}{\zeta_i+x_i}$
- Low variance to $\zeta$ 
  - Note: Invariance across precincts would imply that $\zeta_i=\zeta$, so that election outcome only determined by variations in two parameters: $\alpha_i(y_i,x_i)=\frac{x_i+\zeta y_i}{\zeta+x_i}$

If none of this three cases are satisfied, variation in $\zeta_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?

## `r metad$toc$sec1$unm[7]`

1. Differenc in the cost of voting (e.g., topology, voting rules, dropboxes, socio economics etc.) across precincts $\Rightarrow$ 
1. Make changes to the likelihood of voting $\Rightarrow$ 
1. Simplify so that changes in the likelihood of voting only impact mode 2 $\Rightarrow$ 
1. Higher $\zeta_i$ $\Rightarrow$
1. If new and earlier sample not representative of each other, higher $\Gamma_i$ $\Rightarrow$
1. Which changes the total election outcome through $\alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+1}$

##

The impact on the election outcome, however, would be small or close to non-existens if the conditions
of the existance of a *trivial* Manifold related to opposition form are not satisfied:

- Proportion of the hybrid ballot boxes is already high (Aggregate convergence lemma)
  - Note: $\lim_{\Gamma_i \rightarrow \infty} \alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+g_i}=y_i$
- Correlation between $g$ and $h$ is very high (Twixt lemma)
  - Note: If correlation is 1, we can set $g_i=\rho_h h_i$ so that $\alpha_i(h_i,\Gamma_i)=\frac{\rho_h h_i+\Gamma_i h_i}{\Gamma_i+x_i}$
- Low variance to $\Gamma_i$ 
  - Note: Invariance across precincts would imply that $\Gamma_i=\Gamma$, so that election outcome only determined by variations in two parameters: $\alpha_i=\frac{g_i+\Gamma h_i}{h_i}$

If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?

# `r metad$toc$sec2$nmn`

## `r metad$toc$sec2$unm[1]`

- We have identified three ways of counting
  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
-  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
  -  We are free to *predetermine* **3** of them
  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
  -  Selecting **3** parameters from a set of **5** implies **10** different combinations

## `r metad$toc$sec2$unm[2]`

**20 laws and 40 isometris**

```{r, echo=F}
# Load necessary library
library(tibble)

# Create the data.frame
laws_df <- tribble(
  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
)
# Display the data.frame
kable(laws_df, format = "markdown", escape = FALSE)
```

##

::: {.callout-caution collapse="true"}
## Proportions

```{r, echo=F}
library(kableExtra)
library(tibble)
new_tbl <- data.frame(
  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
)

# Extract the columns
V1 <- new_tbl$V1
V2 <- new_tbl$V2
V3 <- new_tbl$V3
V4 <- new_tbl$V4
Equation1 <- new_tbl$Equation1
Equation2 <- new_tbl$Equation2
Equation3 <- new_tbl$Equation3
Equation4 <- new_tbl$Equation4

# Combine the columns
combined <- data.frame(
  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
)
kable(combined, format = "markdown", escape = FALSE)
```

:::

[@delfino2011analysis]

## `r metad$toc$sec2$unm[3]`

## `r metad$toc$sec2$unm[4]`

## `r metad$toc$sec2$unm[5]`

# `r metad$toc$sec3$nmn`

## `r metad$toc$sec3$unm[1]`

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_n_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_n_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_n_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_n_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_n_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_n_out[['resp']]
```

:::

## `r metad$toc$sec3$unm[2]`

**Example 1: Normal form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex1_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex1_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex1_out[['resp']]
```

:::

##

**Example 2: applying hybrid form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex2_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex2_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex2_out[['resp']]
```

:::

##

**Example 3: applying opposition form**

::: {.panel-tabset}

### `r metad$tabsets[[1]]`

```{r, echo=F}
kableExtra::kbl(app_ex3_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```

### `r metad$tabsets[[2]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['corxy']]
```

### `r metad$tabsets[[3]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['qunt']]
```

### `r metad$tabsets[[4]]`

```{r, echo=F}
app_ex3_out[['ro3d']]
```

### `r metad$tabsets[[5]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['regr']]
```

### `r metad$tabsets[[6]]`

```{r, echo=F, out.width="60%"}
app_ex3_out[['resp']]
```

:::

# `r metad$toc$sec4$nmn` {#litrev}

```{r, echo=FALSE, out.width="20%", fig.cap=""}
p1 <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/ss.png')
knitr::include_graphics(c(p1))
```

`r #Citet(bib, "delfino2011analysis")`

> Abstract: On August 15th, **2004**, Venezuelans had the opportunity to vote
in a Presidential Recall Referendum **to decide whether or not President Hugo
Chávez should be removed from office.** **The process was largely computer-
ized using a touch-screen system.** In general the ballots were not manually
counted. The significance of the high linear correlation (0.99) between the
number of requesting signatures for the recall petition and the number of op-
position votes in computerized centers is analyzed. The same-day audit was
found to be not only ineffective but a source of suspicion...

::: aside
[Link to Youtube-video](https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s)
:::

##

- Venezuela referendum to recall President Hugo Chávez (2004)
	- Mode 1: Computerized Voting Centers
	- Mode 2: Manuel Voting Centers

> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.

```{r, echo=FALSE, out.width="85%", fig.cap=""}
p3 <- paste0(rprojroot::find_rstudio_root_file(),'pngs/manifold.png')
knitr::include_graphics(c(p3))
```

# `r metad$toc$sec5$nmn` {#proced}

# `r metad$toc$sec5$unm[1]`

1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
1. Check for normality of the estimated residual for the Manifold model.

If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.

# `r metad$toc$sec6$nmn`

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="1")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

```{r, echo=FALSE, results='asis',warning=F}
params <- list(name="2")
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```

# `r metad$toc$sec7$nmn`

- At the heart of the difference between a fair and rigged election is the issue of causation
  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate

- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.

##

- Condition on that $R^2$ falls within the critical region.
  - Normal form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2n.png')
knitr::include_graphics(c(pr2n))
```

 - Hybrid form
```{r, echo=F, out.width="40%", fig.cap=""}
pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2h.png')
knitr::include_graphics(c(pr2h))
```

- Our four applications

```{r, echo=F, warning=F, message=F}
#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

# `r metad$toc$sec8$nmn`

::: {#refs}
:::

### 2023-12-26 R/misc_py.R

@@ -1,0 +1,283 @@
+#test <- function(abc=NULL){
+#  library(ManifoldDestiny)
+#  library(ggplot2)
+#  library(dplyr)
+#  library(googlesheets4)
+#  library(htmltools)
+#  library(gridExtra)
+#  md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+#  googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
+#  lapply(paste0("app",2:2), function(x){recoudatr(mda=md[[x]])})
+#}
+#lapply(paste0("app",0:4), function(x){recoudatr(mda=md[[x]])})
+
+#' @export recoudatr
+recoudatr <- function(mda=NULL){
+  gsh <- googlesheets4::read_sheet(mda$sht$url,sheet=mda$sht$pgn,range=mda$sht$rng) %>%
+    data.table::setnames(new=mda$sht$cln) %>%
+    dplyr::select(-starts_with('D')) %>%
+    dplyr::mutate(P=row_number(PN)) %>%
+    dplyr::mutate(R=row_number(RN)) %>%
+    dplyr::mutate(S=!!rlang::parse_expr(mda$sht$stuv[1])) %>%
+    dplyr::mutate(T=!!rlang::parse_expr(mda$sht$stuv[2])) %>%
+    dplyr::mutate(U=!!rlang::parse_expr(mda$sht$stuv[3])) %>%
+    dplyr::mutate(V=!!rlang::parse_expr(mda$sht$stuv[4]))
+  assign(mda$nid,gsh)
+  do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
+  return(gsh)
+}
+
+#' @export gmp
+gmp <- function(terms=c("x2","xy","y2","x3","x2y","y2x","y3")){
+  # Preallocate a list to store expressions
+  nrc <- as.character(rep(1:4))
+  expre <- vector("list", length(terms))
+  # Iterate over the terms
+  for(i in seq_along(terms)){
+    term <- terms[i]
+    nl <- gsub("\\d","",term)
+    chars <- strsplit(term, "")[[1]]
+    ac <- paste0(chars,collapse="*")
+    ind <- unlist(gregexpr("\\d",ac))
+    sapply(1:nchar(nl), function(i){
+      lcl <- regexpr(substring(nl,i,i), term)[[1]]
[…]

### 2023-12-26 R/simulations.R

@@ -21,31 +21,31 @@ ballcastsim <- function(
     dplyr::mutate(p4=1-p5-p6) |>
     dplyr::select(P,ZV,N,p1,p2,p3,p4,p5,p6)
 
-  #ballcodf <- dfm |> dplyr::left_join(probvrnd,by='P') |> base::split(.$P) |>
-  #     purrr::map(function(x){
-  ## Assigning voters in each precinct
-  #cp <- stats::rbinom(x$R,1,x$ZV) 
-  ### Setting up vector frame
-  #dc <- data.frame(P=x$P,ZV=x$ZV,R=x$R,C=cp,p1=x$p1,p2=x$p2,p3=x$p3,p4=x$p4,p5=x$p5,p6=x$p6) |>
-  #  dplyr::mutate(Id=row_number()) |> 
-  #  dplyr::relocate(Id,.before=P)  |>
-  #  dplyr::group_by(Id) |> 
-  #  dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(p1,p2,p3)),sample(4:6,1,prob=c(p4,p5,p6)))) |>
-  #  dplyr::ungroup() 
-  #})  |>
-  #dplyr::bind_rows(.) |>
-  #dplyr::mutate(Id=row_number(P)) |> 
-  #dplyr::relocate(Id,.before=P) |> 
-  #dplyr::mutate(S=ifelse(V==1,1,0)) |> 
-  #dplyr::mutate(T=ifelse(V==4,1,0)) |>  
-  #dplyr::mutate(U=ifelse(V==2,1,0)) |>
-  #dplyr::mutate(V=ifelse(V==5,1,0)) |>
-  #dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
-  #dplyr::select(c('P','R','S','T','U','V')) |>
-  #dplyr::mutate(S=sum(S),T=sum(T),U=sum(U),V=sum(V)) |>
-  #dplyr::distinct() |> 
-  #dplyr::mutate(Z=sum(S+T+U+V)) |>
-  #dplyr::ungroup() 
+  ballcodf <- dfm |> dplyr::left_join(probvrnd,by='P') |> base::split(.$P) |>
+       purrr::map(function(x){
+  # Assigning voters in each precinct
+  cp <- stats::rbinom(x$R,1,x$ZV) 
+  ## Setting up vector frame
[…]

### 2023-12-27 index.qmd
makefile
beff

@@
 **Based upon the ideas developed by Edward K. Solomon**
-
 ![](pngs/md.png)
@@
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("dplyr")
+webr::install(c("dplyr","purrr"))
 library(ManifoldDestinyWASMP)
@@
 ```{webr-r}
-ballcastsim <- function(
-	dfm=app0,
-	probw=c(0.5,0), 	
-	probva=c(0.7,0.2,0.03,0.00), 				
-	probvb=c(0.7,0.2,0.03,0.00), 
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install(c("dplyr","purrr"))
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
+probw=c(0.5,0.02)
+probva=c(0.7,0.2,0.03,0.00)
+probvb=c(0.7,0.2,0.03,0.00)
 ztech=c(0,0)
-			){
-
 # Simulate prob
@@
   dplyr::mutate(p4=1-p5-p6) |>
-    dplyr::select(P,ZV,N,p1,p2,p3,p4,p5,p6)
-
-  #ballcodf <- dfm |> dplyr::left_join(probvrnd,by='P') |> base::split(.$P) |>
-  #     purrr::map(function(x){
-  ## Assigning voters in each precinct
-  #cp <- stats::rbinom(x$R,1,x$ZV) 
-  ### Setting up vector frame
-  #dc <- data.frame(P=x$P,ZV=x$ZV,R=x$R,C=cp,p1=x$p1,p2=x$p2,p3=x$p3,p4=x$p4,p5=x$p5,p6=x$p6) |>
-  #  dplyr::mutate(Id=row_number()) |> 
-  #  dplyr::relocate(Id,.before=P)  |>
-  #  dplyr::group_by(Id) |> 
-  #  dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(p1,p2,p3)),sample(4:6,1,prob=c(p4,p5,p6)))) |>
-  #  dplyr::ungroup() 
-  #})  |>
-  #dplyr::bind_rows(.) |>
-  #dplyr::mutate(Id=row_number(P)) |> 
-  #dplyr::relocate(Id,.before=P) |> 
-  #dplyr::mutate(S=ifelse(V==1,1,0)) |> 
-  #dplyr::mutate(T=ifelse(V==4,1,0)) |>  
-  #dplyr::mutate(U=ifelse(V==2,1,0)) |>
-  #dplyr::mutate(V=ifelse(V==5,1,0)) |>
-  #dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
-  #dplyr::select(c('P','R','S','T','U','V')) |>
-  #dplyr::mutate(S=sum(S),T=sum(T),U=sum(U),V=sum(V)) |>
-  #dplyr::distinct() |> 
-  #dplyr::mutate(Z=sum(S+T+U+V)) |>
-  #dplyr::ungroup() 
-}
-print(ballcastsim())
+  dplyr::select(P,RV,ZV,N,p1,p2,p3,p4,p5,p6) |>
+  dplyr::group_split(P)
+abc <- lapply(seq(1,length(probvrnd)),function(x){
+  inpv <- probvrnd[[x]]
+  dfa <- data.frame(P=rep(inpv$P,inpv$RV),R=inpv$RV,C=stats::rbinom(inpv$RV,1,inpv$ZV)) |> 
+  dplyr::mutate(Id=dplyr::row_number()) |>
+  dplyr::group_by(Id) |>
+  dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(inpv$p1,inpv$p2,inpv$p3)),sample(4:6,1,prob=c(inpv$p4,inpv$p5,inpv$p6)))) |>
+  dplyr::mutate(S=ifelse(V==1,1,0)) |> 
+  dplyr::mutate(T=ifelse(V==4,1,0)) |>  
+  dplyr::mutate(U=ifelse(V==2,1,0)) |>
+  dplyr::mutate(V=ifelse(V==5,1,0)) 
+})
+def <- do.call("rbind", abc) |> 
+  dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
+  dplyr::select(c('P','R','S','T','U','V')) |>
+  dplyr::mutate(S=sum(S),T=sum(T),U=sum(U),V=sum(V)) |>
+  dplyr::distinct() |> 
+  dplyr::mutate(Z=sum(S+T+U+V)) |>
+  dplyr::ungroup() 
+def
 ```
@@
 knitr::knit_exit()
+```
+
+```{r}
+library(dplyr)
+
+# Sample data frame
+df <- data.frame(
+  P = c(1, 2, 1, 2, 3),
+  Value = c("A", "B", "C", "D", "E")
+)
+
+# Split the data frame by the 'P' column
+df_list <- df %>% group_split(P)
+str(df_list)
+# Access the individual groups
+for (group in df_list) {
+  print(group)
+}
 ```

### 2023-12-27 presentation.qmd
beff

@@
 mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
 ```

### 2023-12-27 R/simulations.R

@@ -1,54 +1,42 @@
-library(ManifoldDestiny)
 library(dplyr)
+library(ManifoldDestiny)
 #' @export ballcastsim
-ballcastsim <- function(
-	dfm=app0,
-	probw=c(0.5,0), 	
-	probva=c(0.7,0.2,0.03,0.00), 				
-	probvb=c(0.7,0.2,0.03,0.00), 
-	ztech=c(0,0)
-			){
-
-  # Simulate prob
-  probvrnd <<- dfm |>
-    dplyr::mutate(ZV=rnorm(dplyr::n(),probw[1],probw[2])) |>
-    dplyr::mutate(N=runif(dplyr::n(),ztech[1],ztech[2])) |>
-    dplyr::mutate(p3=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probva[1],probva[3]))))) |>
-    dplyr::mutate(p6=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probvb[1],probvb[3]))))) |>
-    dplyr::mutate(p2=(1-p3)*pmax(0, pmin(1,rnorm(dplyr::n(),probva[2],probva[4])))) |>
-    dplyr::mutate(p5=(1-p6)*pmax(0, pmin(1,rnorm(dplyr::n(),probvb[2],probvb[4])))) |>
-    dplyr::mutate(p1=1-p2-p3) |>
-    dplyr::mutate(p4=1-p5-p6) |>
-    dplyr::select(P,ZV,N,p1,p2,p3,p4,p5,p6)
-
-  ballcodf <- dfm |> dplyr::left_join(probvrnd,by='P') |> base::split(.$P) |>
-       purrr::map(function(x){
-  # Assigning voters in each precinct
-  cp <- stats::rbinom(x$R,1,x$ZV) 
-  ## Setting up vector frame
-  dc <- data.frame(P=x$P,ZV=x$ZV,R=x$R,C=cp,p1=x$p1,p2=x$p2,p3=x$p3,p4=x$p4,p5=x$p5,p6=x$p6) |>
-    dplyr::mutate(Id=row_number()) |> 
-    dplyr::relocate(Id,.before=P)  |>
-    dplyr::group_by(Id) |> 
[…]

### 2023-12-27 index.qmd
updpage

@@
 ```{webr-r}
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install(c("dplyr","purrr"))
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
-probw=c(0.5,0.02)
-probva=c(0.7,0.2,0.03,0.00)
-probvb=c(0.7,0.2,0.03,0.00)
-ztech=c(0,0)
-# Simulate prob
+ballcastsim <- function(
+  dfm=(function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10),
+  probw=c(0.5,0.02),
+  probva=c(0.7,0.2,0.03,0.00),
+  probvb=c(0.7,0.2,0.03,0.00),
+  ztech=c(0,0)){
+
   probvrnd <<- dfm |>
@@
     dplyr::group_split(P)
-abc <- lapply(seq(1,length(probvrnd)),function(x){
+  voticp <- lapply(seq(1,length(probvrnd)),function(x){
     inpv <- probvrnd[[x]]
@@
 })
-def <- do.call("rbind", abc) |> 
+  votpc <- do.call("rbind", voticp) |> 
     dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
@@
     dplyr::ungroup() 
-def
+}
+print(ballcastsim())
 ```

### 2023-12-27 R/simulations.R

@@ -1,55 +1,43 @@
-library(dplyr)
-library(ManifoldDestiny)
 #' @export ballcastsim
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
-probw=c(0.5,0.02)
-probva=c(0.7,0.2,0.03,0.00)
-probvb=c(0.7,0.2,0.03,0.00)
-ztech=c(0,0)
-# Simulate prob
-probvrnd <<- dfm |>
-  dplyr::mutate(ZV=rnorm(dplyr::n(),probw[1],probw[2])) |>
-  dplyr::mutate(N=runif(dplyr::n(),ztech[1],ztech[2])) |>
-  dplyr::mutate(p3=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probva[1],probva[3]))))) |>
-  dplyr::mutate(p6=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probvb[1],probvb[3]))))) |>
-  dplyr::mutate(p2=(1-p3)*pmax(0, pmin(1,rnorm(dplyr::n(),probva[2],probva[4])))) |>
-  dplyr::mutate(p5=(1-p6)*pmax(0, pmin(1,rnorm(dplyr::n(),probvb[2],probvb[4])))) |>
-  dplyr::mutate(p1=1-p2-p3) |>
-  dplyr::mutate(p4=1-p5-p6) |>
-  dplyr::select(P,RV,ZV,N,p1,p2,p3,p4,p5,p6) |>
-  dplyr::group_split(P)
-abc <- lapply(seq(1,length(probvrnd)),function(x){
-  inpv <- probvrnd[[x]]
-  dfa <- data.frame(P=rep(inpv$P,inpv$RV),R=inpv$RV,C=stats::rbinom(inpv$RV,1,inpv$ZV)) |> dplyr::mutate(Id=row_number()) |>
-  dplyr::group_by(Id) |>
-  dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(inpv$p1,inpv$p2,inpv$p3)),sample(4:6,1,prob=c(inpv$p4,inpv$p5,inpv$p6)))) |>
-  dplyr::mutate(S=ifelse(V==1,1,0)) |> 
-  dplyr::mutate(T=ifelse(V==4,1,0)) |>  
[…]

### 2023-12-27 presentation.qmd
updpak

--- 2023-12-26 presentation.qmd
@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
 ```
@@
 # `r #metad$toc$sec1$nmn`
-
-```{r}
-knitr::knit_exit()
-```
 
@@
 
+---
+
+```{webr-r}
+2+2
+```
+
 # `r metad$toc$sec2$nmn`
+
+```{r}
+knitr::knit_exit()
+```
 

### 2023-12-27 script/simulations.R

@@ -85,69 +85,69 @@ probw <- c(m=0.51,s=0.10)
 probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
 probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
 ztech <- c(0,1)	
-app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
-######### Normal form
-app_n_rep <- selreport(app_bal,md$app0)
-app_n_out <- seloutput(app_n_rep)
-app_n_sim <- SimVoterdatabase(app_bal)
-######## Rigged example 1: standard form
-app_ex1_cou <- Countinggraphs(app_bal)
-#print(app_ex1_cou$polyc[[1]][[1]])
-app_ex1_cou$sortpre()
-app_ex1_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
-#app_ex1_cou$setres(NULL,0)
-app_ex1_cou$setres(0.23,0)
-app_ex1_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),TRUE,wn=c(0,0))
-app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
-app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
-######## Rigged example 2: hybrid form
-app_ex2_cou <- Countinggraphs(app_bal)
-pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
-#print(app_ex2_cou$polyc[[1]][[1]])
-app_ex2_cou$sortpre()
-app_ex2_cou$mansys(sygen=list(frm=2,pre=c("alpha","g","h"),end=c("Gamma","Omega"),FALSE,me=c(plnr=1,rot=0)))
-app_ex2_cou$setres(NULL,0)
-app_ex2_cou$setres(0.23,0)
-app_ex2_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
-app_ex2_out <- seloutput(selreport(app_ex2_cou$rdfc,md$app0))
-app_ex2_sim <- SimVoterdatabase(app_ex2_cou$rdfc)
-###### Rigged example 3: Hybrid form
[…]

### 2023-12-27 index.qmd
clean

@@
 ```{webr-r}
-ballcastsim <- function(
-  dfm=(function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10),
-  probw=c(0.5,0.02),
-  probva=c(0.7,0.2,0.03,0.00),
-  probvb=c(0.7,0.2,0.03,0.00),
-  ztech=c(0,0)){
+Countingprocess <- setRefClass("Countingprocess", 
+			       fields=list(sdfc='data.frame',
+					   rdfci='data.frame',
+					   rdfc='data.frame',
+					   rofc='data.frame',
+                                           rdfce='data.frame', 
+					   quintile='data.frame',
+					   desms='data.frame', 
+					   r2list='list', 
+					   predet='list',
+					   sumreg='vector', 
+					   psel='vector', 
+					   polyc='list',
+					   radpar='vector',
+					   parameters='list', 
+					   preend='list', 
+					   parampre='data.frame', 
+                                           rotplotly='list',
+					   se='list',
+					   lx='list',
+					   pl_2dsort='list',
+					   pl_corrxy='list',
+					   pl_rescro='list',
+					   pl_3d_mani='list',  
+					   all_pl_3d_mani='list',
+					   enf='list',
+					   mansysl='list',
+					   gensysl='list',
+					   exnrs='vector',
+					   allvar='list',
+					   eqpar='list',
+					   loss_df='data.frame'
+					   ))
+Countingprocess$methods(initialize=function(sdfinp=NULL,
+					   selvar=c('P','R','S','T','U','V'), 
+					   polyn=9, 
+					   sortby=alpha
+					   ){
 
-  probvrnd <<- dfm |>
-    dplyr::mutate(ZV=rnorm(dplyr::n(),probw[1],probw[2])) |>
-    dplyr::mutate(N=runif(dplyr::n(),ztech[1],ztech[2])) |>
-    dplyr::mutate(p3=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probva[1],probva[3]))))) |>
-    dplyr::mutate(p6=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probvb[1],probvb[3]))))) |>
-    dplyr::mutate(p2=(1-p3)*pmax(0, pmin(1,rnorm(dplyr::n(),probva[2],probva[4])))) |>
-    dplyr::mutate(p5=(1-p6)*pmax(0, pmin(1,rnorm(dplyr::n(),probvb[2],probvb[4])))) |>
-    dplyr::mutate(p1=1-p2-p3) |>
-    dplyr::mutate(p4=1-p5-p6) |>
-    dplyr::select(P,RV,ZV,N,p1,p2,p3,p4,p5,p6) |>
-    dplyr::group_split(P)
-  voticp <- lapply(seq(1,length(probvrnd)),function(x){
-    inpv <- probvrnd[[x]]
-    dfa <- data.frame(P=rep(inpv$P,inpv$RV),R=inpv$RV,C=stats::rbinom(inpv$RV,1,inpv$ZV)) |> 
-    dplyr::mutate(Id=dplyr::row_number()) |>
-    dplyr::group_by(Id) |>
-    dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(inpv$p1,inpv$p2,inpv$p3)),sample(4:6,1,prob=c(inpv$p4,inpv$p5,inpv$p6)))) |>
-    dplyr::mutate(S=ifelse(V==1,1,0)) |> 
-    dplyr::mutate(T=ifelse(V==4,1,0)) |>  
-    dplyr::mutate(U=ifelse(V==2,1,0)) |>
-    dplyr::mutate(V=ifelse(V==5,1,0)) 
 })
-  votpc <- do.call("rbind", voticp) |> 
-    dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
-    dplyr::select(c('P','R','S','T','U','V')) |>
-    dplyr::mutate(S=sum(S),T=sum(T),U=sum(U),V=sum(V)) |>
-    dplyr::distinct() |> 
-    dplyr::mutate(Z=sum(S+T+U+V)) |>
-    dplyr::ungroup() 
-}
-print(ballcastsim())
 ```

### 2023-12-27 R/simulations.R

@@ -1,3 +1,4 @@
+#' @import ManifoldDestiny
 #' @export ballcastsim
 ballcastsim <- function(
   dfm=(function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10),
@@ -36,7 +37,76 @@ ballcastsim <- function(
     dplyr::mutate(Z=sum(S+T+U+V)) |>
     dplyr::ungroup() 
 }
+#' @export Countingprocess
+Countingprocess <- setRefClass("Countingprocess", 
+			       fields=list(sdfc='data.frame',
+					   rdfci='data.frame',
+					   rdfc='data.frame',
+					   rofc='data.frame',
+                                           rdfce='data.frame', 
+					   quintile='data.frame',
+					   desms='data.frame', 
+					   r2list='list', 
+					   predet='list',
+					   sumreg='vector', 
+					   psel='vector', 
+					   polyc='list',
+					   radpar='vector',
+					   parameters='list', 
+					   preend='list', 
+					   parampre='data.frame', 
+                                           rotplotly='list',
+					   se='list',
+					   lx='list',
+					   pl_2dsort='list',
+					   pl_corrxy='list',
+					   pl_rescro='list',
+					   pl_3d_mani='list',  
+					   all_pl_3d_mani='list',
+					   enf='list',
+					   mansysl='list',
+					   gensysl='list',
+					   exnrs='vector',
+					   allvar='list',
+					   eqpar='list',
+					   loss_df='data.frame'
+					   ))
+Countingprocess$methods(initialize=function(sdfinp=NULL,
+					   selvar=c('P','R','S','T','U','V'), 
+					   polyn=9, 
+					   sortby=alpha
+					   ){
+browser()
+  parameters <<- stickers[['parameters']]
+  se <<- eqpar$meqs
+  lx <<- eqpar$meql
+  ils <- c('S','T','U','V')
+  sdfc <<- ballcount(dplyr::select(sdfinp,all_of(selvar)),se=se)
+  rdfci <<- rdfc <<- sdfc %>% 
+    dplyr::arrange(alpha) %>%
+    dplyr::mutate(pri=dplyr::row_number()/length(P)) %>%
+    dplyr::relocate(pri,.before=P) %>%
+    dplyr::relocate(Z,.after=O) 
[…]

### 2023-12-27 script/python/pysympy.py

@@ -17,7 +17,7 @@ import rpy2.robjects as robjects
 from rpy2.robjects.packages import importr, data
 rroot=importr('rprojroot')
 abs_path = rroot.find_rstudio_root_file()[0]
-csvfile=abs_path+'/inst/script/python/csv/parameters.csv'
+csvfile=abs_path+'/script/python/csv/parameters.csv'
 readmodvar = pandas.read_csv(csvfile, sep=',') 
 sympy.var(readmodvar.iloc[:,0])
 beforems = set(dir())

### 2023-12-27 index.qmd
app_bal

@@
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install(c("dplyr","purrr"))
+webr::install(c("dplyr","purrr","magrittr","data.table"))
 library(ManifoldDestinyWASMP)
@@
 ls(package:ManifoldDestinyWASMD)
+library(magrittr)
 ```
 
+# Simulation
+## R2 sim
 ```{webr-r}
-Countingprocess <- setRefClass("Countingprocess", 
-			       fields=list(sdfc='data.frame',
-					   rdfci='data.frame',
-					   rdfc='data.frame',
-					   rofc='data.frame',
-                                           rdfce='data.frame', 
-					   quintile='data.frame',
-					   desms='data.frame', 
-					   r2list='list', 
-					   predet='list',
-					   sumreg='vector', 
-					   psel='vector', 
-					   polyc='list',
-					   radpar='vector',
-					   parameters='list', 
-					   preend='list', 
-					   parampre='data.frame', 
-                                           rotplotly='list',
-					   se='list',
-					   lx='list',
-					   pl_2dsort='list',
-					   pl_corrxy='list',
-					   pl_rescro='list',
-					   pl_3d_mani='list',  
-					   all_pl_3d_mani='list',
-					   enf='list',
-					   mansysl='list',
-					   gensysl='list',
-					   exnrs='vector',
-					   allvar='list',
-					   eqpar='list',
-					   loss_df='data.frame'
-					   ))
-Countingprocess$methods(initialize=function(sdfinp=NULL,
-					   selvar=c('P','R','S','T','U','V'), 
-					   polyn=9, 
-					   sortby=alpha
-					   ){
+dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
+probw <- c(m=0.51,s=0.10)
+probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
+probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
+ztech <- c(0,1)	
+app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
+app_bal 
+```
 
-})
+## Tower
+```{webr-r}
+P  <- c(1,2,3,4,5,6)
+S  <- c(60,60,60,60,60,55)
+T  <- c(40,40,40,40,40,40)
+U  <- c(40,40,40,40,40,40)
+V  <- c(60,60,60,40,40,40)
+Up <- c(40,(40-5),(40-10),40,40,40)
+Vp <- c(60,(60+5),(60+10),40,40,40)
+R  <- c(200,200,200,200,200,200)
+
+## Tower 1
+ex1m <- as.matrix(cbind(S,T,U,V))
+towi <- as.data.frame(ex1m) %>% 
+  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
+  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
+  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
+  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
+  dplyr::select(5:8) %>%
+  t() %>%
+  data.frame() %>%
+  data.table::setnames(paste0("County_",1:6))
+
+towi[3:4,1] <- ""
+towi[4,2] <- ""
+
+## Tower 2
+ex2m <- as.matrix(cbind(S,T,Up,Vp))
+towii <- as.data.frame(ex2m) %>% 
+  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
+  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
+  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
+  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
+  dplyr::select(5:8) %>%
+  t() %>%
+  data.frame() %>%
+  data.table::setnames(paste0("County_",1:6))
+towii[3:4,1] <- ""
+towii[4,2] <- ""
+
+```
+
+## Countinggraphs
+```{webr-r}
+pro_rec_ex1_e <- data.frame(P=c(1,2,3,4,5,6),S=S,T=T,U=U,V=V,R=R)
+pro_rec_ex2_e <- data.frame(P=c(1,2,3,4,5,6),S=S,T=T,U=Up,V=Vp,R=R) 
+pro_rec_ex1 <- pro_rec_ex1_e[1:3,]
+pro_rec_ex2 <- pro_rec_ex2_e[1:3,]
+pro_elc_ex1 <- Countinggraphs(pro_rec_ex1,polyn=1)
+pro_elc_ex2 <- Countinggraphs(pro_rec_ex2,polyn=1)
+#pr_rep_1 <- seloutput <- seloutput(selreport(pro_elc_ex1,md$app4))
+#pr_rep_2 <- seloutput <- seloutput(selreport(pro_elc_ex2,md$app4))
+cx <- round(pro_elc_ex1$sdfc$x,2)
+cy <- round(pro_elc_ex1$sdfc$y,2)
+czeta <- round(pro_elc_ex1$sdfc$zeta,2)
+calpha <- round(pro_elc_ex1$sdfc$alpha,2)
+clambda <- round(pro_elc_ex1$sdfc$lamda,2)
+cg <- round(pro_elc_ex1$sdfc$g,2)
+ch <- round(pro_elc_ex1$sdfc$y,2)
+cGamma <- round(pro_elc_ex1$sdfc$Gamma,2)
+```
+
+# Applications
+```{webr-r}
+
 ```

### 2023-12-27 R/countingprocess.R

@@ -173,7 +173,6 @@ Countingprocess <- setRefClass("Countingprocess",
 					   gensysl='list',
 					   exnrs='vector',
 					   allvar='list',
-					   eqpar='list',
 					   loss_df='data.frame'
 					   ))
 Countingprocess$methods(initialize=function(sdfinp=NULL,
@@ -181,11 +180,6 @@ Countingprocess$methods(initialize=function(sdfinp=NULL,
 					   polyn=9, 
 					   sortby=alpha
 					   ){
-
-  pr_path <- system.file(package='ManifoldDestiny')
-  eqpar <<- ManifoldDestiny::eqpar
-  stickers <- ManifoldDestiny::stickers
-  # Assigning parameters 
   parameters <<- stickers[['parameters']]
   se <<- eqpar$meqs
   lx <<- eqpar$meql
@@ -201,11 +195,11 @@ Countingprocess$methods(initialize=function(sdfinp=NULL,
   ## Polynom
   pnset <- min(length(rdfci$pri)-1,polyn)
   ### Init values standard form
-  polyc[[1]] <<- lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
-  ### Init values hybrid form
-  polyc[[2]] <<- lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
-  ##### Init values opposition form
-  polyc[[3]] <<- lm(rdfci$lamda ~ poly(rdfci$pri, pnset, raw=TRUE))
+  polyc[[1]] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
+  ### Init valuesstats:: hybrid form
+  polyc[[2]] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
+  ##### Init valustats::es opposition form
+  polyc[[3]] <<- stats::lm(rdfci$lamda ~ poly(rdfci$pri, pnset, raw=TRUE))
 
 })
 Countingprocess$methods(r2siminput=function(form=1,latest=0)

### 2023-12-27 shinyapps/empapp/app.R

@@ -1,24 +1,24 @@
-options(scipen=999)
-set.seed(1)
-library(ManifoldDestiny)
-library(dplyr)
-library(ggplot2)
-library(plotly)
-library(htmltools)
-library(gridExtra)
 library(shiny)
-library(DT)
-library(kableExtra)
-library(htmlTable)
-library(usethis)
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/misc.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/realregression.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/countingprocess.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/voterrollanalysis.R'))
-md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+library(plotly)
+#options(scipen=999)
+#set.seed(1)
+#library(ManifoldDestiny)
+#library(dplyr)
+#library(ggplot2)
+#library(htmltools)
+#library(gridExtra)
+#library(DT)
+#library(kableExtra)
+#library(htmlTable)
+#library(usethis)
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/misc.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/realregression.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/countingprocess.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/simulations.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/voterrollanalysis.R'))
+#md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 dlname <- c("app0","app1","app2")
-googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
+#googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
 ###############################################################################################################################################################
[…]

### 2023-12-27 shinyapps/manimp/app.R

@@ -1,28 +1,28 @@
 ######################################################################################
-options(scipen=999)
-set.seed(1)
-library(ManifoldDestiny)
-library(kableExtra)
-library(dplyr)
-library(ggplot2)
-library(htmltools)
-library(gridExtra)
 library(shiny)
 library(plotly)
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/realregression.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/misc.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/voterrollanalysis.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/countingprocess.R'))
-#vl <- ManifoldDestiny::recnav
-dfm <- ManifoldDestiny::miller_stavros_nevada_2020[[1]] %>%
-  dplyr::mutate(S=A1,T=B1,U=A2,V=B2) %>%
-  dplyr::mutate(Z=S+T+U+V+A3+B3, Psi=Z/R) %>%
-  dplyr::mutate(alpha=(S+U)/(Z)) %>% 
-  dplyr::mutate(map=U/(S+T)) %>%
-  dplyr::mutate(mbp=T/(T+V)) %>%
-  dplyr::select(P,R,S,T,U,V)
-#####################################################################################
+#options(scipen=999)
+#set.seed(1)
+#library(ManifoldDestiny)
+#library(kableExtra)
+#library(dplyr)
+#library(ggplot2)
+#library(htmltools)
+#library(gridExtra)
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/realregression.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/simulations.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/misc.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/voterrollanalysis.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/R/countingprocess.R'))
+##vl <- ManifoldDestiny::recnav
[…]

### 2023-12-27 index.qmd
firssim

@@
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install(c("dplyr","purrr","magrittr","data.table"))
+webr::install(c("dplyr","purrr","magrittr","data.table","tidyr"))
 library(ManifoldDestinyWASMP)
@@
 app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
-app_bal 
+SimVoterdatabase(app_bal)
+library(dplyr)
+r2simn()
 ```
@@
 
+```
+
+## Tower
+```{webr-r}
+r2simn()
 ```

### 2023-12-27 R/countingprocess.R

@@ -180,6 +180,8 @@ Countingprocess$methods(initialize=function(sdfinp=NULL,
 					   polyn=9, 
 					   sortby=alpha
 					   ){
+
+  library(ManifoldDestiny)
   parameters <<- stickers[['parameters']]
   se <<- eqpar$meqs
   lx <<- eqpar$meql
@@ -375,6 +377,7 @@ Countingprocess$methods(manimp=function(init_par=NULL,man=TRUE,wn=c(0,0)){
   }
   rdfc <<- dplyr::select(loss_df,P,R,S,T,U,V) %>% ballcount(se=se)
 })
+#' @import ManifoldDestiny
 #' @export Countinggraphs
 Countinggraphs <- setRefClass("Countinggraphs", contains = c('Countingprocess'))
 Countinggraphs$methods(plot2d=function(form=1,

### 2023-12-27 R/simulations.R

@@ -54,11 +54,11 @@ r2simn <- function(nprec=300,
                  std=c('alpha~n+m','alpha~n+m+xi'))[[form]]
     # Box
     dfb <- data.frame(P=seq(1,nprec)) %>%
-    dplyr::mutate(genreg=10^qnorm(runif(n()),regs[1],regs[2])) %>%
+    dplyr::mutate(genreg=10^qnorm(runif(dplyr::n()),regs[1],regs[2])) %>%
     dplyr::mutate(R=round(ifelse(genreg>minmax[2]|genreg<minmax[1],runif(1,minmax[1],minmax[2]),genreg))) %>%
-    dplyr::mutate(Z=round(R*qnorm(runif(n()),turn[1],turn[2]))) %>%
+    dplyr::mutate(Z=round(R*qnorm(runif(dplyr::n()),turn[1],turn[2]))) %>%
     # Form 
-    dplyr::mutate(!!paste0('OpT'):=round(Z*rnorm(n(),Invper[1],Invper[2]))) %>%
+    dplyr::mutate(!!paste0('OpT'):=round(Z*rnorm(dplyr::n(),Invper[1],Invper[2]))) %>%
     dplyr::mutate(!!paste0('TpF'):=Z-OpT) %>% dplyr::mutate(gen_u=rnorm(n(),u[1],u[2])) %>%
     dplyr::mutate(gen_v=rnorm(n(),dv[1],dv[2])+gen_u) %>%
     # Ballots

### 2023-12-27 index.qmd
abc

@@
 ![](pngs/md.png)
+tidyr
 
@@
 SimVoterdatabase(app_bal)
-library(dplyr)
-r2simn()
 ```

### 2023-12-27 R/misc_py.R

@@ -1,283 +1,0 @@
-#test <- function(abc=NULL){
-#  library(ManifoldDestiny)
-#  library(ggplot2)
-#  library(dplyr)
-#  library(googlesheets4)
-#  library(htmltools)
-#  library(gridExtra)
-#  md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-#  googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
-#  lapply(paste0("app",2:2), function(x){recoudatr(mda=md[[x]])})
-#}
-#lapply(paste0("app",0:4), function(x){recoudatr(mda=md[[x]])})
-
-#' @export recoudatr
-recoudatr <- function(mda=NULL){
-  gsh <- googlesheets4::read_sheet(mda$sht$url,sheet=mda$sht$pgn,range=mda$sht$rng) %>%
-    data.table::setnames(new=mda$sht$cln) %>%
-    dplyr::select(-starts_with('D')) %>%
-    dplyr::mutate(P=row_number(PN)) %>%
-    dplyr::mutate(R=row_number(RN)) %>%
-    dplyr::mutate(S=!!rlang::parse_expr(mda$sht$stuv[1])) %>%
-    dplyr::mutate(T=!!rlang::parse_expr(mda$sht$stuv[2])) %>%
-    dplyr::mutate(U=!!rlang::parse_expr(mda$sht$stuv[3])) %>%
-    dplyr::mutate(V=!!rlang::parse_expr(mda$sht$stuv[4]))
-  assign(mda$nid,gsh)
-  do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
-  return(gsh)
-}
-
-#' @export gmp
-gmp <- function(terms=c("x2","xy","y2","x3","x2y","y2x","y3")){
-  # Preallocate a list to store expressions
-  nrc <- as.character(rep(1:4))
-  expre <- vector("list", length(terms))
-  # Iterate over the terms
-  for(i in seq_along(terms)){
-    term <- terms[i]
-    nl <- gsub("\\d","",term)
-    chars <- strsplit(term, "")[[1]]
-    ac <- paste0(chars,collapse="*")
-    ind <- unlist(gregexpr("\\d",ac))
-    sapply(1:nchar(nl), function(i){
-      lcl <- regexpr(substring(nl,i,i), term)[[1]]
[…]

### 2023-12-27 presentation.qmd
abc
befrev

@@
 subtitle: "Based upon the ideas developed by Edward K. Solomon"
-format:
-  revealjs: 
-    smaller: true
-    toc-depth: 1
-    toc: true 
+#format:
+#  revealjs: 
+#    smaller: true
+#    toc-depth: 1
+#    toc: true 
 #webr: 
@@
 ##
+
+```{r}
+knitr::knit_exit()
+```
 
@@
 # `r metad$toc$sec2$nmn`
-
-```{r}
-knitr::knit_exit()
-```
 

### 2023-12-27 R/raceanalysis.R

@@ -173,3 +173,5 @@ Racegraphs$methods(plot2ddynamic_fac=function(){
      #gganimate::ease_aes('linear') +
      #ggplot2::theme_bw()
 })
+
+

### 2023-12-28 presentation.qmd
lastimupd

--- 2023-12-27 presentation.qmd
@@
     toc: true 
-#webr: 
-#  show-startup-message: true    # Disable displaying status of webR initialization
-#  packages: ['dplyr'] # Install R packages on document open
+webr: 
+  show-startup-message: true    # Disable displaying status of webR initialization
+  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
 filters:
@@
 ```{webr-r}
-2+2
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
+probw <- c(m=0.51,s=0.10)
+probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
+probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
+ztech <- c(0,1)	
+app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
+print(SimVoterdatabase(app_bal))
 ```
@@
 :::
+
+```{r}
+knitr::knit_exit()
+```
 

### 2023-12-28 index.qmd
befrev
lastimupd
abc

@@
 
+### Install and load packages
 ```{webr-r}
@@
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install(c("dplyr","purrr","magrittr","data.table","tidyr"))
+webr::install(c("dplyr","purrr","magrittr","data.table","tidyr","plotly"))
 library(ManifoldDestinyWASMP)
@@
 
-# Simulation
-## R2 sim
+### Simulation
 ```{webr-r}
@@
 SimVoterdatabase(app_bal)
+```
+**Last time updated: `r as.Date(Sys.time())`**
+
+```{r, echo=F}
+knitr::knit_exit()
+```
+
+### Simulation
+```{webr-r}
+library(plotly)
+options(browser = 'brave') 
+mtcars$am[which(mtcars$am == 0)] <- 'Automatic'
+mtcars$am[which(mtcars$am == 1)] <- 'Manual'
+mtcars$am <- as.factor(mtcars$am)
+
+fig <- plot_ly(mtcars, x = ~wt, y = ~hp, z = ~qsec, color = ~am, colors = c('#BF382A', '#0C4B8E'))
+fig <- fig %>% add_markers()
+fig <- fig %>% layout(scene = list(xaxis = list(title = 'Weight'),
+                     yaxis = list(title = 'Gross horsepower'),
+                     zaxis = list(title = '1/4 mile time')))
+
+fig
 ```

### 2023-12-30 index.qmd
abc

--- 2023-12-27 index.qmd
@@
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install(c("dplyr","purrr","magrittr","data.table","tidyr"))
+webr::install(c("cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
 library(ManifoldDestinyWASMP)
@@
 library(magrittr)
+md <- ManifoldDestinyWASMD::metad
 ```
 
-# Simulation
-## R2 sim
+### Simulation
 ```{webr-r}
+library(dplyr)
+library(combinat)
+library(htmltools)
+library(ggplot2)
+library(broom)
+library(combinat)
 dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
@@
 SimVoterdatabase(app_bal)
+app_n_rep <- selreport(app0,md$app0)
+app_n_out <- seloutput(app_n_rep)
 ```
 
-## Tower
+### Applications
 ```{webr-r}
-P  <- c(1,2,3,4,5,6)
-S  <- c(60,60,60,60,60,55)
-T  <- c(40,40,40,40,40,40)
-U  <- c(40,40,40,40,40,40)
-V  <- c(60,60,60,40,40,40)
-Up <- c(40,(40-5),(40-10),40,40,40)
-Vp <- c(60,(60+5),(60+10),40,40,40)
-R  <- c(200,200,200,200,200,200)
-
-## Tower 1
-ex1m <- as.matrix(cbind(S,T,U,V))
-towi <- as.data.frame(ex1m) %>% 
-  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
-  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
-  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
-  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
-  dplyr::select(5:8) %>%
-  t() %>%
-  data.frame() %>%
-  data.table::setnames(paste0("County_",1:6))
-
-towi[3:4,1] <- ""
-towi[4,2] <- ""
-
-## Tower 2
-ex2m <- as.matrix(cbind(S,T,Up,Vp))
-towii <- as.data.frame(ex2m) %>% 
-  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
-  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
-  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
-  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
-  dplyr::select(5:8) %>%
-  t() %>%
-  data.frame() %>%
-  data.table::setnames(paste0("County_",1:6))
-towii[3:4,1] <- ""
-towii[4,2] <- ""
-
+library(dplyr)
+library(combinat)
+library(htmltools)
+library(ggplot2)
+library(broom)
+library(combinat)
+app0_rp <- selreport(app0,md$app0)
+app_0_out <- seloutput(app0_rp)
+app1_rp <- selreport(app1,md$app1)
+app_1_out <- seloutput(app1_rp)
+app2_rp <- selreport(app2,md$app2)
+app_2_out <- seloutput(app2_rp)
+app3_rp <- selreport(app2,md$app2)
+app_3_out <- seloutput(app2_rp)
+app4_rp <- selreport(app2,md$app2)
+app_4_out <- seloutput(app2_rp)
 ```
 
-## Tower
-```{webr-r}
-r2simn()
-```
-
-## Countinggraphs
-```{webr-r}
-pro_rec_ex1_e <- data.frame(P=c(1,2,3,4,5,6),S=S,T=T,U=U,V=V,R=R)
-pro_rec_ex2_e <- data.frame(P=c(1,2,3,4,5,6),S=S,T=T,U=Up,V=Vp,R=R) 
-pro_rec_ex1 <- pro_rec_ex1_e[1:3,]
-pro_rec_ex2 <- pro_rec_ex2_e[1:3,]
-pro_elc_ex1 <- Countinggraphs(pro_rec_ex1,polyn=1)
-pro_elc_ex2 <- Countinggraphs(pro_rec_ex2,polyn=1)
-#pr_rep_1 <- seloutput <- seloutput(selreport(pro_elc_ex1,md$app4))
-#pr_rep_2 <- seloutput <- seloutput(selreport(pro_elc_ex2,md$app4))
-cx <- round(pro_elc_ex1$sdfc$x,2)
-cy <- round(pro_elc_ex1$sdfc$y,2)
-czeta <- round(pro_elc_ex1$sdfc$zeta,2)
-calpha <- round(pro_elc_ex1$sdfc$alpha,2)
-clambda <- round(pro_elc_ex1$sdfc$lamda,2)
-cg <- round(pro_elc_ex1$sdfc$g,2)
-ch <- round(pro_elc_ex1$sdfc$y,2)
-cGamma <- round(pro_elc_ex1$sdfc$Gamma,2)
-```
-
-# Applications
-```{webr-r}
-
-```
+**Last time updated: `r as.Date(Sys.time())`**
 
@@
 ```
-
-```{r}
-library(dplyr)
-
-# Sample data frame
-df <- data.frame(
-  P = c(1, 2, 1, 2, 3),
-  Value = c("A", "B", "C", "D", "E")
-)
-
-# Split the data frame by the 'P' column
-df_list <- df %>% group_split(P)
-str(df_list)
-# Access the individual groups
-for (group in df_list) {
-  print(group)
-}
-```
-
-[From Bard:](https://g.co/bard/share/37bfadf733c5)
-
-Published July 22, 2023 at 05:37 AM
-
-> The first problem is that the proportion of votes cast by mail (w) is nearly constant across all precincts.
-This is not what we would expect to see in a fair election, where the proportion of votes cast by mail would vary depending on the demographics of the precinct.
-For example, we would expect to see a higher proportion of votes cast by mail in precincts with a higher population of elderly people.
-
-> The second problem is that we can calculate D knowing only K and A.
-This is also not possible in a fair election, as D should be determined by the number of ballots cast by mail, which is not known until after all ballots have been cast.
-
-> The third problem is that n decreases rapidly over the quantiles of z, meaning that Democrats are more likely to cast their ballots by mail as Republicans perform better overall.
-This is not what we would expect to see in a fair election, as we would expect the proportion of Democrats and Republicans who vote by mail to be relatively constant.
-
-> The fourth problem is that the difference between x and y diverges rapidly over the quantiles of z, meaning that as Republican do better in the early vote, the more they suffer in the mail-in vote.
-This is also not what we would expect to see in a fair election, as we would expect the two types of votes to be relatively correlated.
-
-```{webr-r}
-webr::install("ManifoldDestinyWASM", repos = "https://lotariohw26.github.io/ManifoldDestinyWASM/repo")
-library(ManifoldDestinyWASM)
-ls(package:ManifoldDestinyWASM)
-```

### 2023-12-30 tabsets.qmd
withheader

---
title: "Tabsets"
format: 
  html:
    page-layout: article
#filters:
#  - webr
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
#    footer: <https://lotariohw26.github.io/ManifoldDestiny/>
#execute: 
#  cache: false
bibliography: man_bib.bib
---

Tabcsets

```{r}
knitr::knit_exit()
```

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
library(Hyperinflation)
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/applications.R'))
```

::: {.callout-caution collapse="true"}
## `r md$tabhead[1]`

```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_n_out
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
```

:::

::: {.callout-caution collapse="true"}
## `r md$tabhead[2]`

```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_ex1_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
```

:::

::: {.callout-caution collapse="true"}
## `r md$tabhead[3]`

```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_ex2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
```

:::

::: {.callout-caution collapse="true"}
## `r md$tabhead[4]`

```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_ex3_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
```

:::

::: {.callout-caution collapse="true"}
## Application 0 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_0_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## Application 1 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_1_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## Application 2 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::
::: {.callout-caution collapse="true"}
## Application 3 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::
::: {.callout-caution collapse="true"}
## Application 4 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::
::: {.callout-caution collapse="true"}
## Application 5 
```{r, echo=FALSE, results='asis',warning=F}
app_a_out <- app_2_out 
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

[@delfino2011analysis]

## References

::: {#refs}
:::

### 2023-12-30 shinyapps/r2sim/app.R

@@ -3,13 +3,13 @@ library(magrittr)
 library(ManifoldDestinyWASMP)
 library(ManifoldDestinyWASMD)
 library(ggplot2)
-#options(scipen=999)
-#library(plotly)
-#library(DT)
-#library(kableExtra)
-#library(dplyr)
-#library(htmltools)
-#library(gridExtra)
+options(scipen=999)
+library(plotly)
+library(DT)
+library(kableExtra)
+library(dplyr)
+library(htmltools)
+library(gridExtra)
 ui <- fluidPage(
   titlePanel("R2 Simulator"),
   tabsetPanel(

### 2023-12-30 presentation.qmd
bef

@@
 ```{r, echo=F, message=F, warning=F}
-library(ManifoldDestiny)
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
 library(RefManageR)
@@
 modlat <- eqpar$meql
+md <- ManifoldDestinyWASMD::metad
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
 ```

### 2023-12-30 script/applications.R

@@ -1,22 +1,18 @@
 #######################################################################################################################################################
-options(scipen=999)
-set.seed(1)
-library(ManifoldDestiny)
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
 library(dplyr)
 library(ggplot2)
-library(plotly)
 library(htmltools)
-library(gridExtra)
-library(shiny)
-library(DT)
+library(plotly)
 library(kableExtra)
-library(htmlTable)
-library(usethis)
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/misc.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/realregression.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/countingprocess.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/R/voterrollanalysis.R'))
+library(huxtable)
+library(gridExtra)
+options(scipen=999)
+set.seed(1)
+source(paste0(rprojroot::find_rstudio_root_file(),'/R/wasmconverting.R'))
+md <- ManifoldDestinyWASMD::metad
+#######################################################################################################################################################
 P  <- c(1,2,3,4,5,6)
 S  <- c(60,60,60,60,60,60)
 T  <- c(40,40,40,40,40,40)
@@ -29,7 +25,7 @@ pro_rec_ex1 <- data.frame(P=c(1,2,3),S=S,T=T,U=U,V=V,R=R)
 pro_rec_ex2 <- data.frame(P=c(1,2,3),S=S,T=T,U=Up,V=Vp,R=R) 
 pro_elc_ex1 <- Countinggraphs(pro_rec_ex1,polyn=1)
 pro_elc_ex2 <- Countinggraphs(pro_rec_ex2,polyn=1)
-debug(lapply(paste0("app",4:4), function(x){recoudatr(mda=md[[x]])}))
+#debug(lapply(paste0("app",4:4), function(x){recoudatr(mda=md[[x]])}))
 #########################################################################################################################################################
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 app0 <- get(load(paste0(rprojroot::find_rstudio_root_file(),"/data/app0.rda")))

### 2023-12-30 presentation.qmd
scriptokay

--- 2023-12-28 presentation.qmd
@@
 subtitle: "Based upon the ideas developed by Edward K. Solomon"
-format:
-  revealjs: 
-    smaller: true
-    toc-depth: 1
-    toc: true 
+#format:
+#  revealjs: 
+#    smaller: true
+#    toc-depth: 1
+#    toc: true 
 webr: 
@@
 library(ManifoldDestiny)
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
 library(RefManageR)

### 2023-12-30 addendum/Addendum_az.qmd
firstup

---
title: "Addendum"
subtitle: "Arizona General Election 2022"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

```{r}
knitr::knit_exit()
```

```{r, echo=F, warning=F, message=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
library(plotly)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_tile_view()
xaringanExtra::use_share_again()
xaringanExtra::use_scribble()
xaringanExtra::use_webcam()
xaringanExtra::use_panelset()
modlat <- eqpar$meql
labs <- stickers[['parameters']]
abs_p <- rprojroot::find_rstudio_root_file()
#source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_az.R'))
```

```{r, eval=F, echo=F, message=F, warning=F}
pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/inst/www/addendum/Addendum_az.Rmd')
xaringan::inf_mr(pre_fil)
#rmarkdown::render(pre_fil) 
```

```{r}
knitr::knit_exit()
```

class: inverse, center, middle

# Overview

```{r, echo=FALSE, out.width="80%", fig.cap=""}
pa <- paste0(rprojroot::find_rstudio_root_file(),'/inst/addendum/pngs/ALEXANDER_chart-of-Rs-voting-for-Hobbs.jpg')
knitr::include_graphics(c(pa))
```

---

class: inverse, center, middle

# Maricopa county

---

## [Application 1:`r paste0(unlist(ManifoldDestiny::cap_add_mar[1])[1:3])`]()

- Election system:
  - General election 2022
  - Modes of voting: EDV, (used) MiV (used), EV (used)

- $H_0:$ Normal election 
  - $y_i(\alpha_i,x_i.\zeta_i)$
  - Variation in $\zeta_i$ causes changes to $\alpha_i$

- $H_1:$ Rigged election applying opposition form
  - $y_i(\alpha_i,x_i)=M(x_i,\alpha_i)+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
  - $\zeta_i$ (and as a corollary $\Omega$) invariant to $\alpha_i$

---

.panelset[
.panel[.panel-name[Descriptive]
```{r, echo=F}
format(app_ma_sen_srp[[1]][,1:6],digits=10)
format(app_ma_sen_srp[[1]][,7:18],digits=4)
```
]
.panel[.panel-name[2d plots]
```{r, echo=F}
app_ma_sen_srp[[2]]
```
]
.panel[.panel-name[3d plot]
```{r, echo=F}
app_ma_sen_srp[[3]]
```
]
.panel[.panel-name[Estimation results]
```{r, echo=F}
app_ma_sen_srp[[4]][2]
```
]
.panel[.panel-name[Residuals]
```{r, echo=F}
app_ma_sen_srp[[5]]
```
]]

---

```{r, echo=F, out.width="80%", fig.cap=""}
td
```

---

![](ggplots/prec/race_1_snap)

---

---

![](ggplots/prec/race_2_snap)

---

```{r, echo=F, out.width="80%", fig.cap=""}
kableExtra::kbl(snap_mar$rpoltab,col.names=c("Race","Snap","Polynomial","Integral","R2")) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
```

---

class: inverse, center, middle

# Cohise county

---

## [Application 2:`r paste0(unlist(ManifoldDestiny::cap_add_coh[2][1:3])[1:2])`]()

- Election system
  - General election 2022
  - Modes of voting: EDV, (used) MiV (used), EV (used)

- $H_0:$ Normal election 
  - $y_i(\alpha_i,x_i.\zeta_i)$
  - Variation in $\zeta_i$ causes changes to $\alpha_i$

- $H_1:$ Rigged election applying opposition form
  - $y_i(\alpha_i,x_i)=M(x_i,\alpha_i)+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
  - $\zeta_i$ (and as a corollary $\Omega$) invariant to $\alpha_i$

---

.panelset[
.panel[.panel-name[Descriptive]
```{r, echo=F}
format(app_co_sen_srp[[1]][,1:6],digits=10)
format(app_co_sen_srp[[1]][,7:18],digits=4)
```
]
.panel[.panel-name[2d plots]
```{r, echo=F}
app_co_sen_srp[[2]]
```
]
.panel[.panel-name[3d plot]
```{r, echo=F}
app_co_sen_srp[[3]]
```
]
.panel[.panel-name[Estimation results]
```{r, echo=F}
app_co_sen_srp[[4]][2]
```
]
.panel[.panel-name[Residuals]
```{r, echo=F}
app_co_sen_srp[[5]]
```
]]

---

```{r, echo=F, out.width="80%", fig.cap=""}
plo_sta_all
```

---

```{r, echo=F, out.width="80%", fig.cap=""}
kableExtra::kbl(sna_sta_all$rpoltab,col.names=c("Race","Snap","Polynomial","Integral","R2")) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
```

### 2023-12-30 addendum/Addendum_ne.qmd
firstup

---
title: "Addendum"
subtitle: "Nevada General Election 2022"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

```{r}
knitr::knit_exit()
```

```{r, echo=F, warning=F, message=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
library(plotly)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_tile_view()
xaringanExtra::use_share_again()
xaringanExtra::use_scribble()
xaringanExtra::use_webcam()
xaringanExtra::use_panelset()
modlat <- eqpar$meql
labs <- stickers[['parameters']]
abs_p <- rprojroot::find_rstudio_root_file()
#source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_az.R'))
```

```{r, eval=F, echo=F, message=F, warning=F}
pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/inst/www/addendum/Addendum_ne.Rmd')
xaringan::inf_mr(pre_fil)
#rmarkdown::render(pre_fil) 
```

```{r}
knitr::knit_exit()
```

---
title: "Nevada"
output:
  bookdown::html_document2: default
# https://docs.google.com/document/d/13u3lL_emHyLpog-rFrm7-zk7lKM_AmQd28CJlJ5odFE/edit#
---

```{r}
source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_ne.R'))
```

# Introduction

![](pngs/necawa.png)

[$50,000 Reward!](https://operationsunlight.com/2022/11/26/50000-reward/)

```{r}
plotly::plot_ly(bindf, x = ~g, y = ~h, z = ~alpha, color = ~tpg,
        type = "scatter3d", mode = "markers")
```

# Main results

# Sideeffects

## Sideeffect #1

```{r}
abc <- allreport(fir$sdfc)
abc[[1]][[2]][[4]]
```

```{r}
abc <- allreport(sec$sdfc)
abc[[1]][[2]][[4]]
```
## Sideeffect #2
## Sideeffect #3
## Sideeffect #4

### 2023-12-30 app_par.qmd
firstup

---
title: "Applicaton"
date: "`r Sys.Date()`"
#format: 
#  html:
#    page-layout: article
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
params:
  name: "0"
format: html
engine: knitr
filters:
  - webr
---

```{r, eval=F, echo=F, message=F, warning=F}
pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/app_par.qmd')
quarto::quarto_preview(pre_fil)
params <- list(name="0")
googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
#lapply(paste0("app",0:4), function(x){recoudatr(mda=md[[x]])})
```

```{r, echo=F}
# Start on 50
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- md[[paste0("app",params$name)]]
apprda <- get(load(paste0(rprojroot::find_rstudio_root_file(),'/data/app',params$name,".rda")))
app_a_out <- seloutput(selreport(apprda,mda))
```

## Application: `r mda$nmn`

### Information
- Election system:
  - Type of race: `r mda$race$rcn` 
  - Candidates: `r mda$race$cnd` 
  - Modes of voting: `r mda$race$mod`

- $H_0:$ Normal election 
- $H_1:$ Rigged election: 
  - Manifold object `r mda$mtd$sgs$eq[1]`
  - Solved for `r mda$mtd$sgs$va`

[Link to raw data and independent calculcations](`r mda$sht$url`)
[@sol2022_1]

::: {.panel-tabset}
### `r mda$tabsets[[1]]`
```{r, echo=F}
kableExtra::kbl(app_a_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### `r mda$tabsets[[2]]`
```{r, echo=F, out.width="60%"}
app_a_out[['corxy']]
```
### `r mda$tabsets[[3]]`
```{r, echo=F, out.width="60%"}
app_a_out[['qunt']]
```
### `r mda$tabsets[[4]]`
```{r, echo=F}
app_a_out[['ro3d']]
```
### `r mda$tabsets[[5]]`
```{r, echo=F, out.width="60%"}
app_a_out[['regr']]
```
### `r mda$tabsets[[6]]`
```{r, echo=F, out.width="60%"}
app_a_out[['resp']]
```
:::

### Ballot predictions based on limit information implied by the estimated Manifold object(s)

```{r, echo=F}
#app_a_out$cmp[,1] <- c("Mean total votes", "Number of precincts", "Zero prediction error", "In percentage", "Mean", "Standard Deviation", "Max ballot error", "1+/- prediction error", "2+/- prediction error", "2+/- prediction error", "Percentage within +/-3")
#kableExtra::kbl(app_a_out$cmp,row.names=F,col.names=c("Statistic","Value"),digits=2) %>% kableExtra::kable_paper(full_width = F) 
```

### References

::: {#refs}
:::

### 2023-12-30 tabsets.qmd
firstup

@@
 
-```{r}
-knitr::knit_exit()
-```
-
 ```{r, echo=F, message=F, warning=F}
 library(ManifoldDestiny)
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
 library(RefManageR)
 library(huxtable)
-library(Hyperinflation)
+modlat <- eqpar$meql
+md <- ManifoldDestinyWASMD::metad
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/applications.R'))
+
 ```
@@
 text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 
+```{r}
+knitr::knit_exit()
+```
+
 ::: {.callout-caution collapse="true"}

### 2023-12-30 paper.qmd
paperadd

@@
 
-# Introduction
+```{r, echo=F, message=F, warning=F}
+library(ManifoldDestiny)
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+library(RefManageR)
+library(huxtable)
+modlat <- eqpar$meql
+md <- ManifoldDestinyWASMD::metad
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+```
+
+# `r #metad$toc$sec1$nmn`
+
+ Ed. Solomon
+
+> "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
+
+## `r metad$toc$sec1$unm[1]`
+
+- Two candidates: A, B
+- County with three precincts: 1, 2, 3
+- Two modes of voting
+  - Number of ballots mode 1: S, T
+  - Number of ballots mode 2: U, V
+
+##
+
+```{r, echo=F, caption="Example 1"}
+## Tower 1
+ex1m <- as.matrix(cbind(S,T,U,V))
+towi <- as.data.frame(ex1m) %>% 
+  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
+  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
+  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
+  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
+  dplyr::select(5:8) %>%
+  t() %>%
+  data.frame() %>%
+  data.table::setnames(paste0("County_",1:6))
+
+towi[3:4,1] <- ""
+towi[4,2] <- ""
+lego_hux_nor_i <- hux(towi[,1:3]) 
+lego_hux_nor_i 
+```
+
+```{r, echo=F, caption="Example 2"}
+## Tower 2
+ex2m <- as.matrix(cbind(S,T,Up,Vp))
+towii <- as.data.frame(ex2m) %>% 
+  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
+  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
+  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
+  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
+  dplyr::select(5:8) %>%
+  t() %>%
+  data.frame() %>%
+  data.table::setnames(paste0("County_",1:6))
+towii[3:4,1] <- ""
+towii[4,2] <- ""
+lego_hux_nor_ii <- hux(towii[,1:3]) 
+lego_hux_nor_ii 
+```
+
+## `r metad$toc$sec1$unm[2]`
+
+```{r, echo=F}
+lego_hux_nor <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
+  set_background_color(1, 1:2, "black") %>% 
+  set_background_color(2, 1:2, "grey") %>% 
+  set_text_color(1:2, 1:2, "red") %>% 
+  set_all_borders(brdr(2, "solid", "black"))
+lego_hux_nor %>% set_caption("")
+```
+
+Parameters: ** $x$, $y$, $\zeta$, $\alpha$, $\lambda$ **
+\begin{equation*}
+x=`r modlat$x_s[1]` \text{, }y=`r modlat$y_s[1]`
+\end{equation*}
+\begin{equation*}
+\zeta=`r modlat$zeta_s[1]`
+\end{equation*}
+\begin{equation*}
+\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
+\end{equation*}
+\begin{equation*}
+\lambda=`r modlat$lamda_s[1]`=`r modlat$lamda_s[2]`
+\end{equation*}
+
+##
+
+```{r, echo=F}
+ctone_sf <- 'Election results applying standard form on case I'
+stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
+cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
+kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+Numerical calculation of candidate one total percentage
+- Precinct 1
+ - $\alpha=\frac{`r cx[1]`+`r cy[1]`\cdot `r czeta[1]`}{1+`r czeta[1]`}=`r calpha[1]`$
+- Precinct 2
+ - $\alpha=\frac{`r cx[2]`+`r cy[2]`\cdot `r czeta[2]`}{1+`r czeta[2]`}=`r calpha[2]`$
+- Precinct 3
+ - $\alpha=\frac{`r cx[3]`+`r cy[3]`\cdot `r czeta[3]`}{1+`r czeta[3]`}=`r calpha[3]`$
+
+## `r metad$toc$sec1$unm[3]`
+
+```{r, echo=F}
+lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
+  set_background_color(1:2, 1, "black") %>% 
+  set_background_color(1:2, 2, "grey") %>% 
+  set_text_color(1:2, 1:2, "red") %>% 
+  set_all_borders(brdr(2, "solid", "black"))
+lego_hux_imp %>% set_caption("")
+```
+
+Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
+\begin{equation*}
+g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
+\end{equation*}
+\begin{equation*}
+\Gamma=`r modlat$Gamma_h[1]`
+\end{equation*}
+\begin{equation*}
+\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
+\end{equation*}
+\begin{equation*}
+\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
+\end{equation*}
+
+##
+
+```{r, echo=F}
+ctone_hf <- 'Election results applying hybrid form case I'
+stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
+kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+Numerical calculation of candidate one total percentage
+- Precinct 1
+ - $\alpha=\frac{`r cg[1]`+`r ch[1]`\cdot `r cGamma[1]`}{1+`r cGamma[1]`}=`r calpha[1]`$
+- Precinct 2
+ - $\alpha=\frac{`r cg[2]`+`r ch[2]`\cdot `r cGamma[2]`}{1+`r cGamma[2]`}=`r calpha[2]`$
+- Precinct 3
+ - $\alpha=\frac{`r cg[3]`+`r ch[3]`\cdot `r cGamma[3]`}{1+`r cGamma[3]`}=`r calpha[3]`$
+
+```{r, echo=F}
+ctone_hf <- 'Election results applying hybrid form case II'
+stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
+kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+## `r metad$toc$sec1$unm[4]`
+
+```{r, echo=F}
+lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
+  set_background_color(c(1),c(1), "black") %>% 
+  set_background_color(c(2),c(2), "black") %>% 
+  set_background_color(c(1),c(2), "grey") %>% 
+  set_background_color(c(2),c(1), "grey") %>% 
+  set_text_color(1:2, 1:2, "red") %>% 
+  set_all_borders(brdr(2, "solid", "black"))
+lego_hux_opo %>% set_caption("")
+```
+Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$
+\begin{equation*}
+n=`r modlat$n_o[1]` \text{ , } m=`r modlat$m_o[1]`
+\end{equation*}
+\begin{equation*}
+\xi=`r modlat$xi_o[1]`
+\end{equation*}
+\begin{equation*}
+\Omega=`r modlat$Omega_o[1]`=`r modlat$Omega_o[2]`
+\end{equation*}
+\begin{equation*}
+\lambda=`r modlat$lamda_o[1]`=`r modlat$lamda_o[2]`
+\end{equation*}
+
+##
+
+```{r, echo=F}
+ctone_of <- 'Election results applying opposition form'
+stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
+kableExtra::kbl(format(stfo_sel,digits=4), caption=ctone_of) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+## `r metad$toc$sec1$unm[5]`
+
+- **Step 1:** Each registered voter assign themself (independent of voting technology) to either candidate A or candidate B
+- **Step 2:** Voting technology realized
+- **Step 3:** Registered voters determine whether to vote or not to vote 
+- **Step 4:** If voting, do this by either mode 1 or by mode 2.
+
+```{mermaid}
+  flowchart LR
+  A[Candidate A or B] --> R[A]
+  R --> RV[Vote]
+  RV --> RVE[Non-Mail]
+  RV --> RVM[Mail]
+  R --> RN[Not Vote]
+  DV --> DVE[Non-Mail]
+  DV --> DVM[Mail]
+  A --> D[B]
+  D --> DV[Vote]
+  D --> Dn[Not Vote]
+```
+
+##
+
+- Probability of assigning oneself to candidate A in precinct $i$
+  - $p_{w,i} \sim N(\alpha_i,\sigma^2_{w,i})$
+- Voting technology
+  - $z_i \sim U(0,1)$
+- Probability of not voting in precinct $i$
+  - Candidate A, $p_{nz,a,i}=(1-z_i)p_{n,a,i}\sim N(\alpha_{a,n},\sigma^2_{a,n})$ <br>
+  - Candidate B, $p_{nz,b,i}=(1-z_i)p_{n,b,i}\sim N(\alpha_{b,n},\sigma^2_{b,n})$
+- Probability of voting by mode 2 in precinct $i$
+  - Candidate A, $p_{m2,a,i}=(1-p_{nv,a,i})p_{a,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
+  - Candidate B, $p_{m2,b,i}=(1-p_{nv,b,i})p_{b,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
+- Probability of voting by mode 1 in precinct $i$
+  - Candidate A, $p_{m1,a,i}=1-p_{m2,a,i}-p_{nz,a,i}$ 
+  - Candidate B, $p_{m1,b,i}=1-p_{m2,b,i}-p_{nz,b,i}$
+
+Neutral-voting assumption:
+
+- Decission to vote or not to vote is independent of voting preferences:
+  - $p_{nz,a,i}=p_{nz,a,i}$ 
+- If voting, decission to vote by mode 1 or by mode 2 independent of voting preferences: 
+  - $p_{m2,a,i}=p_{m2,a,i}$
+
+Note: As we will investigate later, this condition might be needed in order to restore a rigged election to its original form.
+
+## `r metad$toc$sec1$unm[6]`
+
+1. Differences in the cost of voting (e.g., topology, voting rules, dropboxes etc.) across precincts $\Rightarrow$
+1. Changes to the likelihood of voting $\Rightarrow$ 
+1. Simplify so that changes in the likelihood of voting only impact Mode 2 $\Rightarrow$ 
+1. Higher $\zeta_i$ $\Rightarrow$
+1. Which changes the total election outcome through $\alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}$
+
+##
+
+The impact on the election outcome, however, would be small or close to non-existens if the conditions
+of the existance of a *trivial* Manifold occuranse related to normal form are not satisfied:
+
+- Proportion of mail-in-votes to election day vote is already high (Aggregate convergence lemma)
+  - Note: $\lim_{\zeta_i \rightarrow \infty} \alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}=y_i$
+- Correlation between $x$ and $y$ is very high (Twixt lemma)
+  - Note: If correlation is 1, we can set $x_i=\rho_s y_i$ so that $\alpha_i(y_i,\zeta_i)=\frac{\rho_s y_i+\zeta_i y_i}{\zeta_i+x_i}$
+- Low variance to $\zeta$ 
+  - Note: Invariance across precincts would imply that $\zeta_i=\zeta$, so that election outcome only determined by variations in two parameters: $\alpha_i(y_i,x_i)=\frac{x_i+\zeta y_i}{\zeta+x_i}$
+
+If none of this three cases are satisfied, variation in $\zeta_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
+
+## `r metad$toc$sec1$unm[7]`
+
+1. Differenc in the cost of voting (e.g., topology, voting rules, dropboxes, socio economics etc.) across precincts $\Rightarrow$ 
+1. Make changes to the likelihood of voting $\Rightarrow$ 
+1. Simplify so that changes in the likelihood of voting only impact mode 2 $\Rightarrow$ 
+1. Higher $\zeta_i$ $\Rightarrow$
+1. If new and earlier sample not representative of each other, higher $\Gamma_i$ $\Rightarrow$
+1. Which changes the total election outcome through $\alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+1}$
+
+##
+
+The impact on the election outcome, however, would be small or close to non-existens if the conditions
+of the existance of a *trivial* Manifold related to opposition form are not satisfied:
+
+- Proportion of the hybrid ballot boxes is already high (Aggregate convergence lemma)
+  - Note: $\lim_{\Gamma_i \rightarrow \infty} \alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+g_i}=y_i$
+- Correlation between $g$ and $h$ is very high (Twixt lemma)
+  - Note: If correlation is 1, we can set $g_i=\rho_h h_i$ so that $\alpha_i(h_i,\Gamma_i)=\frac{\rho_h h_i+\Gamma_i h_i}{\Gamma_i+x_i}$
+- Low variance to $\Gamma_i$ 
+  - Note: Invariance across precincts would imply that $\Gamma_i=\Gamma$, so that election outcome only determined by variations in two parameters: $\alpha_i=\frac{g_i+\Gamma h_i}{h_i}$
+
+If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
+
+---
+
+```{webr-r}
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
+probw <- c(m=0.51,s=0.10)
+probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
+probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
+ztech <- c(0,1)	
+app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
+print(SimVoterdatabase(app_bal))
+```
+
+# `r metad$toc$sec2$nmn`
+
+## `r metad$toc$sec2$unm[1]`
+
+- We have identified three ways of counting
+  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
+  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
+  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
+-  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
+  -  We are free to *predetermine* **3** of them
+  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
+  -  Selecting **3** parameters from a set of **5** implies **10** different combinations
+
+## `r metad$toc$sec2$unm[2]`
+
+**20 laws and 40 isometris**
+
+```{r, echo=F}
+# Load necessary library
+library(tibble)
+
+# Create the data.frame
+laws_df <- tribble(
+  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
+  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
+  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
+  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
+  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
+  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
+  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
+  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
+  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
+  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
+  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
+  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
+  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
+  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
+  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
+  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
+  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
+  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
+  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
+  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
+  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
+)
+# Display the data.frame
+kable(laws_df, format = "markdown", escape = FALSE)
+```
+
+##
+
+::: {.callout-caution collapse="true"}
+## Proportions
+
+```{r, echo=F}
+library(kableExtra)
+library(tibble)
+new_tbl <- data.frame(
+  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
+  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
+  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
+  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
+  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
+  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
+  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
+  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
+)
+
+# Extract the columns
+V1 <- new_tbl$V1
+V2 <- new_tbl$V2
+V3 <- new_tbl$V3
+V4 <- new_tbl$V4
+Equation1 <- new_tbl$Equation1
+Equation2 <- new_tbl$Equation2
+Equation3 <- new_tbl$Equation3
+Equation4 <- new_tbl$Equation4
+
+# Combine the columns
+combined <- data.frame(
+  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
+  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
+  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
+  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
+)
+kable(combined, format = "markdown", escape = FALSE)
+```
+
+:::
+
+[@delfino2011analysis]
+
+## `r metad$toc$sec2$unm[3]`
+
+## `r metad$toc$sec2$unm[4]`
+
+## `r metad$toc$sec2$unm[5]`
+
+# `r metad$toc$sec3$nmn`
+
+## `r metad$toc$sec3$unm[1]`
+
+::: {.panel-tabset}
+
+### `r metad$tabsets[[1]]`
+
+```{r, echo=F}
+kableExtra::kbl(app_n_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+```
+
+### `r metad$tabsets[[2]]`
+
+```{r, echo=F, out.width="60%"}
+app_n_out[['corxy']]
+```
+
+### `r metad$tabsets[[3]]`
+
+```{r, echo=F, out.width="60%"}
+app_n_out[['qunt']]
+```
+
+### `r metad$tabsets[[4]]`
+
+```{r, echo=F}
+app_n_out[['ro3d']]
+```
+
+### `r metad$tabsets[[5]]`
+
+```{r, echo=F, out.width="60%"}
+app_n_out[['regr']]
+```
+
+### `r metad$tabsets[[6]]`
+
+```{r, echo=F, out.width="60%"}
+app_n_out[['resp']]
+```
+
+:::
+
+## `r metad$toc$sec3$unm[2]`
+
+**Example 1: Normal form**
+
+::: {.panel-tabset}
+
+### `r metad$tabsets[[1]]`
+
+```{r, echo=F}
+kableExtra::kbl(app_ex1_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+```
+
+### `r metad$tabsets[[2]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex1_out[['corxy']]
+```
+
+### `r metad$tabsets[[3]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex1_out[['qunt']]
+```
+
+### `r metad$tabsets[[4]]`
+
+```{r, echo=F}
+app_ex1_out[['ro3d']]
+```
+
+### `r metad$tabsets[[5]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex1_out[['regr']]
+```
+
+### `r metad$tabsets[[6]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex1_out[['resp']]
+```
+
+:::
+
+##
+
+**Example 2: applying hybrid form**
+
+::: {.panel-tabset}
+
+### `r metad$tabsets[[1]]`
+
+```{r, echo=F}
+kableExtra::kbl(app_ex2_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+```
+
+### `r metad$tabsets[[2]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex2_out[['corxy']]
+```
+
+### `r metad$tabsets[[3]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex2_out[['qunt']]
+```
+
+### `r metad$tabsets[[4]]`
+
+```{r, echo=F}
+app_ex2_out[['ro3d']]
+```
+
+### `r metad$tabsets[[5]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex2_out[['regr']]
+```
+
+### `r metad$tabsets[[6]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex2_out[['resp']]
+```
+
+:::
+
+##
+
+**Example 3: applying opposition form**
+
+::: {.panel-tabset}
+
+### `r metad$tabsets[[1]]`
+
+```{r, echo=F}
+kableExtra::kbl(app_ex3_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+```
+
+### `r metad$tabsets[[2]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex3_out[['corxy']]
+```
+
+### `r metad$tabsets[[3]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex3_out[['qunt']]
+```
+
+### `r metad$tabsets[[4]]`
+
+```{r, echo=F}
+app_ex3_out[['ro3d']]
+```
+
+### `r metad$tabsets[[5]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex3_out[['regr']]
+```
+
+### `r metad$tabsets[[6]]`
+
+```{r, echo=F, out.width="60%"}
+app_ex3_out[['resp']]
+```
+
+:::
+
+# `r metad$toc$sec4$nmn` {#litrev}
+
+```{r, echo=FALSE, out.width="20%", fig.cap=""}
+p1 <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/ss.png')
+knitr::include_graphics(c(p1))
+```
+
+`r #Citet(bib, "delfino2011analysis")`
+
+> Abstract: On August 15th, **2004**, Venezuelans had the opportunity to vote
+in a Presidential Recall Referendum **to decide whether or not President Hugo
+Chávez should be removed from office.** **The process was largely computer-
+ized using a touch-screen system.** In general the ballots were not manually
+counted. The significance of the high linear correlation (0.99) between the
+number of requesting signatures for the recall petition and the number of op-
+position votes in computerized centers is analyzed. The same-day audit was
+found to be not only ineffective but a source of suspicion...
+
+::: aside
+[Link to Youtube-video](https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s)
+:::
+
+##
+
+- Venezuela referendum to recall President Hugo Chávez (2004)
+	- Mode 1: Computerized Voting Centers
+	- Mode 2: Manuel Voting Centers
+
+> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.
+
+```{r, echo=FALSE, out.width="85%", fig.cap=""}
+p3 <- paste0(rprojroot::find_rstudio_root_file(),'pngs/manifold.png')
+knitr::include_graphics(c(p3))
+```
+
+# `r metad$toc$sec5$nmn` {#proced}
+
+# `r metad$toc$sec5$unm[1]`
+
+1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
+1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
+1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
+1. Check for normality of the estimated residual for the Manifold model.
+
+If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.
+
+# `r metad$toc$sec6$nmn`
+
+```{r, echo=FALSE, results='asis',warning=F}
+params <- list(name="1")
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+
+```{r, echo=FALSE, results='asis',warning=F}
+params <- list(name="2")
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+
+```{r, echo=FALSE, results='asis',warning=F}
+params <- list(name="2")
+app_a_out <- app_2_out 
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+
+```{r, echo=FALSE, results='asis',warning=F}
+params <- list(name="2")
+app_a_out <- app_2_out 
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+
+```{r, echo=FALSE, results='asis',warning=F}
+params <- list(name="2")
+app_a_out <- app_2_out 
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+
+# `r metad$toc$sec7$nmn`
+
+- At the heart of the difference between a fair and rigged election is the issue of causation
+  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
+  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
+
+- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
+	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
+	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
+
+##
+
+- Condition on that $R^2$ falls within the critical region.
+  - Normal form
+```{r, echo=F, out.width="40%", fig.cap=""}
+pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2n.png')
+knitr::include_graphics(c(pr2n))
+```
+
+ - Hybrid form
+```{r, echo=F, out.width="40%", fig.cap=""}
+pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2h.png')
+knitr::include_graphics(c(pr2h))
+```
+
+- Our four applications
+
+```{r, echo=F, warning=F, message=F}
+#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+# `r metad$toc$sec8$nmn`
+
+::: {#refs}
+:::

### 2023-12-30 presentation.qmd
firstup
paperadd

@@
 subtitle: "Based upon the ideas developed by Edward K. Solomon"
-#format:
-#  revealjs: 
-#    smaller: true
-#    toc-depth: 1
-#    toc: true 
+format:
+  revealjs: 
+    smaller: true
+    toc-depth: 1
+    toc: true 
 webr: 
@@
 
-```{r}
-knitr::knit_exit()
-```
-
 ## `r metad$toc$sec3$unm[2]`

### 2023-12-30 shinyapps/r2sim/app.R

@@ -1,7 +1,9 @@
-library(shiny)
-library(magrittr)
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
 library(ManifoldDestinyWASMP)
 library(ManifoldDestinyWASMD)
+library(shiny)
+library(magrittr)
 library(ggplot2)
 options(scipen=999)
 library(plotly)

### 2023-12-31 tabsets.qmd
app50

--- 2023-12-30 tabsets.qmd
@@
 
-Tabcsets
+Tabsets
+
+```{r, echo=F, message=F, warning=F}
+library(ManifoldDestiny)
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+library(RefManageR)
+library(huxtable)
+modlat <- eqpar$meql
+md <- ManifoldDestinyWASMD::metad
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+```
+
+## Application 0 
+```{r, echo=FALSE, results='asis',warning=F}
+app_a_out <- app_0_out 
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
 
@@
 knitr::knit_exit()
-```
-
-```{r, echo=F, message=F, warning=F}
-library(ManifoldDestiny)
-library(RefManageR)
-library(huxtable)
-library(Hyperinflation)
-mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/applications.R'))
 ```
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_n_out
+mda <- md[['app1']]
+apprda <- get('app1')
+app_a_out <- seloutput(selreport(apprda,mda))
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
 text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
-
-:::
 
@@
 
-:::
-
-::: {.callout-caution collapse="true"}
-## Application 0 
-```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_0_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-:::
-
 ::: {.callout-caution collapse="true"}

### 2023-12-31 app_par.qmd
app50
tabsets

@@
 ```{r, echo=F}
-# Start on 50
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
@@
 app_a_out <- seloutput(selreport(apprda,mda))
+```
+
+```{r, echo=F}
+apn <- paste0('app','1')
+mda <- md[[apn]]
 ```
@@
 [Link to raw data and independent calculcations](`r mda$sht$url`)
-[@sol2022_1]
+
+---
 
 ::: {.panel-tabset}
+
 ### `r mda$tabsets[[1]]`
@@
 ```
-
-### References
-
-::: {#refs}
-:::

### 2023-12-31 tabsets.qmd
with50

@@
 
-Tabsets
-
 ```{r, echo=F, message=F, warning=F}
@@
 
+::: {.callout-caution collapse="true"}
+## `r md$tabhead[1]`
+```{r, echo=FALSE, results='asis',warning=F}
+app_a_out <- app_n_out
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+:::
+
+::: {.callout-caution collapse="true"}
+## `r md$tabhead[2]`
+```{r, echo=FALSE, results='asis',warning=F}
+app_a_out <- app_ex1_out 
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+:::
+
+::: {.callout-caution collapse="true"}
+## `r md$tabhead[3]`
+```{r, echo=FALSE, results='asis',warning=F}
+app_a_out <- app_ex2_out 
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+:::
+
+::: {.callout-caution collapse="true"}
+## `r md$tabhead[4]`
+```{r, echo=FALSE, results='asis',warning=F}
+app_a_out <- app_ex3_out 
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+:::
+
+::: {.callout-caution collapse="true"}
 ## Application 0 
@@
 ```
-
-```{r}
-knitr::knit_exit()
-```
-
-::: {.callout-caution collapse="true"}
-## `r md$tabhead[1]`
-
-```{r, echo=FALSE, results='asis',warning=F}
-mda <- md[['app1']]
-apprda <- get('app1')
-app_a_out <- seloutput(selreport(apprda,mda))
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-::: {.callout-caution collapse="true"}
-## `r md$tabhead[2]`
-
-```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_ex1_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
 :::
-
-::: {.callout-caution collapse="true"}
-## `r md$tabhead[3]`
-
-```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_ex2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-:::
-
-::: {.callout-caution collapse="true"}
-## `r md$tabhead[4]`
-
-```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_ex3_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[51:length(text)], collapse = "\n"), quiet = TRUE))
-```
 
@@
 :::
-
-```{r}
-knitr::knit_exit()
-```
 
@@
 :::
-
-[@delfino2011analysis]
-
-## References
-
-::: {#refs}
-:::

### 2023-12-31 app_par.qmd
morepres

@@
 quarto::quarto_preview(pre_fil)
-params <- list(name="0")
-googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
+params <- list(name="1")
 #lapply(paste0("app",0:4), function(x){recoudatr(mda=md[[x]])})
@@
 ```{r, echo=F}
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+library(ManifoldDestiny)
+library(dplyr)
+library(ggplot2)
+library(dplyr)
+library(combinat)
+library(htmltools)
+library(ggplot2)
+library(broom)
+library(combinat)
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-mda <- md[[paste0("app",params$name)]]
-apprda <- get(load(paste0(rprojroot::find_rstudio_root_file(),'/data/app',params$name,".rda")))
-app_a_out <- seloutput(selreport(apprda,mda))
+md$tabsets
+mda <- md['1']
+app1_rp <- selreport(app1,md$app1)
+app_a_out <- seloutput(app1_rp)
 ```
@@
 ```{r, echo=F}
-apn <- paste0('app','1')
-mda <- md[[apn]]
+mda <- md['1']
+app1_rp <- selreport(app1,md$app1)
+app_a_out <- seloutput(app1_rp)
 ```
@@
 
-### `r mda$tabsets[[1]]`
+### `r md$tabsets[[1]]`
+
 ```{r, echo=F}
@@
 ```
-### `r mda$tabsets[[2]]`
+### `r md$tabsets[[2]]`
 ```{r, echo=F, out.width="60%"}
@@
 ```
-### `r mda$tabsets[[3]]`
+### `r md$tabsets[[3]]`
 ```{r, echo=F, out.width="60%"}
@@
 ```
-### `r mda$tabsets[[4]]`
+### `r md$tabsets[[4]]`
 ```{r, echo=F}
@@
 ```
-### `r mda$tabsets[[5]]`
+### `r md$tabsets[[5]]`
 ```{r, echo=F, out.width="60%"}
@@
 ```
-### `r mda$tabsets[[6]]`
+### `r md$tabsets[[6]]`
 ```{r, echo=F, out.width="60%"}
@@
 :::
+
+---
 

### 2023-12-31 paper.qmd
morepres

@@
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 ```

### 2023-12-31 presentation.qmd
tabsets
morepres

@@
 params <- list(name="2")
-app_a_out <- app_2_out 
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')

### 2024-01-01 presentation.qmd
huxed

@@
 
-```{r, echo=F, caption="Example 1"}
-## Tower 1
-ex1m <- as.matrix(cbind(S,T,U,V))
-towi <- as.data.frame(ex1m) %>% 
-  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
-  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
-  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
-  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
-  dplyr::select(5:8) %>%
-  t() %>%
-  data.frame() %>%
-  data.table::setnames(paste0("County_",1:6))
+**Our numerical example**
 
-towi[3:4,1] <- ""
-towi[4,2] <- ""
-lego_hux_nor_i <- hux(towi[,1:3]) 
-lego_hux_nor_i 
+:::: {.columns}
+::: {.column width="50%"}
+Case 1
+:::
+```{r, echo=F}
+clr <- c("black","green","red","blue")
+lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
+  set_text_color(5, 1:2, clr[1]) %>%
+  set_background_color(1, 1:3, clr[2]) %>% 
+  set_background_color(2, 1:3, clr[3]) %>%
+  set_background_color(3:5, 1:3, clr[4]) 
+lego_hux_imp_i
 ```
 
-```{r, echo=F, caption="Example 2"}
-## Tower 2
-ex2m <- as.matrix(cbind(S,T,Up,Vp))
-towii <- as.data.frame(ex2m) %>% 
-  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
-  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
-  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
-  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
-  dplyr::select(5:8) %>%
-  t() %>%
-  data.frame() %>%
-  data.table::setnames(paste0("County_",1:6))
-towii[3:4,1] <- ""
-towii[4,2] <- ""
-lego_hux_nor_ii <- hux(towii[,1:3]) 
-lego_hux_nor_ii 
+::: {.column width="50%"}
+Case 2
+:::
+```{r, echo=F}
+lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
+  set_text_color(5, 1:2, clr[1]) %>%
+  set_background_color(1, 1:3, clr[2]) %>% 
+  set_background_color(2, 1:3, clr[3]) %>%
+  set_background_color(3:5, 1:3, clr[4]) 
+lego_hux_imp_ii
 ```
+::::
 

### 2024-01-01 R/wasmnonverting.R

@@ -26,4 +26,5 @@ py_genpolycoeff <- function(expr=NULL,solvd=NULL,solvf=NULL,eur=c(0, 0, 0),dnr=0
   reticulate::py$genpolycoeff(expr=expr,solvd=solvd,solvf=solvf,eur=as.integer(eur),dnr=dnr)
 }
 #####################################################################################################
-#py_genpolycoeff()
+#py_genpolycoeff(expr=NULL,solvd='z',solvf='u0',eur=c(1, 4, 2),dnr=0)
+#py_polysolver() 

### 2024-01-01 index.qmd
paperadd

@@
 md <- ManifoldDestinyWASMD::metad
-```
-
-### Simulation
-```{webr-r}
 library(dplyr)
@@
 library(combinat)
+```
+
+### Simulation
+```{webr-r}
 dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
@@
 SimVoterdatabase(app_bal)
-app_n_rep <- selreport(app0,md$app0)
+app_n_rep <- selreport(app_bal,md$app0)
 app_n_out <- seloutput(app_n_rep)
+app_n_sim <- SimVoterdatabase(app_bal)
 ```
@@
 ### Applications
+
+#### App1
 ```{webr-r}
-library(dplyr)
-library(combinat)
-library(htmltools)
-library(ggplot2)
-library(broom)
-library(combinat)
-app0_rp <- selreport(app0,md$app0)
-app_0_out <- seloutput(app0_rp)
 app1_rp <- selreport(app1,md$app1)
 app_1_out <- seloutput(app1_rp)
+```
+
+#### App2
+```{webr-r}
 app2_rp <- selreport(app2,md$app2)
 app_2_out <- seloutput(app2_rp)
-app3_rp <- selreport(app2,md$app2)
-app_3_out <- seloutput(app2_rp)
-app4_rp <- selreport(app2,md$app2)
-app_4_out <- seloutput(app2_rp)
 ```

### 2024-01-01 presentation.qmd

@@
     toc: true 
-webr: 
-  show-startup-message: true    # Disable displaying status of webR initialization
-  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
-filters:
-- webr 
-footer: <https://lotariohw26.github.io/ManifoldDestiny/>
+#webr: 
+#  show-startup-message: true    # Disable displaying status of webR initialization
+#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
+##filters:
+#- webr 
+#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
 ---
@@
 If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
-
----
-
-```{webr-r}
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
-probw <- c(m=0.51,s=0.10)
-probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztech <- c(0,1)	
-app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
-print(SimVoterdatabase(app_bal))
-```
 

### 2024-01-01 presentation.qmd
rest

@@
 If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
+
+[Link to R2 simulator for testing](https://shinylive.io/r/app/#h=0&code=NobwRAdghgtgpmAXGKAHVA6ASmANGAYwHsIAXOMpMAdzgCMAnRRASwgGdSoAbbgCgA6YALJQILAGZFuAEwAicTmwCeAdQCCAZWEAFIbgAEDOKiLsDAXgNCAFqVKp2iAPTPuRLgxZEb1AEwAbBgA5iykNgCudBjezsJyAPoa2gDCQgCUAhC0jMxsnDz8QqLiUrIKShBqWvH6RiZmltZgdg5Oru6e3r6BIWGR0bHxSTVpYJkQ3CyMUAzKfCWS0vKKpCrJuhNTM3MLYkvlq+s1clvTDLPz7DYqZzvzMFDBXvYMdxe7wcGonX4TRKg1iR2Hx2AQWKgKBYAJyw96XPg-DzcZTw3ZyAAqaPmAGsoHRuHAAKIAD1IF2xfBkP2Ubyy2w+8zsMG4pCI0nYlOeLBkpPJUAmERYBgAPABaAwSbhCmQ6J5wQQQAwGNakQlyiBwIpgLB+AyaFgwCLcKBshgZXBZZVcOjsOCkDVaxXK634x3agDiF1QNjqVpdAcD7B59FmABkoMoiBFSM7A-GXcGZKGGO64wmM3bCQRSABJCCoGOCMAAN1mLHxhL9YE0WrgOYMUElRAYMEQdQIxYAci3Htxm62hE0hBBezxqwAJZSMHkDmBDqy2adeGTVgDy6DMYW8Sqkg7Aw7AANMwaBEAy6UtSozGYgEXgXgI+cLsZHqGMBGrXfvdDgDAMRASAY771mwOZOHUZbSnATQAMwAAzwZe-o3vG5Bks+RZCMYwQltWWBwKEnB-nAMgGCWHh-uYfDwGIuCcDImR4ORPARHAFgAOSwRgACMACshjwRgfh8RxyHXqhgboXmBZYWAMBsI8JLVsIbCNhAZFKSx0HmHeMC-v+gHkZRDDsJBrHsRxAAsiGGDZiFiVekloXAGGya+YCkBEDDnsxQg6AwRB0PiLBTKQygAUBFFrBAwTtsxUFsU0HFCQJBhCTx8GOShznWq5MkvsWbAlpC5p+WARLZmeBjsMoxEwCxXghWFyjxYYiUwZxqWCbxWXiblAbSZhHkRNWAVBc1YQRUZJLOMEzgQG12lJVYKUYAEPWZdlEkDUN7nFjIeHlXIkhAe+E10KFU2RQYs3zYt5nQclYpCX4PXwQAHNtA0unpf4sE++1CDIFzUGZ5Xfvpf43SDUBg49K0GAh-U-Y2OY7gAQjGbIQMWDARL5hhCFgBP6oaxqmjuGQ5ZJKO5Y8bBpjTzlIqQa4xoVQisxazOSTahLsw4cn83A1M7bTvPxukEwBnTKpumITpCBilaKH64sZjadoOorRQazeNpM2AKsEjBPH6JLqNJimEZRlh+uo4mIbBamut8HLjuBgzEBMw7nuuqbguc55qvm+MluOzL-uyxHgYe6hhtu8rqsGH4Ft+z91su7b0avhnVvO7Mabx9H3u+9Hmuq0Hwuq2n4f5z9UcVwYTfOa3N6txMEwAMTdwYCgSGwMF2gwJZ-lkI9j-+4qSgT6MkHwbAvoYucvukBggP6-p9yTSrBkaJpnv6MgSN8ooSnAY9kARUDo2Pi-uQAJPjECGJvO198N-cAGLmztOElnPo2dgGA-qPlBOSdgPwwgPxfM-QiJYiZ4AyMAYAPEAC66DW4KQgFpGeUAQFgIBhA0y0DYxLxjI-HBSkkGWnGKgjBWCcpeR8kAghoD7z-U7JwUhYVYGUJYa-ZodD0gMMwa3YqpU2GEM4eAnhUC+EUNII-SRf5aEoLQeInKERpEcIfMQ+RZD+HKIiOo+hmimE7UOrooh3DIFGKUY-Q6ZjREWNbqQICM9jDQIIKaBUjjYZg1wAwPw+9cYFg-E0RxET6xORvDhcwVhOwAM0YYFJfgsFxIzNQqAJImidhySSVJhTgAZMvCqbySokl8EEakipPlSmZIMPmEq0NqmqIYHUjpjSS4uh0dUiIdTBllKyQmax1TDp1MmSMiOe4GpWB4qIzsPFcBvVgukSxAYT5nxnjIU0UAMASAuPAPgISoAWAJlMTgNSJDADtAARz4CswksVwg3MvOszJIS6AXMmCwa5Hi7lwEeW9F5wQ3keI+Rs6WBgACkAA+WFBgjRcHIIiP8BAmhkFCgqM5hhMpIXXjlT+7kf5px2qVAgFA1iEnMDPTs0J4KGGhGlOEOUOCkDIvSp5qzcB8VbgxIBtFcbbNQM-PwAoADUHKZAACp2AyCpKfMVZzW6Up4kA+5EQxA0oVKK8VUBcDnVtE0Sl1KcXmGcAYAlaqMV6hnlqnVOKlXfHFXQI1gUTVWDNdi2lBgrU2pypSk+QC9lcEOcchU6qjV2twDK+inL14IqRWGg5ItmDa2gPAEEnZ-IYqMBKi2YAdD5u+UWrsDEi0ADVK3jCJTtK5sZRUxoYAQE+UcAC+Uc+4pGMH44CnR-Sr0oazIBxgNJ-h0J0Pg78BCkGVN3RgRAwZ-ndjlE+qBQ3KvdmI9BcLEUqh5LSZgqAWDRQSO4WKq7iDcHYBYXNYAzlFrLXW-dKaaRMEQLMC4V6+BZrgC2ggrcvisyVagXAUBFB8BJBYDqhhB68AsP+mFkrrAa2CHAIgMAEg3E4EQZ4sBERbmqouMAIZsXhTqDwH0TYrDdQMJdDgcEkIGFQ8zE0toalhEJIeCc-y2QEYakZKtFlzB0AiikPxwQWzKDqHk0jInoJ1AiqRlI0YyAZFY8zDDWGEglimJqaDbByCtpMPOqw7DbEutQDuxp6C0G4AweUgz9plCQkPHs64pEOzSBbIeAkbFNOSu05h7D+mh5GbIBiszTRLOyOIaK2zGT7NvSc4YFz4V3Okc8zYbzzEb1+dIwF0W4wtPodC3plzkWTNUsBLFmR+jOyJdccl4AsFHNNIy25zqzQct5cMAV-8RWlOleC+V3T4XDMkmM9FurFmGtcOs0lzBbXcBWU60PTLPWhDsGkDyHz7ghvNGMKuUbIXdMcadMoCwTKYNxca0tlrK2Vlpcu9wCwQhZX6B0zAD7YA3tBfO9ht7fBru3YsPdxbzXUGtdS5kt7f3ZVfbwD9v7AOzvjeB-iK7N3cB3YW+A6HdnVuvex+9z7SPvuhbR2TwHGtwhwHgAkHBhoeDuzK-GMEPA4AJAQ9wZnYhtX8A6okgwD7u6IQAOx+AxnXJB3ciQBGhN-RCF4F01XtJKUK-ZBtmWvF2re15e4GF7XAftIsh0cwEaHMdFBkwMAAKq5hnTlTEzBU0i1OepxVRPku4BkCwUIpA71WWlv6A315h3KJFvaiU477dO5dztN3iAPeqy9wTH327XGMMMAHoPIfykAjPKLxtiJ5RhgoOCmwTQ-CEvDxMDtWQd6kzQKgCeNwqjqHQHwIUTQhSGEnm0jXo8-wTCyGADt6CgA)
 

### 2024-01-01 abc.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 
 ## R
-cp -f R/wasmconverting.R MD_WASMP/wasmconverting.R
+cp -f R/wasmconverting.R MD_WASMP/R/wasmconverting
 cp -f R/wasmconverting.R MD_WASMS/examples/r/MD-sandbox/wasmconverting.R
 
 ## Shiny

### 2024-01-01 paper.qmd
paperupd

@@
 
----
-
-```{webr-r}
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
-probw <- c(m=0.51,s=0.10)
-probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztech <- c(0,1)	
-app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
-print(SimVoterdatabase(app_bal))
-```
+[Link to R2 simulator for testing](https://shinylive.io/r/app/#h=0&code=NobwRAdghgtgpmAXGKAHVA6ASmANGAYwHsIAXOMpMAdzgCMAnRRASwgGdSoAbbgCgA6YALJQILAGZFuAEwAicTmwCeAdQCCAZWEAFIbgAEDOKiLsDAXgNCAFqVKp2iAPTPuRLgxZEb1AEwAbBgA5iykNgCudBjezsJyAPoa2gDCQgCUAhC0jMxsnDz8QqLiUrIKShBqWvH6RiZmltZgdg5Oru6e3r6BIWGR0bHxSTVpYJkQ3CyMUAzKfCWS0vKKpCrJuhNTM3MLYkvlq+s1clvTDLPz7DYqZzvzMFDBXvYMdxe7wcGonX4TRKg1iR2Hx2AQWKgKBYAJyw96XPg-DzcZTw3ZyAAqaPmAGsoHRuHAAKIAD1IF2xfBkP2Ubyy2w+8zsMG4pCI0nYlOeLBkpPJUAmERYBgAPABaAwSbhCmQ6J5wQQQAwGNakQlyiBwIpgLB+AyaFgwCLcKBshgZXBZZVcOjsOCkDVaxXK634x3agDiF1QNjqVpdAcD7B59FmABkoMoiBFSM7A-GXcGZKGGO64wmM3bCQRSABJCCoGOCMAAN1mLHxhL9YE0WrgOYMUElRAYMEQdQIxYAci3Htxm62hE0hBBezxqwAJZSMHkDmBDqy2adeGTVgDy6DMYW8Sqkg7Aw7AANMwaBEAy6UtSozGYgEXgXgI+cLsZHqGMBGrXfvdDgDAMRASAY771mwOZOHUZbSnATQAMwAAzwZe-o3vG5Bks+RZCMYwQltWWBwKEnB-nAMgGCWHh-uYfDwGIuCcDImR4ORPARHAFgAOSwRgACMACshjwRgfh8RxyHXqhgboXmBZYWAMBsI8JLVsIbCNhAZFKSx0HmHeMC-v+gHkZRDDsJBrHsRxAAsiGGDZiFiVekloXAGGya+YCkBEDDnsxQg6AwRB0PiLBTKQygAUBFFrBAwTtsxUFsU0HFCQJBhCTx8GOShznWq5MkvsWbAlpC5p+WARLZmeBjsMoxEwCxXghWFyjxYYiUwZxqWCbxWXiblAbSZhHkRNWAVBc1YQRUZJLOMEzgQG12lJVYKUYAEPWZdlEkDUN7nFjIeHlXIkhAe+E10KFU2RQYs3zYt5nQclYpCX4PXwQAHNtA0unpf4sE++1CDIFzUGZ5Xfvpf43SDUBg49K0GAh-U-Y2OY7gAQjGbIQMWDARL5hhCFgBP6oaxqmjuGQ5ZJKO5Y8bBpjTzlIqQa4xoVQisxazOSTahLsw4cn83A1M7bTvPxukEwBnTKpumITpCBilaKH64sZjadoOorRQazeNpM2AKsEjBPH6JLqNJimEZRlh+uo4mIbBamut8HLjuBgzEBMw7nuuqbguc55qvm+MluOzL-uyxHgYe6hhtu8rqsGH4Ft+z91su7b0avhnVvO7Mabx9H3u+9Hmuq0Hwuq2n4f5z9UcVwYTfOa3N6txMEwAMTdwYCgSGwMF2gwJZ-lkI9j-+4qSgT6MkHwbAvoYucvukBggP6-p9yTSrBkaJpnv6MgSN8ooSnAY9kARUDo2Pi-uQAJPjECGJvO198N-cAGLmztOElnPo2dgGA-qPlBOSdgPwwgPxfM-QiJYiZ4AyMAYAPEAC66DW4KQgFpGeUAQFgIBhA0y0DYxLxjI-HBSkkGWnGKgjBWCcpeR8kAghoD7z-U7JwUhYVYGUJYa-ZodD0gMMwa3YqpU2GEM4eAnhUC+EUNII-SRf5aEoLQeInKERpEcIfMQ+RZD+HKIiOo+hmimE7UOrooh3DIFGKUY-Q6ZjREWNbqQICM9jDQIIKaBUjjYZg1wAwPw+9cYFg-E0RxET6xORvDhcwVhOwAM0YYFJfgsFxIzNQqAJImidhySSVJhTgAZMvCqbySokl8EEakipPlSmZIMPmEq0NqmqIYHUjpjSS4uh0dUiIdTBllKyQmax1TDp1MmSMiOe4GpWB4qIzsPFcBvVgukSxAYT5nxnjIU0UAMASAuPAPgISoAWAJlMTgNSJDADtAARz4CswksVwg3MvOszJIS6AXMmCwa5Hi7lwEeW9F5wQ3keI+Rs6WBgACkAA+WFBgjRcHIIiP8BAmhkFCgqM5hhMpIXXjlT+7kf5px2qVAgFA1iEnMDPTs0J4KGGhGlOEOUOCkDIvSp5qzcB8VbgxIBtFcbbNQM-PwAoADUHKZAACp2AyCpKfMVZzW6Up4kA+5EQxA0oVKK8VUBcDnVtE0Sl1KcXmGcAYAlaqMV6hnlqnVOKlXfHFXQI1gUTVWDNdi2lBgrU2pypSk+QC9lcEOcchU6qjV2twDK+inL14IqRWGg5ItmDa2gPAEEnZ-IYqMBKi2YAdD5u+UWrsDEi0ADVK3jCJTtK5sZRUxoYAQE+UcAC+Uc+4pGMH44CnR-Sr0oazIBxgNJ-h0J0Pg78BCkGVN3RgRAwZ-ndjlE+qBQ3KvdmI9BcLEUqh5LSZgqAWDRQSO4WKq7iDcHYBYXNYAzlFrLXW-dKaaRMEQLMC4V6+BZrgC2ggrcvisyVagXAUBFB8BJBYDqhhB68AsP+mFkrrAa2CHAIgMAEg3E4EQZ4sBERbmqouMAIZsXhTqDwH0TYrDdQMJdDgcEkIGFQ8zE0toalhEJIeCc-y2QEYakZKtFlzB0AiikPxwQWzKDqHk0jInoJ1AiqRlI0YyAZFY8zDDWGEglimJqaDbByCtpMPOqw7DbEutQDuxp6C0G4AweUgz9plCQkPHs64pEOzSBbIeAkbFNOSu05h7D+mh5GbIBiszTRLOyOIaK2zGT7NvSc4YFz4V3Okc8zYbzzEb1+dIwF0W4wtPodC3plzkWTNUsBLFmR+jOyJdccl4AsFHNNIy25zqzQct5cMAV-8RWlOleC+V3T4XDMkmM9FurFmGtcOs0lzBbXcBWU60PTLPWhDsGkDyHz7ghvNGMKuUbIXdMcadMoCwTKYNxca0tlrK2Vlpcu9wCwQhZX6B0zAD7YA3tBfO9ht7fBru3YsPdxbzXUGtdS5kt7f3ZVfbwD9v7AOzvjeB-iK7N3cB3YW+A6HdnVuvex+9z7SPvuhbR2TwHGtwhwHgAkHBhoeDuzK-GMEPA4AJAQ9wZnYhtX8A6okgwD7u6IQAOx+AxnXJB3ciQBGhN-RCF4F01XtJKUK-ZBtmWvF2re15e4GF7XAftIsh0cwEaHMdFBkwMAAKq5hnTlTEzBU0i1OepxVRPku4BkCwUIpA71WWlv6A315h3KJFvaiU477dO5dztN3iAPeqy9wTH327XGMMMAHoPIfykAjPKLxtiJ5RhgoOCmwTQ-CEvDxMDtWQd6kzQKgCeNwqjqHQHwIUTQhSGEnm0jXo8-wTCyGADt6CgA)
 

### 2024-01-01 abc.sh

@@ -6,9 +6,9 @@ cp -f R/wasmconverting.R MD_WASMS/examples/r/MD-sandbox/wasmconverting.R
 
 ## Shiny
 cp -f shinyapps/r2rsim/app.R MD_WASMS/examples/r/MD-r2rsim/app.R
+cp -f shinyapps/manimp/app.R MD_WASMS/examples/r/MD-manimp/app.R
 cp -f shinyapps/empapp/app.R MD_WASMS/examples/r/MD-empapp/app.R
 cp -f shinyapps/restor/app.R MD_WASMS/examples/r/MD-restor/app.R
-cp -f shinyapps/manimp/app.R MD_WASMS/examples/r/MD-manimp/app.R
 
 # Python
 cp -f script/python/polysolver.py MD_WASMS/examples/python/sandbox/polysolver.py

### 2024-01-01 R/wasmnonverting.R
newNS

@@ -28,3 +28,43 @@ py_genpolycoeff <- function(expr=NULL,solvd=NULL,solvf=NULL,eur=c(0, 0, 0),dnr=0
 #####################################################################################################
 #py_genpolycoeff(expr=NULL,solvd='z',solvf='u0',eur=c(1, 4, 2),dnr=0)
 #py_polysolver() 
+##' @export bm
+bm <- function(){
+   devtools::document()
+   system(paste0('cd ',rprojroot::find_rstudio_root_file(),'; R CMD INSTALL --preclean --no-multiarch --with-keep.source .'))
+}
+#' @export k
+k <- function(){
+    df <-  clipr::write_last_clip()
+}
+
+#' @export l
+l <- function(){
+    open_command <- switch(Sys.info()[['sysname']],
+                           Windows= 'open',
+                           Linux  = 'xdg-open',
+                           Darwin = 'open')
+
+    temp_file <- paste0(tempfile(), '.xlsx')
+    df <-  clipr::write_last_clip()
+    openxlsx::write.xlsx(df, file = temp_file)
+    invisible(system(paste(open_command, temp_file),
+                     ignore.stdout = TRUE, ignore.stderr = TRUE))
+}
+
+#' @export recoudatr
+recoudatr <- function(mda=NULL){
+  gsh <- googlesheets4::read_sheet(mda$sht$url,sheet=mda$sht$pgn,range=mda$sht$rng) %>%
+    data.table::setnames(new=mda$sht$cln) %>%
+    dplyr::select(-starts_with('D')) %>%
+    dplyr::mutate(P=row_number(PN)) %>%
+    dplyr::mutate(R=row_number(RN)) %>%
+    dplyr::mutate(S=!!rlang::parse_expr(mda$sht$stuv[1])) %>%
+    dplyr::mutate(T=!!rlang::parse_expr(mda$sht$stuv[2])) %>%
+    dplyr::mutate(U=!!rlang::parse_expr(mda$sht$stuv[3])) %>%
+    dplyr::mutate(V=!!rlang::parse_expr(mda$sht$stuv[4]))
+  assign(mda$nid,gsh)
+  do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
+  return(gsh)
+}
+#####################################################################################################

### 2024-01-02 index.qmd
chunkadded

@@
 
+#### Normal
+```{webr-r}
+app_n_rep <- selreport(app_bal,md$app0)
+app_n_out <- seloutput(app_n_rep)
+app_n_sim <- SimVoterdatabase(app_bal)
+```
+
+#### Rig 1: Normal
+```{webr-r}
+app_ex1_cou <- Countinggraphs(app_bal)
+print(app_ex1_cou$polyc[[1]][[1]])
+app_ex1_cou$sortpre()
+#app_ex1_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
+##app_ex1_cou$setres(NULL,0)
+#app_ex1_cou$setres(0.23,0)
+#app_ex1_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),TRUE,wn=c(0,0))
+#app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
+#app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
+```
+
+#### Rig 2: Hybdrid
+```{webr-r}
+app_ex2_cou <- Countinggraphs(app_bal)
+pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
+print(app_ex2_cou$polyc[[1]][[1]])
+#app_ex2_cou$sortpre()
+#app_ex2_cou$mansys(sygen=list(frm=2,pre=c("alpha","g","h"),end=c("Gamma","Omega"),FALSE,me=c(plnr=1,rot=0)))
+#app_ex2_cou$setres(NULL,0)
+#app_ex2_cou$setres(0.23,0)
+#app_ex2_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
+#app_ex2_out <- seloutput(selreport(app_ex2_cou$rdfc,md$app0))
+#app_ex2_sim <- SimVoterdatabase(app_ex2_cou$rdfc)
+```
+
+#### Rig 3: Opposition
+```{webr-r}
+app_ex3_cou <- Countinggraphs(app_bal)
+pri_int_ex3 <- app_ex3_cou$polyc[[1]][[1]]
+app_ex3_cou$sortpre()
+#app_ex3_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
+#app_ex3_cou$setres(NULL,0)
+#app_ex3_cou$setres(0.23,0)
+#app_ex3_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
+#app_ex3_out <- seloutput(selreport(app_ex3_cou$rdfc,md$app0))
+#app_ex3_sim <- SimVoterdatabase(app_ex3_cou$rdfc)
+#####################################################################################################################################################################
+```
+
 ### Applications

### 2024-01-02 index.qmd
haplo

--- 2024-01-01 index.qmd
@@
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install(c("cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
+webr::install(c("AlgebraicHaploPackage","cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
 library(ManifoldDestinyWASMP)
@@
 library(broom)
+library(tidyr)
 library(combinat)
+library(AlgebraicHaploPackage)
 ```
@@
 app_n_sim <- SimVoterdatabase(app_bal)
+```
+
+#### Normal
+```{webr-r}
+app_n_rep <- selreport(app_bal,md$app0)
+app_n_out <- seloutput(app_n_rep)
+app_n_sim <- SimVoterdatabase(app_bal)
+```
+
+#### Functions
+```{webr-r}
+2+2
+```
+
+#### Rig 1: Normal
+```{webr-r}
+app_ex1_cou <- Countinggraphs(app_bal)
+print(app_ex1_cou$polyc[[1]][[1]])
+app_ex1_cou$sortpre()
+app_ex1_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
+app_ex1_cou$setres(0.23,0)
+app_ex1_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),TRUE,wn=c(0,0))
+app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
+app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
+```
+
+#### Rig 2: Hybdrid
+```{webr-r}
+app_ex2_cou <- Countinggraphs(app_bal)
+pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
+print(app_ex2_cou$polyc[[1]][[1]])
+app_ex2_cou$sortpre()
+app_ex2_cou$mansys(sygen=list(frm=2,pre=c("alpha","g","h"),end=c("Gamma","Omega"),FALSE,me=c(plnr=1,rot=0)))
+app_ex2_cou$setres(0.23,0)
+app_ex2_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
+app_ex2_out <- seloutput(selreport(app_ex2_cou$rdfc,md$app0))
+app_ex2_sim <- SimVoterdatabase(app_ex2_cou$rdfc)
+```
+
+#### Rig 3: Opposition
+```{webr-r}
+app_ex3_cou <- Countinggraphs(app_bal)
+pri_int_ex3 <- app_ex3_cou$polyc[[1]][[1]]
+app_ex3_cou$sortpre()
+app_ex3_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
+app_ex3_cou$setres(0.23,0)
+app_ex3_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
+app_ex3_out <- seloutput(selreport(app_ex3_cou$rdfc,md$app0))
+app_ex3_sim <- SimVoterdatabase(app_ex3_cou$rdfc)
 ```

### 2024-01-05 presentation.qmd
newfunctions

@@
 md <- ManifoldDestinyWASMD::metad
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))

### 2024-01-05 index.qmd
newbefrev
sticker

@@
 ![](pngs/md.png)
-tidyr
 
@@
 ```{webr-r}
+wasmconload()
 webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")

### 2024-01-05 presentation.qmd
sticker

--- 2024-01-01 presentation.qmd
@@
 ```{r, echo=F, message=F, warning=F}
-library(ManifoldDestiny)
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-library(RefManageR)
-library(huxtable)
-modlat <- eqpar$meql
-md <- ManifoldDestinyWASMD::metad
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+ManifoldDestiny::wasmnonload()
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 ```

### 2024-01-05 script/R/applications.R

@@ -1,5 +1,3 @@
-library(ManifoldDestiny)
-wasmnonload()
 #######################################################################################################################################################
 P  <- c(1,2,3,4,5,6)
 S  <- c(60,60,60,60,60,60)

### 2024-01-05 presentation.qmd
modlat

@@
 ```{r, echo=F, message=F, warning=F}
+library(ManifoldDestiny)
 ManifoldDestiny::wasmnonload()
@@
 :::
+
+```{r}
+knitr::knit_exit()
+```

### 2024-01-05 script/R/applications.R

@@ -1,3 +1,5 @@
+library(ManifoldDestiny)
+ManifoldDestiny::wasmnonload()
 #######################################################################################################################################################
 P  <- c(1,2,3,4,5,6)
 S  <- c(60,60,60,60,60,60)

### 2024-01-05 script/R/simulations.R

@@ -1,4 +1,6 @@
 #######################################################################################################################################################
+library(ManifoldDestiny)
+ManifoldDestiny::wasmnonload()
 ##### Proto example 1 and 2
 P  <- c(1,2,3,4,5,6)
 S  <- c(60,60,60,60,60,55)

### 2024-01-05 presentation.qmd
tabupd

@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
+modlat <- eqpar$meql
 ```

### 2024-01-05 paper.qmd
papdel

--- 2023-12-31 paper.qmd
@@
 ---
-
-```{r, echo=F, message=F, warning=F}
-library(ManifoldDestiny)
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-library(RefManageR)
-library(huxtable)
-modlat <- eqpar$meql
-md <- ManifoldDestinyWASMD::metad
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
-metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-```
-
-# `r #metad$toc$sec1$nmn`
-
- Ed. Solomon
-
-> "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
-
-## `r metad$toc$sec1$unm[1]`
-
-- Two candidates: A, B
-- County with three precincts: 1, 2, 3
-- Two modes of voting
-  - Number of ballots mode 1: S, T
-  - Number of ballots mode 2: U, V
-
-##
-
-```{r, echo=F, caption="Example 1"}
-## Tower 1
-ex1m <- as.matrix(cbind(S,T,U,V))
-towi <- as.data.frame(ex1m) %>% 
-  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
-  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
-  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
-  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
-  dplyr::select(5:8) %>%
-  t() %>%
-  data.frame() %>%
-  data.table::setnames(paste0("County_",1:6))
-
-towi[3:4,1] <- ""
-towi[4,2] <- ""
-lego_hux_nor_i <- hux(towi[,1:3]) 
-lego_hux_nor_i 
-```
-
-```{r, echo=F, caption="Example 2"}
-## Tower 2
-ex2m <- as.matrix(cbind(S,T,Up,Vp))
-towii <- as.data.frame(ex2m) %>% 
-  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
-  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
-  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
-  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
-  dplyr::select(5:8) %>%
-  t() %>%
-  data.frame() %>%
-  data.table::setnames(paste0("County_",1:6))
-towii[3:4,1] <- ""
-towii[4,2] <- ""
-lego_hux_nor_ii <- hux(towii[,1:3]) 
-lego_hux_nor_ii 
-```
-
-## `r metad$toc$sec1$unm[2]`
-
-```{r, echo=F}
-lego_hux_nor <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
-  set_background_color(1, 1:2, "black") %>% 
-  set_background_color(2, 1:2, "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_nor %>% set_caption("")
-```
-
-Parameters: ** $x$, $y$, $\zeta$, $\alpha$, $\lambda$ **
-\begin{equation*}
-x=`r modlat$x_s[1]` \text{, }y=`r modlat$y_s[1]`
-\end{equation*}
-\begin{equation*}
-\zeta=`r modlat$zeta_s[1]`
-\end{equation*}
-\begin{equation*}
-\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
-\end{equation*}
-\begin{equation*}
-\lambda=`r modlat$lamda_s[1]`=`r modlat$lamda_s[2]`
-\end{equation*}
-
-##
-
-```{r, echo=F}
-ctone_sf <- 'Election results applying standard form on case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
-cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-Numerical calculation of candidate one total percentage
-- Precinct 1
- - $\alpha=\frac{`r cx[1]`+`r cy[1]`\cdot `r czeta[1]`}{1+`r czeta[1]`}=`r calpha[1]`$
-- Precinct 2
- - $\alpha=\frac{`r cx[2]`+`r cy[2]`\cdot `r czeta[2]`}{1+`r czeta[2]`}=`r calpha[2]`$
-- Precinct 3
- - $\alpha=\frac{`r cx[3]`+`r cy[3]`\cdot `r czeta[3]`}{1+`r czeta[3]`}=`r calpha[3]`$
-
-## `r metad$toc$sec1$unm[3]`
-
-```{r, echo=F}
-lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
-  set_background_color(1:2, 1, "black") %>% 
-  set_background_color(1:2, 2, "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_imp %>% set_caption("")
-```
-
-Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
-\begin{equation*}
-g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
-\end{equation*}
-\begin{equation*}
-\Gamma=`r modlat$Gamma_h[1]`
-\end{equation*}
-\begin{equation*}
-\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
-\end{equation*}
-\begin{equation*}
-\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
-\end{equation*}
-
-##
-
-```{r, echo=F}
-ctone_hf <- 'Election results applying hybrid form case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-Numerical calculation of candidate one total percentage
-- Precinct 1
- - $\alpha=\frac{`r cg[1]`+`r ch[1]`\cdot `r cGamma[1]`}{1+`r cGamma[1]`}=`r calpha[1]`$
-- Precinct 2
- - $\alpha=\frac{`r cg[2]`+`r ch[2]`\cdot `r cGamma[2]`}{1+`r cGamma[2]`}=`r calpha[2]`$
-- Precinct 3
- - $\alpha=\frac{`r cg[3]`+`r ch[3]`\cdot `r cGamma[3]`}{1+`r cGamma[3]`}=`r calpha[3]`$
-
-```{r, echo=F}
-ctone_hf <- 'Election results applying hybrid form case II'
-stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-## `r metad$toc$sec1$unm[4]`
-
-```{r, echo=F}
-lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
-  set_background_color(c(1),c(1), "black") %>% 
-  set_background_color(c(2),c(2), "black") %>% 
-  set_background_color(c(1),c(2), "grey") %>% 
-  set_background_color(c(2),c(1), "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_opo %>% set_caption("")
-```
-Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$
-\begin{equation*}
-n=`r modlat$n_o[1]` \text{ , } m=`r modlat$m_o[1]`
-\end{equation*}
-\begin{equation*}
-\xi=`r modlat$xi_o[1]`
-\end{equation*}
-\begin{equation*}
-\Omega=`r modlat$Omega_o[1]`=`r modlat$Omega_o[2]`
-\end{equation*}
-\begin{equation*}
-\lambda=`r modlat$lamda_o[1]`=`r modlat$lamda_o[2]`
-\end{equation*}
-
-##
-
-```{r, echo=F}
-ctone_of <- 'Election results applying opposition form'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
-kableExtra::kbl(format(stfo_sel,digits=4), caption=ctone_of) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-## `r metad$toc$sec1$unm[5]`
-
-- **Step 1:** Each registered voter assign themself (independent of voting technology) to either candidate A or candidate B
-- **Step 2:** Voting technology realized
-- **Step 3:** Registered voters determine whether to vote or not to vote 
-- **Step 4:** If voting, do this by either mode 1 or by mode 2.
-
-```{mermaid}
-  flowchart LR
-  A[Candidate A or B] --> R[A]
-  R --> RV[Vote]
-  RV --> RVE[Non-Mail]
-  RV --> RVM[Mail]
-  R --> RN[Not Vote]
-  DV --> DVE[Non-Mail]
-  DV --> DVM[Mail]
-  A --> D[B]
-  D --> DV[Vote]
-  D --> Dn[Not Vote]
-```
-
-##
-
-- Probability of assigning oneself to candidate A in precinct $i$
-  - $p_{w,i} \sim N(\alpha_i,\sigma^2_{w,i})$
-- Voting technology
-  - $z_i \sim U(0,1)$
-- Probability of not voting in precinct $i$
-  - Candidate A, $p_{nz,a,i}=(1-z_i)p_{n,a,i}\sim N(\alpha_{a,n},\sigma^2_{a,n})$ <br>
-  - Candidate B, $p_{nz,b,i}=(1-z_i)p_{n,b,i}\sim N(\alpha_{b,n},\sigma^2_{b,n})$
-- Probability of voting by mode 2 in precinct $i$
-  - Candidate A, $p_{m2,a,i}=(1-p_{nv,a,i})p_{a,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
-  - Candidate B, $p_{m2,b,i}=(1-p_{nv,b,i})p_{b,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
-- Probability of voting by mode 1 in precinct $i$
-  - Candidate A, $p_{m1,a,i}=1-p_{m2,a,i}-p_{nz,a,i}$ 
-  - Candidate B, $p_{m1,b,i}=1-p_{m2,b,i}-p_{nz,b,i}$
-
-Neutral-voting assumption:
-
-- Decission to vote or not to vote is independent of voting preferences:
-  - $p_{nz,a,i}=p_{nz,a,i}$ 
-- If voting, decission to vote by mode 1 or by mode 2 independent of voting preferences: 
-  - $p_{m2,a,i}=p_{m2,a,i}$
-
-Note: As we will investigate later, this condition might be needed in order to restore a rigged election to its original form.
-
-## `r metad$toc$sec1$unm[6]`
-
-1. Differences in the cost of voting (e.g., topology, voting rules, dropboxes etc.) across precincts $\Rightarrow$
-1. Changes to the likelihood of voting $\Rightarrow$ 
-1. Simplify so that changes in the likelihood of voting only impact Mode 2 $\Rightarrow$ 
-1. Higher $\zeta_i$ $\Rightarrow$
-1. Which changes the total election outcome through $\alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}$
-
-##
-
-The impact on the election outcome, however, would be small or close to non-existens if the conditions
-of the existance of a *trivial* Manifold occuranse related to normal form are not satisfied:
-
-- Proportion of mail-in-votes to election day vote is already high (Aggregate convergence lemma)
-  - Note: $\lim_{\zeta_i \rightarrow \infty} \alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}=y_i$
-- Correlation between $x$ and $y$ is very high (Twixt lemma)
-  - Note: If correlation is 1, we can set $x_i=\rho_s y_i$ so that $\alpha_i(y_i,\zeta_i)=\frac{\rho_s y_i+\zeta_i y_i}{\zeta_i+x_i}$
-- Low variance to $\zeta$ 
-  - Note: Invariance across precincts would imply that $\zeta_i=\zeta$, so that election outcome only determined by variations in two parameters: $\alpha_i(y_i,x_i)=\frac{x_i+\zeta y_i}{\zeta+x_i}$
-
-If none of this three cases are satisfied, variation in $\zeta_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
-
-## `r metad$toc$sec1$unm[7]`
-
-1. Differenc in the cost of voting (e.g., topology, voting rules, dropboxes, socio economics etc.) across precincts $\Rightarrow$ 
-1. Make changes to the likelihood of voting $\Rightarrow$ 
-1. Simplify so that changes in the likelihood of voting only impact mode 2 $\Rightarrow$ 
-1. Higher $\zeta_i$ $\Rightarrow$
-1. If new and earlier sample not representative of each other, higher $\Gamma_i$ $\Rightarrow$
-1. Which changes the total election outcome through $\alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+1}$
-
-##
-
-The impact on the election outcome, however, would be small or close to non-existens if the conditions
-of the existance of a *trivial* Manifold related to opposition form are not satisfied:
-
-- Proportion of the hybrid ballot boxes is already high (Aggregate convergence lemma)
-  - Note: $\lim_{\Gamma_i \rightarrow \infty} \alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+g_i}=y_i$
-- Correlation between $g$ and $h$ is very high (Twixt lemma)
-  - Note: If correlation is 1, we can set $g_i=\rho_h h_i$ so that $\alpha_i(h_i,\Gamma_i)=\frac{\rho_h h_i+\Gamma_i h_i}{\Gamma_i+x_i}$
-- Low variance to $\Gamma_i$ 
-  - Note: Invariance across precincts would imply that $\Gamma_i=\Gamma$, so that election outcome only determined by variations in two parameters: $\alpha_i=\frac{g_i+\Gamma h_i}{h_i}$
-
-If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
-
----
-
-```{webr-r}
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
-probw <- c(m=0.51,s=0.10)
-probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztech <- c(0,1)	
-app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
-print(SimVoterdatabase(app_bal))
-```
-
-# `r metad$toc$sec2$nmn`
-
-## `r metad$toc$sec2$unm[1]`
-
-- We have identified three ways of counting
-  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
-  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
-  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
--  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
-  -  We are free to *predetermine* **3** of them
-  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
-  -  Selecting **3** parameters from a set of **5** implies **10** different combinations
-
-## `r metad$toc$sec2$unm[2]`
-
-**20 laws and 40 isometris**
-
-```{r, echo=F}
-# Load necessary library
-library(tibble)
-
-# Create the data.frame
-laws_df <- tribble(
-  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
-  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
-  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
-  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
-  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
-  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
-  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
-  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
-  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
-  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
-  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
-  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
-  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
-  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
-  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
-  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
-  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
-  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
-  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
-  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
-  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
-)
-# Display the data.frame
-kable(laws_df, format = "markdown", escape = FALSE)
-```
-
-##
-
-::: {.callout-caution collapse="true"}
-## Proportions
-
-```{r, echo=F}
-library(kableExtra)
-library(tibble)
-new_tbl <- data.frame(
-  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
-  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
-  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
-  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
-  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
-  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
-  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
-  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
-)
-
-# Extract the columns
-V1 <- new_tbl$V1
-V2 <- new_tbl$V2
-V3 <- new_tbl$V3
-V4 <- new_tbl$V4
-Equation1 <- new_tbl$Equation1
-Equation2 <- new_tbl$Equation2
-Equation3 <- new_tbl$Equation3
-Equation4 <- new_tbl$Equation4
-
-# Combine the columns
-combined <- data.frame(
-  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
-  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
-  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
-  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
-)
-kable(combined, format = "markdown", escape = FALSE)
-```
-
-:::
-
-[@delfino2011analysis]
-
-## `r metad$toc$sec2$unm[3]`
-
-## `r metad$toc$sec2$unm[4]`
-
-## `r metad$toc$sec2$unm[5]`
-
-# `r metad$toc$sec3$nmn`
-
-## `r metad$toc$sec3$unm[1]`
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_n_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_n_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['resp']]
-```
-
-:::
-
-## `r metad$toc$sec3$unm[2]`
-
-**Example 1: Normal form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex1_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex1_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['resp']]
-```
-
-:::
-
-##
-
-**Example 2: applying hybrid form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex2_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex2_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['resp']]
-```
-
-:::
-
-##
-
-**Example 3: applying opposition form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex3_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex3_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['resp']]
-```
-
-:::
-
-# `r metad$toc$sec4$nmn` {#litrev}
-
-```{r, echo=FALSE, out.width="20%", fig.cap=""}
-p1 <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/ss.png')
-knitr::include_graphics(c(p1))
-```
-
-`r #Citet(bib, "delfino2011analysis")`
-
-> Abstract: On August 15th, **2004**, Venezuelans had the opportunity to vote
-in a Presidential Recall Referendum **to decide whether or not President Hugo
-Chávez should be removed from office.** **The process was largely computer-
-ized using a touch-screen system.** In general the ballots were not manually
-counted. The significance of the high linear correlation (0.99) between the
-number of requesting signatures for the recall petition and the number of op-
-position votes in computerized centers is analyzed. The same-day audit was
-found to be not only ineffective but a source of suspicion...
-
-::: aside
-[Link to Youtube-video](https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s)
-:::
-
-##
-
-- Venezuela referendum to recall President Hugo Chávez (2004)
-	- Mode 1: Computerized Voting Centers
-	- Mode 2: Manuel Voting Centers
-
-> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.
-
-```{r, echo=FALSE, out.width="85%", fig.cap=""}
-p3 <- paste0(rprojroot::find_rstudio_root_file(),'pngs/manifold.png')
-knitr::include_graphics(c(p3))
-```
-
-# `r metad$toc$sec5$nmn` {#proced}
-
-# `r metad$toc$sec5$unm[1]`
-
-1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
-1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
-1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
-1. Check for normality of the estimated residual for the Manifold model.
-
-If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.
-
-# `r metad$toc$sec6$nmn`
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="1")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app_a_out <- app_2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app_a_out <- app_2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app_a_out <- app_2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-# `r metad$toc$sec7$nmn`
-
-- At the heart of the difference between a fair and rigged election is the issue of causation
-  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
-  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
-
-- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
-	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
-	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
-
-##
-
-- Condition on that $R^2$ falls within the critical region.
-  - Normal form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2n.png')
-knitr::include_graphics(c(pr2n))
-```
-
- - Hybrid form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2h.png')
-knitr::include_graphics(c(pr2h))
-```
-
-- Our four applications
-
-```{r, echo=F, warning=F, message=F}
-#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-# `r metad$toc$sec8$nmn`
-
-::: {#refs}
-:::

### 2024-01-05 paper.qmd
upd

--- 2024-01-01 paper.qmd
@@
 library(ManifoldDestiny)
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-library(RefManageR)
-library(huxtable)
-modlat <- eqpar$meql
-md <- ManifoldDestinyWASMD::metad
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+ManifoldDestiny::wasmnonload()
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
+modlat <- eqpar$meql
 ```

### 2024-01-05 presentation.qmd
upd

--- 2024-01-05 presentation.qmd
@@
 ```{r, echo=F, message=F, warning=F}
+#Sys.info()[['sysname']]=="Emscripten"
 library(ManifoldDestiny)

### 2024-01-05 R/wasmnonverting.R

@@ -1,17 +1,3 @@
-#' @export wasmnonload
-wasmnonload <- function(){
-  source(paste0(rprojroot::find_rstudio_root_file(),'/R/wasmconverting.R'))
-  source(paste0(rprojroot::find_rstudio_root_file(),'/R/wasmnonverting.R'))
-  # Import
-  library(dplyr)
-  library(ggplot2)
-  library(htmltools)
-  library(plotly)
-  library(kableExtra)
-  library(huxtable)
-  library(gridExtra)
-  # New
-}
 #' @export py_polysolver
 py_polysolver <- function(degree=1,kvec=NULL){
   path_fqs <- paste0(rprojroot::find_rstudio_root_file(),"/script/python")

### 2024-01-05 paper.qmd
browserback

@@
 ```{r, echo=F, message=F, warning=F}
-library(ManifoldDestiny)
-ManifoldDestiny::wasmnonload()
+#Sys.info()[['sysname']]=="Emscripten"
+ManifoldDestiny::wasmconload()
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))

### 2024-01-05 R/wasmconverting.R

@@ -22,6 +22,7 @@ wasmconload <- function(){
       source(paste0(rprojroot::find_rstudio_root_file(),'/R/wasmconverting.R'))
       source(paste0(rprojroot::find_rstudio_root_file(),'/R/wasmnonverting.R'))
       # Import
+      library(ManifoldDestiny)
       library(dplyr)
       library(ggplot2)
       library(htmltools)

### 2024-01-05 script/R/simulations.R

@@ -1,6 +1,4 @@
 #######################################################################################################################################################
-library(ManifoldDestiny)
-ManifoldDestiny::wasmnonload()
 ##### Proto example 1 and 2
 P  <- c(1,2,3,4,5,6)
 S  <- c(60,60,60,60,60,55)

### 2024-01-06 presentation.qmd
firdrains

@@
 
-[Link to R2 simulator for testing](https://shinylive.io/r/app/#h=0&code=NobwRAdghgtgpmAXGKAHVA6ASmANGAYwHsIAXOMpMAdzgCMAnRRASwgGdSoAbbgCgA6YALJQILAGZFuAEwAicTmwCeAdQCCAZWEAFIbgAEDOKiLsDAXgNCAFqVKp2iAPTPuRLgxZEb1AEwAbBgA5iykNgCudBjezsJyAPoa2gDCQgCUAhC0jMxsnDz8QqLiUrIKShBqWvH6RiZmltZgdg5Oru6e3r6BIWGR0bHxSTVpYJkQ3CyMUAzKfCWS0vKKpCrJuhNTM3MLYkvlq+s1clvTDLPz7DYqZzvzMFDBXvYMdxe7wcGonX4TRKg1iR2Hx2AQWKgKBYAJyw96XPg-DzcZTw3ZyAAqaPmAGsoHRuHAAKIAD1IF2xfBkP2Ubyy2w+8zsMG4pCI0nYlOeLBkpPJUAmERYBgAPABaAwSbhCmQ6J5wQQQAwGNakQlyiBwIpgLB+AyaFgwCLcKBshgZXBZZVcOjsOCkDVaxXK634x3agDiF1QNjqVpdAcD7B59FmABkoMoiBFSM7A-GXcGZKGGO64wmM3bCQRSABJCCoGOCMAAN1mLHxhL9YE0WrgOYMUElRAYMEQdQIxYAci3Htxm62hE0hBBezxqwAJZSMHkDmBDqy2adeGTVgDy6DMYW8Sqkg7Aw7AANMwaBEAy6UtSozGYgEXgXgI+cLsZHqGMBGrXfvdDgDAMRASAY771mwOZOHUZbSnATQAMwAAzwZe-o3vG5Bks+RZCMYwQltWWBwKEnB-nAMgGCWHh-uYfDwGIuCcDImR4ORPARHAFgAOSwRgACMACshjwRgfh8RxyHXqhgboXmBZYWAMBsI8JLVsIbCNhAZFKSx0HmHeMC-v+gHkZRDDsJBrHsRxAAsiGGDZiFiVekloXAGGya+YCkBEDDnsxQg6AwRB0PiLBTKQygAUBFFrBAwTtsxUFsU0HFCQJBhCTx8GOShznWq5MkvsWbAlpC5p+WARLZmeBjsMoxEwCxXghWFyjxYYiUwZxqWCbxWXiblAbSZhHkRNWAVBc1YQRUZJLOMEzgQG12lJVYKUYAEPWZdlEkDUN7nFjIeHlXIkhAe+E10KFU2RQYs3zYt5nQclYpCX4PXwQAHNtA0unpf4sE++1CDIFzUGZ5Xfvpf43SDUBg49K0GAh-U-Y2OY7gAQjGbIQMWDARL5hhCFgBP6oaxqmjuGQ5ZJKO5Y8bBpjTzlIqQa4xoVQisxazOSTahLsw4cn83A1M7bTvPxukEwBnTKpumITpCBilaKH64sZjadoOorRQazeNpM2AKsEjBPH6JLqNJimEZRlh+uo4mIbBamut8HLjuBgzEBMw7nuuqbguc55qvm+MluOzL-uyxHgYe6hhtu8rqsGH4Ft+z91su7b0avhnVvO7Mabx9H3u+9Hmuq0Hwuq2n4f5z9UcVwYTfOa3N6txMEwAMTdwYCgSGwMF2gwJZ-lkI9j-+4qSgT6MkHwbAvoYucvukBggP6-p9yTSrBkaJpnv6MgSN8ooSnAY9kARUDo2Pi-uQAJPjECGJvO198N-cAGLmztOElnPo2dgGA-qPlBOSdgPwwgPxfM-QiJYiZ4AyMAYAPEAC66DW4KQgFpGeUAQFgIBhA0y0DYxLxjI-HBSkkGWnGKgjBWCcpeR8kAghoD7z-U7JwUhYVYGUJYa-ZodD0gMMwa3YqpU2GEM4eAnhUC+EUNII-SRf5aEoLQeInKERpEcIfMQ+RZD+HKIiOo+hmimE7UOrooh3DIFGKUY-Q6ZjREWNbqQICM9jDQIIKaBUjjYZg1wAwPw+9cYFg-E0RxET6xORvDhcwVhOwAM0YYFJfgsFxIzNQqAJImidhySSVJhTgAZMvCqbySokl8EEakipPlSmZIMPmEq0NqmqIYHUjpjSS4uh0dUiIdTBllKyQmax1TDp1MmSMiOe4GpWB4qIzsPFcBvVgukSxAYT5nxnjIU0UAMASAuPAPgISoAWAJlMTgNSJDADtAARz4CswksVwg3MvOszJIS6AXMmCwa5Hi7lwEeW9F5wQ3keI+Rs6WBgACkAA+WFBgjRcHIIiP8BAmhkFCgqM5hhMpIXXjlT+7kf5px2qVAgFA1iEnMDPTs0J4KGGhGlOEOUOCkDIvSp5qzcB8VbgxIBtFcbbNQM-PwAoADUHKZAACp2AyCpKfMVZzW6Up4kA+5EQxA0oVKK8VUBcDnVtE0Sl1KcXmGcAYAlaqMV6hnlqnVOKlXfHFXQI1gUTVWDNdi2lBgrU2pypSk+QC9lcEOcchU6qjV2twDK+inL14IqRWGg5ItmDa2gPAEEnZ-IYqMBKi2YAdD5u+UWrsDEi0ADVK3jCJTtK5sZRUxoYAQE+UcAC+Uc+4pGMH44CnR-Sr0oazIBxgNJ-h0J0Pg78BCkGVN3RgRAwZ-ndjlE+qBQ3KvdmI9BcLEUqh5LSZgqAWDRQSO4WKq7iDcHYBYXNYAzlFrLXW-dKaaRMEQLMC4V6+BZrgC2ggrcvisyVagXAUBFB8BJBYDqhhB68AsP+mFkrrAa2CHAIgMAEg3E4EQZ4sBERbmqouMAIZsXhTqDwH0TYrDdQMJdDgcEkIGFQ8zE0toalhEJIeCc-y2QEYakZKtFlzB0AiikPxwQWzKDqHk0jInoJ1AiqRlI0YyAZFY8zDDWGEglimJqaDbByCtpMPOqw7DbEutQDuxp6C0G4AweUgz9plCQkPHs64pEOzSBbIeAkbFNOSu05h7D+mh5GbIBiszTRLOyOIaK2zGT7NvSc4YFz4V3Okc8zYbzzEb1+dIwF0W4wtPodC3plzkWTNUsBLFmR+jOyJdccl4AsFHNNIy25zqzQct5cMAV-8RWlOleC+V3T4XDMkmM9FurFmGtcOs0lzBbXcBWU60PTLPWhDsGkDyHz7ghvNGMKuUbIXdMcadMoCwTKYNxca0tlrK2Vlpcu9wCwQhZX6B0zAD7YA3tBfO9ht7fBru3YsPdxbzXUGtdS5kt7f3ZVfbwD9v7AOzvjeB-iK7N3cB3YW+A6HdnVuvex+9z7SPvuhbR2TwHGtwhwHgAkHBhoeDuzK-GMEPA4AJAQ9wZnYhtX8A6okgwD7u6IQAOx+AxnXJB3ciQBGhN-RCF4F01XtJKUK-ZBtmWvF2re15e4GF7XAftIsh0cwEaHMdFBkwMAAKq5hnTlTEzBU0i1OepxVRPku4BkCwUIpA71WWlv6A315h3KJFvaiU477dO5dztN3iAPeqy9wTH327XGMMMAHoPIfykAjPKLxtiJ5RhgoOCmwTQ-CEvDxMDtWQd6kzQKgCeNwqjqHQHwIUTQhSGEnm0jXo8-wTCyGADt6CgA)
+[R2 simulator application]({{< var shn1 >}})
 
@@
 
+---
+
+[xxx application]({{< var shn2 >}})
+
+---
+
 # `r metad$toc$sec4$nmn` {#litrev}
@@
 ```
+---
+
+[xxx application]({{< var shn3 >}})
+
+---
+
+# Restoration
+
+[xxx application]({{< var shn4 >}})
+
+---
 

### 2024-01-06 tabsets.qmd
firdrains

@@
 
+[R2 simulator]({{< var shn1 >}})
+
+```{r}
+knitr::knit_exit()
+```
+
 ```{r, echo=F, message=F, warning=F}

### 2024-01-06 presentation.qmd
proof

@@
 
-```{r, echo=F, message=F, warning=F}
+```{r, echo=F, message=F, warning=F, results='hide'}
 #Sys.info()[['sysname']]=="Emscripten"
@@
 modlat <- eqpar$meql
+library(huxtable)
+library(kableExtra)
 ```
 
-# `r #metad$toc$sec1$nmn`
+# `r metad$toc$sec1$nmn`
 
@@
 
-**Our numerical example**
+**Our two stylized numerical example**
 
@@
 
-Parameters: ** $x$, $y$, $\zeta$, $\alpha$, $\lambda$ **
+Parameters:**$x$, $y$, $\zeta$, $\alpha$, $\lambda$**
+
 \begin{equation*}
@@
 Numerical calculation of candidate one total percentage
+
 - Precinct 1
@@
   - $\alpha=\frac{`r cg[3]`+`r ch[3]`\cdot `r cGamma[3]`}{1+`r cGamma[3]`}=`r calpha[3]`$
+
+---
 
@@
 ```
+
 Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$
@@
 
+[Application 1: Election process simulator]({{< var shn1 >}})
+
+---
+
 Neutral-voting assumption:
@@
 
-[R2 simulator application]({{< var shn1 >}})
-
 # `r metad$toc$sec2$nmn`
@@
 # Display the data.frame
-kable(laws_df, format = "markdown", escape = FALSE)
+kable(laws_df, format = "markdown", escape = FALSE) %>% kableExtra::kable_styling(font_size=16)
 ```
@@
 ## Proportions
-
 ```{r, echo=F}
@@
 )
-kable(combined, format = "markdown", escape = FALSE)
+kable(combined, format = "markdown", escape = FALSE) %>% kableExtra::kable_styling(font_size=16)
 ```
@@
 ## `r metad$toc$sec2$unm[5]`
+
+- Loss function
+  - $M(,)=$x+y$
+    - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
+    - Also: Euler rotation
+  - System approach Demands mulitvariate Manifold Equations
+    - Abc
+    - Def
+  - Constrain on implementation
+    - Flipping votes on one mode
+    - Vote registration until upper limit
+
+---
+
+```{r, echo=F, out.width="80%", fig.cap=""}
+bI <- paste0(rprojroot::find_rstudio_root_file(),'pngs/loss_5_conditions.png')
+knitr::include_graphics(bI)
+```
 
@@
 
----
-
-[xxx application]({{< var shn2 >}})
-
----
-
 # `r metad$toc$sec4$nmn` {#litrev}
@@
 
+[Application]({{< var shn2 >}})
+
 ```{r, echo=FALSE, results='asis',warning=F}
@@
 
-# Restoration
+# `r metad$toc$sec7$nmn`
 
@@
 
-# `r metad$toc$sec7$nmn`
+# `r metad$toc$sec8$nmn`
 
@@
 
-# `r metad$toc$sec8$nmn`
+# `r metad$toc$sec9$nmn`
 

### 2024-01-06 R/raceanalysis.R

@@ -1,0 +1,177 @@
+# ' @export Raceanalysis
+Raceanalysis <- setRefClass("Raceanalysis",fields=list(
+							       sdfcs='data.frame',
+							       descs='data.frame',
+							       quints='data.frame', 
+							       quints_rank='data.frame',
+							       rpoltab='data.frame',
+							       cogals='list',
+							       rdfcs='list', 
+							       parameters='list'
+							       ))
+Raceanalysis$methods(initialize=function(snap_df){
+  #browser()
+  abs_p <- rprojroot::find_rstudio_root_file()
+  stickers <- ManifoldDestiny::stickers
+  parameters <<- stickers[['parameters']]
+
+  sn <- unique(snap_df$SNAP); 
+  snl <- length(sn)
+  rn <- unique(snap_df$RACENR)
+  rnl <- length(rn)
+
+  # Descriptive table
+  str_vec_i <- c("S","T","U","V","Z")
+  str_vec_s <- c("alpha")
+
+  # I Adding total ballots
+  descs <<- snap_df %>%
+    dplyr::mutate(Z=S+T+U+V) %>%
+    dplyr::group_by(SNAP,RACENR) %>%
+    dplyr::summarize_at(vars(all_of(str_vec_i)), list(sum=sum,sd=sd)) %>%
+    dplyr::arrange(RACENR,SNAP) %>%
+    dplyr::mutate(alpha=(S_sum+U_sum)/Z_sum) %>%
+    dplyr::mutate(x=(S_sum)/(S_sum+T_sum)) %>%
+    dplyr::mutate(y=(U_sum)/(U_sum+V_sum)) %>%
+    dplyr::mutate(Omega=(S_sum+T_sum)/Z_sum) %>%
+    dplyr::group_by(RACENR) %>%
+    dplyr::mutate(CZ=round(Z_sum/last(Z_sum),digits=4))
+
+  # II  Changes
+  sdfcs <<- snap_df %>%
+    dplyr::left_join(dplyr::select(descs,SNAP,RACENR,CZ),by=c("SNAP","RACENR")) %>%
+    dplyr::arrange(RACENR,P,SNAP) %>%
+    dplyr::group_by(RACENR,P) %>%
+    # Total ballots in precinct
+    dplyr::mutate(ZP=S+T+U+V) %>%
+    dplyr::mutate(CZP=ZP/last(ZP))  %>%
[…]

### 2024-01-06 R/wasmconverting.R

@@ -1,38 +1,30 @@
 #' @export wasmconload
 wasmconload <- function(){
   ifelse(Sys.info()[['sysname']]=="Emscripten", 
-    {
-      # commands to be executed if the condition is TRUE
-      #webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+  {
+      # Commands to be executed if the condition is TRUE
+      webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
       webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-      webr::install("ggplot2")
+      webr::install(c("AlgebraicHaploPackage","cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
       library(ManifoldDestinyWASMP)
       library(ManifoldDestinyWASMD)
-      # Import
-      library(dplyr)
-      library(ggplot2)
-      library(htmltools)
-      library(plotly)
-      library(kableExtra)
-      library(huxtable)
-      library(gridExtra)
-      # New
-    },
-    {
-      # commands to be executed if the condition is FALSE
+  },
+  {
+      # Commands to be executed if the condition is FALSE
+      library(ManifoldDestiny)
       source(paste0(rprojroot::find_rstudio_root_file(),'/R/wasmconverting.R'))
       source(paste0(rprojroot::find_rstudio_root_file(),'/R/wasmnonverting.R'))
-      # Import
-      library(ManifoldDestiny)
-      library(dplyr)
-      library(ggplot2)
-      library(htmltools)
-      library(plotly)
-      library(kableExtra)
-      library(huxtable)
-      library(gridExtra)
-      # New
-    })
+  })
+  library(plotly)
+  library(dplyr)
+  library(shiny)
+  library(combinat)
+  library(htmltools)
+  library(ggplot2)
+  library(broom)
+  library(tidyr)
+  library(combinat)
+  library(AlgebraicHaploPackage)
 }
 #########################################################################################################################################################
 #' @export py_polysolverW

### 2024-01-07 abc.qmd
an

---
title: "econ"
#format: 
#  html:
#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
#    include-in-body:
#          - text: |
#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
---

<head>
      <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
      <link rel="stylesheet" href="https://kineticgraphs.org/css/kg.0.2.7.css">
</head>

<div class="kg-container">
schema: EconSchema
layout:
  OneGraph:
    graph:
      xAxis: 
        title: "Good 1"
      yAxis: 
        title: "Good 2"
      objects: 
      - EconBudgetLine:
          p1: 1
          p2: 2
          m: 8
          label: {text: M, location: 0.9}
</div>

::: {.kg-container}
schema: EconSchema
layout:
  OneGraph:
    graph:
      xAxis: 
        title: "Good 1"
      yAxis: 
        title: "Good 2"
      objects: 
      - EconBudgetLine:
          p1: 1
          p2: 2
          m: 8
          label: {text: M, location: 0.9}
:::

```{r}
knitr::knit_exit()
```

<p id=ary></p>
<p id=nmb></p>
<p id=str></p>

<head>
      <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
</head>
<body>
    Pyodide test page <br>
    Open your browser console to see Pyodide output
    <script type="text/javascript">
      async function main(){
        let pyodide = await loadPyodide();
        console.log(pyodide.runPython(`
            import sys
            sys.version
        `));
        pyodide.runPython("print(1*5)");
      }
      main();
    </script>
</body>

```{r}
knitr::knit_exit()
```

<html>
  <head>
    <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
  </head>

  <body>
    <p>
      You can execute any Python code. Just enter something in the box below and
      click the button.
    </p>
    <input id="code" value="sum([1, 2, 3, 4, 5])" />
    <button onclick="evaluatePython()">Run</button>
    <br />
    <br />
    <div>Output:</div>
    <textarea id="output" style="width: 100%;" rows="6" disabled></textarea>

    <script>
      const output = document.getElementById("output");
      const code = document.getElementById("code");

      function addToOutput(s) {
        output.value += ">>>" + code.value + "\n" + s + "\n";
      }

      output.value = "Initializing...\n";
      // init Pyodide
      async function main() {
        let pyodide = await loadPyodide();
        output.value += "Ready!\n";
        return pyodide;
      }
      let pyodideReadyPromise = main();

      async function evaluatePython() {
        let pyodide = await pyodideReadyPromise;
        try {
          let output = pyodide.runPython(code.value);
          addToOutput(output);
        } catch (err) {
          addToOutput(err);
        }
      }
    </script>
  </body>
</html>

#! fix deviation from mean
import sympy, pandas, numpy
from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
def rall(sel=[0, 0, 0]):
    n, m = symbols('n m')

    rxy = Matrix([[m, -n, 0], 
                  [n, m, 0],
                  [0, 0, 1]])

    rxz = Matrix([[m, 0, -n], 
                  [0, 1, 0],
                  [n, 0, m]])

    ryx = Matrix([[m, n, 0], 
                  [-n, m, 0],
                  [0, 0, 1]])

    ryz = Matrix([[1, 0, 0], 
                  [0, m, -n],
                  [0, n, m]])

    rzx = Matrix([[m, 0, n], 
                  [0, 1, 0],
                  [-n, 0, m]])

    rzy = Matrix([[1, 0, 0], 
                  [0, m, n],
                  [0, -n, m]])

    ps = [0, rxy, rxz, ryx, ryz, rzx, rzy]

    allrot = [ps[i] for i in sel]
    return allrot

def genpolycoeff(expr=None, solvd='z', solvf='u0', eur=[1, 4, 2], plr=3,dnr=2):
    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
    x, y, z = sympy.symbols('x y z')
    sum_eur = sum(eur)
    # Without rotation
    if sum_eur == 0:
        exprc = expr + '-' + solvd
        asexpr = sympify(exprc)
        polys = poly(asexpr, sympify(solvf)).all_coeffs()
        abc = []
        uvw = []
        ABCDE = [0, 0, 0, 0, 0]
        ABCDE[:len(polys)] = polys
        return ABCDE, abc, uvw
    # With rotation
    else:
        expr = ['k0+k1*x+k2*y', 'k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2', 'k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3'][plr-1]
        dxyz = {'x': 1, 'y': 2, 'z': 3}
        # Defining
        x,  y,  z  = sympy.symbols('x y z')
        ui, vi, wi = sympy.symbols('ui vi wi')
        u0, v0, w0 = sympy.symbols('u0 v0 w0')
        u1, v1, w1 = sympy.symbols('u1 v1 w1')
        u2, v2, w2 = sympy.symbols('u2 v2 w2')
        a1, a2, a3 = sympy.symbols('a1 a2 a3')
        b1, b2, b3 = sympy.symbols('b1 b2 b3')
        c1, c2, c3 = sympy.symbols('c1 c2 c3')
        m1, m2, m3 = sympy.symbols('m1 m2 m3')
        n1, n2, n3 = sympy.symbols('n1 n2 n3')
        mu, mv, mw = sympy.symbols('mu mv mw')
        # Replace
        PS = rall(sel=eur)
        r0 = Matrix([u0, v0, w0])
        r1 = PS[0].subs([(n, n1), (m, m1)]) * r0
        r2 = PS[1].subs([(n, n2), (m, m2)]) * r1
        RR = PS[2].subs([(n, n3), (m, m3)]) * r2
        sympy.expand(RR.row(0)[0])
        sympy.expand(RR.row(1)[0])
        sympy.expand(RR.row(2)[0])
        av = sympy.collect(sympy.expand(RR.row(0)[0]), (u0, v0, w0))
        bv = sympy.collect(sympy.expand(RR.row(1)[0]), (u0, v0, w0))
        cv = sympy.collect(sympy.expand(RR.row(2)[0]), (u0, v0, w0))
        a1s = av.coeff(u0)
        a2s = av.coeff(v0)
        a3s = av.coeff(w0)
        b1s = bv.coeff(u0)
        b2s = bv.coeff(v0)
        b3s = bv.coeff(w0)
        c1s = cv.coeff(u0)
        c2s = cv.coeff(v0)
        c3s = cv.coeff(w0)
        Eu = Eq(x, a1s * u0 + a2s * v0 + a3s * w0)
        Ev = Eq(y, b1s * u0 + b2s * v0 + b3s * w0)
        Ew = Eq(z, c1s * u0 + c2s * v0 + c3s * w0)
        abc = [a1s, a2s, a3s, b1s, b2s, b3s, c1s, c2s, c3s]
        # Manual
        pvar = [w0, v0, u0, w0**2, v0*w0, v0**2, u0*w0, u0*v0, u0**2, w0**3, v0*w0**2, v0**2*w0, v0**2*w0, v0**3, u0*w0**2, u0*v0*w0, u0*v0**2, u0**2*w0, u0**2*v0, u0**3]
        # Connect to rotmat
        Eu = Eq(x, a1 * u0 + a2 * v0 + a3 * w0)
        Ev = Eq(y, b1 * u0 + b2 * v0 + b3 * w0)
        Ew = Eq(z, c1 * u0 + c2 * v0 + c3 * w0)
        exprf = sympify(expr + '-' + solvd)
        exprc = exprf.subs([(x, solve(Eu, x)[0]), (y, solve(Ev, y)[0]), (z, solve(Ew, z)[0])])
        exprr = collect(expand(exprc), pvar)
        xr = [] 
        yr = []
        zr = []
        clma = ['u0','v0','w0','d','var','expr','expr2']
        eqsn = len(exprr.args)
        data = [["0"] * 7 for _ in range(eqsn)]
        matarch = pandas.DataFrame(data, columns=clma)
        matarch.loc[0, ['expr','expr2']]=exprr.args[0]
        matarch.loc[0, ['d']]='d_000'
        for i in range(1, eqsn):
            expt = exprr.args[i]
            expr = expt.args[-1]
            varn = expt / expr
            nrfs = len(varn.free_symbols)
            matarch.loc[i, 'var'] = str(varn)
            for j in range(0,nrfs):
                varn = expt.args[j].as_base_exp()[0]
                pown = expt.args[j].as_base_exp()[1]
                matarch.loc[i, str(varn)] = pown
            subd = {a1: a1s, a2: a2s, a3: a3s,b1: b1s, b2: b2s, b3: b3s,c1: c1s, c2: c2s, c3: c3s}
            matarch.loc[i, 'expr'] = expr
            matarch.loc[i, 'expr2'] = expr.subs(subd) 
            cmbx = int(matarch.loc[i, 'u0'])
            cmby = int(matarch.loc[i, 'v0'])
            cmbz = int(matarch.loc[i, 'w0'])
            dr = sum([cmbx, cmby, cmbz])
            matarch.loc[i,'d']='d_'+"".join([str(dr),str(cmbx),str(cmby)])
    dic1 = matarch.set_index('d')['expr'].to_dict()
    dic2 = matarch.set_index('d')['expr2'].to_dict()
    dic = [dic1,dic2][0]
    A=[dic['d_330'],
       dic['d_303'],
       dic['d_300']]
    B=[dic['d_320']*z+dic['d_321']*y+dic['d_220'],
       dic['d_302']*z+dic['d_312']*x+dic['d_202'],
       dic['d_301']*x+dic['d_310']*y+dic['d_200']]
    C=[dic['d_310']*z**2+dic['d_311']*y*z+dic['d_312']*y**2+dic['d_210']*z+dic['d_211']*y+dic['d_110'],
       dic['d_301']*z**2+dic['d_311']*y*z+dic['d_321']*y**2+dic['d_201']*z+dic['d_211']*y+dic['d_101'],
       dic['d_302']*z**2+dic['d_311']*y*z+dic['d_320']*y**2+dic['d_201']*z+dic['d_210']*y+dic['d_110']]
    D=[dic['d_300']*z**3+dic['d_301']*y*z**2+dic['d_302']*y**2*z+dic['d_303']*y**3+dic['d_200']*z**2+dic['d_201']*y*z+dic['d_202']*y**2+dic['d_100']*z+dic['d_101']*y+dic['d_000'],
       dic['d_300']*z**3+dic['d_310']*y*z**2+dic['d_320']*y**2*z+dic['d_330']*y**3+dic['d_200']*z**2+dic['d_210']*y*z+dic['d_220']*y**2+dic['d_100']*z+dic['d_110']*y+dic['d_000'],
       dic['d_303']*z**3+dic['d_312']*y*z**2+dic['d_321']*y**2*z+dic['d_330']*y**3+dic['d_202']*z**2+dic['d_211']*y*z+dic['d_220']*y**2+dic['d_101']*z+dic['d_110']*y+dic['d_000']]
    E=[0,0,0,0]
    nrs = dxyz[solvd]-1
    ABCDE = [0, 0, 0, 0, 0]
    ABCDE[0] = str(A[nrs])
    ABCDE[1] = str(B[nrs])
    ABCDE[2] = str(C[nrs])
    ABCDE[3] = str(D[nrs])
    ABCDE[4] = str(E[nrs])
    msl = ['u0','v0','w0','expr','expr2']
    matarch[msl]=matarch[msl].astype(str)
    return ABCDE, matarch, abc

### 2024-01-07 index.qmd
buildinstall
an

--- 2024-01-02 index.qmd
@@
   - webr
+format: 
+  html:
+    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
+    include-in-body:
+          - text: |
+              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
 ---

### 2024-01-07 abc.qmd
delabc

@@
 ---
-
 <head>
+      <link rel="stylesheet" href="https://kineticgraphs.org/css/kg.0.2.7.css">
       <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
-      <link rel="stylesheet" href="https://kineticgraphs.org/css/kg.0.2.7.css">
 </head>
 
+<body>
 <div class="kg-container">
@@
 </div>
+</body>
 
-::: {.kg-container}
-schema: EconSchema
-layout:
-  OneGraph:
-    graph:
-      xAxis: 
-        title: "Good 1"
-      yAxis: 
-        title: "Good 2"
-      objects: 
-      - EconBudgetLine:
-          p1: 1
-          p2: 2
-          m: 8
-          label: {text: M, location: 0.9}
-:::
-
-```{r}
+```{r, eval=T}
 knitr::knit_exit()
@@
 
-<p id=ary></p>
-<p id=nmb></p>
-<p id=str></p>
-
-<head>
-      <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
-</head>
-<body>
-    Pyodide test page <br>
-    Open your browser console to see Pyodide output
-    <script type="text/javascript">
-      async function main(){
-        let pyodide = await loadPyodide();
-        console.log(pyodide.runPython(`
-            import sys
-            sys.version
-        `));
-        pyodide.runPython("print(1*5)");
-      }
-      main();
-    </script>
-</body>
-
-```{r}
-knitr::knit_exit()
-```
-
-<html>
 <head>
@@
 </body>
-</html>
+
+```{r}
+knitr::knit_exit()
+```
+
+::: {.kg-container}
+schema: EconSchema
+layout:
+  OneGraph:
+    graph:
+      xAxis: 
+        title: "Good 1"
+      yAxis: 
+        title: "Good 2"
+      objects: 
+      - EconBudgetLine:
+          p1: 1
+          p2: 2
+          m: 8
+          label: {text: M, location: 0.9}
+:::
 
@@
     return ABCDE, matarch, abc
+
+<head>
+      <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
+</head>
+<body>
+    Pyodide test page <br>
+    Open your browser console to see Pyodide output
+    <script type="text/javascript">
+      async function main(){
+        let pyodide = await loadPyodide();
+        console.log(pyodide.runPython(`
+            import sys
+            sys.version
+        `));
+        pyodide.runPython("print(1*5)");
+      }
+      main();
+    </script>
+</body>
+
+<p id=ary></p>
+<p id=nmb></p>
+<p id=str></p>

### 2024-01-07 presentation.qmd
befinds20

@@
   set_background_color(2, 1:3, clr[3]) %>%
-  set_background_color(3:5, 1:3, clr[4]) 
+  set_background_color(3, 1:3, clr[4]) %>%
+  set_background_color(4, 2:3, clr[4]) %>%
+  set_background_color(5, 3:3, clr[4]) %>%
+  set_font_size(16)
+
 lego_hux_imp_i
@@
   set_background_color(2, 1:3, clr[3]) %>%
-  set_background_color(3:5, 1:3, clr[4]) 
+  set_background_color(3, 1:3, clr[4]) %>%
+  set_background_color(4, 2:3, clr[4]) %>%
+  set_background_color(5, 3:3, clr[4]) %>%
+  set_font_size(16)
+
 lego_hux_imp_ii
@@
 
-```{r, echo=F}
-# Load necessary library
-library(tibble)
+## `r metad$toc$sec2$unm[3]`
 
-# Create the data.frame
-laws_df <- tribble(
-  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
-  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
-  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
-  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
-  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
-  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
-  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
-  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
-  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
-  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
-  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
-  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
-  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
-  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
-  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
-  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
-  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
-  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
-  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
-  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
-  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
-)
-# Display the data.frame
-kable(laws_df, format = "markdown", escape = FALSE) %>% kableExtra::kable_styling(font_size=16)
-```
+:::: {.columns}
 
-##
+::: {.column width="50%"}
 
-::: {.callout-caution collapse="true"}
-## Proportions
-```{r, echo=F}
-library(kableExtra)
-library(tibble)
-new_tbl <- data.frame(
-  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
-  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
-  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
-  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
-  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
-  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
-  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
-  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
-)
+*Standard form*
 
-# Extract the columns
-V1 <- new_tbl$V1
-V2 <- new_tbl$V2
-V3 <- new_tbl$V3
-V4 <- new_tbl$V4
-Equation1 <- new_tbl$Equation1
-Equation2 <- new_tbl$Equation2
-Equation3 <- new_tbl$Equation3
-Equation4 <- new_tbl$Equation4
+Setting the first three parameters:
 
-# Combine the columns
-combined <- data.frame(
-  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
-  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
-  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
-  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
-)
-kable(combined, format = "markdown", escape = FALSE) %>% kableExtra::kable_styling(font_size=16)
+- $x_i=\frac{s_i}{s_i+t_i}$
+- $y_i=\frac{u_i}{u_i+v_i}$
+- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$
+
+Backsolve for
+
+- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
+- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
+
+:::
+
+::: {.column width="50%"}
+
+*Opposition form*
+
+Setting the first three parameters:
+
+- $g_i=\frac{s_i}{s_i+t_i}$
+- $h_i=\frac{u_i}{u_i+v_i}$
+- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$
+
+Backsolve for
+
+- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
+- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
+
+:::
+
+::::
+
+---
+
+**Properties**:
+
+- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
+- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
+
+## `r metad$toc$sec2$unm[4]`
+
+**Setting the prefered election outcome**
+
+:::: {.columns}
+
+::: {.column width="40%"}
+
+Non-rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+#0app_n_out[[4]] 
 ```
@@
 
-[@delfino2011analysis]
+::: {.column width="60%"}
 
-## `r metad$toc$sec2$unm[3]`
+Rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+#app
+```
 
-## `r metad$toc$sec2$unm[4]`
+:::
+
+::::
+
+---
+
+**Normal**
+<br>
+\begin{equation*}
+f(x)_{0}^{1}=
+`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+\end{equation*}
+
+Election outome
+```{r, echo=F}
+#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+```
+
+<br>
+**Rigged**
+<br>
+
+$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+
+Election outome
+```{r, echo=F}
+#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+```
+
+---
+
+### Rigged election example 1: applying normal form
+
+- Setting for eaching precinct the first three parameters
+ - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
+ - $x_i=\frac{a_i}{a_i+b_i}$ (true observations)
+ - $y_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(x_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
+- Backsolve for
+ - $\zeta_i(x_i,\alpha_i,y_i)=\frac{x_i-\alpha_i}{\alpha_i-y_i}$
+ - $\lambda_i(x_i,\zeta_i,y_i)=\frac{x_i-\zeta_i (1-y_i)}{\zeta_i+1}$
+
+---
+
+**Properties**:
+
+- 3<sup>rd</sup> $y_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 4<sup>th</sup>. Changes in $\zeta_i$ - and as a corrollary $\Omega_i$ - is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\alpha_i$
+
+---
+
+### Rigged election example 2: applying hybrid form
+
+- Setting for eaching precinct the first three parameters
+ - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
+ - $h_i=\frac{s_i}{s_i+v_i}$ (true observations)
+ - $g_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(h_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
+- Backsolve form
+ - $\Gamma_i(g_i,\alpha_i,h_i)=\frac{g_i-\alpha_i}{\alpha_i-h_i}$
+ - $\Omega_i(g_i,\Gamma,h_i)=-\alpha_i+\frac{\Gamma_i+2g_i}{\Gamma_i+1}$
+
+---
+
+**Properties**:
+
+- 5<sup>th</sup> $y_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 6<sup>th</sup> Changes in $\Gamma_i$ - and as a corrollary $\lambda_i$ - is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\alpha_i$
+
+---
+
+### Rigged election example 3: applying opposition form
+
+- Setting for eaching precinct the first three parameters
+ - $\lambda_i=<...>$ (i.e., equal or less than the prefered election outcome)
+ - $n_i=\frac{a_i}{a_i+c_i}$ (true observations)
+ - $m_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(n_i,\lambda_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_{t_i} \sim N(0,\sigma^2)$
+- Backsolve for
+ - $\Omega_i(n_i,m_i,\lambda_i) = \frac{\lambda_i(n_i-m_i)-m_i(2n_i-1)}{1-(n_i+m_i)}$
+ - $\xi_i(n_i,m_i,\Omega_i)=\frac{m_i-\Omega_i}{\Omega_i-n_i}$
+
+---
+
+**Properties**:
+
+- 7<sup>th</sup> $m_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 8<sup>th</sup> Changes in $\xi_i$ is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\lambda_i$
+
+---
+
+**Setting the prefered election outcome**
+
+:::: {.columns}
+
+::: {.column width="50%"}
+
+Non-rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+app_n_out[[4]] 
+```
+
+:::
+
+::: {.column width="50%"}
+
+Rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+app_ex1_out[[4]] 
+```
+:::
+
+::::
+
+---
+
+**Normal**
+<br>
+\begin{equation*}
+f(x)_{0}^{1}=
+`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+\end{equation*}
+
+Election outome
+```{r, echo=F}
+sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+```
+
+<br>
+**Rigged**
+<br>
+
+$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+
+Election outome
+```{r, echo=F}
+sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+```
+
+---
 

### 2024-01-07 tabsets.qmd
tabsets
befinds20

--- 2023-12-31 tabsets.qmd
@@
 ```{r, echo=F, message=F, warning=F}
-library(ManifoldDestiny)
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-library(RefManageR)
-library(huxtable)
+ManifoldDestiny::wasmconload()
 modlat <- eqpar$meql
 md <- ManifoldDestinyWASMD::metad
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))

### 2024-01-07 presentation.qmd
break

@@
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
@@
 **20 laws and 40 isometris**
+
+```{r}
+kable(laws_df1, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
+```
 

### 2024-01-07 presentation.qmd
tryagin
latest

@@
 ```{r}
-kable(laws_df1, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
+#kable(laws_df1, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
 ```
+
+**20 laws and 40 isometris**
+
+```{r, echo=F}
+# Load necessary library
+library(tibble)
+
+# Create the data.frame
+laws_df <- tribble(
+  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
+  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
+  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
+  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
+  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
+  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
+  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
+  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
+  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
+  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
+  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
+  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
+  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
+  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
+  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
+  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
+  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
+  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
+  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
+  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
+  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
+)
+# Display the data.frame
+kable(laws_df, format = "markdown", escape = FALSE)
+```
+
+##
+
+::: {.callout-caution collapse="true"}
+## Proportions
+
+```{r, echo=F}
+library(kableExtra)
+library(tibble)
+new_tbl <- data.frame(
+  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
+  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
+  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
+  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
+  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
+  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
+  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
+  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
+)
+
+# Extract the columns
+V1 <- new_tbl$V1
+V2 <- new_tbl$V2
+V3 <- new_tbl$V3
+V4 <- new_tbl$V4
+Equation1 <- new_tbl$Equation1
+Equation2 <- new_tbl$Equation2
+Equation3 <- new_tbl$Equation3
+Equation4 <- new_tbl$Equation4
+
+# Combine the columns
+combined <- data.frame(
+  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
+  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
+  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
+  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
+)
+kable(combined, format = "markdown", escape = FALSE)
+```
+
+:::
 
@@
 
+---
+
 `r #Citet(bib, "delfino2011analysis")`

### 2024-01-07 paper.qmd
moreupd

--- 2024-01-05 paper.qmd
@@
 
-```{r, echo=F, message=F, warning=F}
-library(ManifoldDestiny)
-ManifoldDestiny::wasmnonload()
+```{r, echo=F, message=F, warning=F, results='hide'}
+#Sys.info()[['sysname']]=="Emscripten"
+ManifoldDestiny::wasmconload()
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
@@
 
-[Link to R2 simulator for testing](https://shinylive.io/r/app/#h=0&code=NobwRAdghgtgpmAXGKAHVA6ASmANGAYwHsIAXOMpMAdzgCMAnRRASwgGdSoAbbgCgA6YALJQILAGZFuAEwAicTmwCeAdQCCAZWEAFIbgAEDOKiLsDAXgNCAFqVKp2iAPTPuRLgxZEb1AEwAbBgA5iykNgCudBjezsJyAPoa2gDCQgCUAhC0jMxsnDz8QqLiUrIKShBqWvH6RiZmltZgdg5Oru6e3r6BIWGR0bHxSTVpYJkQ3CyMUAzKfCWS0vKKpCrJuhNTM3MLYkvlq+s1clvTDLPz7DYqZzvzMFDBXvYMdxe7wcGonX4TRKg1iR2Hx2AQWKgKBYAJyw96XPg-DzcZTw3ZyAAqaPmAGsoHRuHAAKIAD1IF2xfBkP2Ubyy2w+8zsMG4pCI0nYlOeLBkpPJUAmERYBgAPABaAwSbhCmQ6J5wQQQAwGNakQlyiBwIpgLB+AyaFgwCLcKBshgZXBZZVcOjsOCkDVaxXK634x3agDiF1QNjqVpdAcD7B59FmABkoMoiBFSM7A-GXcGZKGGO64wmM3bCQRSABJCCoGOCMAAN1mLHxhL9YE0WrgOYMUElRAYMEQdQIxYAci3Htxm62hE0hBBezxqwAJZSMHkDmBDqy2adeGTVgDy6DMYW8Sqkg7Aw7AANMwaBEAy6UtSozGYgEXgXgI+cLsZHqGMBGrXfvdDgDAMRASAY771mwOZOHUZbSnATQAMwAAzwZe-o3vG5Bks+RZCMYwQltWWBwKEnB-nAMgGCWHh-uYfDwGIuCcDImR4ORPARHAFgAOSwRgACMACshjwRgfh8RxyHXqhgboXmBZYWAMBsI8JLVsIbCNhAZFKSx0HmHeMC-v+gHkZRDDsJBrHsRxAAsiGGDZiFiVekloXAGGya+YCkBEDDnsxQg6AwRB0PiLBTKQygAUBFFrBAwTtsxUFsU0HFCQJBhCTx8GOShznWq5MkvsWbAlpC5p+WARLZmeBjsMoxEwCxXghWFyjxYYiUwZxqWCbxWXiblAbSZhHkRNWAVBc1YQRUZJLOMEzgQG12lJVYKUYAEPWZdlEkDUN7nFjIeHlXIkhAe+E10KFU2RQYs3zYt5nQclYpCX4PXwQAHNtA0unpf4sE++1CDIFzUGZ5Xfvpf43SDUBg49K0GAh-U-Y2OY7gAQjGbIQMWDARL5hhCFgBP6oaxqmjuGQ5ZJKO5Y8bBpjTzlIqQa4xoVQisxazOSTahLsw4cn83A1M7bTvPxukEwBnTKpumITpCBilaKH64sZjadoOorRQazeNpM2AKsEjBPH6JLqNJimEZRlh+uo4mIbBamut8HLjuBgzEBMw7nuuqbguc55qvm+MluOzL-uyxHgYe6hhtu8rqsGH4Ft+z91su7b0avhnVvO7Mabx9H3u+9Hmuq0Hwuq2n4f5z9UcVwYTfOa3N6txMEwAMTdwYCgSGwMF2gwJZ-lkI9j-+4qSgT6MkHwbAvoYucvukBggP6-p9yTSrBkaJpnv6MgSN8ooSnAY9kARUDo2Pi-uQAJPjECGJvO198N-cAGLmztOElnPo2dgGA-qPlBOSdgPwwgPxfM-QiJYiZ4AyMAYAPEAC66DW4KQgFpGeUAQFgIBhA0y0DYxLxjI-HBSkkGWnGKgjBWCcpeR8kAghoD7z-U7JwUhYVYGUJYa-ZodD0gMMwa3YqpU2GEM4eAnhUC+EUNII-SRf5aEoLQeInKERpEcIfMQ+RZD+HKIiOo+hmimE7UOrooh3DIFGKUY-Q6ZjREWNbqQICM9jDQIIKaBUjjYZg1wAwPw+9cYFg-E0RxET6xORvDhcwVhOwAM0YYFJfgsFxIzNQqAJImidhySSVJhTgAZMvCqbySokl8EEakipPlSmZIMPmEq0NqmqIYHUjpjSS4uh0dUiIdTBllKyQmax1TDp1MmSMiOe4GpWB4qIzsPFcBvVgukSxAYT5nxnjIU0UAMASAuPAPgISoAWAJlMTgNSJDADtAARz4CswksVwg3MvOszJIS6AXMmCwa5Hi7lwEeW9F5wQ3keI+Rs6WBgACkAA+WFBgjRcHIIiP8BAmhkFCgqM5hhMpIXXjlT+7kf5px2qVAgFA1iEnMDPTs0J4KGGhGlOEOUOCkDIvSp5qzcB8VbgxIBtFcbbNQM-PwAoADUHKZAACp2AyCpKfMVZzW6Up4kA+5EQxA0oVKK8VUBcDnVtE0Sl1KcXmGcAYAlaqMV6hnlqnVOKlXfHFXQI1gUTVWDNdi2lBgrU2pypSk+QC9lcEOcchU6qjV2twDK+inL14IqRWGg5ItmDa2gPAEEnZ-IYqMBKi2YAdD5u+UWrsDEi0ADVK3jCJTtK5sZRUxoYAQE+UcAC+Uc+4pGMH44CnR-Sr0oazIBxgNJ-h0J0Pg78BCkGVN3RgRAwZ-ndjlE+qBQ3KvdmI9BcLEUqh5LSZgqAWDRQSO4WKq7iDcHYBYXNYAzlFrLXW-dKaaRMEQLMC4V6+BZrgC2ggrcvisyVagXAUBFB8BJBYDqhhB68AsP+mFkrrAa2CHAIgMAEg3E4EQZ4sBERbmqouMAIZsXhTqDwH0TYrDdQMJdDgcEkIGFQ8zE0toalhEJIeCc-y2QEYakZKtFlzB0AiikPxwQWzKDqHk0jInoJ1AiqRlI0YyAZFY8zDDWGEglimJqaDbByCtpMPOqw7DbEutQDuxp6C0G4AweUgz9plCQkPHs64pEOzSBbIeAkbFNOSu05h7D+mh5GbIBiszTRLOyOIaK2zGT7NvSc4YFz4V3Okc8zYbzzEb1+dIwF0W4wtPodC3plzkWTNUsBLFmR+jOyJdccl4AsFHNNIy25zqzQct5cMAV-8RWlOleC+V3T4XDMkmM9FurFmGtcOs0lzBbXcBWU60PTLPWhDsGkDyHz7ghvNGMKuUbIXdMcadMoCwTKYNxca0tlrK2Vlpcu9wCwQhZX6B0zAD7YA3tBfO9ht7fBru3YsPdxbzXUGtdS5kt7f3ZVfbwD9v7AOzvjeB-iK7N3cB3YW+A6HdnVuvex+9z7SPvuhbR2TwHGtwhwHgAkHBhoeDuzK-GMEPA4AJAQ9wZnYhtX8A6okgwD7u6IQAOx+AxnXJB3ciQBGhN-RCF4F01XtJKUK-ZBtmWvF2re15e4GF7XAftIsh0cwEaHMdFBkwMAAKq5hnTlTEzBU0i1OepxVRPku4BkCwUIpA71WWlv6A315h3KJFvaiU477dO5dztN3iAPeqy9wTH327XGMMMAHoPIfykAjPKLxtiJ5RhgoOCmwTQ-CEvDxMDtWQd6kzQKgCeNwqjqHQHwIUTQhSGEnm0jXo8-wTCyGADt6CgA)
-
 # `r metad$toc$sec2$nmn`
@@
 ## `r metad$toc$sec2$unm[2]`
+
+**20 laws and 40 isometris**
+
+```{r}
+#kable(laws_df1, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
+```
 
@@
 
-[@delfino2011analysis]
+## `r metad$toc$sec2$unm[3]`
 
-## `r metad$toc$sec2$unm[3]`
+:::: {.columns}
+
+::: {.column width="50%"}
+
+*Standard form*
+
+Setting the first three parameters:
+
+- $x_i=\frac{s_i}{s_i+t_i}$
+- $y_i=\frac{u_i}{u_i+v_i}$
+- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$
+
+Backsolve for
+
+- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
+- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
+
+:::
+
+::: {.column width="50%"}
+
+*Opposition form*
+
+Setting the first three parameters:
+
+- $g_i=\frac{s_i}{s_i+t_i}$
+- $h_i=\frac{u_i}{u_i+v_i}$
+- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$
+
+Backsolve for
+
+- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
+- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
+
+:::
+
+::::
+
+---
+
+**Properties**:
+
+- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
+- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
 
@@
 
+**Setting the prefered election outcome**
+
+:::: {.columns}
+
+::: {.column width="40%"}
+
+Non-rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+#0app_n_out[[4]] 
+```
+
+:::
+
+::: {.column width="60%"}
+
+Rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+#app
+```
+
+:::
+
+::::
+
+---
+
+**Normal**
+<br>
+\begin{equation*}
+f(x)_{0}^{1}=
+`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+\end{equation*}
+
+Election outome
+```{r, echo=F}
+#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+```
+
+<br>
+**Rigged**
+<br>
+
+$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+
+Election outome
+```{r, echo=F}
+#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+```
+
+---
+
+### Rigged election example 1: applying normal form
+
+- Setting for eaching precinct the first three parameters
+ - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
+ - $x_i=\frac{a_i}{a_i+b_i}$ (true observations)
+ - $y_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(x_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
+- Backsolve for
+ - $\zeta_i(x_i,\alpha_i,y_i)=\frac{x_i-\alpha_i}{\alpha_i-y_i}$
+ - $\lambda_i(x_i,\zeta_i,y_i)=\frac{x_i-\zeta_i (1-y_i)}{\zeta_i+1}$
+
+---
+
+**Properties**:
+
+- 3<sup>rd</sup> $y_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 4<sup>th</sup>. Changes in $\zeta_i$ - and as a corrollary $\Omega_i$ - is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\alpha_i$
+
+---
+
+### Rigged election example 2: applying hybrid form
+
+- Setting for eaching precinct the first three parameters
+ - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
+ - $h_i=\frac{s_i}{s_i+v_i}$ (true observations)
+ - $g_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(h_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
+- Backsolve form
+ - $\Gamma_i(g_i,\alpha_i,h_i)=\frac{g_i-\alpha_i}{\alpha_i-h_i}$
+ - $\Omega_i(g_i,\Gamma,h_i)=-\alpha_i+\frac{\Gamma_i+2g_i}{\Gamma_i+1}$
+
+---
+
+**Properties**:
+
+- 5<sup>th</sup> $y_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 6<sup>th</sup> Changes in $\Gamma_i$ - and as a corrollary $\lambda_i$ - is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\alpha_i$
+
+---
+
+### Rigged election example 3: applying opposition form
+
+- Setting for eaching precinct the first three parameters
+ - $\lambda_i=<...>$ (i.e., equal or less than the prefered election outcome)
+ - $n_i=\frac{a_i}{a_i+c_i}$ (true observations)
+ - $m_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(n_i,\lambda_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_{t_i} \sim N(0,\sigma^2)$
+- Backsolve for
+ - $\Omega_i(n_i,m_i,\lambda_i) = \frac{\lambda_i(n_i-m_i)-m_i(2n_i-1)}{1-(n_i+m_i)}$
+ - $\xi_i(n_i,m_i,\Omega_i)=\frac{m_i-\Omega_i}{\Omega_i-n_i}$
+
+---
+
+**Properties**:
+
+- 7<sup>th</sup> $m_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 8<sup>th</sup> Changes in $\xi_i$ is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\lambda_i$
+
+---
+
+**Setting the prefered election outcome**
+
+:::: {.columns}
+
+::: {.column width="50%"}
+
+Non-rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+app_n_out[[4]] 
+```
+
+:::
+
+::: {.column width="50%"}
+
+Rigged election using standard form
+```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
+app_ex1_out[[4]] 
+```
+:::
+
+::::
+
+---
+
+**Normal**
+<br>
+\begin{equation*}
+f(x)_{0}^{1}=
+`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+\end{equation*}
+
+Election outome
+```{r, echo=F}
+sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+```
+
+<br>
+**Rigged**
+<br>
+
+$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+
+Election outome
+```{r, echo=F}
+sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+```
+
+---
+
 ## `r metad$toc$sec2$unm[5]`
+
+- Loss function
+  - $M(,)=$x+y$
+    - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
+    - Also: Euler rotation
+  - System approach Demands mulitvariate Manifold Equations
+    - Abc
+    - Def
+  - Constrain on implementation
+    - Flipping votes on one mode
+    - Vote registration until upper limit
+
+---
+
+```{r, echo=F, out.width="80%", fig.cap=""}
+bI <- paste0(rprojroot::find_rstudio_root_file(),'pngs/loss_5_conditions.png')
+knitr::include_graphics(bI)
+```
 
@@
 ```
+---
+
+[xxx application]({{< var shn3 >}})
+
+---
 
 # `r metad$toc$sec7$nmn`
+
+[xxx application]({{< var shn4 >}})
+
+---
+
+# `r metad$toc$sec8$nmn`
 

### 2024-01-07 presentation.qmd
app1234

@@
 
-[Application 1: Election process simulator]({{< var shn1 >}})
-
 ---
@@
 
+[Application 1: Election process simulator]({{< var shn1 >}})
+
 ## `r metad$toc$sec1$unm[7]`
@@
 If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
+
+[Application 1: Election process simulator]({{< var shn1 >}})
 
@@
 ::::
+
+[Application 2: Rigged election process simulator]({{< var shn2 >}})
 
@@
 
+[Application 3: Rigged election analyzer]({{< var shn3 >}})
+
 # `r metad$toc$sec6$nmn`
-
-[Application]({{< var shn2 >}})
 
@@
 
-[xxx application]({{< var shn3 >}})
-
----
-
 # `r metad$toc$sec7$nmn`
 
-[xxx application]({{< var shn4 >}})
+[Application 4: Restoration of a rigged election]({{< var shn4 >}})
 
@@
 ```{r, echo=F, warning=F, message=F}
-#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```

### 2024-01-08 paper.qmd
addedpoly

@@
   set_font_size(16)
-
 lego_hux_imp_i
@@
 
-**20 laws and 40 isometris**
-
-```{r}
-#kable(laws_df1, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=12)
-```
-
+::: {.callout-caution collapse="true"}
 **20 laws and 40 isometris**
@@
 # Display the data.frame
-kable(laws_df, format = "markdown", escape = FALSE)
+kable(laws_df, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```
 
-##
+:::
+
+---
 
@@
 )
-kable(combined, format = "markdown", escape = FALSE)
+kable(combined, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```
@@
 
-[Application 2: Rigged election process simulator]({{< var shn2 >}})
-
----
-
 **Properties**:
@@
 - 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
+
+[Application 2: Rigged election process simulator]({{< var shn2 >}})
 
@@
 
-::: {.column width="40%"}
-
+::: {.column width="50%"}
 Non-rigged election using standard form
-```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
-#0app_n_out[[4]] 
+```{r}
+app_n_out[[4]] 
 ```
@@
 
-::: {.column width="60%"}
+::: {.column width="50%"}
 
 Rigged election using standard form
-```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
-#app
+```{r}
+app_ex1_out[[4]] 
 ```
@@
 \begin{equation*}
-f(x)_{0}^{1}=
-`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
 \end{equation*}
@@
 ```{r, echo=F}
-#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
 ```
@@
 
-$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
 
@@
 ```{r, echo=F}
-#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
 ```

### 2024-01-08 script/R/simulations.R

@@ -65,6 +65,7 @@ app_n_out <- seloutput(app_n_rep)
 app_n_sim <- SimVoterdatabase(app_bal)
 ######## Rigged example 1: standard form
 app_ex1_cou <- Countinggraphs(app_bal)
+pri_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
 #print(app_ex1_cou$polyc[[1]][[1]])
 app_ex1_cou$sortpre()
 app_ex1_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))

### 2024-01-08 script/R/simulations.R
paperprespol

@@ -70,6 +70,7 @@ pri_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
 app_ex1_cou$sortpre()
 app_ex1_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
 app_ex1_cou$setres(0.23,0)
+pos_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
 app_ex1_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),TRUE,wn=c(0,0))
 app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
 app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
@@ -80,6 +81,7 @@ pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
 app_ex2_cou$sortpre()
 app_ex2_cou$mansys(sygen=list(frm=2,pre=c("alpha","g","h"),end=c("Gamma","Omega"),FALSE,me=c(plnr=1,rot=0)))
 app_ex2_cou$setres(0.23,0)
+pos_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
 app_ex2_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
 app_ex2_out <- seloutput(selreport(app_ex2_cou$rdfc,md$app0))
 app_ex2_sim <- SimVoterdatabase(app_ex2_cou$rdfc)
@@ -89,6 +91,7 @@ pri_int_ex3 <- app_ex3_cou$polyc[[1]][[1]]
 app_ex3_cou$sortpre()
 app_ex3_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
 app_ex3_cou$setres(0.23,0)
+pos_int_ex3 <- app_ex3_cou$polyc[[1]][[1]]
 app_ex3_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
 app_ex3_out <- seloutput(selreport(app_ex3_cou$rdfc,md$app0))
 app_ex3_sim <- SimVoterdatabase(app_ex3_cou$rdfc)

### 2024-01-14 randpython.qmd
allplugged

---
title: "abc"
---

# Abc

[Coatless](https://www.youtube.com/watch?v=PZx9d21HnTo)

@thecoatlessprofessor7674
1 month ago
Great question. The short gist is yes in the *interactive* context for now.

We'll likely need to make another extension that wraps before {quarto-webr} and {quarto-pyodide} to enable cross talk in the *non-interactive**/**output* contexts.

### 2024-01-21 presentation.qmd
paperprespol
break

@@
 ```{r, echo=F}
-sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
 ```
@@
 
-$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
 
@@
 ```{r, echo=F}
-sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
 ```
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex3)),3))`$
 \end{equation*}
@@
 ```{r, echo=F}
-sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
+polynom::integral(round(polynom::polynomial(unname(pri_int_ex3))),c(0,1))
 ```
@@
 
-$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex3)),3))`$
 
@@
 ```{r, echo=F}
-sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
+polynom::integral(round(polynom::polynomial(unname(pos_int_ex3))),c(0,1))
+```
+```{r}
+knitr::knit_exit()
 ```
@@
 
+```{r}
+knitr::knit_exit()
+```
+
 # `r metad$toc$sec6$nmn`

### 2024-01-21 script/R/applications.R

@@ -17,12 +17,20 @@ md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/m
 app0 <- get(load(paste0(rprojroot::find_rstudio_root_file(),"/data/app0.rda")))
 app0_rp <- selreport(app0,md$app0)
 app_0_out <- seloutput(app0_rp)
-app1_rp <- selreport(app1,md$app1)
-app_1_out <- seloutput(app1_rp)
-app2_rp <- selreport(app2,md$app2)
-app_2_out <- seloutput(app2_rp)
-app3_rp <- selreport(app2,md$app2)
-app_3_out <- seloutput(app2_rp)
-app4_rp <- selreport(app2,md$app2)
-app_4_out <- seloutput(app2_rp)
+app1_rp <- selreport(app0,md$app0)
+app_1_out <- seloutput(app0_rp)
+app2_rp <- selreport(app0,md$app0)
+app_2_out <- seloutput(app0_rp)
+app3_rp <- selreport(app0,md$app0)
+app_3_out <- seloutput(app0_rp)
+app4_rp <- selreport(app0,md$app0)
+app_4_out <- seloutput(app0_rp)
+#app1_rp <- selreport(app1,md$app1)
+#app_1_out <- seloutput(app1_rp)
+#app2_rp <- selreport(app2,md$app2)
+#app_2_out <- seloutput(app2_rp)
+#app3_rp <- selreport(app2,md$app2)
+#app_3_out <- seloutput(app2_rp)
+#app4_rp <- selreport(app2,md$app2)
+#app_4_out <- seloutput(app2_rp)
 ##########################################################################################################################################################

### 2024-01-22 paper.qmd
paperprespol
starwork

@@
 
-```{r, echo=F, message=F, warning=F, results='hide'}
-#Sys.info()[['sysname']]=="Emscripten"
-ManifoldDestiny::wasmconload()
-metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
-modlat <- eqpar$meql
-library(huxtable)
-library(kableExtra)
+```{r, echo=FALSE, results='asis',warning=F}
+presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
+textm <- readLines(presm)
+cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
 ```
-
-# `r metad$toc$sec1$nmn`
-
- Ed. Solomon
-
-> "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
-
-## `r metad$toc$sec1$unm[1]`
-
-- Two candidates: A, B
-- County with three precincts: 1, 2, 3
-- Two modes of voting
-  - Number of ballots mode 1: S, T
-  - Number of ballots mode 2: U, V
-
-##
-
-**Our two stylized numerical example**
-
-:::: {.columns}
-::: {.column width="50%"}
-Case 1
-:::
-```{r, echo=F}
-clr <- c("black","green","red","blue")
-lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
-  set_text_color(5, 1:2, clr[1]) %>%
-  set_background_color(1, 1:3, clr[2]) %>% 
-  set_background_color(2, 1:3, clr[3]) %>%
-  set_background_color(3, 1:3, clr[4]) %>%
-  set_background_color(4, 2:3, clr[4]) %>%
-  set_background_color(5, 3:3, clr[4]) %>%
-  set_font_size(16)
-lego_hux_imp_i
-```
-
-::: {.column width="50%"}
-Case 2
-:::
-```{r, echo=F}
-lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
-  set_text_color(5, 1:2, clr[1]) %>%
-  set_background_color(1, 1:3, clr[2]) %>% 
-  set_background_color(2, 1:3, clr[3]) %>%
-  set_background_color(3, 1:3, clr[4]) %>%
-  set_background_color(4, 2:3, clr[4]) %>%
-  set_background_color(5, 3:3, clr[4]) %>%
-  set_font_size(16)
-
-lego_hux_imp_ii
-```
-::::
-
-## `r metad$toc$sec1$unm[2]`
-
-```{r, echo=F}
-lego_hux_nor <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
-  set_background_color(1, 1:2, "black") %>% 
-  set_background_color(2, 1:2, "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_nor %>% set_caption("")
-```
-
-Parameters:**$x$, $y$, $\zeta$, $\alpha$, $\lambda$**
-
-\begin{equation*}
-x=`r modlat$x_s[1]` \text{, }y=`r modlat$y_s[1]`
-\end{equation*}
-\begin{equation*}
-\zeta=`r modlat$zeta_s[1]`
-\end{equation*}
-\begin{equation*}
-\alpha=`r modlat$alpha_s[1]`=`r modlat$alpha_s[2]`
-\end{equation*}
-\begin{equation*}
-\lambda=`r modlat$lamda_s[1]`=`r modlat$lamda_s[2]`
-\end{equation*}
-
-##
-
-```{r, echo=F}
-ctone_sf <- 'Election results applying standard form on case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
-cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-Numerical calculation of candidate one total percentage
-
-- Precinct 1
-  - $\alpha=\frac{`r cx[1]`+`r cy[1]`\cdot `r czeta[1]`}{1+`r czeta[1]`}=`r calpha[1]`$
-- Precinct 2
-  - $\alpha=\frac{`r cx[2]`+`r cy[2]`\cdot `r czeta[2]`}{1+`r czeta[2]`}=`r calpha[2]`$
-- Precinct 3
-  - $\alpha=\frac{`r cx[3]`+`r cy[3]`\cdot `r czeta[3]`}{1+`r czeta[3]`}=`r calpha[3]`$
-
-## `r metad$toc$sec1$unm[3]`
-
-```{r, echo=F}
-lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
-  set_background_color(1:2, 1, "black") %>% 
-  set_background_color(1:2, 2, "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_imp %>% set_caption("")
-```
-
-Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
-\begin{equation*}
-g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
-\end{equation*}
-\begin{equation*}
-\Gamma=`r modlat$Gamma_h[1]`
-\end{equation*}
-\begin{equation*}
-\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
-\end{equation*}
-\begin{equation*}
-\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
-\end{equation*}
-
-##
-
-```{r, echo=F}
-ctone_hf <- 'Election results applying hybrid form case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-Numerical calculation of candidate one total percentage
-
-- Precinct 1
-  - $\alpha=\frac{`r cg[1]`+`r ch[1]`\cdot `r cGamma[1]`}{1+`r cGamma[1]`}=`r calpha[1]`$
-- Precinct 2
-  - $\alpha=\frac{`r cg[2]`+`r ch[2]`\cdot `r cGamma[2]`}{1+`r cGamma[2]`}=`r calpha[2]`$
-- Precinct 3
-  - $\alpha=\frac{`r cg[3]`+`r ch[3]`\cdot `r cGamma[3]`}{1+`r cGamma[3]`}=`r calpha[3]`$
-
----
-
-```{r, echo=F}
-ctone_hf <- 'Election results applying hybrid form case II'
-stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-## `r metad$toc$sec1$unm[4]`
-
-```{r, echo=F}
-lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
-  set_background_color(c(1),c(1), "black") %>% 
-  set_background_color(c(2),c(2), "black") %>% 
-  set_background_color(c(1),c(2), "grey") %>% 
-  set_background_color(c(2),c(1), "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_opo %>% set_caption("")
-```
-
-Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$
-\begin{equation*}
-n=`r modlat$n_o[1]` \text{ , } m=`r modlat$m_o[1]`
-\end{equation*}
-\begin{equation*}
-\xi=`r modlat$xi_o[1]`
-\end{equation*}
-\begin{equation*}
-\Omega=`r modlat$Omega_o[1]`=`r modlat$Omega_o[2]`
-\end{equation*}
-\begin{equation*}
-\lambda=`r modlat$lamda_o[1]`=`r modlat$lamda_o[2]`
-\end{equation*}
-
-##
-
-```{r, echo=F}
-ctone_of <- 'Election results applying opposition form'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
-kableExtra::kbl(format(stfo_sel,digits=4), caption=ctone_of) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-## `r metad$toc$sec1$unm[5]`
-
-- **Step 1:** Each registered voter assign themself (independent of voting technology) to either candidate A or candidate B
-- **Step 2:** Voting technology realized
-- **Step 3:** Registered voters determine whether to vote or not to vote 
-- **Step 4:** If voting, do this by either mode 1 or by mode 2.
-
-```{mermaid}
-  flowchart LR
-  A[Candidate A or B] --> R[A]
-  R --> RV[Vote]
-  RV --> RVE[Non-Mail]
-  RV --> RVM[Mail]
-  R --> RN[Not Vote]
-  DV --> DVE[Non-Mail]
-  DV --> DVM[Mail]
-  A --> D[B]
-  D --> DV[Vote]
-  D --> Dn[Not Vote]
-```
-
-##
-
-- Probability of assigning oneself to candidate A in precinct $i$
-  - $p_{w,i} \sim N(\alpha_i,\sigma^2_{w,i})$
-- Voting technology
-  - $z_i \sim U(0,1)$
-- Probability of not voting in precinct $i$
-  - Candidate A, $p_{nz,a,i}=(1-z_i)p_{n,a,i}\sim N(\alpha_{a,n},\sigma^2_{a,n})$ <br>
-  - Candidate B, $p_{nz,b,i}=(1-z_i)p_{n,b,i}\sim N(\alpha_{b,n},\sigma^2_{b,n})$
-- Probability of voting by mode 2 in precinct $i$
-  - Candidate A, $p_{m2,a,i}=(1-p_{nv,a,i})p_{a,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
-  - Candidate B, $p_{m2,b,i}=(1-p_{nv,b,i})p_{b,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
-- Probability of voting by mode 1 in precinct $i$
-  - Candidate A, $p_{m1,a,i}=1-p_{m2,a,i}-p_{nz,a,i}$ 
-  - Candidate B, $p_{m1,b,i}=1-p_{m2,b,i}-p_{nz,b,i}$
-
----
-
-Neutral-voting assumption:
-
-- Decission to vote or not to vote is independent of voting preferences:
-  - $p_{nz,a,i}=p_{nz,a,i}$ 
-- If voting, decission to vote by mode 1 or by mode 2 independent of voting preferences: 
-  - $p_{m2,a,i}=p_{m2,a,i}$
-
-Note: As we will investigate later, this condition might be needed in order to restore a rigged election to its original form.
-
-## `r metad$toc$sec1$unm[6]`
-
-1. Differences in the cost of voting (e.g., topology, voting rules, dropboxes etc.) across precincts $\Rightarrow$
-1. Changes to the likelihood of voting $\Rightarrow$ 
-1. Simplify so that changes in the likelihood of voting only impact Mode 2 $\Rightarrow$ 
-1. Higher $\zeta_i$ $\Rightarrow$
-1. Which changes the total election outcome through $\alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}$
-
-##
-
-The impact on the election outcome, however, would be small or close to non-existens if the conditions
-of the existance of a *trivial* Manifold occuranse related to normal form are not satisfied:
-
-- Proportion of mail-in-votes to election day vote is already high (Aggregate convergence lemma)
-  - Note: $\lim_{\zeta_i \rightarrow \infty} \alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}=y_i$
-- Correlation between $x$ and $y$ is very high (Twixt lemma)
-  - Note: If correlation is 1, we can set $x_i=\rho_s y_i$ so that $\alpha_i(y_i,\zeta_i)=\frac{\rho_s y_i+\zeta_i y_i}{\zeta_i+x_i}$
-- Low variance to $\zeta$ 
-  - Note: Invariance across precincts would imply that $\zeta_i=\zeta$, so that election outcome only determined by variations in two parameters: $\alpha_i(y_i,x_i)=\frac{x_i+\zeta y_i}{\zeta+x_i}$
-
-If none of this three cases are satisfied, variation in $\zeta_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
-
-[Application 1: Election process simulator]({{< var shn1 >}})
-
-## `r metad$toc$sec1$unm[7]`
-
-1. Differenc in the cost of voting (e.g., topology, voting rules, dropboxes, socio economics etc.) across precincts $\Rightarrow$ 
-1. Make changes to the likelihood of voting $\Rightarrow$ 
-1. Simplify so that changes in the likelihood of voting only impact mode 2 $\Rightarrow$ 
-1. Higher $\zeta_i$ $\Rightarrow$
-1. If new and earlier sample not representative of each other, higher $\Gamma_i$ $\Rightarrow$
-1. Which changes the total election outcome through $\alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+1}$
-
-##
-
-The impact on the election outcome, however, would be small or close to non-existens if the conditions
-of the existance of a *trivial* Manifold related to opposition form are not satisfied:
-
-- Proportion of the hybrid ballot boxes is already high (Aggregate convergence lemma)
-  - Note: $\lim_{\Gamma_i \rightarrow \infty} \alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+g_i}=y_i$
-- Correlation between $g$ and $h$ is very high (Twixt lemma)
-  - Note: If correlation is 1, we can set $g_i=\rho_h h_i$ so that $\alpha_i(h_i,\Gamma_i)=\frac{\rho_h h_i+\Gamma_i h_i}{\Gamma_i+x_i}$
-- Low variance to $\Gamma_i$ 
-  - Note: Invariance across precincts would imply that $\Gamma_i=\Gamma$, so that election outcome only determined by variations in two parameters: $\alpha_i=\frac{g_i+\Gamma h_i}{h_i}$
-
-If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
-
-[Application 1: Election process simulator]({{< var shn1 >}})
-
-# `r metad$toc$sec2$nmn`
-
-## `r metad$toc$sec2$unm[1]`
-
-- We have identified three ways of counting
-  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
-  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
-  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
--  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
-  -  We are free to *predetermine* **3** of them
-  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
-  -  Selecting **3** parameters from a set of **5** implies **10** different combinations
-
-## `r metad$toc$sec2$unm[2]`
-
-::: {.callout-caution collapse="true"}
-**20 laws and 40 isometris**
-
-```{r, echo=F}
-# Load necessary library
-library(tibble)
-
-# Create the data.frame
-laws_df <- tribble(
-  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
-  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
-  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
-  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
-  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
-  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
-  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
-  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
-  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
-  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
-  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
-  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
-  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
-  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
-  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
-  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
-  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
-  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
-  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
-  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
-  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
-)
-# Display the data.frame
-kable(laws_df, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-:::
-
----
-
-::: {.callout-caution collapse="true"}
-## Proportions
-
-```{r, echo=F}
-library(kableExtra)
-library(tibble)
-new_tbl <- data.frame(
-  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
-  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
-  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
-  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
-  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
-  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
-  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
-  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
-)
-
-# Extract the columns
-V1 <- new_tbl$V1
-V2 <- new_tbl$V2
-V3 <- new_tbl$V3
-V4 <- new_tbl$V4
-Equation1 <- new_tbl$Equation1
-Equation2 <- new_tbl$Equation2
-Equation3 <- new_tbl$Equation3
-Equation4 <- new_tbl$Equation4
-
-# Combine the columns
-combined <- data.frame(
-  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
-  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
-  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
-  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
-)
-kable(combined, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-:::
-
-## `r metad$toc$sec2$unm[3]`
-
-:::: {.columns}
-
-::: {.column width="50%"}
-
-*Standard form*
-
-Setting the first three parameters:
-
-- $x_i=\frac{s_i}{s_i+t_i}$
-- $y_i=\frac{u_i}{u_i+v_i}$
-- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$
-
-Backsolve for
-
-- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::: {.column width="50%"}
-
-*Opposition form*
-
-Setting the first three parameters:
-
-- $g_i=\frac{s_i}{s_i+t_i}$
-- $h_i=\frac{u_i}{u_i+v_i}$
-- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$
-
-Backsolve for
-
-- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::::
-
-**Properties**:
-
-- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
-- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
-
-[Application 2: Rigged election process simulator]({{< var shn2 >}})
-
-## `r metad$toc$sec2$unm[4]`
-
-**Setting the prefered election outcome**
-
-:::: {.columns}
-
-::: {.column width="50%"}
-Non-rigged election using standard form
-```{r}
-app_n_out[[4]] 
-```
-
-:::
-
-::: {.column width="50%"}
-
-Rigged election using standard form
-```{r}
-app_ex1_out[[4]] 
-```
-
-:::
-
-::::
-
----
-
-**Normal**
-<br>
-\begin{equation*}
-f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
-\end{equation*}
-
-Election outome
-```{r, echo=F}
-sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
-```
-
-<br>
-**Rigged**
-<br>
-
-$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
-
-Election outome
-```{r, echo=F}
-sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
-```
-
----
-
-### Rigged election example 1: applying normal form
-
-- Setting for eaching precinct the first three parameters
- - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
- - $x_i=\frac{a_i}{a_i+b_i}$ (true observations)
- - $y_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(x_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
-- Backsolve for
- - $\zeta_i(x_i,\alpha_i,y_i)=\frac{x_i-\alpha_i}{\alpha_i-y_i}$
- - $\lambda_i(x_i,\zeta_i,y_i)=\frac{x_i-\zeta_i (1-y_i)}{\zeta_i+1}$
-
----
-
-**Properties**:
-
-- 3<sup>rd</sup> $y_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 4<sup>th</sup>. Changes in $\zeta_i$ - and as a corrollary $\Omega_i$ - is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\alpha_i$
-
----
-
-### Rigged election example 2: applying hybrid form
-
-- Setting for eaching precinct the first three parameters
- - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
- - $h_i=\frac{s_i}{s_i+v_i}$ (true observations)
- - $g_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(h_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
-- Backsolve form
- - $\Gamma_i(g_i,\alpha_i,h_i)=\frac{g_i-\alpha_i}{\alpha_i-h_i}$
- - $\Omega_i(g_i,\Gamma,h_i)=-\alpha_i+\frac{\Gamma_i+2g_i}{\Gamma_i+1}$
-
----
-
-**Properties**:
-
-- 5<sup>th</sup> $y_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 6<sup>th</sup> Changes in $\Gamma_i$ - and as a corrollary $\lambda_i$ - is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\alpha_i$
-
----
-
-### Rigged election example 3: applying opposition form
-
-- Setting for eaching precinct the first three parameters
- - $\lambda_i=<...>$ (i.e., equal or less than the prefered election outcome)
- - $n_i=\frac{a_i}{a_i+c_i}$ (true observations)
- - $m_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(n_i,\lambda_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_{t_i} \sim N(0,\sigma^2)$
-- Backsolve for
- - $\Omega_i(n_i,m_i,\lambda_i) = \frac{\lambda_i(n_i-m_i)-m_i(2n_i-1)}{1-(n_i+m_i)}$
- - $\xi_i(n_i,m_i,\Omega_i)=\frac{m_i-\Omega_i}{\Omega_i-n_i}$
-
----
-
-**Properties**:
-
-- 7<sup>th</sup> $m_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 8<sup>th</sup> Changes in $\xi_i$ is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\lambda_i$
-
----
-
-**Setting the prefered election outcome**
-
-:::: {.columns}
-
-::: {.column width="50%"}
-
-Non-rigged election using standard form
-```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
-app_n_out[[4]] 
-```
-
-:::
-
-::: {.column width="50%"}
-
-Rigged election using standard form
-```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
-app_ex1_out[[4]] 
-```
-:::
-
-::::
-
----
-
-**Normal**
-<br>
-\begin{equation*}
-f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
-\end{equation*}
-
-Election outome
-```{r, echo=F}
-sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
-```
-
-<br>
-**Rigged**
-<br>
-
-$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
-
-Election outome
-```{r, echo=F}
-sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
-```
-
----
-
-## `r metad$toc$sec2$unm[5]`
-
-- Loss function
-  - $M(,)=$x+y$
-    - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
-    - Also: Euler rotation
-  - System approach Demands mulitvariate Manifold Equations
-    - Abc
-    - Def
-  - Constrain on implementation
-    - Flipping votes on one mode
-    - Vote registration until upper limit
-
----
-
-```{r, echo=F, out.width="80%", fig.cap=""}
-bI <- paste0(rprojroot::find_rstudio_root_file(),'pngs/loss_5_conditions.png')
-knitr::include_graphics(bI)
-```
-
-# `r metad$toc$sec3$nmn`
-
-## `r metad$toc$sec3$unm[1]`
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_n_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_n_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['resp']]
-```
-
-:::
-
-## `r metad$toc$sec3$unm[2]`
-
-**Example 1: Normal form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex1_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex1_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['resp']]
-```
-
-:::
-
-##
-
-**Example 2: applying hybrid form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex2_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex2_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['resp']]
-```
-
-:::
-
-##
-
-**Example 3: applying opposition form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex3_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex3_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['resp']]
-```
-
-:::
-
-# `r metad$toc$sec4$nmn` {#litrev}
-
-```{r, echo=FALSE, out.width="20%", fig.cap=""}
-p1 <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/ss.png')
-knitr::include_graphics(c(p1))
-```
-
----
-
-`r #Citet(bib, "delfino2011analysis")`
-
-> Abstract: On August 15th, **2004**, Venezuelans had the opportunity to vote
-in a Presidential Recall Referendum **to decide whether or not President Hugo
-Chávez should be removed from office.** **The process was largely computer-
-ized using a touch-screen system.** In general the ballots were not manually
-counted. The significance of the high linear correlation (0.99) between the
-number of requesting signatures for the recall petition and the number of op-
-position votes in computerized centers is analyzed. The same-day audit was
-found to be not only ineffective but a source of suspicion...
-
-::: aside
-[Link to Youtube-video](https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s)
-:::
-
-##
-
-- Venezuela referendum to recall President Hugo Chávez (2004)
-	- Mode 1: Computerized Voting Centers
-	- Mode 2: Manuel Voting Centers
-
-> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.
-
-```{r, echo=FALSE, out.width="85%", fig.cap=""}
-p3 <- paste0(rprojroot::find_rstudio_root_file(),'pngs/manifold.png')
-knitr::include_graphics(c(p3))
-```
-
-# `r metad$toc$sec5$nmn` {#proced}
-
-# `r metad$toc$sec5$unm[1]`
-
-1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
-1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
-1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
-1. Check for normality of the estimated residual for the Manifold model.
-
-If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.
-
-[Application 3: Rigged election analyzer]({{< var shn3 >}})
-
-# `r metad$toc$sec6$nmn`
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="1")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
----
-
-# `r metad$toc$sec7$nmn`
-
-[Application 4: Restoration of a rigged election]({{< var shn4 >}})
-
----
-
-# `r metad$toc$sec8$nmn`
-
-- At the heart of the difference between a fair and rigged election is the issue of causation
-  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
-  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
-
-- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
-	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
-	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
-
-##
-
-- Condition on that $R^2$ falls within the critical region.
-  - Normal form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2n.png')
-knitr::include_graphics(c(pr2n))
-```
-
- - Hybrid form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2h.png')
-knitr::include_graphics(c(pr2h))
-```
-
-- Our four applications
-
-```{r, echo=F, warning=F, message=F}
-kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-# `r metad$toc$sec9$nmn`
-
-::: {#refs}
-:::
-
-```{r}
-knitr::knit_exit()
-```

### 2024-01-27 presentation.qmd
starwork
break

@@
     toc: true 
+execute: 
+  cache: false
 #webr: 
@@
 ```
-```{r}
-knitr::knit_exit()
-```
 
@@
 
-- Loss function
+- Specify a loss function
+  - $\sum_{p=1}^{P}(\alpha_p-\overline{\alpha})^2$
 - $M(,)=$x+y$
@@
 - System approach Demands mulitvariate Manifold Equations
-    - Abc
-    - Def
+  - Univariate manifold Equation
+  - Multivariate Manifold Equations
 - Constrain on implementation
@@
 
+# `r metad$toc$sec6$nmn`
+
 ```{r}
@@
 ```
-
-# `r metad$toc$sec6$nmn`
 

### 2024-01-27 R/wasmconverting.R

@@ -1,6 +1,6 @@
 #' @export wasmconload
 wasmconload <- function(){
-  ifelse(Sys.info()[['sysname']]=="Emscripten", 
+  ifelse(Sys.info()[['sysname']]=="Emscripten",
   {
       # Commands to be executed if the condition is TRUE
       webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
@@ -28,9 +28,9 @@ wasmconload <- function(){
   library(AlgebraicHaploPackage)
 }
 #########################################################################################################################################################
-#' @export py_polysolverW
+# ' @export py_polysolverW
 #py_polysolverW <- function(degree=1,kvec=NULL){
-#  vec <- kvec[!is.na(kvec)] 
+#  vec <- kvec[!is.na(kvec)]
 #  # Linear
 #  if (degree==1) {
 #    retv <- Re(AlgebraicHaploPackage::cubic(A=vec[1],B=vec[2],C=0,D=0))[1]
@@ -47,18 +47,18 @@ wasmconload <- function(){
 manobj <- function(enfl=NULL,dfa=NULL,svar='y'){
   polyc <- setNames(as.vector(lapply(enfl, as.character)),LETTERS[1:5])
   la_e <- unlist(polyc[c(LETTERS[1:5])])
-  pnr <- sum(la_e!="0") 
+  pnr <- sum(la_e!="0")
   rootdf <- dfa  %>%
     dplyr::mutate(A=pareq(la_e[1],c(as.list(.[,])))) %>%
     dplyr::mutate(B=pareq(la_e[2],c(as.list(.[,])))) %>%
-    dplyr::mutate(C=pareq(la_e[3],c(as.list(.[,])))) %>% 
-    dplyr::mutate(D=pareq(la_e[3],c(as.list(.[,])))) %>% 
+    dplyr::mutate(C=pareq(la_e[3],c(as.list(.[,])))) %>%
+    dplyr::mutate(D=pareq(la_e[3],c(as.list(.[,])))) %>%
     dplyr::mutate(E=pareq(la_e[3],c(as.list(.[,])))) %>%
     dplyr::group_by(P) %>%
     #dplyr::mutate(polsolv=py_polysolverW(pnr-1,c(A,B,C,D,E)[1:pnr])) %>%
[…]

### 2024-01-27 data-raw/labeling.R

@@ -8,7 +8,7 @@ library(DataEditR)
 # Metad
 ###############################################################################################################
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-usethis::use_data(metad,overwrite=TRUE)
+usethis::use_data(md,overwrite=TRUE)
 ################################################################################################################
 # Model
 ###############################################################################################################

### 2024-01-28 script/R/simulations.R
abc

@@ -1,6 +1,5 @@
 set.seed(1)
 ManifoldDestiny::wasmconload()
-
 #######################################################################################################################################################
 ##### Proto example 1 and 2
 P  <- c(1,2,3,4,5,6)
@@ -71,23 +70,12 @@ app_ex1_cou <- Countinggraphs(app_bal)
 pri_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
 app_ex1_cou$mansys(sygen=list(frm=1,
 			      pre=c("alpha","x","y"),
-			      end=c("zeta","lamda"),
+			      end=c("zeta","lamda","Omega"),
 			      me=c(plnr=1,rot=0),
 			      lf="(alpha-alpha_s)^2"))
-app_ex1_cou$setres(0.17,1)
-app_ex1_cou$enf[[1]]
+app_ex1_cou$setres(0.19,1)
 pos_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
 app_ex1_cou$manimp(init_par=c(k0=0.0,k1=0.50,k2=0.50),wn=c(0,0),man=TRUE)
-sum(app_ex1_cou$rdfc[c('S','U')])/sum(app_ex1_cou$rdfc[c('S','T','U','V')])
-
-
-
-View(app_ex1_cou$loss_df)
-mean(Countingprocess(dplyr::select(app_ex1_cou$rdfc,P,R,S,T,U,V))$rdfci$alpha)
-
-sum(app_ex1_cou$loss_df$U-app_ex1_cou$loss_df$U_m)
-sum(app_ex1_cou$loss_df$V-app_ex1_cou$loss_df$V_m)
-
 app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
 app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
 ######## Rigged example 2: hybrid form
@@ -95,10 +83,10 @@ app_ex2_cou <- Countinggraphs(app_bal)
 pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
 app_ex2_cou$mansys(sygen=list(frm=2,
 			      pre=c("alpha","h","g"),
-			      end=c("Gamma","Omega"),
+			      end=c("Gamma","Omega","lamda"),
[…]

### 2024-01-28 R/wasmconverting.R
break

@@ -445,6 +445,7 @@ Countingprocess <- setRefClass("Countingprocess",
 					   gensysl='list',
 					   exnrs='vector',
 					   allvar='list',
+					   allstuv='list',
 					   loss_df='data.frame',
 					   loss_ls='list'
 					   ))
@@ -601,6 +602,7 @@ Countingprocess$methods(mansys=function(sygen=NULL){
   mansysl <<- sygen
   sho <- c("_s","_h","_o")[[mansysl$frm]]
   allvar <<- list(pre=mansysl$pre,end=mansysl$end)
+  allstuv <<- list(mansysl$stuv)
   exnrs <<- gsub('v',mansysl$pre[2], gsub('u',mansysl$pre[3],peqs[mansysl$me[['plnr']]]))
   enf[[1]] <<- unname(stats::predict(polyc[[mansysl$frm]]))
   enf[[2]] <<- eqpar$meqs[[paste0(mansysl$pre[2],sho)]]
@@ -629,6 +631,7 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
   ## Variables
   lof <- function(kvec=NULL){
     names(kvec) <- paste0("k",seq(0,length(kvec)-1))
+    #View(loss_df)
     loss_df <<- rdfci %>%
       dplyr::select(P,R,S,T,U,V,Z,all_of(allvec)) %>%
       data.table::setnames(allvec,altvec) %>%
@@ -650,13 +653,15 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
       dplyr::mutate(!!allvec[6]:=pareq(se[[endp[2]]][2],c(as.list(.[,])))) %>%
       dplyr::mutate(LSV:=pareq(mansysl$lf,c(as.list(.[,])))) %>%
       ##### Backsolving for ballots
-      dplyr::mutate(S_m=pareq(se[[paste0('S',sho)]][1],as.list(.[])))  %>%
-      dplyr::mutate(T_m=pareq(se[[paste0('T',sho)]][1],as.list(.[])))  %>%
-      dplyr::mutate(U_m=floor(pareq(se[[paste0('U',sho)]][1],as.list(.[]))))  %>%
-      dplyr::mutate(V_m=floor(pareq(se[[paste0('V',sho)]][1],as.list(.[]))))  %>%
+      dplyr::mutate(!!stuv[1]:=pareq(se[[paste0('S',sho)]][1],as.list(.[])))  %>%
[…]

### 2024-01-28 script/R/simulations.R

@@ -71,6 +71,7 @@ pri_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
 app_ex1_cou$mansys(sygen=list(frm=1,
 			      pre=c("alpha","x","y"),
 			      end=c("zeta","lamda","Omega"),
+			      stuv=c("S","T","U","V"),
 			      me=c(plnr=1,rot=0),
 			      lf="(alpha-alpha_s)^2"))
 app_ex1_cou$setres(0.19,1)
@@ -80,14 +81,16 @@ app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
 app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
 ######## Rigged example 2: hybrid form
 app_ex2_cou <- Countinggraphs(app_bal)
-pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
+pri_int_ex2 <- app_ex2_cou$polyc[[2]][[1]]
 app_ex2_cou$mansys(sygen=list(frm=2,
 			      pre=c("alpha","h","g"),
 			      end=c("Gamma","Omega","lamda"),
+			      stuv=c("S","T","U","V"),
 			      me=c(plnr=1,rot=0),
 			      lf="(alpha-alpha_h)^2"))
 app_ex2_cou$setres(0.19,0)
-pos_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
+pos_int_ex2 <- app_ex2_cou$polyc[[2]][[1]]
+app_ex2_o <- Countinggraphs(app_ex2_cou$rdfc)
 app_ex2_cou$manimp(init_par=c(k0=0.0,k1=0.50,k2=0.50),wn=c(0,0),man=TRUE)
 app_ex2_out <- seloutput(selreport(app_ex2_cou$rdfc,md$app0))
 app_ex2_sim <- SimVoterdatabase(app_ex2_cou$rdfc)
@@ -97,7 +100,8 @@ pri_int_ex3 <- app_ex3_cou$polyc[[1]][[1]]
 app_ex3_cou$sortpre()
 app_ex3_cou$mansys(sygen=list(frm=1,
 			      pre=c("alpha","x","y"),
-			      end=c("zeta","lamda"),
+			      end=c("zeta","lamda","Omega"),
+			      stuv=c("S","T","U","V"),
 			      me=c(plnr=1,rot=0),
[…]

### 2024-02-03 R/wasmconverting.R
delcom

@@ -632,6 +632,8 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
   lof <- function(kvec=NULL){
     names(kvec) <- paste0("k",seq(0,length(kvec)-1))
     print(kvec)
+    #browser()
+    #View(loss_df)
     loss_df <<- rdfci %>%
       dplyr::select(P,R,S,T,U,V,Z,all_of(allvec)) %>%
       data.table::setnames(allvec,altvec) %>%
@@ -654,11 +656,11 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
       dplyr::mutate(LSV:=pareq(mansysl$lf,c(as.list(.[,])))) %>%
       ##### Backsolving for ballots
       ## Observatinal values
-      dplyr::mutate(!!stuv[1]:=pareq(se[[paste0('S',sho)]][1],as.list(.[])))  %>%
-      dplyr::mutate(!!stuv[2]:=pareq(se[[paste0('T',sho)]][1],as.list(.[])))  %>%
+      dplyr::mutate(!!paste0(stuv[1],'_m'):=pareq(se[[paste0(stuv[1],sho)]][1],as.list(.[])))  %>%
+      dplyr::mutate(!!paste0(stuv[2],'_m'):=pareq(se[[paste0(stuv[2],sho)]][1],as.list(.[])))  %>%
       ## Changed ballots
-      dplyr::mutate(!!stuv[3]:=floor(pareq(se[[paste0('U',sho)]][2],as.list(.[]))))  %>%
-      dplyr::mutate(!!stuv[4]:=floor(pareq(se[[paste0('V',sho)]][2],as.list(.[]))))  %>%
+      dplyr::mutate(!!paste0(stuv[3],'_m'):=floor(pareq(se[[paste0(stuv[3],sho)]][2],as.list(.[]))))  %>%
+      dplyr::mutate(!!paste0(stuv[4],'_m'):=floor(pareq(se[[paste0(stuv[4],sho)]][2],as.list(.[]))))  %>%
       #! other options
       dplyr::mutate(Z_m=S_m+T_m+U_m+V_m) %>%
       dplyr::mutate(R_m=R) %>%
@@ -675,7 +677,7 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
   }
   # Init
[…]

### 2024-02-11 presentation.qmd
break
abc
mone
worknow

@@
 ---
-title: "Manifold Destiny - or how to rig an election"
-subtitle: "Based upon the ideas developed by Edward K. Solomon"
-format:
-  revealjs: 
-    smaller: true
-    toc-depth: 1
-    toc: true 
-execute: 
-  cache: false
+title: Manifold Destiny - or how to rig an election
+#subtitle: "Based upon the ideas developed by Edward K. Solomon"
+#format:
+#  revealjs: 
+#    smaller: true
+#    toc-depth: 1
+#    toc: true 
+#execute: 
+#  cache: false
 #webr: 
@@
 
-**Our two stylized numerical example**
+**Our two stylized numerical cases**
 
@@
 ```{r, echo=F}
-#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
-polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
+#pri_int_ex1
+#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
+mean(app_ex1_cou$rdfc$alpha)
 ```
@@
 ```{r, echo=F}
-#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
-polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
+#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
+pos_int_ex1
 ```
@@
 
+```{r}
+knitr::knit_exit()
+```
+
 **Setting the prefered election outcome**
@@
 ---
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-02-11 abc.R

@@ -17,4 +17,14 @@ ui <- fluidPage(
 server <- function(input, output) {}
 
 shinyApp(ui, server)
-#
+
+tekst <- "Først, det med pengemengdevekst blir i liten grad lært bort til studentene fordi de fleste læreboker ikke dekker dette. Men til tross for dette, har jeg selv dekket temaet de gangene jeg underviste i makroøkonomi (vil DM mine notater). Dersom inflasjonsmålet er på 2 prosent og det ikke skjer teknologisk framgang, bør også pengemengdeveksten være på 2 prosent (noe som gir eksponsiell vekst) dersom man kommuniserer at man skal oppfylle dette målet (i pengepolitikk bør .Generelt vil en økning i pengemengden omdirigere ressurstene i økonomien på en raskere måte. Det er mulig her å peke situasjoner hvor dette er nyttig:1. Raskere kunne starte opp nye bedrifter som tar i bruk nye og moderne teknologi 2. En økonomisk opphenting etter en stor nedgangskonjunktur vil gå raskere 3. Holde i livet sektorer som er konkurstruede, men hvor det anses som samfunnsnyttig nyttig at kunnskapen som bedriftene besitter ikke spres for vær og vind ved en konkurs. 4. Økte investeringer kommer på bekostning av konsum, og dermed på lang sikt gir økonomisk vekst. 1. Få for stor investering i ulønnsome prosjekter 2. Omfordelignseffekt 3. Holde i live ulønnsomme bedrifter I bunn og grunnn vil en effektiv pengepolitkk gå ut på å balansere alle disse hensynene. Er selv ingen styringsoptimist på dette området, og ønsker derfor i størst mulig grad en forutsigbar pengepolitkk. Mener vi har to gode eksempler som viser at det kan gå galt begge veier. - Strupingen av pengemengden etter bankkrisen 1929 som forlenget den store depresjonene. - Økningen i pengemengden under pandemien(?) i perioden. 2020-2022, som delvis forklarer den  høye inflasjonen som vi har i dag."
+
+
+
+cat(chatgpt::ask_chatgpt(paste0("Fiks språk: ",tekst)))
+
+
+
+
+

### 2024-02-15 paper.qmd
delcom
mone
running

@@
 
+```{r}
+knitr::knit_exit()
+```
+
 ```{r, echo=FALSE, results='asis',warning=F}
-presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
-textm <- readLines(presm)
-cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
+#presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
+#textm <- readLines(presm)
+#cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
 ```

### 2024-04-27 index.qmd
abc

@@
 ![](pngs/md.png)
+
+```{mermaid}
+%% R/wasmconverting.R
+%%| echo: false
+classDiagram
+    note for abc "a"
+    note for cde "b"
+    note for fgh "c"
+    class SimVoterdatabase{
+        +field1
+        +abc1()
+    }
+    class Abc{
+        +field1
+        +abc1()
+    }
+    class Def{
+        +field1
+        +abc1()
+    }
+    class Ghi{
+        +field1
+        +abc1()
+    }
+    Initmodelnum --|> Abc
+    Initmodelnum --|> Def
+    Initmodelnum --|> Ghi
+```
+
+```{mermaid}
+%% R/wasmconverting.R
+%% Countinggraphs 
+%%| echo: false
+classDiagram
+    note for abc "a"
+    note for cde "b"
+    note for fgh "c"
+    class Countingprocess{
+        +field1
+        +abc1()
+    }
+    class Abc{
+        +field1
+        +abc1()
+    }
+    class Def{
+        +field1
+        +abc1()
+    }
+    class Ghi{
+        +field1
+        +abc1()
+    }
+    Initmodelnum --|> Abc
+    Initmodelnum --|> Def
+    Initmodelnum --|> Ghi
+    class Countinggraphs{
+        +field1
+        +abc1()
+    }
+```
+
+```{mermaid}
+%% R/wasmconverting.R
+%% Countinggraphs 
+%%| echo: false
+classDiagram
+    note for abc "a"
+    note for cde "b"
+    note for fgh "c"
+    class Estimation{
+        +field1
+        +abc1()
+    }
+    class Abc{
+        +field1
+        +abc1()
+    }
+    class Def{
+        +field1
+        +abc1()
+    }
+    class Ghi{
+        +field1
+        +abc1()
+    }
+    Initmodelnum --|> Abc
+    Initmodelnum --|> Def
+    Initmodelnum --|> Ghi
+```
+
+**Last time updated: `r as.Date(Sys.time())`**
+
+```{r, echo=F}
+knitr::knit_exit()
+```
 
@@
 ```
-
-**Last time updated: `r as.Date(Sys.time())`**
-
-```{r, echo=F}
-knitr::knit_exit()
-```

### 2024-04-27 abc.py

@@ -1,4 +1,7 @@
-def greet(name):
-  print("Hello, " + name + "!")
+from libqtile import qtile
 
+if qtile.core.name == "x11":
+    term = "kitty"
+elif qtile.core.name == "wayland":
+    term = "kitty"
 

### 2024-07-06 docs/randpython.qmd
var

--- 2024-01-07 abc.qmd
@@
 ---
-title: "econ"
-#format: 
-#  html:
-#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
-#    include-in-body:
-#          - text: |
-#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
+title: "R and Python integration"
 ---
-<head>
-      <link rel="stylesheet" href="https://kineticgraphs.org/css/kg.0.2.7.css">
-      <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
-</head>
 
-<body>
-<div class="kg-container">
-schema: EconSchema
-  layout:
-    OneGraph:
-      graph:
-        xAxis: 
-          title: "Good 1"
-        yAxis: 
-          title: "Good 2"
-        objects: 
-        - EconBudgetLine:
-            p1: 1
-            p2: 2
-            m: 8
-            label: {text: M, location: 0.9}
-</div>
-</body>
+[Coatless](https://www.youtube.com/watch?v=PZx9d21HnTo)
 
-```{r, eval=T}
-knitr::knit_exit()
-```
+@thecoatlessprofessor7674
+1 month ago
+Great question. The short gist is yes in the *interactive* context for now.
+
+We'll likely need to make another extension that wraps before {quarto-webr} and {quarto-pyodide} to enable cross talk in the *non-interactive**/**output* contexts.
+
+# Python
 
@@
 
-```{r}
-knitr::knit_exit()
-```
+# R
 
-::: {.kg-container}
-schema: EconSchema
-layout:
-  OneGraph:
-    graph:
-      xAxis: 
-        title: "Good 1"
-      yAxis: 
-        title: "Good 2"
-      objects: 
-      - EconBudgetLine:
-          p1: 1
-          p2: 2
-          m: 8
-          label: {text: M, location: 0.9}
-:::
+<div>
+  <pre><code id="out">Loading webR, please wait...</code></pre>
+  <input spellcheck="false" autocomplete="off" id="input" type="text">
+  <button onclick="globalThis.sendInput()" id="run">Run</button>
+</div>
 
-#! fix deviation from mean
-import sympy, pandas, numpy
-from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
-def rall(sel=[0, 0, 0]):
-    n, m = symbols('n m')
+<script type="module">
+  /* Create a webR console using the Console helper class */
+  import { Console } from 'https://webr.r-wasm.org/latest/webr.mjs';
+  const webRConsole = new Console({
+    stdout: line => document.getElementById('out').append(line + '\n'),
+    stderr: line => document.getElementById('out').append(line + '\n'),
+    prompt: p => document.getElementById('out').append(p),
+  });
+  webRConsole.run();
 
-    rxy = Matrix([[m, -n, 0], 
-                  [n, m, 0],
-                  [0, 0, 1]])
+  /* Write to the webR console using the ``stdin()`` method */
+  let input = document.getElementById('input');
+  globalThis.sendInput = () => {
+    webRConsole.stdin(input.value);
+    document.getElementById('out').append(input.value + '\n');
+    input.value = "";
+  }
 
-    rxz = Matrix([[m, 0, -n], 
-                  [0, 1, 0],
-                  [n, 0, m]])
-
-    ryx = Matrix([[m, n, 0], 
-                  [-n, m, 0],
-                  [0, 0, 1]])
-
-    ryz = Matrix([[1, 0, 0], 
-                  [0, m, -n],
-                  [0, n, m]])
-
-    rzx = Matrix([[m, 0, n], 
-                  [0, 1, 0],
-                  [-n, 0, m]])
-
-    rzy = Matrix([[1, 0, 0], 
-                  [0, m, n],
-                  [0, -n, m]])
-
-    ps = [0, rxy, rxz, ryx, ryz, rzx, rzy]
-
-    allrot = [ps[i] for i in sel]
-    return allrot
-
-def genpolycoeff(expr=None, solvd='z', solvf='u0', eur=[1, 4, 2], plr=3,dnr=2):
-    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
-    x, y, z = sympy.symbols('x y z')
-    sum_eur = sum(eur)
-    # Without rotation
-    if sum_eur == 0:
-        exprc = expr + '-' + solvd
-        asexpr = sympify(exprc)
-        polys = poly(asexpr, sympify(solvf)).all_coeffs()
-        abc = []
-        uvw = []
-        ABCDE = [0, 0, 0, 0, 0]
-        ABCDE[:len(polys)] = polys
-        return ABCDE, abc, uvw
-    # With rotation
-    else:
-        expr = ['k0+k1*x+k2*y', 'k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2', 'k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3'][plr-1]
-        dxyz = {'x': 1, 'y': 2, 'z': 3}
-        # Defining
-        x,  y,  z  = sympy.symbols('x y z')
-        ui, vi, wi = sympy.symbols('ui vi wi')
-        u0, v0, w0 = sympy.symbols('u0 v0 w0')
-        u1, v1, w1 = sympy.symbols('u1 v1 w1')
-        u2, v2, w2 = sympy.symbols('u2 v2 w2')
-        a1, a2, a3 = sympy.symbols('a1 a2 a3')
-        b1, b2, b3 = sympy.symbols('b1 b2 b3')
-        c1, c2, c3 = sympy.symbols('c1 c2 c3')
-        m1, m2, m3 = sympy.symbols('m1 m2 m3')
-        n1, n2, n3 = sympy.symbols('n1 n2 n3')
-        mu, mv, mw = sympy.symbols('mu mv mw')
-        # Replace
-        PS = rall(sel=eur)
-        r0 = Matrix([u0, v0, w0])
-        r1 = PS[0].subs([(n, n1), (m, m1)]) * r0
-        r2 = PS[1].subs([(n, n2), (m, m2)]) * r1
-        RR = PS[2].subs([(n, n3), (m, m3)]) * r2
-        sympy.expand(RR.row(0)[0])
-        sympy.expand(RR.row(1)[0])
-        sympy.expand(RR.row(2)[0])
-        av = sympy.collect(sympy.expand(RR.row(0)[0]), (u0, v0, w0))
-        bv = sympy.collect(sympy.expand(RR.row(1)[0]), (u0, v0, w0))
-        cv = sympy.collect(sympy.expand(RR.row(2)[0]), (u0, v0, w0))
-        a1s = av.coeff(u0)
-        a2s = av.coeff(v0)
-        a3s = av.coeff(w0)
-        b1s = bv.coeff(u0)
-        b2s = bv.coeff(v0)
-        b3s = bv.coeff(w0)
-        c1s = cv.coeff(u0)
-        c2s = cv.coeff(v0)
-        c3s = cv.coeff(w0)
-        Eu = Eq(x, a1s * u0 + a2s * v0 + a3s * w0)
-        Ev = Eq(y, b1s * u0 + b2s * v0 + b3s * w0)
-        Ew = Eq(z, c1s * u0 + c2s * v0 + c3s * w0)
-        abc = [a1s, a2s, a3s, b1s, b2s, b3s, c1s, c2s, c3s]
-        # Manual
-        pvar = [w0, v0, u0, w0**2, v0*w0, v0**2, u0*w0, u0*v0, u0**2, w0**3, v0*w0**2, v0**2*w0, v0**2*w0, v0**3, u0*w0**2, u0*v0*w0, u0*v0**2, u0**2*w0, u0**2*v0, u0**3]
-        # Connect to rotmat
-        Eu = Eq(x, a1 * u0 + a2 * v0 + a3 * w0)
-        Ev = Eq(y, b1 * u0 + b2 * v0 + b3 * w0)
-        Ew = Eq(z, c1 * u0 + c2 * v0 + c3 * w0)
-        exprf = sympify(expr + '-' + solvd)
-        exprc = exprf.subs([(x, solve(Eu, x)[0]), (y, solve(Ev, y)[0]), (z, solve(Ew, z)[0])])
-        exprr = collect(expand(exprc), pvar)
-        xr = [] 
-        yr = []
-        zr = []
-        clma = ['u0','v0','w0','d','var','expr','expr2']
-        eqsn = len(exprr.args)
-        data = [["0"] * 7 for _ in range(eqsn)]
-        matarch = pandas.DataFrame(data, columns=clma)
-        matarch.loc[0, ['expr','expr2']]=exprr.args[0]
-        matarch.loc[0, ['d']]='d_000'
-        for i in range(1, eqsn):
-            expt = exprr.args[i]
-            expr = expt.args[-1]
-            varn = expt / expr
-            nrfs = len(varn.free_symbols)
-            matarch.loc[i, 'var'] = str(varn)
-            for j in range(0,nrfs):
-                varn = expt.args[j].as_base_exp()[0]
-                pown = expt.args[j].as_base_exp()[1]
-                matarch.loc[i, str(varn)] = pown
-            subd = {a1: a1s, a2: a2s, a3: a3s,b1: b1s, b2: b2s, b3: b3s,c1: c1s, c2: c2s, c3: c3s}
-            matarch.loc[i, 'expr'] = expr
-            matarch.loc[i, 'expr2'] = expr.subs(subd) 
-            cmbx = int(matarch.loc[i, 'u0'])
-            cmby = int(matarch.loc[i, 'v0'])
-            cmbz = int(matarch.loc[i, 'w0'])
-            dr = sum([cmbx, cmby, cmbz])
-            matarch.loc[i,'d']='d_'+"".join([str(dr),str(cmbx),str(cmby)])
-    dic1 = matarch.set_index('d')['expr'].to_dict()
-    dic2 = matarch.set_index('d')['expr2'].to_dict()
-    dic = [dic1,dic2][0]
-    A=[dic['d_330'],
-       dic['d_303'],
-       dic['d_300']]
-    B=[dic['d_320']*z+dic['d_321']*y+dic['d_220'],
-       dic['d_302']*z+dic['d_312']*x+dic['d_202'],
-       dic['d_301']*x+dic['d_310']*y+dic['d_200']]
-    C=[dic['d_310']*z**2+dic['d_311']*y*z+dic['d_312']*y**2+dic['d_210']*z+dic['d_211']*y+dic['d_110'],
-       dic['d_301']*z**2+dic['d_311']*y*z+dic['d_321']*y**2+dic['d_201']*z+dic['d_211']*y+dic['d_101'],
-       dic['d_302']*z**2+dic['d_311']*y*z+dic['d_320']*y**2+dic['d_201']*z+dic['d_210']*y+dic['d_110']]
-    D=[dic['d_300']*z**3+dic['d_301']*y*z**2+dic['d_302']*y**2*z+dic['d_303']*y**3+dic['d_200']*z**2+dic['d_201']*y*z+dic['d_202']*y**2+dic['d_100']*z+dic['d_101']*y+dic['d_000'],
-       dic['d_300']*z**3+dic['d_310']*y*z**2+dic['d_320']*y**2*z+dic['d_330']*y**3+dic['d_200']*z**2+dic['d_210']*y*z+dic['d_220']*y**2+dic['d_100']*z+dic['d_110']*y+dic['d_000'],
-       dic['d_303']*z**3+dic['d_312']*y*z**2+dic['d_321']*y**2*z+dic['d_330']*y**3+dic['d_202']*z**2+dic['d_211']*y*z+dic['d_220']*y**2+dic['d_101']*z+dic['d_110']*y+dic['d_000']]
-    E=[0,0,0,0]
-    nrs = dxyz[solvd]-1
-    ABCDE = [0, 0, 0, 0, 0]
-    ABCDE[0] = str(A[nrs])
-    ABCDE[1] = str(B[nrs])
-    ABCDE[2] = str(C[nrs])
-    ABCDE[3] = str(D[nrs])
-    ABCDE[4] = str(E[nrs])
-    msl = ['u0','v0','w0','expr','expr2']
-    matarch[msl]=matarch[msl].astype(str)
-    return ABCDE, matarch, abc
-
-<head>
-      <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
-</head>
-<body>
-    Pyodide test page <br>
-    Open your browser console to see Pyodide output
-    <script type="text/javascript">
-      async function main(){
-        let pyodide = await loadPyodide();
-        console.log(pyodide.runPython(`
-            import sys
-            sys.version
-        `));
-        pyodide.runPython("print(1*5)");
-      }
-      main();
+  /* Send input on Enter key */
+  input.addEventListener(
+    "keydown",
+    (evt) => {if(evt.keyCode === 13) globalThis.sendInput()}
+  );
 </script>
-</body>
-
-<p id=ary></p>
-<p id=nmb></p>
-<p id=str></p>

### 2024-07-06 index.qmd
break
ab
var

--- 2024-01-07 index.qmd
@@
 ![](pngs/md.png)
+
+**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
+
+```{r, echo=F}
+knitr::knit_exit()
+```
+
+```{mermaid}
+%%| echo: false
+classDiagram
+    note "From Duck1 till Zebra"
+    note for SimVoterdatabase "can fly\ncan swim\ncan dive\ncan help in debugging"
+    class SimVoterdatabase{
+        +field1
+        +abc1()
+    }
+    class Countingprocess{
+        +field1
+        +abc1()
+    }
+    class Countinggraphs{
+        +field1
+        +abc1()
+    }
+    class Estimation{
+        +field1
+        +abc1()
+    }
+    Countingprocess --|> Countinggraphs
+```
+
+**Last time updated: `r as.Date(Sys.time())`**
+
+```{r, echo=F}
+knitr::knit_exit()
+```
 

### 2024-07-06 R/wasmnonverting.R

@@ -35,6 +35,8 @@ bm <- function(){
    devtools::document()
    system(paste0('cd ',rprojroot::find_rstudio_root_file(),'; R CMD INSTALL --preclean --no-multiarch --with-keep.source .'))
 }
+
+
 #' @export k
 k <- function(){
     df <-  clipr::write_last_clip()
@@ -56,6 +58,7 @@ l <- function(){
 
 #' @export recoudatr
 recoudatr <- function(mda=NULL){
+	browser()
   gsh <- googlesheets4::read_sheet(mda$sht$url,sheet=mda$sht$pgn,range=mda$sht$rng) %>%
     data.table::setnames(new=mda$sht$cln) %>%
     dplyr::select(-starts_with('D')) %>%

### 2024-07-06 data-raw/county_recorder.R

@@ -8,8 +8,9 @@ library(usethis)
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-#googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
-#gs4_auth()
+googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
+gs4_auth()
+
 lapply(paste0("app",1:4), function(x){recoudatr(mda=md[[x]])})
 
 

### 2024-07-06 index.qmd
upd

--- 2024-01-07 index.qmd
@@
 ---
-
-# Manifold Destiny - or how to rig an election
-**Based upon the ideas developed by Edward K. Solomon**
-![](pngs/md.png)
-
-### Install and load packages
-```{webr-r}
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install(c("AlgebraicHaploPackage","cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
-library(ManifoldDestinyWASMP)
-ls(package:ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-ls(package:ManifoldDestinyWASMD)
-library(magrittr)
-md <- ManifoldDestinyWASMD::metad
-library(dplyr)
-library(combinat)
-library(htmltools)
-library(ggplot2)
-library(broom)
-library(tidyr)
-library(combinat)
-library(AlgebraicHaploPackage)
-```
-
-### Simulation
-```{webr-r}
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
-probw <- c(m=0.51,s=0.10)
-probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztech <- c(0,1)	
-app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
-SimVoterdatabase(app_bal)
-app_n_rep <- selreport(app_bal,md$app0)
-app_n_out <- seloutput(app_n_rep)
-app_n_sim <- SimVoterdatabase(app_bal)
-```
-
-#### Normal
-```{webr-r}
-app_n_rep <- selreport(app_bal,md$app0)
-app_n_out <- seloutput(app_n_rep)
-app_n_sim <- SimVoterdatabase(app_bal)
-```
-
-#### Functions
-```{webr-r}
-2+2
-```
-
-#### Rig 1: Normal
-```{webr-r}
-app_ex1_cou <- Countinggraphs(app_bal)
-print(app_ex1_cou$polyc[[1]][[1]])
-app_ex1_cou$sortpre()
-app_ex1_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
-app_ex1_cou$setres(0.23,0)
-app_ex1_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),TRUE,wn=c(0,0))
-app_ex1_out <- seloutput(selreport(app_ex1_cou$rdfc,md$app0))
-app_ex1_sim <- SimVoterdatabase(app_ex1_cou$rdfc)
-```
-
-#### Rig 2: Hybdrid
-```{webr-r}
-app_ex2_cou <- Countinggraphs(app_bal)
-pri_int_ex2 <- app_ex2_cou$polyc[[1]][[1]]
-print(app_ex2_cou$polyc[[1]][[1]])
-app_ex2_cou$sortpre()
-app_ex2_cou$mansys(sygen=list(frm=2,pre=c("alpha","g","h"),end=c("Gamma","Omega"),FALSE,me=c(plnr=1,rot=0)))
-app_ex2_cou$setres(0.23,0)
-app_ex2_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
-app_ex2_out <- seloutput(selreport(app_ex2_cou$rdfc,md$app0))
-app_ex2_sim <- SimVoterdatabase(app_ex2_cou$rdfc)
-```
-
-#### Rig 3: Opposition
-```{webr-r}
-app_ex3_cou <- Countinggraphs(app_bal)
-pri_int_ex3 <- app_ex3_cou$polyc[[1]][[1]]
-app_ex3_cou$sortpre()
-app_ex3_cou$mansys(sygen=list(frm=1,pre=c("alpha","x","y"),end=c("zeta","lamda"),me=c(plnr=1,rot=0)))
-app_ex3_cou$setres(0.23,0)
-app_ex3_cou$manimp(init_par=c(k0=0.0,k1=0.5,k2=0.5),wn=c(0,0))
-app_ex3_out <- seloutput(selreport(app_ex3_cou$rdfc,md$app0))
-app_ex3_sim <- SimVoterdatabase(app_ex3_cou$rdfc)
-```
-
-### Applications
-
-#### App1
-```{webr-r}
-app1_rp <- selreport(app1,md$app1)
-app_1_out <- seloutput(app1_rp)
-```
-
-#### App2
-```{webr-r}
-app2_rp <- selreport(app2,md$app2)
-app_2_out <- seloutput(app2_rp)
-```
-
-**Last time updated: `r as.Date(Sys.time())`**
-
-```{r, echo=F}
-knitr::knit_exit()
-```

### 2024-07-06 abc.R

@@ -1,37 +1,0 @@
-# R/wasmconverting.R
-ManifoldDestiny::wasmconload()
-source("R/wasmconverting.R")
-library(ggplot2)
-library(dplyr)
-# Abc
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
-probw <- c(m=0.51,s=0.10)
-probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztech <- c(0,1)	
-app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
-########### Normal form
-app_n_rep <- selreport(app_bal,md$app0)
-app_n_out <- seloutput(app_n_rep)
-app_n_sim <- SimVoterdatabase(app_bal)
-########## Rigged example 1: standard form without rotation
-frms <- 1
-plnrvec <- c(1,2,3)[1]
-rotv <- list(list(fr=c(1,10),sr=c(4,0),tr=c(2,0)),list(fr=c(1,14.378100),sr=c(4,49.762610),tr=c(2,11.5781)))[[1]]
-app_ex1_cou <- Countinggraphs(app_bal)
-pri_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
-app_ex1_cou$mansys(sygen=list(frm=frms,
-			      pre=c("alpha","x","y"),
-			      end=c("zeta","Omega","lamda"),
-			      stuv=c("S","T","U","V"),
-			      plnr=plnrvec,
-			      rot=rotv,
-			      lf="(alpha-alpha_s)^2"))
-s1o <- app_ex1_cou$setres(0.19,1)
-app_ex1_cou$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=F)
-pos_int_ex1 <- app_ex1_cou$polyc[[1]][[1]]
-assign("app0nr",app_ex1_cou$loss_df)
-usethis::use_data(app0nr,overwrite = TRUE)
-
-
-

### 2024-07-07 presentation.qmd
running
abc

@@
 ---
-title: Manifold Destiny - or how to rig an election
-#subtitle: "Based upon the ideas developed by Edward K. Solomon"
-#format:
-#  revealjs: 
-#    smaller: true
-#    toc-depth: 1
-#    toc: true 
+title: "Abc"
+subtitle: "Based upon the ideas developed by Edward K. Solomon"
+format:
+  revealjs: 
+    smaller: true
+    toc-depth: 1
+    toc: true 
 #execute: 
@@
 ---
+
+ABC
+
+```{r}
+knitr::knit_exit()
+```
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-07-07 index.qmd
sumupd

@@
   - webr
-format: 
-  html:
-    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
-    include-in-body:
-          - text: |
-              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
+#format: 
+#  html:
+#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
+#    include-in-body:
+#          - text: |
+#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
 ---
+
+# Manifold Destiny - or how to rig an election
+**Based upon the ideas developed by Edward K. Solomon**
+![](pngs/md.png)
+
+**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

### 2024-07-07 presentation.qmd
sumupd

@@
 ---
-title: "Abc"
+title: "{{< var titll >}}"
 subtitle: "Based upon the ideas developed by Edward K. Solomon"
@@
 
-ABC
+# {{< var sec1.nmn >}}
+# {{< var sec2.nmn >}}
+# {{< var sec3.nmn >}}
+# {{< var sec4.nmn >}}
+# {{< var sec5.nmn >}}
+# {{< var sec6.nmn >}}
+# {{< var sec7.nmn >}}
+# {{< var sec8.nmn >}}
+# {{< var sec9.nmn >}}
 

### 2024-07-07 data-raw/recorder.R
abc

@@ -15,10 +15,7 @@ googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
 ################################################################################################################
 mda <- qenvar$app7 
 googlesheets4::sheet_names(mda$url) 
-#abc <- googlesheets4::read_sheet(mda$url,sheet=2,range="A16:P50") 
 recoudatr(qenvar$app7)
-
-
 #md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 #md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
 #md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/_variables.yml"))

### 2024-07-07 index.qmd
abc
templated

@@
   - webr
-#format: 
-#  html:
-#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
-#    include-in-body:
-#          - text: |
-#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
 ---
@@
 **Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
+
+This is a webR-enabled code cell in a Quarto HTML document.
+
+```{webr-r}
+fit = lm(mpg ~ am, data = mtcars)
+summary(fit)
+```
+
+Abc

### 2024-07-07 data-raw/recorder.R

@@ -11,7 +11,7 @@ source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 qenvar <- yaml::yaml.load_file("../_variables.yml")
 googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
-#lapply(qenvar[paste0("app", 0:4)], recoudatr)
+lapply(qenvar[paste0("app", 0:4)], recoudatr)
 ################################################################################################################
 mda <- qenvar$app7 
 googlesheets4::sheet_names(mda$url) 

### 2024-07-07 presentation.qmd
break

--- 2024-07-07 presentation.qmd
@@
 #- webr 
-#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
+footer: <https://lotariohw26.github.io/ManifoldDestiny/>
 ---
 
-ABC
-
-```{r}
-knitr::knit_exit()
-```
-
-```{r}
-knitr::knit_exit()
-```
-
 ```{r, echo=F, message=F, warning=F, results='hide'}
+library(huxtable)
+library(kableExtra)
 #Sys.info()[['sysname']]=="Emscripten"
-ManifoldDestiny::wasmconload()
+#ManifoldDestiny::wasmconload()
 metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 modlat <- eqpar$meql
-library(huxtable)
-library(kableExtra)
 ```
+
+# {{< var sec1.nmn >}}
+Ed. Solomon
+
+> "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
+
+# {{< var sec2.nmn >}}
+# {{< var sec3.nmn >}}
+# {{< var sec4.nmn >}}
+# {{< var sec5.nmn >}}
+# {{< var sec6.nmn >}}
+# {{< var sec7.nmn >}}
+# {{< var sec8.nmn >}}
+# {{< var sec9.nmn >}}
 
@@
 > "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
+
+```{r}
+knitr::knit_exit()
+```
 
@@
 kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+```{r}
+knitr::knit_exit()
 ```

### 2024-07-07 index.qmd
spl

@@
 output: github_document
-always_allow_html: true
 execute: 
   cache: false
+webr:
+  show-startup-message: false      # Display status of webR initialization
+  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
+  packages: ['dplyr','data.table']             # Pre-install dependencies
 filters:
@@
 ---
+
+```{r}
+# script/R/simulations.R
+```
 
@@
 ```{webr-r}
-fit = lm(mpg ~ am, data = mtcars)
-summary(fit)
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
 ```
-
-Abc

### 2024-07-07 randpython.qmd
spl

@@
 ---
-title: "abc"
+title: ""
+output: github_document
+always_allow_html: true
+execute: 
+  cache: false
+filters:
+  - webr
 ---
 
-# Abc
+```{r}
+# script/R/simulations.R
+```
+
+1.
+
+```{webr-r}
+fit = lm(mpg ~ am, data = mtcars)
+summary(fit)
+```
+
+```{r,echo=F}
+knitr::knit_exit()
+```
 
@@
 We'll likely need to make another extension that wraps before {quarto-webr} and {quarto-pyodide} to enable cross talk in the *non-interactive**/**output* contexts.
+
+# Python
+
+<head>
+  <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
+</head>
+
+<body>
+  <p>
+    You can execute any Python code. Just enter something in the box below and
+    click the button.
+  </p>
+  <input id="code" value="sum([1, 2, 3, 4, 5])" />
+  <button onclick="evaluatePython()">Run</button>
+  <br />
+  <br />
+  <div>Output:</div>
+  <textarea id="output" style="width: 100%;" rows="6" disabled></textarea>
+
+  <script>
+    const output = document.getElementById("output");
+    const code = document.getElementById("code");
+
+    function addToOutput(s) {
+      output.value += ">>>" + code.value + "\n" + s + "\n";
+    }
+
+    output.value = "Initializing...\n";
+    // init Pyodide
+    async function main() {
+      let pyodide = await loadPyodide();
+      output.value += "Ready!\n";
+      return pyodide;
+    }
+    let pyodideReadyPromise = main();
+
+    async function evaluatePython() {
+      let pyodide = await pyodideReadyPromise;
+      try {
+        let output = pyodide.runPython(code.value);
+        addToOutput(output);
+      } catch (err) {
+        addToOutput(err);
+      }
+    }
+  </script>
+</body>
+
+# R
+
+<div>
+  <pre><code id="out">Loading webR, please wait...</code></pre>
+  <input spellcheck="false" autocomplete="off" id="input" type="text">
+  <button onclick="globalThis.sendInput()" id="run">Run</button>
+</div>
+
+<script type="module">
+  /* Create a webR console using the Console helper class */
+  import { Console } from 'https://webr.r-wasm.org/latest/webr.mjs';
+  const webRConsole = new Console({
+    stdout: line => document.getElementById('out').append(line + '\n'),
+    stderr: line => document.getElementById('out').append(line + '\n'),
+    prompt: p => document.getElementById('out').append(p),
+  });
+  webRConsole.run();
+
+  /* Write to the webR console using the ``stdin()`` method */
+  let input = document.getElementById('input');
+  globalThis.sendInput = () => {
+    webRConsole.stdin(input.value);
+    document.getElementById('out').append(input.value + '\n');
+    input.value = "";
+  }
+
+  /* Send input on Enter key */
+  input.addEventListener(
+    "keydown",
+    (evt) => {if(evt.keyCode === 13) globalThis.sendInput()}
+  );
+</script>

### 2024-07-07 randpython.qmd
okay

@@
 
-1.
+```{webr-r}
+webr::install(c("dplyr","purrr"))
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
+library(dplyr)
+library(ManifoldDestinyWASMP)
+ls("package:dplyr")
+ls("package:ManifoldDestinyWASMP")
+data(package="ManifoldDestinyWASMD")
+```
 
@@
 summary(fit)
+
 ```

### 2024-07-07 randpython.qmd
abc

--- 2024-07-07 randpython.qmd
@@
   cache: false
+webr:
+  show-startup-message: false      # Display status of webR initialization
+  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
+  packages: ['dplyr','data.table']             # Pre-install dependencies
 filters:
+  - panelize
   - webr
+  - pyodide
 ---
@@
 ```{r}
+# https://github.cm/coatless-quarto/panelize
 # script/R/simulations.R
+# {{< audio file="abc.mp3" caption="Sample Audio File">}}
 ```
 
-1.
+:::{.to-webr}
+```{r}
+a <- 1 
+```
+:::
+
+:::{.to-webr}
+```{r}
+b <- 2
+```
+:::
+
+:::{.to-webr}
+```{r}
+c <- a*b
+c
+```
+:::
+
+**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
+
+This is a webR-enabled code cell in a Quarto HTML document.
+
+```{webr-r}
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
+```
 
@@
 </script>
+
+:::{.to-webr}
+```{r}
+webr::install(c("dplyr","purrr"))
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
+library(dplyr)
+library(ManifoldDestinyWASMP)
+ls("package:dplyr")
+ls("package:ManifoldDestinyWASMP")
+data(package="ManifoldDestinyWASMD")
+```
+:::
+
+:::{.to-pyodide}
+```{python}
+4 + 5
+```
+:::

### 2024-07-07 index.qmd
abc
csv

--- 2024-07-07 index.qmd
@@
 ---
-title: ""
+title: "Manifold Destiny - or how to rig an election"
 output: github_document
-always_allow_html: true
 execute: 
   cache: false
+webr:
+  show-startup-message: true      # Display status of webR initialization
+  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
+  packages: ['dplyr','data.table','readr']             # Pre-install dependencies
+  cell-options:
+    autorun: true
 filters:
+  - panelize
   - webr
@@
 
-# Manifold Destiny - or how to rig an election
+```{r, echo=F}
+# script/R/simulations.R
+```
+
 **Based upon the ideas developed by Edward K. Solomon**
@@
 
+# Testing
+## Installling packages
+```{webr-r}
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
+```
+
+## Loading  data
+```{webr-r}
+dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
+```
+
+```{webr-r}
+ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
+ad
+```
+
 **Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
 
-This is a webR-enabled code cell in a Quarto HTML document.
+```{r, echo=F}
+knitr::knit_exit()
+```
+
+{{< audio file="abc.mp3" caption="Sample Audio File">}}
 
 ```{webr-r}
-fit = lm(mpg ~ am, data = mtcars)
-summary(fit)
+webr::mount(
+  mountpoint = "/data",
+  source = "https://example.com/output.data"
+)
 ```
-
-Abc

### 2024-07-07 index.qmd
metda

@@
 # Testing
+## ABC
+Write some text here
+```{web-r}
+```
+
+abc
+
 ## Installling packages
@@
 dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
+# readr::read.csv("/tmp/RtmpHKcMHo/d5ace5deaed228c73ccaf4fb/0.csv")
 ```
@@
 ```{webr-r}
-ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
-ad
+# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
+# ad
 ```

### 2024-07-07 metaview.qmd
break

---
title: ""
output: html_document
---

```{r setup, include=FALSE}
library(yaml)
library(knitr)
## Load the YAML data from a file
yaml_data <- yaml::read_yaml("_variables.yml")
## Function to display each application's data
pretty_print_list <- function(x) {
  for (name in names(x)) {
    cat(paste0(name, ": "))
    value <- x[[name]]
    if (is.null(value)) {
      cat("NULL")
    } else if (is.atomic(value)) {
      cat(toString(value))
    } else if (is.list(value)) {
      cat("list()")
    }
    cat("\n")
  }
}

```

# App0

```{r, echo=F}
pretty_print_list(yaml_data$app0)
```

### 2024-07-08 presentation.qmd
closer

@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
 #source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
@@
 > "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
+
+```{r}
+knitr::knit_exit()
+```
+
+## `r metad$toc$sec1$unm[1]`
+
+- Two candidates: A, B
+- County with three precincts: 1, 2, 3
+- Two modes of voting
+  - Number of ballots mode 1: S, T
+  - Number of ballots mode 2: U, V
+
+##
+
+**Our two stylized numerical cases**
+
+:::: {.columns}
+::: {.column width="50%"}
+Case 1
+:::
+```{r, echo=F}
+clr <- c("black","green","red","blue")
+lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
+  set_text_color(5, 1:2, clr[1]) %>%
+  set_background_color(1, 1:3, clr[2]) %>% 
+  set_background_color(2, 1:3, clr[3]) %>%
+  set_background_color(3, 1:3, clr[4]) %>%
+  set_background_color(4, 2:3, clr[4]) %>%
+  set_background_color(5, 3:3, clr[4]) %>%
+  set_font_size(16)
+lego_hux_imp_i
+```
+
+::: {.column width="50%"}
+Case 2
+:::
+```{r, echo=F}
+lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
+  set_text_color(5, 1:2, clr[1]) %>%
+  set_background_color(1, 1:3, clr[2]) %>% 
+  set_background_color(2, 1:3, clr[3]) %>%
+  set_background_color(3, 1:3, clr[4]) %>%
+  set_background_color(4, 2:3, clr[4]) %>%
+  set_background_color(5, 3:3, clr[4]) %>%
+  set_font_size(16)
+
+lego_hux_imp_ii
+```
+::::
 

### 2024-07-08 R/wasmconverting.R

@@ -1,3 +1,4 @@
+#########################################################################################################################################################
 #' @export wasmconload
 wasmconload <- function(){
   ifelse(Sys.info()[['sysname']]=="Emscripten",
@@ -93,6 +94,7 @@ gmp <- function(terms=c("x2","xy","y2","x3","x2y","y2x","y3")){
 selreport <- function(
 		      baldata=NULL
 		      ){
+	#browser()
   da <- baldata[[1]]
   md <- baldata[[2]]
   frm <- md$fr
@@ -619,6 +621,7 @@ Countingprocess$methods(setres=function(czset=NULL,prnt=0){
 Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
 					man=FALSE,
 					lfpar=list(mtd=1,lwr= c(0.0,0.0,0.0),upr = c(0,1,1))){
+
   ## Variables
   lof <- function(kvec=NULL,prn=T){
     kvnr <- c(3,6,10,17)[mansysl$plnr]

### 2024-07-08 R/wasmnonverting.R

@@ -18,6 +18,7 @@ recoudatr <- function(mda=NULL,prn=1){
 py_polysolver <- function(degree=1,abcde=NULL){
   path_fqs <- paste0(rprojroot::find_rstudio_root_file(),"/script/python")
   #path_fqs <- system.file("script/python",package = "ManifoldDestiny")
+  reticulate::import("numba")
   fqs <- reticulate::import_from_path("fqs", path =path_fqs)
   np <- reticulate::import("numpy")
   vec <- abcde[!is.na(abcde)] 

### 2024-07-08 script/python/polysolver_old2.py

@@ -1,332 +1,0 @@
-#!!! fix deviation from mean
-import sympy, pandas, numpy
-from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
-def rall(sel=[0, 0, 0]):
-    n, m = symbols('n m')
-    
-    rxy = Matrix([[m, -n, 0], 
-                  [n, m, 0],
-                  [0, 0, 1]])
-    
-    rxz = Matrix([[m, 0, -n], 
-                  [0, 1, 0],
-                  [n, 0, m]])
-    
-    ryx = Matrix([[m, n, 0], 
-                  [-n, m, 0],
-                  [0, 0, 1]])
-    
-    ryz = Matrix([[1, 0, 0], 
-                  [0, m, -n],
-                  [0, n, m]])
-    
-    rzx = Matrix([[m, 0, n], 
-                  [0, 1, 0],
-                  [-n, 0, m]])
-    
-    rzy = Matrix([[1, 0, 0], 
-                  [0, m, n],
-                  [0, -n, m]])
-    
-    ps = [0, rxy, rxz, ryx, ryz, rzx, rzy]
-    
-    allrot = [ps[i] for i in sel]
-    return allrot
-
-#def genpolycoeff(expr=None, solvd='z', solvf='u0', eur=[1, 4, 2], plr=3,dnr=2):
-def genpolycoeff(expr=None, solvd='z', solvf='u0', eur=[0, 0, 0], plr=3):
-    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
-    x, y, z = sympy.symbols('x y z')
-    sum_eur = sum(eur)
-    # Without rotation
-    if sum_eur == 0:
-        exprc = expr + '-' + solvd
-        asexpr = sympify(exprc)
-        polys = poly(asexpr, sympify(solvf)).all_coeffs()
-        abc = []
-        uvw = []
-        ABCDE = [0, 0, 0, 0, 0]
-        ABCDE[:len(polys)] = polys
-        return ABCDE, abc, uvw
-    # With rotation
-    else:
[…]

### 2024-07-08 presentation.qmd
befrev

@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 modlat <- eqpar$meql
@@
 > "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
-
-```{r}
-knitr::knit_exit()
-```
-
-## `r metad$toc$sec1$unm[1]`
 
@@
 
-##
+# {{< var sec2.nmn >}}
+# {{< var sec3.nmn >}}
+# {{< var sec4.nmn >}}
+# {{< var sec5.nmn >}}
+# {{< var sec6.nmn >}}
+# {{< var sec7.nmn >}}
+# {{< var sec8.nmn >}}
+# {{< var sec9.nmn >}}
+
+```{r}
+knitr::knit_exit()
+```
+
+## `r metad$toc$sec1$unm[1]`
 
@@
 ::::
-
-# {{< var sec2.nmn >}}
-# {{< var sec3.nmn >}}
-# {{< var sec4.nmn >}}
-# {{< var sec5.nmn >}}
-# {{< var sec6.nmn >}}
-# {{< var sec7.nmn >}}
-# {{< var sec8.nmn >}}
-# {{< var sec9.nmn >}}
 

### 2024-07-08 index.qmd
headlines

@@
 ---
-title: "Manifold Destiny - or how to rig an election"
+title: "{{< var titll >}}"
 output: github_document

### 2024-07-08 paper.qmd
abc
templated
headlines

@@
 ---
-title: ""
+title: "{{< var titll >}}"
 abstract: "Abstract goes here"
@@
 
-```{r}
+# {{< var sec1.nmn >}}
+## {{< var sec1.un1 >}}
+## {{< var sec1.un2 >}}
+## {{< var sec1.un3 >}}
+## {{< var sec1.un4 >}}
+## {{< var sec1.un5 >}}
+## {{< var sec1.un6 >}}
+## {{< var sec1.un7 >}}
+
+# {{< var sec2.nmn >}}
+## {{< var sec2.un1 >}}
+## {{< var sec2.un2 >}}
+## {{< var sec2.un3 >}}
+## {{< var sec2.un4 >}}
+## {{< var sec2.un4 >}}
+
+# {{< var sec3.nmn >}}
+## {{< var sec3.un1 >}}
+## {{< var sec3.un2 >}}
+
+# {{< var sec5.nmn >}}
+
+# {{< var sec6.nmn >}}
+## {{< var sec6.un1 >}}
+## {{< var sec6.un2 >}}
+## {{< var sec6.un3 >}}
+## {{< var sec6.un4 >}}
+## {{< var sec6.un4 >}}
+
+# {{< var sec7.nmn >}}
+## {{< var sec7.un1 >}}
+
+# {{< var sec8.nmn >}}
+
+```{r,echo=F}
 knitr::knit_exit()

### 2024-07-08 presentation.qmd
headlines

@@
 md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/20laws40isos.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
+laws_df1 <- ManifoldDestiny::eqdef$meql
+laws_df2 <- ManifoldDestiny::eqdef$meqs
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/r/simulations.r'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 modlat <- eqpar$meql
@@
 
-- Two candidates: A, B
-- County with three precincts: 1, 2, 3
-- Two modes of voting
-  - Number of ballots mode 1: S, T
-  - Number of ballots mode 2: U, V
+# {{< var sec1.nmn >}}
+## {{< var sec1.un1 >}}
+## {{< var sec1.un2 >}}
+## {{< var sec1.un3 >}}
+## {{< var sec1.un4 >}}
+## {{< var sec1.un5 >}}
+## {{< var sec1.un6 >}}
+## {{< var sec1.un7 >}}
 
 # {{< var sec2.nmn >}}
+## {{< var sec2.un1 >}}
+## {{< var sec2.un2 >}}
+## {{< var sec2.un3 >}}
+## {{< var sec2.un4 >}}
+## {{< var sec2.un4 >}}
+
 # {{< var sec3.nmn >}}
-# {{< var sec4.nmn >}}
+## {{< var sec3.un1 >}}
+## {{< var sec3.un2 >}}
+
 # {{< var sec5.nmn >}}
+
 # {{< var sec6.nmn >}}
+## {{< var sec6.un1 >}}
+## {{< var sec6.un2 >}}
+## {{< var sec6.un3 >}}
+## {{< var sec6.un4 >}}
+
 # {{< var sec7.nmn >}}
+## {{< var sec7.un1 >}}
+
 # {{< var sec8.nmn >}}
+
 # {{< var sec9.nmn >}}
+
+::: {#refs}
+:::
 

### 2024-07-08 script/R/stylized.R

@@ -1,0 +1,56 @@
+library(ggplot2)
+library(dplyr)
+library(ManifoldDestiny)
+library(htmltools)
+#######################################################################################################################################################
+##### Proto example 1 and 2
+P  <- c(1,2,3,4,5,6)
+S  <- c(60,60,60,60,60,55)
+T  <- c(40,40,40,40,40,40)
+U  <- c(40,40,40,40,40,40)
+V  <- c(60,60,60,40,40,40)
+Up <- c(40,(40-5),(40-10),40,40,40)
+Vp <- c(60,(60+5),(60+10),40,40,40)
+R  <- c(200,200,200,200,200,200)
+## Tower 1
+ex1m <- as.matrix(cbind(S,T,U,V))
+towi <- as.data.frame(ex1m) %>% 
+  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
+  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
+  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
+  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
+  dplyr::select(5:8) %>%
+  t() %>%
+  data.frame() %>%
+  data.table::setnames(paste0("County_",1:6))
+towi[3:4,1] <- ""
+towi[4,2] <- ""
+## Tower 2
+ex2m <- as.matrix(cbind(S,T,Up,Vp))
+towii <- as.data.frame(ex2m) %>% 
+  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
+  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
+  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
+  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
+  dplyr::select(5:8) %>%
+  t() %>%
+  data.frame() %>%
+  data.table::setnames(paste0("County_",1:6))
+towii[3:4,1] <- ""
+towii[4,2] <- ""
+#########################################################################################################################################################
+pro_rec_ex1_e <- data.frame(P=c(1,2,3,4,5,6),S=S,T=T,U=U,V=V,R=R)
[…]

### 2024-07-08 index.qmd
abc

@@
   show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['dplyr','data.table','readr']             # Pre-install dependencies
+  packages: ['dplyr','data.table','readr','ggplotly']             # Pre-install dependencies
   cell-options:
@@
 
-# Testing
-## ABC
-Write some text here
-```{web-r}
-```
-
-abc
+# Testing (latest from Ed's Youtube stream)
 
 ## Installling packages
+
 ```{webr-r}
@@
 webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
-# readr::read.csv("/tmp/RtmpHKcMHo/d5ace5deaed228c73ccaf4fb/0.csv")
+df <- ManifoldDestinyWASMD::yout
+dplyr::select(df[[1]],S,T,U,V)
 ```
 
-## Loading  data
+[Nevada](https://docs.google.com/spreadsheets/d/1gCfmuK44sUeb0Hb0plAc8VllPSjtUiEHWlJjeHq3xXY/edit?gid=0#gid=0)
+
 ```{webr-r}
-dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
+library(plotly)                                                                                          
+# Create sample data                                                                                     
+x <- seq(-5, 5, length.out = 100)                                                                        
+y <- x                                                                                                   
+z <- outer(x, y, function(x, y) cos(sqrt(x^2 + y^2)))
+
+# Create 3D scatter plot                                                                                 
+plot_ly(x = x, y = y, z = z, type = "scatter3d", mode = "markers")                                       
 ```
@@
 ```{webr-r}
-# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
-# ad
+library(ggplot2)
+
+# Create a sample data frame                                                                             
+data <- data.frame(                                                                                      
+  x = c(1, 2, 3, 4, 5),                                                                                  
+  y = c(2, 3, 5, 7, 6)                                                                                   
+)
+
+# Create a scatter plot using ggplot2                                                                    
+ggplot(data, aes(x = x, y = y)) +                                                                        
+  geom_point()                                                                                           
 ```
@@
 knitr::knit_exit()
+```
+
+```{webr-r}
+# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
+# ad
 ```

### 2024-07-08 presentation.qmd
abc

@@
 
+![](images/ss.png){width=300}
+
+> abstract: on august 15th, **2004**, venezuelans had the opportunity to vote
+in a presidential recall referendum **to decide whether or not president hugo
+chávez should be removed from office.** **the process was largely computer-
+ized using a touch-screen system.** in general the ballots were not manually
+counted. the significance of the high linear correlation (0.99) between the
+number of requesting signatures for the recall petition and the number of op-
+position votes in computerized centers is analyzed. The same-day audit was
+found to be not only ineffective but a source of suspicion...
+
+{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
+
+---
+
+![](images/manifold.png){width=300}
+
+---
+
 # {{< var sec6.nmn >}}
@@
 # {{< var sec9.nmn >}}
+
+- At the heart of the difference between a fair and rigged election is the issue of causation
+  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
+  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
+
+- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
+	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
+	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
+
+##
+
+- Condition on that $R^2$ falls within the critical region.
+  - Normal form
+```{r, echo=F, out.width="40%", fig.cap=""}
+pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2n.png')
+knitr::include_graphics(c(pr2n))
+```
+
+ - Hybrid form
+```{r, echo=F, out.width="40%", fig.cap=""}
+pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2h.png')
+knitr::include_graphics(c(pr2h))
+```
+
+- Our four applications
 

### 2024-07-09 tabsets.qmd
running
prerender

@@
 ---
+
+```{r, echo=F, message=F, warning=F}
+ManifoldDestiny::wasmconload()
+#modlat <- eqpar$meql
+#md <- ManifoldDestinyWASMD::metad
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
+#metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+#mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+```
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-07-09 prerendr.R

@@ -1,0 +1,38 @@
+##############################################################################################################
+library(ManifoldDestiny)
+###############################################################################################################
+metadata <- yaml::yaml.load_file(paste0(rprojroot::find_rstudio_root_file(),"/_variables.yml"))
+usethis::use_data(metadata)
+
+# Model
+fdm <- paste0(rprojroot::find_rstudio_root_file(),'/script/python/pysympy.py')
+reticulate::source_python(fdm)
+eqpar <- list(meql=reticulate::py$modeql,meqs=reticulate::py$modeqs)
+## Saving data
+usethis::use_data(eqpar, overwrite = TRUE)
+
+# 20 laws and 40 isos
+fdm <- paste0(rprojroot::find_rstudio_root_file(),'/script/python/20_laws_40_isos.py')
+reticulate::source_python(fdm)
+eqdef <- list(meql=reticulate::py$dfl,meqs=reticulate::py$dfs)
+
+# Saving data
+usethis::use_data(eqdef, overwrite = TRUE)
+stickers <-
+  list(parameters=list(
+  standard=c("alpha","x","y","zeta","lamda","Omega"),
+  hybrid=c("alpha","g","h","Gamma","Omega","lamda"),
+  opposition=c("alpha","m","n","xi","lamda","Omega")),
+  forms=list('_s','o_h','h_o')) 
+usethis::use_data(stickers, overwrite = TRUE)
+
+# Cubic
+peqs <-c(
+'k0 + k1*u + k2*v',
+'k0 + k1*u + k2*v + k3*u**2 + k4*v**2 + k5*u*v',
+'k0 + k1*u + k2*v + k3*u**2 + k4*v**2 + k5*u*v + k6*v**3 + k7*u*v + k8*u**2*v + k9*u*v**2',
+'k0 + k1*u + k2*v + k3*u**2 + k4*v**2 + k5*u*v + k6*u**3 + k7*v**3 + k8*u**2*v + k9*u*v**2 + k10*u**4 + k11*v**4 + k12*u**3*v + k13*u**2*v**2 + k14*u*v**3 +k15*u**4*v + k16*u*v**2')
+usethis::use_data(peqs, overwrite = TRUE)
+
+ManifoldDestiny::bm()
+

### 2024-07-09 app_par.qmd
tabsets

@@
 
-```{r, eval=F, echo=F, message=F, warning=F}
-pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/app_par.qmd')
-quarto::quarto_preview(pre_fil)
-params <- list(name="1")
-#lapply(paste0("app",0:4), function(x){recoudatr(mda=md[[x]])})
-```
-
-```{r, echo=F}
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-library(ManifoldDestiny)
-library(dplyr)
-library(ggplot2)
-library(dplyr)
-library(combinat)
-library(htmltools)
-library(ggplot2)
-library(broom)
-library(combinat)
-md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-md$tabsets
-mda <- md['1']
-app1_rp <- selreport(app1,md$app1)
-app_a_out <- seloutput(app1_rp)
-```
-
-```{r, echo=F}
-mda <- md['1']
-app1_rp <- selreport(app1,md$app1)
-app_a_out <- seloutput(app1_rp)
+```{r, echo=F,message=FALSE,warning=FALSE}
+ManifoldDestiny::wasmconload()
+#library(ManifoldDestinyWASMP)
+#library(ManifoldDestinyWASMD)
+#library(ManifoldDestiny)
+#library(dplyr)
+#library(ggplot2)
+#library(dplyr)
+#library(combinat)
+#library(htmltools)
+#library(ggplot2)
+#library(broom)
+#library(combinat)
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+mda <- app0[[2]]
+app0_rp <- selreport(app0)
+app_0_out <- seloutput(app0_rp)
+mda$rcn
 ```
@@
 ## Application: `r mda$nmn`
+### Information
+- Election system:
+  - Type of race: `r mda$rcn` 
+  - Candidates: `r mda$cnd` 
+  - Modes of voting: `r mda$mod` 
+- $H_0:$ Normal election 
+- $H_1:$ Rigged election: 
+  - Manifold object $`r mda$eq[1]`$
+  - Solved for `r mda$va`
+
+[Link to raw data and independent calculcations](`r mda$url`)
 
 ### Information
-- Election system:
-  - Type of race: `r mda$race$rcn` 
-  - Candidates: `r mda$race$cnd` 
-  - Modes of voting: `r mda$race$mod`
 
-- $H_0:$ Normal election 
-- $H_1:$ Rigged election: 
-  - Manifold object `r mda$mtd$sgs$eq[1]`
-  - Solved for `r mda$mtd$sgs$va`
+### {{< var tabh.h1 >}}
 
-[Link to raw data and independent calculcations](`r mda$sht$url`)
+---
+
+::: {.panel-tabset}
+
+### {{< var tabs.h1 >}}
+
+```{r, echo=F}
+```
+### {{< var tabs.h2 >}}
+```{r, echo=F, out.width="60%"}
+```
+### {{< var tabs.h3 >}}
+```{r, echo=F, out.width="60%"}
+```
+### {{< var tabs.h4 >}}
+```{r, echo=F}
+```
+### {{< var tabs.h5 >}}
+```{r, echo=F, out.width="60%"}
+```
+### {{< var tabs.h6 >}}
+```{r, echo=F, out.width="60%"}
+```
+:::
+
+---
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-07-09 tabsets.qmd
appapr
tabsets

--- 2024-01-07 tabsets.qmd
@@
 #  cache: false
+# app_par.qmd
 bibliography: man_bib.bib
 ---
+
+```{r, echo=F, message=F, warning=F}
+ManifoldDestiny::wasmconload()
+md <- ManifoldDestiny::metd
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
+```
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-07-09 app_par.qmd
application

@@
 ---
-title: "Applicaton"
-date: "`r Sys.Date()`"
+#title: "Applicaton"
 #format: 
@@
 ManifoldDestiny::wasmconload()
+library(ManifoldDestiny)
 #library(ManifoldDestinyWASMP)
 #library(ManifoldDestinyWASMD)
-#library(ManifoldDestiny)
 #library(dplyr)
@@
 mda <- app0[[2]]
-app0_rp <- selreport(app0)
-app_0_out <- seloutput(app0_rp)
-mda$rcn
+asrp <- selreport(app0)
+asop <- seloutput(asrp)
 ```
@@
 ```{r, echo=F}
+kableExtra::kbl(asop[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```
@@
 ```{r, echo=F, out.width="60%"}
+asop[['corxy']]
 ```
@@
 ```{r, echo=F, out.width="60%"}
+asop[['qunt']]
 ```
@@
 ```{r, echo=F}
+asop[['ro3d']]
 ```
@@
 ```{r, echo=F, out.width="60%"}
+asop[['regr']]
 ```
@@
 ```{r, echo=F, out.width="60%"}
+asop[['resp']]
 ```
@@
 
----
-
-```{r}
+```{r, echo=F}
 knitr::knit_exit()
 ```
-
----
-
-::: {.panel-tabset}
-
-### `r md$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_a_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-### `r md$tabsets[[2]]`
-```{r, echo=F, out.width="60%"}
-app_a_out[['corxy']]
-```
-### `r md$tabsets[[3]]`
-```{r, echo=F, out.width="60%"}
-app_a_out[['qunt']]
-```
-### `r md$tabsets[[4]]`
-```{r, echo=F}
-app_a_out[['ro3d']]
-```
-### `r md$tabsets[[5]]`
-```{r, echo=F, out.width="60%"}
-app_a_out[['regr']]
-```
-### `r md$tabsets[[6]]`
-```{r, echo=F, out.width="60%"}
-app_a_out[['resp']]
-```
-:::
 
@@
 ```{r, echo=F}
-#app_a_out$cmp[,1] <- c("Mean total votes", "Number of precincts", "Zero prediction error", "In percentage", "Mean", "Standard Deviation", "Max ballot error", "1+/- prediction error", "2+/- prediction error", "2+/- prediction error", "Percentage within +/-3")
-#kableExtra::kbl(app_a_out$cmp,row.names=F,col.names=c("Statistic","Value"),digits=2) %>% kableExtra::kable_paper(full_width = F) 
+asop$cmp[,1] <- c("Mean total votes", "Number of precincts", "Zero prediction error", "In percentage", "Mean", "Standard Deviation", "Max ballot error", "1+/- prediction error", "2+/- prediction error", "2+/- prediction error", "Percentage within +/-3")
+kableExtra::kbl(asop$cmp,row.names=F,col.names=c("Statistic","Value"),digits=2) %>% kableExtra::kable_paper(full_width = F) 
 ```

### 2024-07-09 app_par.qmd
tabsets

@@
 library(ManifoldDestiny)
-#library(ManifoldDestinyWASMP)
-#library(ManifoldDestinyWASMD)
-#library(dplyr)
-#library(ggplot2)
-#library(dplyr)
-#library(combinat)
-#library(htmltools)
-#library(ggplot2)
-#library(broom)
-#library(combinat)
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))

### 2024-07-09 tabsets.qmd
tabsets

@@
 ---
-title: "Tabsets"
-format: 
-  html:
-    page-layout: article
-#filters:
-#  - webr
-#format:
-#  revealjs: 
-#    smaller: true
-#    toc-depth: 1
-#    toc: true 
-#    footer: <https://lotariohw26.github.io/ManifoldDestiny/>
-#execute: 
-#  cache: false
-# app_par.qmd
-bibliography: man_bib.bib
+title: ""
 ---
@@
 
-```{r}
-knitr::knit_exit()
-```
-
-```{r, echo=F, message=F, warning=F}
+```{r, echo=F,message=FALSE,warning=FALSE}
 ManifoldDestiny::wasmconload()
-modlat <- eqpar$meql
-md <- ManifoldDestinyWASMD::metad
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
-metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+library(ManifoldDestiny)
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+mda <- app0[[2]]
+asrp <- selreport(app0)
+asop <- seloutput(asrp)
 ```
@@
 ::: {.callout-caution collapse="true"}
-## `r md$tabhead[1]`
+## {{< var tabh.h1 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_n_out
+#app_a_out <- app_0_out 
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
 text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ::: {.callout-caution collapse="true"}
-## `r md$tabhead[2]`
+## {{< var tabh.h2 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_ex1_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+#app_a_out <- app_1_out 
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ::: {.callout-caution collapse="true"}
-## `r md$tabhead[3]`
+## {{< var tabh.h3 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_ex2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+#app_a_out <- app_2_out 
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ::: {.callout-caution collapse="true"}
-## `r md$tabhead[4]`
+## {{< var sec6.un1 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_ex3_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+#app_a_out <- app_2_out 
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ::: {.callout-caution collapse="true"}
-## Application 0 
+## {{< var sec6.un2 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_0_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+#app_a_out <- app_2_out 
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ::: {.callout-caution collapse="true"}
-## Application 1 
+## {{< var sec6.un3 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_1_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+#app_a_out <- app_2_out 
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ::: {.callout-caution collapse="true"}
-## Application 2 
+## {{< var sec6.un4 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+#app_a_out <- app_2_out 
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
 :::
-::: {.callout-caution collapse="true"}
-## Application 3 
-```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+
+```{r, echo=F}
+knitr::knit_exit()
 ```
-:::
-::: {.callout-caution collapse="true"}
-## Application 4 
-```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-:::
-::: {.callout-caution collapse="true"}
-## Application 5 
-```{r, echo=FALSE, results='asis',warning=F}
-app_a_out <- app_2_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-:::

### 2024-07-09 presentation.qmd
beftoc

@@
 ## {{< var sec1.un1 >}}
-## {{< var sec1.un2 >}}
-## {{< var sec1.un3 >}}
-## {{< var sec1.un4 >}}
-## {{< var sec1.un5 >}}
-## {{< var sec1.un6 >}}
-## {{< var sec1.un7 >}}
-
-# {{< var sec2.nmn >}}
-## {{< var sec2.un1 >}}
-## {{< var sec2.un2 >}}
-## {{< var sec2.un3 >}}
-## {{< var sec2.un4 >}}
-## {{< var sec2.un4 >}}
-
-# {{< var sec3.nmn >}}
-## {{< var sec3.un1 >}}
-## {{< var sec3.un2 >}}
-
-# {{< var sec5.nmn >}}
-
-![](images/ss.png){width=300}
-
-> abstract: on august 15th, **2004**, venezuelans had the opportunity to vote
-in a presidential recall referendum **to decide whether or not president hugo
-chávez should be removed from office.** **the process was largely computer-
-ized using a touch-screen system.** in general the ballots were not manually
-counted. the significance of the high linear correlation (0.99) between the
-number of requesting signatures for the recall petition and the number of op-
-position votes in computerized centers is analyzed. The same-day audit was
-found to be not only ineffective but a source of suspicion...
-
-{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
-
----
-
-![](images/manifold.png){width=300}
-
----
-
-# {{< var sec6.nmn >}}
-## {{< var sec6.un1 >}}
-## {{< var sec6.un2 >}}
-## {{< var sec6.un3 >}}
-## {{< var sec6.un4 >}}
-
-# {{< var sec7.nmn >}}
-## {{< var sec7.un1 >}}
-
-# {{< var sec8.nmn >}}
-
-# {{< var sec9.nmn >}}
-
-- At the heart of the difference between a fair and rigged election is the issue of causation
-  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
-  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
-
-- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
-	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
-	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
-
-##
-
-- Condition on that $R^2$ falls within the critical region.
-  - Normal form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2n.png')
-knitr::include_graphics(c(pr2n))
-```
-
- - Hybrid form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2h.png')
-knitr::include_graphics(c(pr2h))
-```
-
-- Our four applications
-
-::: {#refs}
-:::
-
-```{r}
-knitr::knit_exit()
-```
-
-## `r metad$toc$sec1$unm[1]`
-
-**Our two stylized numerical cases**
-
-:::: {.columns}
-::: {.column width="50%"}
-Case 1
-:::
-```{r, echo=F}
-clr <- c("black","green","red","blue")
-lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
-  set_text_color(5, 1:2, clr[1]) %>%
-  set_background_color(1, 1:3, clr[2]) %>% 
-  set_background_color(2, 1:3, clr[3]) %>%
-  set_background_color(3, 1:3, clr[4]) %>%
-  set_background_color(4, 2:3, clr[4]) %>%
-  set_background_color(5, 3:3, clr[4]) %>%
-  set_font_size(16)
-lego_hux_imp_i
-```
-
-::: {.column width="50%"}
-Case 2
-:::
-```{r, echo=F}
-lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
-  set_text_color(5, 1:2, clr[1]) %>%
-  set_background_color(1, 1:3, clr[2]) %>% 
-  set_background_color(2, 1:3, clr[3]) %>%
-  set_background_color(3, 1:3, clr[4]) %>%
-  set_background_color(4, 2:3, clr[4]) %>%
-  set_background_color(5, 3:3, clr[4]) %>%
-  set_font_size(16)
-
-lego_hux_imp_ii
-```
-::::
-
-# `r metad$toc$sec1$nmn`
-
-Ed. Solomon
-
-> "At the very core of this article lay the assumption of Causality, that the **Effect cannot precede the Cause**; likewise, the **Aggregate Percentage of a Candidate cannot precede the Election Day and the Mail-in Percentages of that candidate**.
-
-```{r}
-knitr::knit_exit()
-```
-
-## `r metad$toc$sec1$unm[1]`
-
 - Two candidates: A, B
@@
 ::::
-
-## `r metad$toc$sec1$unm[2]`
-
+## {{< var sec1.un2 >}}
 ```{r, echo=F}
@@
 
-```{r}
-knitr::knit_exit()
-```
-
 Numerical calculation of candidate one total percentage
@@
 
-## `r metad$toc$sec1$unm[3]`
-
+## {{< var sec1.un3 >}}
 ```{r, echo=F}
@@
 
-## `r metad$toc$sec1$unm[4]`
-
+## {{< var sec1.un4 >}}
 ```{r, echo=F}
@@
 
-## `r metad$toc$sec1$unm[5]`
+## {{< var sec1.un5 >}}
 
@@
 
-## `r metad$toc$sec1$unm[6]`
+## {{< var sec1.un6 >}}
 
@@
 
-## `r metad$toc$sec1$unm[7]`
+## {{< var sec1.un7 >}}
 
@@
 
-# `r metad$toc$sec2$nmn`
-
-## `r metad$toc$sec2$unm[1]`
-
+# {{< var sec2.nmn >}}
+## {{< var sec2.un1 >}}
 - We have identified three ways of counting
@@
 
-## `r metad$toc$sec2$unm[2]`
-
+## {{< var sec2.un2 >}}
 ::: {.callout-caution collapse="true"}
@@
 :::
-
-## `r metad$toc$sec2$unm[3]`
+## {{< var sec2.un3 >}}
 
@@
 
-## `r metad$toc$sec2$unm[4]`
+## {{< var sec2.un4 >}}
 
@@
 ```{r}
-app_n_out[[4]] 
+#app_n_out[[4]] 
 ```
@@
 ```{r}
-app_ex1_out[[4]] 
+#app_ex1_out[[4]] 
 ```
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
 \end{equation*}
@@
 #polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
-mean(app_ex1_cou$rdfc$alpha)
+#mean(app_ex1_cou$rdfc$alpha)
 ```
@@
 
-$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
 
@@
 #polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
-pos_int_ex1
+#pos_int_ex1
 ```
@@
 
----
+# {{< var sec3.nmn >}}
 
-```{r}
-knitr::knit_exit()
-```
+## {{< var sec3.un1 >}}
 
-**Setting the prefered election outcome**
+## {{< var sec3.un2 >}}
 
-:::: {.columns}
+# {{< var sec5.nmn >}}
 
-::: {.column width="50%"}
+![](images/ss.png){width=300}
 
-Non-rigged election using standard form
-```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
-app_n_out[[4]] 
-```
-
-:::
-
-::: {.column width="50%"}
-
-Rigged election using standard form
-```{r, echo=F, echo=F, out.width="150%", fig.cap=""}
-app_ex1_out[[4]] 
-```
-:::
-
-::::
-
----
-
-**Normal**
-<br>
-\begin{equation*}
-f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pri_int_ex3)),3))`$
-\end{equation*}
-
-Election outome
-```{r, echo=F}
-#sum(dplyr::select(app_n_out[['rdfc']],S,U))/sum(dplyr::select(app_n_out[['rdfc']],S,T,U,V))
-polynom::integral(round(polynom::polynomial(unname(pri_int_ex3))),c(0,1))
-```
-
-<br>
-**Rigged**
-<br>
-
-$f(x)_{0}^{1}=`r paste0(round(polynom::polynomial(unname(pos_int_ex3)),3))`$
-
-Election outome
-```{r, echo=F}
-#sum(dplyr::select(app_ex1_out[['rdfc']],S,U))/sum(dplyr::select(app_ex1_out[['rdfc']],S,T,U,V))
-polynom::integral(round(polynom::polynomial(unname(pos_int_ex3))),c(0,1))
-```
-
----
-
-```{r}
-knitr::knit_exit()
-```
-
-## `r metad$toc$sec2$unm[5]`
-
-- Specify a loss function
-  - $\sum_{p=1}^{P}(\alpha_p-\overline{\alpha})^2$
-- $M(,)=$x+y$
-  - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
-  - Also: Euler rotation
-- System approach Demands mulitvariate Manifold Equations
-  - Univariate manifold Equation
-  - Multivariate Manifold Equations
-- Constrain on implementation
-  - Flipping votes on one mode
-  - Vote registration until upper limit
-
----
-
-```{r, echo=F, out.width="80%", fig.cap=""}
-bI <- paste0(rprojroot::find_rstudio_root_file(),'pngs/loss_5_conditions.png')
-knitr::include_graphics(bI)
-```
-
-# `r metad$toc$sec3$nmn`
-
-## `r metad$toc$sec3$unm[1]`
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_n_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_n_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_n_out[['resp']]
-```
-
-:::
-
-## `r metad$toc$sec3$unm[2]`
-
-**Example 1: Normal form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex1_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex1_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex1_out[['resp']]
-```
-
-:::
-
-##
-
-**Example 2: applying hybrid form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex2_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex2_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex2_out[['resp']]
-```
-
-:::
-
-##
-
-**Example 3: applying opposition form**
-
-::: {.panel-tabset}
-
-### `r metad$tabsets[[1]]`
-
-```{r, echo=F}
-kableExtra::kbl(app_ex3_out[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-### `r metad$tabsets[[2]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['corxy']]
-```
-
-### `r metad$tabsets[[3]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['qunt']]
-```
-
-### `r metad$tabsets[[4]]`
-
-```{r, echo=F}
-app_ex3_out[['ro3d']]
-```
-
-### `r metad$tabsets[[5]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['regr']]
-```
-
-### `r metad$tabsets[[6]]`
-
-```{r, echo=F, out.width="60%"}
-app_ex3_out[['resp']]
-```
-
-:::
-
-# `r metad$toc$sec4$nmn` {#litrev}
-
-```{r, echo=FALSE, out.width="20%", fig.cap=""}
-p1 <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/ss.png')
-knitr::include_graphics(c(p1))
-```
-
----
-
-`r #Citet(bib, "delfino2011analysis")`
-
-> Abstract: On August 15th, **2004**, Venezuelans had the opportunity to vote
-in a Presidential Recall Referendum **to decide whether or not President Hugo
-Chávez should be removed from office.** **The process was largely computer-
-ized using a touch-screen system.** In general the ballots were not manually
-counted. The significance of the high linear correlation (0.99) between the
+> abstract: on august 15th, **2004**, venezuelans had the opportunity to vote
+in a presidential recall referendum **to decide whether or not president hugo
+chávez should be removed from office.** **the process was largely computer-
+ized using a touch-screen system.** in general the ballots were not manually
+counted. the significance of the high linear correlation (0.99) between the
 number of requesting signatures for the recall petition and the number of op-
@@
 
-::: aside
-[Link to Youtube-video](https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s)
-:::
+---
 
-##
+{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
 
-- Venezuela referendum to recall President Hugo Chávez (2004)
-	- Mode 1: Computerized Voting Centers
-	- Mode 2: Manuel Voting Centers
+---
 
-> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.
+![](images/manifold.png){width=300}
 
-```{r, echo=FALSE, out.width="85%", fig.cap=""}
-p3 <- paste0(rprojroot::find_rstudio_root_file(),'pngs/manifold.png')
-knitr::include_graphics(c(p3))
-```
+---
 
-# `r metad$toc$sec5$nmn` {#proced}
-
-# `r metad$toc$sec5$unm[1]`
+# {{< var sec6.nmn >}}
 
@@
 
-[Application 3: Rigged election analyzer]({{< var shn3 >}})
+## {{< var sec6.un1 >}}
+## {{< var sec6.un2 >}}
+## {{< var sec6.un3 >}}
+## {{< var sec6.un4 >}}
 
-# `r metad$toc$sec6$nmn`
+# {{< var sec7.nmn >}}
 
-```{r}
-knitr::knit_exit()
-```
+## {{< var sec7.un1 >}}
 
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="1")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
+# {{< var sec8.nmn >}}
 
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-params <- list(name="2")
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
----
-
-# `r metad$toc$sec7$nmn`
-
-[Application 4: Restoration of a rigged election]({{< var shn4 >}})
-
----
-
-# `r metad$toc$sec8$nmn`
+# {{< var sec9.nmn >}}
 
@@
 ```{r, echo=F, out.width="40%", fig.cap=""}
-pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2n.png')
+pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2n.png')
 knitr::include_graphics(c(pr2n))
@@
 ```{r, echo=F, out.width="40%", fig.cap=""}
-pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/pngs/r2h.png')
+pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2h.png')
 knitr::include_graphics(c(pr2h))
@@
 - Our four applications
-
-```{r, echo=F, warning=F, message=F}
-kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-# `r metad$toc$sec9$nmn`
 

### 2024-07-09 index.qmd
abc
prerender
first

@@
 ```{webr-r}
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-df <- ManifoldDestinyWASMD::yout
-dplyr::select(df[[1]],S,T,U,V)
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+library(ManifoldDestinyWASMP)
+ls(package:ManifoldDestinyWASMP)data(package='ManifoldDestinyWASMD')
 ```
@@
 [Nevada](https://docs.google.com/spreadsheets/d/1gCfmuK44sUeb0Hb0plAc8VllPSjtUiEHWlJjeHq3xXY/edit?gid=0#gid=0)
+
+**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
+
+```{r, echo=F}
+knitr::knit_exit()
+```
+
+```{webr-r}
+# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
+# ad
+```
+
+```{webr-r}
+library(ggplot2)
+
+# Create a sample data frame                                                                             
+data <- data.frame(                                                                                      
+  x = c(1, 2, 3, 4, 5),                                                                                  
+  y = c(2, 3, 5, 7, 6)                                                                                   
+)
+
+# Create a scatter plot using ggplot2                                                                    
+ggplot(data, aes(x = x, y = y)) + geom_point()                                                                                           
+```
 
@@
 
-```{webr-r}
-library(ggplot2)
-
-# Create a sample data frame                                                                             
-data <- data.frame(                                                                                      
-  x = c(1, 2, 3, 4, 5),                                                                                  
-  y = c(2, 3, 5, 7, 6)                                                                                   
-)
-
-# Create a scatter plot using ggplot2                                                                    
-ggplot(data, aes(x = x, y = y)) +                                                                        
-  geom_point()                                                                                           
-```
-
-**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
-
-```{r, echo=F}
-knitr::knit_exit()
-```
-
-```{webr-r}
-# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
-# ad
-```
-
 {{< audio file="abc.mp3" caption="Sample Audio File">}}

### 2024-07-09 index.qmd
abc

--- 2024-07-08 index.qmd
@@
 ```{webr-r}
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
 webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+ls(package:ManifoldDestinyWASMP)
+data(package='ManifoldDestinyWASMD')
+```
+
+```{webr-r}
 df <- ManifoldDestinyWASMD::yout

### 2024-07-09 index.qmd
abc

@@
 data(package='ManifoldDestinyWASMD')
+library(ggplot2)
+library(combinat)
+library(plotly)
+library(htmltools)
+library(broom)
 ```

### 2024-07-09 R/wasmconverting.R

@@ -9,6 +9,12 @@ wasmconload <- function(){
       webr::install(c("AlgebraicHaploPackage","cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
       library(ManifoldDestinyWASMP)
       library(ManifoldDestinyWASMD)
+      #
+      library(ggplot2)
+      library(combinat)
+      library(plotly)
+      library(htmltools)
+      library(broom)
   },
   {
       # Commands to be executed if the condition is FALSE

### 2024-07-09 index.qmd
newpackges
upd

@@
 ```{webr-r}
-df <- ManifoldDestinyWASMD::yout
-dplyr::select(df[[1]],S,T,U,V)
+dfl <- ManifoldDestinyWASMD::yout
+df <- dplyr::select(dfl[[1]],S,T,U,V)
+```
+
+```{webr-r}
+df
+```
+
+```{webr-r}
+ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
+ad
 ```
@@
 ```
-
-```{webr-r}
-# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
-# ad
-```
-
-```{webr-r}
-library(ggplot2)
-
-# Create a sample data frame                                                                             
-data <- data.frame(                                                                                      
-  x = c(1, 2, 3, 4, 5),                                                                                  
-  y = c(2, 3, 5, 7, 6)                                                                                   
-)
-
-# Create a scatter plot using ggplot2                                                                    
-ggplot(data, aes(x = x, y = y)) + geom_point()                                                                                           
-```
-
-```{webr-r}
-library(plotly)                                                                                          
-# Create sample data                                                                                     
-x <- seq(-5, 5, length.out = 100)                                                                        
-y <- x                                                                                                   
-z <- outer(x, y, function(x, y) cos(sqrt(x^2 + y^2)))
-
-# Create 3D scatter plot                                                                                 
-plot_ly(x = x, y = y, z = z, type = "scatter3d", mode = "markers")                                       
-```
-
-{{< audio file="abc.mp3" caption="Sample Audio File">}}
-
-```{webr-r}
-webr::mount(
-  mountpoint = "/data",
-  source = "https://example.com/output.data"
-)
-```

### 2024-07-09 paper.qmd
upd

@@
 ## {{< var sec2.un4 >}}
-## {{< var sec2.un4 >}}
+## {{< var sec2.un5 >}}
 
@@
 ## {{< var sec6.un3 >}}
-## {{< var sec6.un4 >}}
 ## {{< var sec6.un4 >}}

### 2024-07-09 presentation.qmd
upd

@@
 
-# {{< var sec1.nmn >}}
 ## {{< var sec1.un1 >}}

### 2024-07-09 abc.qmd
bbilio

--- 2024-01-07 abc.qmd
@@
 ---
-title: "econ"
-#format: 
-#  html:
-#    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
-#    include-in-body:
-#          - text: |
-#              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
+title: ""
+webr:
+  show-startup-message: true      # Display status of webR initialization
+  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
+  packages: ['dplyr','data.table','readr','ggplotly']             # Pre-install dependencies
+  cell-options:
+    autorun: true
+filters:
+  - panelize
+  - pyodide
+  - webr
 ---
 
-<head>
-      <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
-      <link rel="stylesheet" href="https://kineticgraphs.org/css/kg.0.2.7.css">
-</head>
+## Web-R
 
-<div class="kg-container">
-schema: EconSchema
-layout:
-  OneGraph:
-    graph:
-      xAxis: 
-        title: "Good 1"
-      yAxis: 
-        title: "Good 2"
-      objects: 
-      - EconBudgetLine:
-          p1: 1
-          p2: 2
-          m: 8
-          label: {text: M, location: 0.9}
-</div>
-
-::: {.kg-container}
-schema: EconSchema
-layout:
-  OneGraph:
-    graph:
-      xAxis: 
-        title: "Good 1"
-      yAxis: 
-        title: "Good 2"
-      objects: 
-      - EconBudgetLine:
-          p1: 1
-          p2: 2
-          m: 8
-          label: {text: M, location: 0.9}
+:::{.to-webr}
+```{r}
+1 + 1
+```
 :::
 
-```{r}
-knitr::knit_exit()
+## Pyodide
+
+:::{.to-pyodide}
+```{python}
+x = [1, 2]
+print(x)
 ```
-
-<p id=ary></p>
-<p id=nmb></p>
-<p id=str></p>
-
-<head>
-      <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
-</head>
-<body>
-    Pyodide test page <br>
-    Open your browser console to see Pyodide output
-    <script type="text/javascript">
-      async function main(){
-        let pyodide = await loadPyodide();
-        console.log(pyodide.runPython(`
-            import sys
-            sys.version
-        `));
-        pyodide.runPython("print(1*5)");
-      }
-      main();
-    </script>
-</body>
-
-```{r}
-knitr::knit_exit()
-```
-
-<html>
-  <head>
-    <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
-  </head>
-
-  <body>
-    <p>
-      You can execute any Python code. Just enter something in the box below and
-      click the button.
-    </p>
-    <input id="code" value="sum([1, 2, 3, 4, 5])" />
-    <button onclick="evaluatePython()">Run</button>
-    <br />
-    <br />
-    <div>Output:</div>
-    <textarea id="output" style="width: 100%;" rows="6" disabled></textarea>
-
-    <script>
-      const output = document.getElementById("output");
-      const code = document.getElementById("code");
-
-      function addToOutput(s) {
-        output.value += ">>>" + code.value + "\n" + s + "\n";
-      }
-
-      output.value = "Initializing...\n";
-      // init Pyodide
-      async function main() {
-        let pyodide = await loadPyodide();
-        output.value += "Ready!\n";
-        return pyodide;
-      }
-      let pyodideReadyPromise = main();
-
-      async function evaluatePython() {
-        let pyodide = await pyodideReadyPromise;
-        try {
-          let output = pyodide.runPython(code.value);
-          addToOutput(output);
-        } catch (err) {
-          addToOutput(err);
-        }
-      }
-    </script>
-  </body>
-</html>
-
-#! fix deviation from mean
-import sympy, pandas, numpy
-from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
-def rall(sel=[0, 0, 0]):
-    n, m = symbols('n m')
-
-    rxy = Matrix([[m, -n, 0], 
-                  [n, m, 0],
-                  [0, 0, 1]])
-
-    rxz = Matrix([[m, 0, -n], 
-                  [0, 1, 0],
-                  [n, 0, m]])
-
-    ryx = Matrix([[m, n, 0], 
-                  [-n, m, 0],
-                  [0, 0, 1]])
-
-    ryz = Matrix([[1, 0, 0], 
-                  [0, m, -n],
-                  [0, n, m]])
-
-    rzx = Matrix([[m, 0, n], 
-                  [0, 1, 0],
-                  [-n, 0, m]])
-
-    rzy = Matrix([[1, 0, 0], 
-                  [0, m, n],
-                  [0, -n, m]])
-
-    ps = [0, rxy, rxz, ryx, ryz, rzx, rzy]
-
-    allrot = [ps[i] for i in sel]
-    return allrot
-
-def genpolycoeff(expr=None, solvd='z', solvf='u0', eur=[1, 4, 2], plr=3,dnr=2):
-    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
-    x, y, z = sympy.symbols('x y z')
-    sum_eur = sum(eur)
-    # Without rotation
-    if sum_eur == 0:
-        exprc = expr + '-' + solvd
-        asexpr = sympify(exprc)
-        polys = poly(asexpr, sympify(solvf)).all_coeffs()
-        abc = []
-        uvw = []
-        ABCDE = [0, 0, 0, 0, 0]
-        ABCDE[:len(polys)] = polys
-        return ABCDE, abc, uvw
-    # With rotation
-    else:
-        expr = ['k0+k1*x+k2*y', 'k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2', 'k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3'][plr-1]
-        dxyz = {'x': 1, 'y': 2, 'z': 3}
-        # Defining
-        x,  y,  z  = sympy.symbols('x y z')
-        ui, vi, wi = sympy.symbols('ui vi wi')
-        u0, v0, w0 = sympy.symbols('u0 v0 w0')
-        u1, v1, w1 = sympy.symbols('u1 v1 w1')
-        u2, v2, w2 = sympy.symbols('u2 v2 w2')
-        a1, a2, a3 = sympy.symbols('a1 a2 a3')
-        b1, b2, b3 = sympy.symbols('b1 b2 b3')
-        c1, c2, c3 = sympy.symbols('c1 c2 c3')
-        m1, m2, m3 = sympy.symbols('m1 m2 m3')
-        n1, n2, n3 = sympy.symbols('n1 n2 n3')
-        mu, mv, mw = sympy.symbols('mu mv mw')
-        # Replace
-        PS = rall(sel=eur)
-        r0 = Matrix([u0, v0, w0])
-        r1 = PS[0].subs([(n, n1), (m, m1)]) * r0
-        r2 = PS[1].subs([(n, n2), (m, m2)]) * r1
-        RR = PS[2].subs([(n, n3), (m, m3)]) * r2
-        sympy.expand(RR.row(0)[0])
-        sympy.expand(RR.row(1)[0])
-        sympy.expand(RR.row(2)[0])
-        av = sympy.collect(sympy.expand(RR.row(0)[0]), (u0, v0, w0))
-        bv = sympy.collect(sympy.expand(RR.row(1)[0]), (u0, v0, w0))
-        cv = sympy.collect(sympy.expand(RR.row(2)[0]), (u0, v0, w0))
-        a1s = av.coeff(u0)
-        a2s = av.coeff(v0)
-        a3s = av.coeff(w0)
-        b1s = bv.coeff(u0)
-        b2s = bv.coeff(v0)
-        b3s = bv.coeff(w0)
-        c1s = cv.coeff(u0)
-        c2s = cv.coeff(v0)
-        c3s = cv.coeff(w0)
-        Eu = Eq(x, a1s * u0 + a2s * v0 + a3s * w0)
-        Ev = Eq(y, b1s * u0 + b2s * v0 + b3s * w0)
-        Ew = Eq(z, c1s * u0 + c2s * v0 + c3s * w0)
-        abc = [a1s, a2s, a3s, b1s, b2s, b3s, c1s, c2s, c3s]
-        # Manual
-        pvar = [w0, v0, u0, w0**2, v0*w0, v0**2, u0*w0, u0*v0, u0**2, w0**3, v0*w0**2, v0**2*w0, v0**2*w0, v0**3, u0*w0**2, u0*v0*w0, u0*v0**2, u0**2*w0, u0**2*v0, u0**3]
-        # Connect to rotmat
-        Eu = Eq(x, a1 * u0 + a2 * v0 + a3 * w0)
-        Ev = Eq(y, b1 * u0 + b2 * v0 + b3 * w0)
-        Ew = Eq(z, c1 * u0 + c2 * v0 + c3 * w0)
-        exprf = sympify(expr + '-' + solvd)
-        exprc = exprf.subs([(x, solve(Eu, x)[0]), (y, solve(Ev, y)[0]), (z, solve(Ew, z)[0])])
-        exprr = collect(expand(exprc), pvar)
-        xr = [] 
-        yr = []
-        zr = []
-        clma = ['u0','v0','w0','d','var','expr','expr2']
-        eqsn = len(exprr.args)
-        data = [["0"] * 7 for _ in range(eqsn)]
-        matarch = pandas.DataFrame(data, columns=clma)
-        matarch.loc[0, ['expr','expr2']]=exprr.args[0]
-        matarch.loc[0, ['d']]='d_000'
-        for i in range(1, eqsn):
-            expt = exprr.args[i]
-            expr = expt.args[-1]
-            varn = expt / expr
-            nrfs = len(varn.free_symbols)
-            matarch.loc[i, 'var'] = str(varn)
-            for j in range(0,nrfs):
-                varn = expt.args[j].as_base_exp()[0]
-                pown = expt.args[j].as_base_exp()[1]
-                matarch.loc[i, str(varn)] = pown
-            subd = {a1: a1s, a2: a2s, a3: a3s,b1: b1s, b2: b2s, b3: b3s,c1: c1s, c2: c2s, c3: c3s}
-            matarch.loc[i, 'expr'] = expr
-            matarch.loc[i, 'expr2'] = expr.subs(subd) 
-            cmbx = int(matarch.loc[i, 'u0'])
-            cmby = int(matarch.loc[i, 'v0'])
-            cmbz = int(matarch.loc[i, 'w0'])
-            dr = sum([cmbx, cmby, cmbz])
-            matarch.loc[i,'d']='d_'+"".join([str(dr),str(cmbx),str(cmby)])
-    dic1 = matarch.set_index('d')['expr'].to_dict()
-    dic2 = matarch.set_index('d')['expr2'].to_dict()
-    dic = [dic1,dic2][0]
-    A=[dic['d_330'],
-       dic['d_303'],
-       dic['d_300']]
-    B=[dic['d_320']*z+dic['d_321']*y+dic['d_220'],
-       dic['d_302']*z+dic['d_312']*x+dic['d_202'],
-       dic['d_301']*x+dic['d_310']*y+dic['d_200']]
-    C=[dic['d_310']*z**2+dic['d_311']*y*z+dic['d_312']*y**2+dic['d_210']*z+dic['d_211']*y+dic['d_110'],
-       dic['d_301']*z**2+dic['d_311']*y*z+dic['d_321']*y**2+dic['d_201']*z+dic['d_211']*y+dic['d_101'],
-       dic['d_302']*z**2+dic['d_311']*y*z+dic['d_320']*y**2+dic['d_201']*z+dic['d_210']*y+dic['d_110']]
-    D=[dic['d_300']*z**3+dic['d_301']*y*z**2+dic['d_302']*y**2*z+dic['d_303']*y**3+dic['d_200']*z**2+dic['d_201']*y*z+dic['d_202']*y**2+dic['d_100']*z+dic['d_101']*y+dic['d_000'],
-       dic['d_300']*z**3+dic['d_310']*y*z**2+dic['d_320']*y**2*z+dic['d_330']*y**3+dic['d_200']*z**2+dic['d_210']*y*z+dic['d_220']*y**2+dic['d_100']*z+dic['d_110']*y+dic['d_000'],
-       dic['d_303']*z**3+dic['d_312']*y*z**2+dic['d_321']*y**2*z+dic['d_330']*y**3+dic['d_202']*z**2+dic['d_211']*y*z+dic['d_220']*y**2+dic['d_101']*z+dic['d_110']*y+dic['d_000']]
-    E=[0,0,0,0]
-    nrs = dxyz[solvd]-1
-    ABCDE = [0, 0, 0, 0, 0]
-    ABCDE[0] = str(A[nrs])
-    ABCDE[1] = str(B[nrs])
-    ABCDE[2] = str(C[nrs])
-    ABCDE[3] = str(D[nrs])
-    ABCDE[4] = str(E[nrs])
-    msl = ['u0','v0','w0','expr','expr2']
-    matarch[msl]=matarch[msl].astype(str)
-    return ABCDE, matarch, abc
+:::

### 2024-07-09 index.qmd
latest

@@
   show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['dplyr','data.table','readr','ggplotly']             # Pre-install dependencies
+  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom'] 
   cell-options:
@@
 ```{webr-r}
+#| echo: fenced
+#| eval: true
 webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
@@
 library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
 ls(package:ManifoldDestinyWASMP)
 data(package='ManifoldDestinyWASMD')
-library(ggplot2)
-library(combinat)
-library(plotly)
-library(htmltools)
-library(broom)
-```
-
-```{webr-r}
 dfl <- ManifoldDestinyWASMD::yout
@@
 ```{webr-r}
-df
-```
-
-```{webr-r}
-ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
-ad
 ```

### 2024-07-09 randpython.qmd
abcran
latest

--- 2024-07-07 randpython.qmd
@@
   cache: false
+webr:
+  show-startup-message: false      # Display status of webR initialization
+  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
+  packages: ['dplyr','data.table']             # Pre-install dependencies
 filters:
+  - panelize
   - webr
+  - pyodide
 ---
-
-```{r}
-# script/R/simulations.R
-```
-
-1.
-
-```{webr-r}
-fit = lm(mpg ~ am, data = mtcars)
-summary(fit)
-```
-
-```{r,echo=F}
-knitr::knit_exit()
-```
 
@@
 </script>
+
+**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

### 2024-07-09 rigging.qmd
latest

--- 2024-07-09 randpython.qmd
@@
 ---
-
-[Coatless](https://www.youtube.com/watch?v=PZx9d21HnTo)
-
-@thecoatlessprofessor7674
-1 month ago
-Great question. The short gist is yes in the *interactive* context for now.
-
-We'll likely need to make another extension that wraps before {quarto-webr} and {quarto-pyodide} to enable cross talk in the *non-interactive**/**output* contexts.
-
-# Python
-
-<head>
-  <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
-</head>
-
-<body>
-  <p>
-    You can execute any Python code. Just enter something in the box below and
-    click the button.
-  </p>
-  <input id="code" value="sum([1, 2, 3, 4, 5])" />
-  <button onclick="evaluatePython()">Run</button>
-  <br />
-  <br />
-  <div>Output:</div>
-  <textarea id="output" style="width: 100%;" rows="6" disabled></textarea>
-
-  <script>
-    const output = document.getElementById("output");
-    const code = document.getElementById("code");
-
-    function addToOutput(s) {
-      output.value += ">>>" + code.value + "\n" + s + "\n";
-    }
-
-    output.value = "Initializing...\n";
-    // init Pyodide
-    async function main() {
-      let pyodide = await loadPyodide();
-      output.value += "Ready!\n";
-      return pyodide;
-    }
-    let pyodideReadyPromise = main();
-
-    async function evaluatePython() {
-      let pyodide = await pyodideReadyPromise;
-      try {
-        let output = pyodide.runPython(code.value);
-        addToOutput(output);
-      } catch (err) {
-        addToOutput(err);
-      }
-    }
-  </script>
-</body>
-
-# R
-
-<div>
-  <pre><code id="out">Loading webR, please wait...</code></pre>
-  <input spellcheck="false" autocomplete="off" id="input" type="text">
-  <button onclick="globalThis.sendInput()" id="run">Run</button>
-</div>
-
-<script type="module">
-  /* Create a webR console using the Console helper class */
-  import { Console } from 'https://webr.r-wasm.org/latest/webr.mjs';
-  const webRConsole = new Console({
-    stdout: line => document.getElementById('out').append(line + '\n'),
-    stderr: line => document.getElementById('out').append(line + '\n'),
-    prompt: p => document.getElementById('out').append(p),
-  });
-  webRConsole.run();
-
-  /* Write to the webR console using the ``stdin()`` method */
-  let input = document.getElementById('input');
-  globalThis.sendInput = () => {
-    webRConsole.stdin(input.value);
-    document.getElementById('out').append(input.value + '\n');
-    input.value = "";
-  }
-
-  /* Send input on Enter key */
-  input.addEventListener(
-    "keydown",
-    (evt) => {if(evt.keyCode === 13) globalThis.sendInput()}
-  );
-</script>
-
-**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

### 2024-07-09 simulations.qmd
latest

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
webr:
  show-startup-message: false      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','ggplot2','combinat','plotly','htmltools','broom'] # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - webr
  - pyodide
---

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMP)
data(package='ManifoldDestinyWASMD')
library(ggplot2)
library(combinat)
library(plotly)
library(htmltools)
library(broom)
set.seed(1)
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
probw <- c(m=0.51,s=0.10)
probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
ztech <- c(0,1)	
mdn <- list(frn=1,eq="alpha=k0+k1*x+k2*y")
app_bal <- list(df=ballcastsim(dfm,probw,probva,probvb,ztech),list(fr=1,eq="alpha=k0+k1*x+k2*y"))
app_bal[1]
```

```{webr-r}
```

**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

```{r,echo=F}
knitr::knit_exit()
```

### 2024-07-09 randpython.qmd
python

@@
 title: ""
-output: github_document
-always_allow_html: true
 execute: 
@@
   show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['dplyr','data.table']             # Pre-install dependencies
+  packages: ['dplyr','data.table','ggplot2','combinat','plotly','htmltools','broom'] # Pre-install dependencies
+  cell-options:
+    autorun: true
 filters:
@@
 
-[Coatless](https://www.youtube.com/watch?v=PZx9d21HnTo)
+```{pyodide-python}
+import sympy, pandas, numpy
+from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
+def rall(sel=[0, 0, 0]):
+    n, m = symbols('n m')
 
-@thecoatlessprofessor7674
-1 month ago
-Great question. The short gist is yes in the *interactive* context for now.
+    rxy = Matrix([[m, -n, 0], 
+                  [n, m, 0],
+                  [0, 0, 1]])
 
-We'll likely need to make another extension that wraps before {quarto-webr} and {quarto-pyodide} to enable cross talk in the *non-interactive**/**output* contexts.
+    rxz = Matrix([[m, 0, -n], 
+                  [0, 1, 0],
+                  [n, 0, m]])
+
+    ryx = Matrix([[m, n, 0], 
+                  [-n, m, 0],
+                  [0, 0, 1]])
+
+    ryz = Matrix([[1, 0, 0], 
+                  [0, m, -n],
+                  [0, n, m]])
+
+    rzx = Matrix([[m, 0, n], 
+                  [0, 1, 0],
+                  [-n, 0, m]])
+
+    rzy = Matrix([[1, 0, 0], 
+                  [0, m, n],
+                  [0, -n, m]])
+
+    ps = [0, rxy, rxz, ryx, ryz, rzx, rzy]
+
+    allrot = [ps[i] for i in sel]
+    return allrot
+
+def genpolycoeff(plr=1,parm=["alpha", "x", "y"],solvd='alpha',eur=[0, 0, 0]):
+    x, y, z = sympy.symbols('x y z')
+    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
+    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
+    expr = [Eq(z,k0+k1*x+k2*y),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3)][plr-1]
+    sum_eur = sum(eur)
+    # Without rotation
+    if sum_eur == 0:
+        exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
+        polys = poly(exprc, sympify(solvd)).all_coeffs()
+        abc = []
+        uvw = []
+        ABCDE = [0, 0, 0, 0, 0]
+        ABCDE[:len(polys)] = polys
+        return ABCDE 
+    # With rotation
+    else:
+        dxyz = {'x': 1, 'y': 2, 'z': 3}
+        # Defining
+        x,  y,  z  = sympy.symbols('x y z')
+        ui, vi, wi = sympy.symbols('ui vi wi')
+        u0, v0, w0 = sympy.symbols('u0 v0 w0')
+        u1, v1, w1 = sympy.symbols('u1 v1 w1')
+        u2, v2, w2 = sympy.symbols('u2 v2 w2')
+        a1, a2, a3 = sympy.symbols('a1 a2 a3')
+        b1, b2, b3 = sympy.symbols('b1 b2 b3')
+        c1, c2, c3 = sympy.symbols('c1 c2 c3')
+        m1, m2, m3 = sympy.symbols('m1 m2 m3')
+        n1, n2, n3 = sympy.symbols('n1 n2 n3')
+        mu, mv, mw = sympy.symbols('mu mv mw')
+        # Replace
+        PS = rall(sel=eur)
+        r0 = Matrix([u0, v0, w0])
+        r1 = PS[0].subs([(n, n1), (m, m1)]) * r0
+        r2 = PS[1].subs([(n, n2), (m, m2)]) * r1
+        RR = PS[2].subs([(n, n3), (m, m3)]) * r2
+        sympy.expand(RR.row(0)[0])
+        sympy.expand(RR.row(1)[0])
+        sympy.expand(RR.row(2)[0])
+        av = sympy.collect(sympy.expand(RR.row(0)[0]), (u0, v0, w0))
+        bv = sympy.collect(sympy.expand(RR.row(1)[0]), (u0, v0, w0))
+        cv = sympy.collect(sympy.expand(RR.row(2)[0]), (u0, v0, w0))
+        a1s = av.coeff(u0)
+        a2s = av.coeff(v0)
+        a3s = av.coeff(w0)
+        b1s = bv.coeff(u0)
+        b2s = bv.coeff(v0)
+        b3s = bv.coeff(w0)
+        c1s = cv.coeff(u0)
+        c2s = cv.coeff(v0)
+        c3s = cv.coeff(w0)
+        Eu = Eq(x, a1s * u0 + a2s * v0 + a3s * w0)
+        Ev = Eq(y, b1s * u0 + b2s * v0 + b3s * w0)
+        Ew = Eq(z, c1s * u0 + c2s * v0 + c3s * w0)
+        abc = [a1s, a2s, a3s, b1s, b2s, b3s, c1s, c2s, c3s]
+        # Manual
+        pvar = [w0, v0, u0, w0**2, v0*w0, v0**2, u0*w0, u0*v0, u0**2, w0**3, v0*w0**2, v0**2*w0, v0**2*w0, v0**3, u0*w0**2, u0*v0*w0, u0*v0**2, u0**2*w0, u0**2*v0, u0**3]
+        # Connect to rotmat
+        Eu = Eq(x, a1 * u0 + a2 * v0 + a3 * w0)
+        Ev = Eq(y, b1 * u0 + b2 * v0 + b3 * w0)
+        Ew = Eq(z, c1 * u0 + c2 * v0 + c3 * w0)
+        # Start with non-rotated
+        exprf = solve(expr,z)[0]-z
+        exprc = exprf.subs([(x, solve(Eu, x)[0]), (y, solve(Ev, y)[0]), (z, solve(Ew, z)[0])])
+        # Reorganize
+        exprr = collect(expand(exprc), pvar)
+        xr = [] 
+        yr = []
+        zr = []
+        clma = ['u0','v0','w0','d','var','expr','expr2']
+        eqsn = len(exprr.args)
+        data = [["0"] * 7 for _ in range(eqsn)]
+        matarch = pandas.DataFrame(data, columns=clma)
+        matarch.loc[0, ['expr','expr2']]=exprr.args[0]
+        matarch.loc[0, ['d']]='d_000'
+        for i in range(1, eqsn):
+            expt = exprr.args[i]
+            expr = expt.args[-1]
+            varn = expt / expr
+            nrfs = len(varn.free_symbols)
+            matarch.loc[i, 'var'] = str(varn)
+            for j in range(0,nrfs):
+                varn = expt.args[j].as_base_exp()[0]
+                pown = expt.args[j].as_base_exp()[1]
+                matarch.loc[i, str(varn)] = pown
+                subd = {a1: a1s, a2: a2s, a3: a3s,b1: b1s, b2: b2s, b3: b3s,c1: c1s, c2: c2s, c3: c3s}
+                matarch.loc[i, 'expr'] = expr
+                matarch.loc[i, 'expr2'] = expr.subs(subd) 
+                cmbx = int(matarch.loc[i, 'u0'])
+                cmby = int(matarch.loc[i, 'v0'])
+                cmbz = int(matarch.loc[i, 'w0'])
+                dr = sum([cmbx, cmby, cmbz])
+                matarch.loc[i,'d']='d_'+"".join([str(dr),str(cmbx),str(cmby)])
+                dic1 = matarch.set_index('d')['expr'].to_dict()
+                dic2 = matarch.set_index('d')['expr2'].to_dict()
+                dic = [dic1,dic2][0]
+                nrs = dxyz[solvd]-1
+        ABCDE = [0, 0, 0, 0, 0]
+        A=Matrix([0,0,0])
+        B=Matrix([0,0,0])
+        C=Matrix([0,0,0])
+        D=Matrix([0,0,0])
+        E=Matrix([0,0,0])
+        if plr in [3]:
+            A[0] +=  dic['d_330']
+            A[1] +=  dic['d_303']
+            A[2] +=  dic['d_300']
+            B[0] +=  dic['d_320']*u0+dic['d_321']*w0
+            B[1] +=  dic['d_302']*u0+dic['d_312']*v0
+            B[2] +=  dic['d_301']*w0+dic['d_310']*v0
+            C[0] +=  dic['d_310']*u0**2+dic['d_311']*u0*w0+dic['d_312']*w0**2+dic['d_110']
+            C[1] +=  dic['d_301']*u0**2+dic['d_311']*u0*v0+dic['d_321']*v0**2+dic['d_101']
+            C[2] +=  dic['d_302']*w0**2+dic['d_311']*w0*v0+dic['d_320']*w0**2+dic['d_201']*v0+dic['d_210']*w0+dic['d_110']
+            D[0] += dic['d_300']*u0**3+dic['d_301']*w0*u0**2+dic['d_302']*w0**2*u0+dic['d_303']*w0**3
+            D[1] += dic['d_300']*u0**3+dic['d_310']*u0*v0**2+dic['d_320']*v0**2*u0+dic['d_330']*v0**3
+            D[2] += dic['d_303']*v0**3+dic['d_312']*w0*v0**2+dic['d_321']*w0**2*v0+dic['d_330']*v0**3
+        if plr in [2,3]:
+            B[0] += dic['d_220']
+            B[1] += dic['d_202']
+            B[2] += dic['d_200']
+            C[0] += dic['d_210']*u0+dic['d_211']*w0
+            C[1] += dic['d_201']*u0+dic['d_211']*v0
+            C[2] += dic['d_201']*v0+dic['d_210']*w0
+            D[0] += dic['d_200']*u0**2+dic['d_201']*w0*u0+dic['d_202']*w0**2
+            D[1] += dic['d_200']*u0**2+dic['d_210']*v0*u0+dic['d_220']*v0**2
+            D[2] += dic['d_202']*v0**2+dic['d_211']*v0*w0+dic['d_220']*w0**2
+        if plr in [1,2,3]:
+            C[0] += dic['d_110']
+            C[1] += dic['d_101']
+            C[2] += dic['d_110']
+            D[0] += dic['d_100']*u0+dic['d_101']*w0+dic['d_000']
+            D[1] += dic['d_100']*u0+dic['d_110']*v0+dic['d_000']
+            D[2] += dic['d_101']*v0+dic['d_110']*w0+dic['d_000']
+        ABCDE[0] = A[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
+        ABCDE[1] = B[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
+        ABCDE[2] = C[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
+        ABCDE[3] = D[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
+        ABCDE[4] = E[nrs]
+        indpr = [[2,3,4,0,1],[1,2,3,4,0],[0,1,2,3,4]]
+        ABCDE = [ABCDE[i] for i in indpr[plr-1]]
+        msl = ['u0','v0','w0','expr','expr2']
+        matarch[msl]=matarch[msl].astype(str)
+        return ABCDE, matarch, abc
+
+```
+
+```{pyodide-python}
+genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y') 
+genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y',eur=[1, 4, 2])[0]
+```
+
+```{pyodide-python}
+def pareq(ste='(x + y*zeta)/(zeta + 1)', **kwargs):
+    return eval(ste, kwargs)
+```
+
+```{pyodide-python}
+pareq(ste='(x + y*zeta)/(zeta + 1)', x=0.75, y=0.25, zeta=1)
+pareq(ste='(x + y*zeta)/(zeta + 1)', y=0.25, zeta=1,x=2.75)
+```
 
@@
 **Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
+
+```{r, echo=F}
+knitr::knit_exit()
+```

### 2024-07-09 rigging.qmd
python

@@
 ---
+
+```{webr-r}
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+ls(package:ManifoldDestinyWASMP)
+data(package='ManifoldDestinyWASMD')
+library(ggplot2)
+library(combinat)
+library(plotly)
+library(htmltools)
+library(broom)
+set.seed(1)
+dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
+probw <- c(m=0.51,s=0.10)
+probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
+probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
+ztech <- c(0,1)	
+mdn <- list(frn=1,eq="alpha=k0+k1*x+k2*y")
+app_bal <- list(df=ballcastsim(dfm,probw,probva,probvb,ztech),list(fr=1,eq="alpha=k0+k1*x+k2*y"))
+app_bal[1]
+```
+
+```{webr-r}
+abc <- SimVoterdatabase()
+```

### 2024-07-09 analyzer.qmd
python
glance

--- 2024-07-09 simulations.qmd
@@
 
+## Install
+
 ```{webr-r}
+#| echo: fenced
+#| eval: true
 webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
@@
 library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
 ls(package:ManifoldDestinyWASMP)
 data(package='ManifoldDestinyWASMD')
-library(ggplot2)
-library(combinat)
-library(plotly)
-library(htmltools)
-library(broom)
-set.seed(1)
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
-probw <- c(m=0.51,s=0.10)
-probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztech <- c(0,1)	
-mdn <- list(frn=1,eq="alpha=k0+k1*x+k2*y")
-app_bal <- list(df=ballcastsim(dfm,probw,probva,probvb,ztech),list(fr=1,eq="alpha=k0+k1*x+k2*y"))
-app_bal[1]
 ```
 
+## Select case
+
 ```{webr-r}
+dfl <- ManifoldDestinyWASMD::yout
 ```
 
-**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
+## Counting
 
-```{r,echo=F}
-knitr::knit_exit()
+```{webr-r}
+Countingprocess(dfl)
 ```
+
+## Estimation

### 2024-07-09 index.qmd
glance

@@
   show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom'] 
+  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
   cell-options:
@@
 library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
 ls(package:ManifoldDestinyWASMP)
@@
 dfl <- ManifoldDestinyWASMD::yout
-df <- dplyr::select(dfl[[1]],S,T,U,V)
 ```
@@
 ```{webr-r}
+coi <- Countingprocess(dfl[[1]])
+ges <- Estimation(coi$rdfc,2)
+ges$regression("alpha=k0+k1*g+k2*h")
+ges$diagnostics()
+broom::tidy(ges$regsum[[1]])
+broom::glance(ges$regsum[[1]])
 ```

### 2024-07-10 tabsets.qmd
bbilio
wokring

@@
 
-```{r, echo=F, message=F, warning=F}
-ManifoldDestiny::wasmconload()
-md <- ManifoldDestiny::metd
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
-```
-
-```{r, echo=F,message=FALSE,warning=FALSE}
+```{r, echo=F, warnings=F,messages=T}
 ManifoldDestiny::wasmconload()
@@
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
-mda <- app0[[2]]
-asrp <- selreport(app0)
-asop <- seloutput(asrp)
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 ```
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-#app_a_out <- app_0_out 
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-text <- readLines(app1_fil)
+#apst <- app_n_out
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
 #cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
@@
 ## {{< var tabh.h3 >}}
+```{r, echo=FALSE, results='asis',warning=F}
+#app_a_out <- app_2_out 
+#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+#text <- readLines(app1_fil)
+#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+:::
+
+::: {.callout-caution collapse="true"}
+## {{< var tabh.h4 >}}
 ```{r, echo=FALSE, results='asis',warning=F}

### 2024-07-10 tabsets.qmd
befrev

@@
 ```{r, echo=FALSE, results='asis',warning=F}
-#apst <- app_n_out
-#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-#text <- readLines(app1_fil)
-#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+apps <- seln
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-#app_a_out <- app_1_out 
-#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-#text <- readLines(app1_fil)
-#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+apps <- seln
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-#app_a_out <- app_2_out 
-#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-#text <- readLines(app1_fil)
-#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+apps <- seln
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-#app_a_out <- app_2_out 
-#app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
-#text <- readLines(app1_fil)
-#cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+apps <- seln
+app_a_out <- seln
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/app_par.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```

### 2024-07-10 tab.qmd
okay

---
title: ""
params:
  name: "0"
---

```{r, echo=F}
params$name
```

```{r, echo=F,message=FALSE,warning=FALSE}
sw <- as.numeric(params$name)
if(sw == 0) {
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
apps <- ManifoldDestiny::app0
}
```

```{r}
adat <- apps[[1]]
amet <- apps[[2]]
cogr <- Countinggraphs(apps[[1]])
selo <- seloutput(selreport(apps))
copl <- cogr$polyc[[1]][[1]]
```

::: {.panel-tabset}

### {{< var tabs.h1 >}}

```{r, echo=F}
kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### {{< var tabs.h2 >}}
```{r, echo=F, out.width="60%"}
selo[['corxy']]
```
### {{< var tabs.h3 >}}
```{r, echo=F, out.width="60%"}
selo[['qunt']]
```
### {{< var tabs.h4 >}}
```{r, echo=F}
selo[['ro3d']]
```
### {{< var tabs.h5 >}}
```{r, echo=F, out.width="60%"}
selo[['regr']]
```
### {{< var tabs.h6 >}}
```{r, echo=F, out.width="60%"}
selo[['resp']]
```
:::

### 2024-07-10 tabset.qmd
okay

---
title: "ABC"
---

```{r, echo=F, warnings=F,messages=T}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
```

::: {.callout-caution collapse="true"}
## {{< var tabh.h1 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h2 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h3 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var tabh.h4 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un1 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un2 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un3 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app_a_out <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

::: {.callout-caution collapse="true"}
## {{< var sec6.un4 >}}
```{r, echo=FALSE, results='asis',warning=F}
apps <- basc
app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
text <- readLines(app1_fil)
cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
```
:::

### 2024-07-10 script/R/simulations.R

@@ -16,27 +16,27 @@ prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
 ztec <- c(0,1)	
 basc <- list(df=ballcastsim(perv,prow,proa,prob,ztec),list(fr=1,eq="alpha=k0+k1*x+k2*y"))
 # Normal form
-cogr <- Countinggraphs(basc[[1]])
-seln <- seloutput(selreport(basc))
-copl <- cogr$polyc[[1]][[1]]
 # Rigged election
-frms <- c(1,1,1)
-plnr <- c(1,2,3)
-exs <- c("ex1", "ex2", "ex3")
-pvec <- c(1,2,3)[1]
-rigv <- lapply(exs, function(x) { 
-  cogr$mansys(sygen=list(frm=1, 
-  		pre=c("alpha","x","y"),
-  		end=c("zeta","Omega","lamda"),
-  		stuv=c("S","T","U","V"),
-  		plnr=1,
-  		lf="(alpha-alpha_s)^2"))
-  cogr$setres(0.19,1)
-  #cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
-  rigc <- basc
-  sero <- seloutput(selreport(rigc))
-  return(list(sero,sero))
-})
+#cogr <- Countinggraphs(basc[[1]])
+#seln <- seloutput(selreport(basc))
+#copl <- cogr$polyc[[1]][[1]]
+#frms <- c(1,1,1)
+#plnr <- c(1,2,3)
+#exs <- c("ex1", "ex2", "ex3")
+#pvec <- c(1,2,3)[1]
+#rigv <- lapply(exs, function(x) { 
+#  cogr$mansys(sygen=list(frm=1, 
+#  		pre=c("alpha","x","y"),
+#  		end=c("zeta","Omega","lamda"),
+#  		stuv=c("S","T","U","V"),
+#  		plnr=1,
+#  		lf="(alpha-alpha_s)^2"))
+#  cogr$setres(0.19,1)
+#  #cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
+#  rigc <- basc
+#  sero <- seloutput(selreport(rigc))
+#  return(list(sero,sero))
+#})
 #ismv <- SimVoterdatabase(basc[[1]])
 #crpl <- SimVoterdatabase(rigc[[1]])
 ####################################################################################################################################################################

### 2024-07-10 tabset.qmd
setup

@@
 ---
-title: "ABC"
+title: ""
 ---
 
-```{r, echo=F, warnings=F,messages=T}
+```{r}
+#| echo: false
+#| output: false
+#| message: false
 ManifoldDestiny::wasmconload()

### 2024-07-10 tabset.qmd
abc

@@
 ::: {.callout-caution collapse="true"}
-## {{< var tabh.h1 >}}
+## {{< var tabh.h0 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
@@
 ::: {.callout-caution collapse="true"}
+## {{< var tabh.h1 >}}
+```{r, echo=FALSE, results='asis',warning=F}
+apps <- rigv[[1]]
+app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
+text <- readLines(app1_fil)
+cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```
+:::
+
+::: {.callout-caution collapse="true"}
 ## {{< var tabh.h2 >}}
 ```{r, echo=FALSE, results='asis',warning=F}
-apps <- basc
+apps <- rigv[[2]]
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-apps <- basc
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
-```
-:::
-
-::: {.callout-caution collapse="true"}
-## {{< var tabh.h4 >}}
-```{r, echo=FALSE, results='asis',warning=F}
-apps <- basc
+apps <- rigv[[3]]
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')

### 2024-07-10 script/R/simulations.R

@@ -15,7 +15,6 @@ proa <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
 prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
 ztec <- c(0,1)	
 basc <- list(df=ballcastsim(perv,prow,proa,prob,ztec),list(fr=1,eq="alpha=k0+k1*x+k2*y"))
-# Normal form
 # Rigged election
 cogr <- Countinggraphs(basc[[1]])
 copl <- cogr$polyc[[1]][[1]]
@@ -31,7 +30,7 @@ rigv <- lapply(exs, function(x) {
   		plnr=1,
   		lf="(alpha-alpha_s)^2"))
   cogr$setres(0.19,1)
-  cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
+  #cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
   rasc <- basc
   return(rasc)
 })

### 2024-07-10 tab.qmd
updapp

@@
 
-```{r, echo=F}
+```{r, echo=T}
 params$name
@@
 ```{r, echo=F,message=FALSE,warning=FALSE}
+#| echo: false
+#| output: false
+#| message: false
 sw <- as.numeric(params$name)
@@
 ```{r}
+#| echo: false
+#| output: false
+#| message: false
+#| warning: false
 adat <- apps[[1]]

### 2024-07-10 tabset.qmd
abc
updapp

@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 ```
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-apps <- basc
+apps <- app1
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-apps <- basc
+apps <- app2
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-apps <- basc
+apps <- app3
 app_a_out <- basc
@@
 ```{r, echo=FALSE, results='asis',warning=F}
-apps <- basc
+apps <- app4
 app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')

### 2024-07-11 paper.qmd
abc

@@
 ---
+
+```{r}
+library(ManifoldDestiny)
+library(huxtable)
+library(kableExtra)
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+```
 
@@
 # {{< var sec3.nmn >}}
+
 ## {{< var sec3.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- basc
+```
+{{< include tab.qmd >}}
+
 ## {{< var sec3.un2 >}}
+### Normal form
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[1]]
+```
+{{< include tab.qmd >}}
+
+### Hybrid
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[2]]
+```
+{{< include tab.qmd >}}
+
+### Opposition
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[3]]
+```
+{{< include tab.qmd >}}
 
@@
 # {{< var sec6.nmn >}}
+
 ## {{< var sec6.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- ManifoldDestiny::app1
+```
+{{< include tab.qmd >}}
+
 ## {{< var sec6.un2 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- ManifoldDestiny::app2
+```
+{{< include tab.qmd >}}
+
 ## {{< var sec6.un3 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- ManifoldDestiny::app2
+```
+{{< include tab.qmd >}}
+
 ## {{< var sec6.un4 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- ManifoldDestiny::app4
+```
+{{< include tab.qmd >}}
 
@@
 ```
-
-```{r, echo=FALSE, results='asis',warning=F}
-#presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
-#textm <- readLines(presm)
-#cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
-```

### 2024-07-11 tab.qmd
abc

@@
----
-title: ""
-params:
-  name: "0"
----
-
-```{r, echo=T}
-params$name
-```
-
 ```{r, echo=F,message=FALSE,warning=FALSE}
@@
 #| message: false
+params <- list(name="0")
 sw <- as.numeric(params$name)

### 2024-07-11 script/R/simulations.R

@@ -32,7 +32,8 @@ rigv <- lapply(exs, function(x) {
   		lf="(alpha-alpha_s)^2"))
   cogr$setres(0.19,1)
   cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
-  rasc <-cogr$rdfc
+  rasc <- basc
+  #rasc <-cogr$rdfc
   return(rasc)
 })
 ####################################################################################################################################################################

### 2024-07-11 tab.qmd
tabset

@@
-```{r, echo=F,message=FALSE,warning=FALSE}
-#| echo: false
-#| output: false
-#| message: false
-params <- list(name="0")
-sw <- as.numeric(params$name)
-if(sw == 0) {
-ManifoldDestiny::wasmconload()
-library(ManifoldDestiny)
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
-apps <- ManifoldDestiny::app0
-}
-```
-
 ```{r}

### 2024-07-11 paper.qmd
brak

--- 2024-07-09 paper.qmd
@@
 ---
+
+```{r}
+ManifoldDestiny::wasmconload()
+library(ManifoldDestiny)
+library(huxtable)
+library(kableExtra)
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+```
 
@@
 # {{< var sec3.nmn >}}
+
 ## {{< var sec3.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- basc
+```
+{{< include tabpar.qmd >}}
+
 ## {{< var sec3.un2 >}}
+### Normal form
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[1]]
+```
+{{< include tab.qmd >}}
+
+---
+
+### Hybrid
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[2]]
+```
+{{< include tab.qmd >}}
+
+---
+
+### Opposition
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[3]]
+```
+
+{{< include tab.qmd >}}
 
@@
 # {{< var sec6.nmn >}}
+
 ## {{< var sec6.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app1
+```
+{{< include tabpar.qmd >}}
+
 ## {{< var sec6.un2 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app2
+```
+{{< include tabpar.qmd >}}
+
 ## {{< var sec6.un3 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app2
+```
+{{< include tabpar.qmd >}}
 ## {{< var sec6.un4 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app4
+```
+{{< include tabpar.qmd >}}
 
@@
 # {{< var sec8.nmn >}}
-
-```{r,echo=F}
-knitr::knit_exit()
-```
-
-```{r, echo=FALSE, results='asis',warning=F}
-#presm <- paste0(rprojroot::find_rstudio_root_file(), '/presentation.qmd')
-#textm <- readLines(presm)
-#cat(knitr::knit_child(text = paste(textm[25:length(textm)], collapse = "\n"), quiet = TRUE))
-```

### 2024-07-11 presentation.qmd
abc

@@
 ```{r, echo=F, message=F, warning=F, results='hide'}
+ManifoldDestiny::wasmconload()
 library(huxtable)
 library(kableExtra)
-#Sys.info()[['sysname']]=="Emscripten"
-#ManifoldDestiny::wasmconload()
-metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
-md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
+library(ManifoldDestiny)
 laws_df1 <- ManifoldDestiny::eqdef$meql
@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/r/simulations.r'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
 #source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
@@
 
-##
+---
 
@@
 ::: {.column width="50%"}
-Case 1
 :::
 ```{r, echo=F}
+#| label: fig-1.1
+#| fig-cap: "Case 1:"
 clr <- c("black","green","red","blue")
@@
 
+---
+
 ::: {.column width="50%"}
-Case 2
 :::
 ```{r, echo=F}
+#| label: fig-1.2
+#| fig-cap: "Case 2:"
 lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
@@
 ```{r, echo=F}
-ctone_sf <- 'Election results applying standard form on case I'
+#| label: tbl-sfc1
+#| tbl-cap: 'Election results applying standard form on case I'
 stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
 cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 ```{r, echo=F}
-lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
+lego_hux_imp <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
   set_background_color(1:2, 1, "black") %>% 
@@
 ```{r, echo=F}
-ctone_hf <- 'Election results applying hybrid form case I'
+#| label: tbl-sfc2
+#| tbl-cap: 'Election results applying hybrid form case I'
 stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 ```{r, echo=F}
-ctone_hf <- 'Election results applying hybrid form case II'
+#| label: tbl-hfc2
+#| tbl-cap: 'Election results applying hybrid form case II'
 stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 ```{r, echo=F}
-ctone_of <- 'Election results applying opposition form'
+#| label: tbl-hfc3
+#| tbl-cap: 'Election results applying hybrid form case II'
 stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
-kableExtra::kbl(format(stfo_sel,digits=4), caption=ctone_of) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 [Application 1: Election process simulator]({{< var shn1 >}})
+
+```{r, echo=F}
+knitr::knit_exit()
+```
 
@@
 ## {{< var sec3.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- basc
+```
+{{< include tabpar.qmd >}}
 
 ## {{< var sec3.un2 >}}
+
+### Normal form
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[1]]
+```
+{{< include tab.qmd >}}
+
+---
+
+### Hybrid
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[2]]
+```
+{{< include tab.qmd >}}
+
+---
+
+### Opposition
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[3]]
+```
+{{< include tab.qmd >}}
 
@@
 
-{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
+![](images/manifold.png){width=300}
 
@@
 
-![](images/manifold.png){width=300}
+** Abc | S-A **
 
----
+{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
 
@@
 ## {{< var sec6.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app1
+```
+{{< include tabpar.qmd >}}
+
 ## {{< var sec6.un2 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app2
+```
+{{< include tabpar.qmd >}}
+
 ## {{< var sec6.un3 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app2
+```
+{{< include tabpar.qmd >}}
 ## {{< var sec6.un4 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app4
+```
+{{< include tabpar.qmd >}}
 
@@
 # {{< var sec8.nmn >}}
-
-# {{< var sec9.nmn >}}
 
@@
 
+```{r, echo=F, warning=F, message=F}
+#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+# {{< var sec9.nmn >}}
+
 ::: {#refs}
 :::
-
-```{r}
-knitr::knit_exit()
-```

### 2024-07-12 presentation.qmd
tabbed

@@
   - Number of ballots mode 1: S, T
-  - Number of ballots mode 2: U, V
+  - Number of ballots mode 2: V, U
 
@@
 #| label: fig-1.1
-#| fig-cap: "Case 1:"
+#| fig-cap: "Case 1:.."
 clr <- c("black","green","red","blue")
@@
 #| label: fig-1.2
-#| fig-cap: "Case 2:"
+#| fig-cap: "Case 2:..."
 lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%

### 2024-07-12 presentation.qmd
justtowi

@@
   set_font_size(16)
-
 lego_hux_imp_ii
@@
 ::::
+
 ## {{< var sec1.un2 >}}
@@
 \end{equation*}
-
-##
 

### 2024-07-12 R/wasmconverting.R

@@ -242,7 +242,7 @@ seloutput <- function(selreport=NULL){
   l3 <- selreport[[2]]$resplots[[1]][[3]]
   l4 <- selreport[[2]]$resplots[[1]][[4]]
   tab8 <- cowplot::plot_grid(plotlist=list(l1,l2,l3,l4))
-  tab8 <- selreport[[2]]$comdesc
+  tab9 <- selreport[[2]]$comdesc
   tab10 <- selreport[[4]]
   tab11 <- selreport[[5]]$pl_2dsort
   tab12 <- selreport[[6]]
@@ -548,7 +548,7 @@ Countingprocess$methods(plext=function(){
     dplyr::mutate(xy=x*y)
 })
 
-Countingprocess$methods(purging=function(z=0,stuv=c(0,0,0,0),blup=c(0,1),eqp=c("alpha=k0+k1*x+k2*y"),pri=0){
+Countingprocess$methods(purging=function(z=0,stuv=c(0,0,0,0),blup=c(0,1),eqp=c("alpha=k0+k1*x+k2*y"),rnk=0,pres=NULL,pri=0){
   rdfv <- rdfci %>%
     dplyr::arrange(P) %>%
     dplyr::filter(Z>=stuv[1]) %>%
@@ -557,14 +557,19 @@ Countingprocess$methods(purging=function(z=0,stuv=c(0,0,0,0),blup=c(0,1),eqp=c("
     dplyr::filter(U>=stuv[3]) %>%
     dplyr::filter(V>=stuv[4]) %>%
     ## Percentages
+    #sum(dplyr::select(rdfv,S,T,U,V))
     dplyr::filter(if_all(c(alpha,x,y,g,h,m,n),~.>blup[1]&.<blup[2]))
     # Fit filter
+    #browser()
+    #eqp <- "V=k0+k1*Z+k2*S"
     erdfv <- Estimation(rdfv)
     erdfv$regression(eqp)
+    erdfv$regsum[[1]]
     rdfc <<- erdfv$predict_df %>%
             dplyr::mutate(pre_rnk=dplyr::row_number(desc(deva))) %>%
             dplyr::arrange(pre_rnk) %>%
-            #dplyr::filter(pre_rnk>regr[[2]]) %>% dplyr::filter(!P%in%pref) %>%
+            dplyr::filter(pre_rnk>rnk) %>% 
+	    dplyr::filter(!P%in%pres) %>%
[…]

### 2024-07-12 presentation.qmd
break
ac

@@
     toc: true 
-#execute: 
-#  cache: false
-#webr: 
-#  show-startup-message: true    # Disable displaying status of webR initialization
-#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
-##filters:
-#- webr 
+execute: 
+  cache: true
 footer: <https://lotariohw26.github.io/ManifoldDestiny/>
@@
 
-:::: {.columns}
-::: {.column width="50%"}
-:::
 ```{r, echo=F}
@@
 
----
-
-::: {.column width="50%"}
-:::
 ```{r, echo=F}
@@
 ```
-::::
 
@@
 
+---
+
 ```{r, echo=F}
@@
 #| tbl-cap: 'Election results applying standard form on case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
-cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+#kableExtra::kbl(format(stfc1,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 
-## {{< var sec1.un3 >}}
-```{r, echo=F}
-lego_hux_imp <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
-  set_background_color(1:2, 1, "black") %>% 
-  set_background_color(1:2, 2, "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_imp %>% set_caption("")
-```
-
-Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
-\begin{equation*}
-g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
-\end{equation*}
-\begin{equation*}
-\Gamma=`r modlat$Gamma_h[1]`
-\end{equation*}
-\begin{equation*}
-\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
-\end{equation*}
-\begin{equation*}
-\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
-\end{equation*}
-
-##
+---
 
@@
 #| label: tbl-sfc2
-#| tbl-cap: 'Election results applying hybrid form case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+#| tbl-cap: 'Election results applying hybrid form on case II'
+#kableExtra::kbl(format(stfc2,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
-
-Numerical calculation of candidate one total percentage
-
-- Precinct 1
-  - $\alpha=\frac{`r cg[1]`+`r ch[1]`\cdot `r cGamma[1]`}{1+`r cGamma[1]`}=`r calpha[1]`$
-- Precinct 2
-  - $\alpha=\frac{`r cg[2]`+`r ch[2]`\cdot `r cGamma[2]`}{1+`r cGamma[2]`}=`r calpha[2]`$
-- Precinct 3
-  - $\alpha=\frac{`r cg[3]`+`r ch[3]`\cdot `r cGamma[3]`}{1+`r cGamma[3]`}=`r calpha[3]`$
-
----
-
-```{r, echo=F}
-#| label: tbl-hfc2
-#| tbl-cap: 'Election results applying hybrid form case II'
-stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-## {{< var sec1.un4 >}}
-```{r, echo=F}
-lego_hux_opo <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
-  set_background_color(c(1),c(1), "black") %>% 
-  set_background_color(c(2),c(2), "black") %>% 
-  set_background_color(c(1),c(2), "grey") %>% 
-  set_background_color(c(2),c(1), "grey") %>% 
-  set_text_color(1:2, 1:2, "red") %>% 
-  set_all_borders(brdr(2, "solid", "black"))
-lego_hux_opo %>% set_caption("")
-```
-
-Parameters: $m$, $n$, $\xi$, $\lambda$, $\Omega$
-\begin{equation*}
-n=`r modlat$n_o[1]` \text{ , } m=`r modlat$m_o[1]`
-\end{equation*}
-\begin{equation*}
-\xi=`r modlat$xi_o[1]`
-\end{equation*}
-\begin{equation*}
-\Omega=`r modlat$Omega_o[1]`=`r modlat$Omega_o[2]`
-\end{equation*}
-\begin{equation*}
-\lambda=`r modlat$lamda_o[1]`=`r modlat$lamda_o[2]`
-\end{equation*}
-
-##
-
-```{r, echo=F}
-#| label: tbl-hfc3
-#| tbl-cap: 'Election results applying hybrid form case II'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-## {{< var sec1.un5 >}}
-
-- **Step 1:** Each registered voter assign themself (independent of voting technology) to either candidate A or candidate B
-- **Step 2:** Voting technology realized
-- **Step 3:** Registered voters determine whether to vote or not to vote 
-- **Step 4:** If voting, do this by either mode 1 or by mode 2.
-
-```{mermaid}
-  flowchart LR
-  A[Candidate A or B] --> R[A]
-  R --> RV[Vote]
-  RV --> RVE[Non-Mail]
-  RV --> RVM[Mail]
-  R --> RN[Not Vote]
-  DV --> DVE[Non-Mail]
-  DV --> DVM[Mail]
-  A --> D[B]
-  D --> DV[Vote]
-  D --> Dn[Not Vote]
-```
-
-##
-
-- Probability of assigning oneself to candidate A in precinct $i$
-  - $p_{w,i} \sim N(\alpha_i,\sigma^2_{w,i})$
-- Voting technology
-  - $z_i \sim U(0,1)$
-- Probability of not voting in precinct $i$
-  - Candidate A, $p_{nz,a,i}=(1-z_i)p_{n,a,i}\sim N(\alpha_{a,n},\sigma^2_{a,n})$ <br>
-  - Candidate B, $p_{nz,b,i}=(1-z_i)p_{n,b,i}\sim N(\alpha_{b,n},\sigma^2_{b,n})$
-- Probability of voting by mode 2 in precinct $i$
-  - Candidate A, $p_{m2,a,i}=(1-p_{nv,a,i})p_{a,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
-  - Candidate B, $p_{m2,b,i}=(1-p_{nv,b,i})p_{b,mv}\sim N(\alpha_{a,mv},\sigma^2_{a,mv})$ 
-- Probability of voting by mode 1 in precinct $i$
-  - Candidate A, $p_{m1,a,i}=1-p_{m2,a,i}-p_{nz,a,i}$ 
-  - Candidate B, $p_{m1,b,i}=1-p_{m2,b,i}-p_{nz,b,i}$
-
----
-
-Neutral-voting assumption:
-
-- Decission to vote or not to vote is independent of voting preferences:
-  - $p_{nz,a,i}=p_{nz,a,i}$ 
-- If voting, decission to vote by mode 1 or by mode 2 independent of voting preferences: 
-  - $p_{m2,a,i}=p_{m2,a,i}$
-
-Note: As we will investigate later, this condition might be needed in order to restore a rigged election to its original form.
-
-## {{< var sec1.un6 >}}
-
-1. Differences in the cost of voting (e.g., topology, voting rules, dropboxes etc.) across precincts $\Rightarrow$
-1. Changes to the likelihood of voting $\Rightarrow$ 
-1. Simplify so that changes in the likelihood of voting only impact Mode 2 $\Rightarrow$ 
-1. Higher $\zeta_i$ $\Rightarrow$
-1. Which changes the total election outcome through $\alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}$
-
-##
-
-The impact on the election outcome, however, would be small or close to non-existens if the conditions
-of the existance of a *trivial* Manifold occuranse related to normal form are not satisfied:
-
-- Proportion of mail-in-votes to election day vote is already high (Aggregate convergence lemma)
-  - Note: $\lim_{\zeta_i \rightarrow \infty} \alpha_i=\frac{x_i+\zeta_i y_i}{\zeta_i+x_i}=y_i$
-- Correlation between $x$ and $y$ is very high (Twixt lemma)
-  - Note: If correlation is 1, we can set $x_i=\rho_s y_i$ so that $\alpha_i(y_i,\zeta_i)=\frac{\rho_s y_i+\zeta_i y_i}{\zeta_i+x_i}$
-- Low variance to $\zeta$ 
-  - Note: Invariance across precincts would imply that $\zeta_i=\zeta$, so that election outcome only determined by variations in two parameters: $\alpha_i(y_i,x_i)=\frac{x_i+\zeta y_i}{\zeta+x_i}$
-
-If none of this three cases are satisfied, variation in $\zeta_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
-
-[Application 1: Election process simulator]({{< var shn1 >}})
-
-## {{< var sec1.un7 >}}
-
-1. Differenc in the cost of voting (e.g., topology, voting rules, dropboxes, socio economics etc.) across precincts $\Rightarrow$ 
-1. Make changes to the likelihood of voting $\Rightarrow$ 
-1. Simplify so that changes in the likelihood of voting only impact mode 2 $\Rightarrow$ 
-1. Higher $\zeta_i$ $\Rightarrow$
-1. If new and earlier sample not representative of each other, higher $\Gamma_i$ $\Rightarrow$
-1. Which changes the total election outcome through $\alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+1}$
-
-##
-
-The impact on the election outcome, however, would be small or close to non-existens if the conditions
-of the existance of a *trivial* Manifold related to opposition form are not satisfied:
-
-- Proportion of the hybrid ballot boxes is already high (Aggregate convergence lemma)
-  - Note: $\lim_{\Gamma_i \rightarrow \infty} \alpha_i=\frac{g_i+\zeta_i h_i}{\zeta_i+g_i}=y_i$
-- Correlation between $g$ and $h$ is very high (Twixt lemma)
-  - Note: If correlation is 1, we can set $g_i=\rho_h h_i$ so that $\alpha_i(h_i,\Gamma_i)=\frac{\rho_h h_i+\Gamma_i h_i}{\Gamma_i+x_i}$
-- Low variance to $\Gamma_i$ 
-  - Note: Invariance across precincts would imply that $\Gamma_i=\Gamma$, so that election outcome only determined by variations in two parameters: $\alpha_i=\frac{g_i+\Gamma h_i}{h_i}$
-
-If none of this three cases are satisfied, variation in $\Gamma_i$ should explain part of the election result. But how much should we expect within a county (2%, 5%, 10%)?
-
-[Application 1: Election process simulator]({{< var shn1 >}})
-
-```{r, echo=F}
-knitr::knit_exit()
-```
-
-# {{< var sec2.nmn >}}
-## {{< var sec2.un1 >}}
-- We have identified three ways of counting
-  - *Standard form* ( $x$, $y$, $\zeta$, $\alpha$, $\lambda$ )
-  - *Hybrid form* ( $g$, $h$, $\alpha$, $\Gamma$, $\Omega$ )
-  - *Opposition form* ( $n$, $m$, $\xi$, $\Omega$, $\lambda$ )
--  Each form can (throught its parametric tautologies) determine the 5 parameters that have been listed.
-  -  We are free to *predetermine* **3** of them
-  -  The remaining **2** must be *backsolved*, this based on information from the first three parameters.
-  -  Selecting **3** parameters from a set of **5** implies **10** different combinations
-
-## {{< var sec2.un2 >}}
-::: {.callout-caution collapse="true"}
-**20 laws and 40 isometris**
-
-```{r, echo=F}
-# Load necessary library
-library(tibble)
-
-# Create the data.frame
-laws_df <- tribble(
-  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
-  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
-  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
-  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
-  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
-  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
-  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
-  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
-  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
-  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
-  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
-  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
-  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
-  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
-  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
-  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
-  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
-  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
-  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
-  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
-  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
-)
-# Display the data.frame
-kable(laws_df, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-:::
-
----
-
-::: {.callout-caution collapse="true"}
-## Proportions
-
-```{r, echo=F}
-library(kableExtra)
-library(tibble)
-new_tbl <- data.frame(
-  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
-  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
-  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
-  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
-  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
-  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
-  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
-  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
-)
-
-# Extract the columns
-V1 <- new_tbl$V1
-V2 <- new_tbl$V2
-V3 <- new_tbl$V3
-V4 <- new_tbl$V4
-Equation1 <- new_tbl$Equation1
-Equation2 <- new_tbl$Equation2
-Equation3 <- new_tbl$Equation3
-Equation4 <- new_tbl$Equation4
-
-# Combine the columns
-combined <- data.frame(
-  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
-  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
-  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
-  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
-)
-kable(combined, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-
-:::
-## {{< var sec2.un3 >}}
-
-:::: {.columns}
-
-::: {.column width="50%"}
-
-*Standard form*
-
-Setting the first three parameters:
-
-- $x_i=\frac{s_i}{s_i+t_i}$
-- $y_i=\frac{u_i}{u_i+v_i}$
-- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$
-
-Backsolve for
-
-- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::: {.column width="50%"}
-
-*Opposition form*
-
-Setting the first three parameters:
-
-- $g_i=\frac{s_i}{s_i+t_i}$
-- $h_i=\frac{u_i}{u_i+v_i}$
-- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$
-
-Backsolve for
-
-- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::::
-
-**Properties**:
-
-- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
-- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
-
-[Application 2: Rigged election process simulator]({{< var shn2 >}})
-
-## {{< var sec2.un4 >}}
-
-**Setting the prefered election outcome**
-
-:::: {.columns}
-
-::: {.column width="50%"}
-Non-rigged election using standard form
-```{r}
-#app_n_out[[4]] 
-```
-
-:::
-
-::: {.column width="50%"}
-
-Rigged election using standard form
-```{r}
-#app_ex1_out[[4]] 
-```
-
-:::
-
-::::
-
----
-
-**Normal**
-<br>
-\begin{equation*}
-f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
-\end{equation*}
-
-Election outome 
-```{r, echo=F}
-#pri_int_ex1
-#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
-#mean(app_ex1_cou$rdfc$alpha)
-```
-
-<br>
-**Rigged**
-<br>
-
-$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
-
-Election outome
-```{r, echo=F}
-#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
-#pos_int_ex1
-```
-
----
-
-### Rigged election example 1: applying normal form
-
-- Setting for eaching precinct the first three parameters
- - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
- - $x_i=\frac{a_i}{a_i+b_i}$ (true observations)
- - $y_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(x_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
-- Backsolve for
- - $\zeta_i(x_i,\alpha_i,y_i)=\frac{x_i-\alpha_i}{\alpha_i-y_i}$
- - $\lambda_i(x_i,\zeta_i,y_i)=\frac{x_i-\zeta_i (1-y_i)}{\zeta_i+1}$
-
----
-
-**Properties**:
-
-- 3<sup>rd</sup> $y_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 4<sup>th</sup>. Changes in $\zeta_i$ - and as a corrollary $\Omega_i$ - is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\alpha_i$
-
----
-
-### Rigged election example 2: applying hybrid form
-
-- Setting for eaching precinct the first three parameters
- - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
- - $h_i=\frac{s_i}{s_i+v_i}$ (true observations)
- - $g_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(h_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
-- Backsolve form
- - $\Gamma_i(g_i,\alpha_i,h_i)=\frac{g_i-\alpha_i}{\alpha_i-h_i}$
- - $\Omega_i(g_i,\Gamma,h_i)=-\alpha_i+\frac{\Gamma_i+2g_i}{\Gamma_i+1}$
-
----
-
-**Properties**:
-
-- 5<sup>th</sup> $y_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 6<sup>th</sup> Changes in $\Gamma_i$ - and as a corrollary $\lambda_i$ - is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\alpha_i$
-
----
-
-### Rigged election example 3: applying opposition form
-
-- Setting for eaching precinct the first three parameters
- - $\lambda_i=<...>$ (i.e., equal or less than the prefered election outcome)
- - $n_i=\frac{a_i}{a_i+c_i}$ (true observations)
- - $m_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(n_i,\lambda_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_{t_i} \sim N(0,\sigma^2)$
-- Backsolve for
- - $\Omega_i(n_i,m_i,\lambda_i) = \frac{\lambda_i(n_i-m_i)-m_i(2n_i-1)}{1-(n_i+m_i)}$
- - $\xi_i(n_i,m_i,\Omega_i)=\frac{m_i-\Omega_i}{\Omega_i-n_i}$
-
----
-
-**Properties**:
-
-- 7<sup>th</sup> $m_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 8<sup>th</sup> Changes in $\xi_i$ is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\lambda_i$
-
-# {{< var sec3.nmn >}}
-
-## {{< var sec3.un1 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- basc
-```
-{{< include tabpar.qmd >}}
-
-## {{< var sec3.un2 >}}
-
-### Normal form
-```{r}
-#| echo: false
-#| output: false
-apps <- rigv[[1]]
-```
-{{< include tab.qmd >}}
-
----
-
-### Hybrid
-```{r}
-#| echo: false
-#| output: false
-apps <- rigv[[2]]
-```
-{{< include tab.qmd >}}
-
----
-
-### Opposition
-```{r}
-#| echo: false
-#| output: false
-apps <- rigv[[3]]
-```
-{{< include tab.qmd >}}
-
-# {{< var sec5.nmn >}}
-
-![](images/ss.png){width=300}
-
-> abstract: on august 15th, **2004**, venezuelans had the opportunity to vote
-in a presidential recall referendum **to decide whether or not president hugo
-chávez should be removed from office.** **the process was largely computer-
-ized using a touch-screen system.** in general the ballots were not manually
-counted. the significance of the high linear correlation (0.99) between the
-number of requesting signatures for the recall petition and the number of op-
-position votes in computerized centers is analyzed. The same-day audit was
-found to be not only ineffective but a source of suspicion...
-
----
-
-![](images/manifold.png){width=300}
-
----
-
-** Abc | S-A **
-
-{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
-
-# {{< var sec6.nmn >}}
-
-1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
-1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
-1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
-1. Check for normality of the estimated residual for the Manifold model.
-
-If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.
-
-## {{< var sec6.un1 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app1
-```
-{{< include tabpar.qmd >}}
-
-## {{< var sec6.un2 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app2
-```
-{{< include tabpar.qmd >}}
-
-## {{< var sec6.un3 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app2
-```
-{{< include tabpar.qmd >}}
-## {{< var sec6.un4 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app4
-```
-{{< include tabpar.qmd >}}
-
-# {{< var sec7.nmn >}}
-
-## {{< var sec7.un1 >}}
-
-# {{< var sec8.nmn >}}
-
-- At the heart of the difference between a fair and rigged election is the issue of causation
-  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
-  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
-
-- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
-	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
-	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
-
----
-
-- Condition on that $R^2$ falls within the critical region.
-  - Normal form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2n.png')
-knitr::include_graphics(c(pr2n))
-```
-
- - Hybrid form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2h.png')
-knitr::include_graphics(c(pr2h))
-```
-
-- Our four applications
-
-```{r, echo=F, warning=F, message=F}
-#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-# {{< var sec9.nmn >}}
-
-::: {#refs}
-:::

### 2024-07-12 presentation.qmd
morepres

--- 2024-07-12 presentation.qmd
@@
     toc: true 
-#execute: 
-#  cache: false
-#webr: 
-#  show-startup-message: true    # Disable displaying status of webR initialization
-#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
-##filters:
-#- webr 
+execute: 
+  cache: false
 footer: <https://lotariohw26.github.io/ManifoldDestiny/>
@@
 modlat <- eqpar$meql
+cx
 ```
@@
 #| tbl-cap: 'Election results applying standard form on case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
-cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(stfc1,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
   - $\alpha=\frac{`r cx[3]`+`r cy[3]`\cdot `r czeta[3]`}{1+`r czeta[3]`}=`r calpha[3]`$
+
+---
+
+```{r, echo=F}
+#| label: tbl-sfc2
+#| tbl-cap: 'Election results applying hybrid form on case II'
+kableExtra::kbl(format(stfc2,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
 
@@
 
-##
+---
 
 ```{r, echo=F}
-#| label: tbl-sfc2
+#| label: tbl-hfc1
 #| tbl-cap: 'Election results applying hybrid form case I'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(hyfc1,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 #| tbl-cap: 'Election results applying hybrid form case II'
-stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(hyfc2,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 
-##
+---
 
 ```{r, echo=F}
-#| label: tbl-hfc3
+#| label: tbl-ofc1
 #| tbl-cap: 'Election results applying hybrid form case II'
-stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
-kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+kableExtra::kbl(format(opfc1,digits=4)) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+---
+
+```{r, echo=F}
+#| label: tbl-ofc2
+#| tbl-cap: 'Election results applying hybrid form case II'
+kableExtra::kbl(format(opfc2,digits=4)) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
 ```
@@
 [Application 1: Election process simulator]({{< var shn1 >}})
-
-```{r, echo=F}
-knitr::knit_exit()
-```
 
@@
 ## {{< var sec2.un3 >}}
-
-:::: {.columns}
-
-::: {.column width="50%"}
-
-*Standard form*
-
-Setting the first three parameters:
-
-- $x_i=\frac{s_i}{s_i+t_i}$
-- $y_i=\frac{u_i}{u_i+v_i}$
-- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$
-
-Backsolve for
-
-- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::: {.column width="50%"}
-
-*Opposition form*
-
-Setting the first three parameters:
-
-- $g_i=\frac{s_i}{s_i+t_i}$
-- $h_i=\frac{u_i}{u_i+v_i}$
-- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$
-
-Backsolve for
-
-- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::::
-
-**Properties**:
-
-- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
-- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
-
-[Application 2: Rigged election process simulator]({{< var shn2 >}})
-
-## {{< var sec2.un4 >}}
-
-**Setting the prefered election outcome**
-
-:::: {.columns}
-
-::: {.column width="50%"}
-Non-rigged election using standard form
-```{r}
-#app_n_out[[4]] 
-```
-
-:::
-
-::: {.column width="50%"}
-
-Rigged election using standard form
-```{r}
-#app_ex1_out[[4]] 
-```
-
-:::
-
-::::
-
----
-
-**Normal**
-<br>
-\begin{equation*}
-f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
-\end{equation*}
-
-Election outome 
-```{r, echo=F}
-#pri_int_ex1
-#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
-#mean(app_ex1_cou$rdfc$alpha)
-```
-
-<br>
-**Rigged**
-<br>
-
-$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
-
-Election outome
-```{r, echo=F}
-#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
-#pos_int_ex1
-```
-
----
-
-### Rigged election example 1: applying normal form
-
-- Setting for eaching precinct the first three parameters
- - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
- - $x_i=\frac{a_i}{a_i+b_i}$ (true observations)
- - $y_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(x_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
-- Backsolve for
- - $\zeta_i(x_i,\alpha_i,y_i)=\frac{x_i-\alpha_i}{\alpha_i-y_i}$
- - $\lambda_i(x_i,\zeta_i,y_i)=\frac{x_i-\zeta_i (1-y_i)}{\zeta_i+1}$
-
----
-
-**Properties**:
-
-- 3<sup>rd</sup> $y_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 4<sup>th</sup>. Changes in $\zeta_i$ - and as a corrollary $\Omega_i$ - is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\alpha_i$
-
----
-
-### Rigged election example 2: applying hybrid form
-
-- Setting for eaching precinct the first three parameters
- - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
- - $h_i=\frac{s_i}{s_i+v_i}$ (true observations)
- - $g_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(h_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
-- Backsolve form
- - $\Gamma_i(g_i,\alpha_i,h_i)=\frac{g_i-\alpha_i}{\alpha_i-h_i}$
- - $\Omega_i(g_i,\Gamma,h_i)=-\alpha_i+\frac{\Gamma_i+2g_i}{\Gamma_i+1}$
-
----
-
-**Properties**:
-
-- 5<sup>th</sup> $y_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 6<sup>th</sup> Changes in $\Gamma_i$ - and as a corrollary $\lambda_i$ - is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\alpha_i$
-
----
-
-### Rigged election example 3: applying opposition form
-
-- Setting for eaching precinct the first three parameters
- - $\lambda_i=<...>$ (i.e., equal or less than the prefered election outcome)
- - $n_i=\frac{a_i}{a_i+c_i}$ (true observations)
- - $m_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(n_i,\lambda_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_{t_i} \sim N(0,\sigma^2)$
-- Backsolve for
- - $\Omega_i(n_i,m_i,\lambda_i) = \frac{\lambda_i(n_i-m_i)-m_i(2n_i-1)}{1-(n_i+m_i)}$
- - $\xi_i(n_i,m_i,\Omega_i)=\frac{m_i-\Omega_i}{\Omega_i-n_i}$
-
----
-
-**Properties**:
-
-- 7<sup>th</sup> $m_i$ can now be determined by *two* equations
-  - a. Tautology (must hold)
-  - b. Manifold equation + error term (white noise)
-- 8<sup>th</sup> Changes in $\xi_i$ is now 
-  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
-  - b. Has no longer any causal impact on $\lambda_i$
-
-# {{< var sec3.nmn >}}
-
-## {{< var sec3.un1 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- basc
-```
-{{< include tabpar.qmd >}}
-
-## {{< var sec3.un2 >}}
-
-### Normal form
-```{r}
-#| echo: false
-#| output: false
-apps <- rigv[[1]]
-```
-{{< include tab.qmd >}}
-
----
-
-### Hybrid
-```{r}
-#| echo: false
-#| output: false
-apps <- rigv[[2]]
-```
-{{< include tab.qmd >}}
-
----
-
-### Opposition
-```{r}
-#| echo: false
-#| output: false
-apps <- rigv[[3]]
-```
-{{< include tab.qmd >}}
-
-# {{< var sec5.nmn >}}
-
-![](images/ss.png){width=300}
-
-> abstract: on august 15th, **2004**, venezuelans had the opportunity to vote
-in a presidential recall referendum **to decide whether or not president hugo
-chávez should be removed from office.** **the process was largely computer-
-ized using a touch-screen system.** in general the ballots were not manually
-counted. the significance of the high linear correlation (0.99) between the
-number of requesting signatures for the recall petition and the number of op-
-position votes in computerized centers is analyzed. The same-day audit was
-found to be not only ineffective but a source of suspicion...
-
----
-
-![](images/manifold.png){width=300}
-
----
-
-** Abc | S-A **
-
-{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
-
-# {{< var sec6.nmn >}}
-
-1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
-1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
-1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
-1. Check for normality of the estimated residual for the Manifold model.
-
-If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.
-
-## {{< var sec6.un1 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app1
-```
-{{< include tabpar.qmd >}}
-
-## {{< var sec6.un2 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app2
-```
-{{< include tabpar.qmd >}}
-
-## {{< var sec6.un3 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app2
-```
-{{< include tabpar.qmd >}}
-## {{< var sec6.un4 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- app4
-```
-{{< include tabpar.qmd >}}
-
-# {{< var sec7.nmn >}}
-
-## {{< var sec7.un1 >}}
-
-# {{< var sec8.nmn >}}
-
-- At the heart of the difference between a fair and rigged election is the issue of causation
-  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
-  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
-
-- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
-	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
-	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
-
----
-
-- Condition on that $R^2$ falls within the critical region.
-  - Normal form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2n <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2n.png')
-knitr::include_graphics(c(pr2n))
-```
-
- - Hybrid form
-```{r, echo=F, out.width="40%", fig.cap=""}
-pr2h <- paste0(rprojroot::find_rstudio_root_file(),'/images/r2h.png')
-knitr::include_graphics(c(pr2h))
-```
-
-- Our four applications
-
-```{r, echo=F, warning=F, message=F}
-#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
-```
-
-# {{< var sec9.nmn >}}
-
-::: {#refs}
-:::

### 2024-07-12 presentation.qmd
break

@@
 :::
+
 ## {{< var sec2.un3 >}}
+
+:::: {.columns}
+
+::: {.column width="50%"}
+
+*Standard form*
+
+Setting the first three parameters:
+
+- $x_i=\frac{s_i}{s_i+t_i}$
+- $y_i=\frac{u_i}{u_i+v_i}$
+- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$
+
+Backsolve for
+
+- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
+- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
+
+:::
+
+::: {.column width="50%"}
+
+*Opposition form*
+
+Setting the first three parameters:
+
+- $g_i=\frac{s_i}{s_i+t_i}$
+- $h_i=\frac{u_i}{u_i+v_i}$
+- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$
+
+Backsolve for
+
+- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
+- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
+
+:::
+
+::::
+
+**Properties**:
+
+- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
+- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
+
+[Application 2: Rigged election process simulator]({{< var shn2 >}})
+
+## {{< var sec2.un4 >}}
+
+**Setting the prefered election outcome**
+
+:::: {.columns}
+
+::: {.column width="50%"}
+Non-rigged election using standard form
+```{r}
+#app_n_out[[4]] 
+```
+
+:::
+
+::: {.column width="50%"}
+
+Rigged election using standard form
+```{r}
+#app_ex1_out[[4]] 
+```
+
+:::
+
+::::
+
+---
+
+**Normal**
+<br>
+\begin{equation*}
+f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+\end{equation*}
+
+Election outome 
+```{r, echo=F}
+#pri_int_ex1
+#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
+#mean(app_ex1_cou$rdfc$alpha)
+```
+
+<br>
+**Rigged**
+<br>
+
+$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+
+Election outome
+```{r, echo=F}
+#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
+#pos_int_ex1
+```
+
+---
+
+### Rigged election example 1: applying normal form
+
+- Setting for eaching precinct the first three parameters
+ - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
+ - $x_i=\frac{a_i}{a_i+b_i}$ (true observations)
+ - $y_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(x_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
+- Backsolve for
+ - $\zeta_i(x_i,\alpha_i,y_i)=\frac{x_i-\alpha_i}{\alpha_i-y_i}$
+ - $\lambda_i(x_i,\zeta_i,y_i)=\frac{x_i-\zeta_i (1-y_i)}{\zeta_i+1}$
+
+---
+
+**Properties**:
+
+- 3<sup>rd</sup> $y_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 4<sup>th</sup>. Changes in $\zeta_i$ - and as a corrollary $\Omega_i$ - is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\alpha_i$
+
+---
+
+### Rigged election example 2: applying hybrid form
+
+- Setting for eaching precinct the first three parameters
+ - $\alpha_i=<...>$ (i.e., equal to the prefered election outcome)
+ - $h_i=\frac{s_i}{s_i+v_i}$ (true observations)
+ - $g_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(h_i,\alpha_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_t \sim N(0,\sigma^2)$
+- Backsolve form
+ - $\Gamma_i(g_i,\alpha_i,h_i)=\frac{g_i-\alpha_i}{\alpha_i-h_i}$
+ - $\Omega_i(g_i,\Gamma,h_i)=-\alpha_i+\frac{\Gamma_i+2g_i}{\Gamma_i+1}$
+
+---
+
+**Properties**:
+
+- 5<sup>th</sup> $y_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 6<sup>th</sup> Changes in $\Gamma_i$ - and as a corrollary $\lambda_i$ - is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\alpha_i$
+
+---
+
+### Rigged election example 3: applying opposition form
+
+- Setting for eaching precinct the first three parameters
+ - $\lambda_i=<...>$ (i.e., equal or less than the prefered election outcome)
+ - $n_i=\frac{a_i}{a_i+c_i}$ (true observations)
+ - $m_i=\overset{\text{Manifold equation}}{\overbrace{\overset{}{M(n_i,\lambda_i,\underset{\text{outside information}}{...})}}}+\epsilon_t \text{ where } \epsilon_{t_i} \sim N(0,\sigma^2)$
+- Backsolve for
+ - $\Omega_i(n_i,m_i,\lambda_i) = \frac{\lambda_i(n_i-m_i)-m_i(2n_i-1)}{1-(n_i+m_i)}$
+ - $\xi_i(n_i,m_i,\Omega_i)=\frac{m_i-\Omega_i}{\Omega_i-n_i}$
+
+---
+
+**Properties**:
+
+- 7<sup>th</sup> $m_i$ can now be determined by *two* equations
+  - a. Tautology (must hold)
+  - b. Manifold equation + error term (white noise)
+- 8<sup>th</sup> Changes in $\xi_i$ is now 
+  - a. Solely caused by the error term $\epsilon_i$ and, if used, the non-linear part of the Manifold equation.
+  - b. Has no longer any causal impact on $\lambda_i$

### 2024-07-12 prerendr.R

@@ -48,3 +48,6 @@
 #
 #
 
+#source("data-raw/recorder.R")
+
+

### 2024-07-13 presentation.qmd
updprese

@@
 footer: <https://lotariohw26.github.io/ManifoldDestiny/>
+output: 
+  html_document:
+    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
+nocite: |
+  @*
 ---
@@
 #source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+appnf <- seloutput(selreport(basc))
+appr1 <- seloutput(selreport(rigv[[1]]))
+appr2 <- seloutput(selreport(rigv[[2]]))
+appr3 <- seloutput(selreport(rigv[[3]]))
 #source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
@@
 
-## {{< var sec2.un2 >}}
-::: {.callout-caution collapse="true"}
-**20 laws and 40 isometris**
+---
 
-```{r, echo=F}
-# Load necessary library
-library(tibble)
+### 40 isometris
 
-# Create the data.frame
-laws_df <- tribble(
-  ~Law_Number, ~North_vs_South, ~West_vs_East, ~Diagonal_vs_Diagonal,
-  "First Law", "$x_{1}=\\alpha_{1}+\\zeta(\\alpha_{1}-y_{1})$", "$g_{1}=\\alpha_{1}+\\gamma(\\alpha_{1}-h_{1})$", "$m_{1}=\\Omega_{1}+\\xi(\\Omega_{1}-n_{1})$",
-  "Second Law", "$x_{1}=\\lambda_{1}+\\zeta(\\lambda_{1}-y_{2})$", "$g_{1}=\\Omega_{1}+\\gamma(\\Omega_{1}-h_{2})$", "$m_{1}=\\lambda_{1}+\\xi(\\lambda_{1}-n_{2})$",
-  "Third Law", "$x_{1}=\\frac{\\alpha_{1}y_{2}-\\lambda_{1}y_{1}}{(\\alpha_{1}-\\lambda_{1})-(y_{1}-y_{2})}$", "$g_{1}=\\frac{\\alpha_{1}h_{2}-\\Omega_{1}h_{1}}{(\\alpha_{1}-\\Omega_{1})-(h_{1}-h_{2})}$", "$m_{1}=\\frac{\\Omega_{1}n_{2}-\\lambda_{1}n_{1}}{(\\Omega_{1}-\\lambda_{1})-(n_{1}-n_{2})}$",
-  "Fourth Law", "$x_{1}=\\frac{\\lambda_{1}+\\alpha_{1}-\\Omega_{2}}{2\\Omega_{1}}$", "$g_{1}=\\frac{\\Omega_{1}+\\alpha_{1}-\\lambda_{2}}{2\\lambda_{1}}$", "$m_{1}=\\frac{\\lambda_{1}+\\Omega_{1}-\\alpha_{2}}{2\\alpha_{1}}$",
-  "Fifth Law", "$y_{1}=\\alpha_{1}-\\zeta^{-1}(\\alpha_{1}-x_{1})$", "$h_{1}=\\alpha_{1}-\\gamma^{-1}(\\alpha_{1}-g_{1})$", "$n_{1}=\\Omega_{1}-\\xi^{-1}(\\Omega_{1}-m_{1})$",
-  "Sixth Law", "$y_{1}=\\lambda_{2}-\\zeta^{-1}(\\lambda_{1}-x_{1})$", "$h_{1}=\\Omega_{2}-\\gamma^{-1}(\\Omega_{1}-g_{1})$", "$n_{1}=\\lambda_{2}-\\xi^{-1}(\\lambda_{1}-m_{1})$",
-  "Seventh Law", "$y_{1}=\\frac{x_{1}\\lambda_{2}-x_{2}\\alpha_{1}}{(\\lambda_{2}-\\alpha_{1})-(x_{2}-x_{1})}$", "$h_{1}=\\frac{g_{1}\\Omega_{2}-g_{2}\\alpha_{1}}{(\\Omega_{2}-\\alpha_{1})-(g_{2}-g_{1})}$", "$n_{1}=\\frac{m_{1}\\lambda_{2}-m_{2}\\Omega_{1}}{(\\lambda_{2}-\\Omega_{1})-(m_{2}-m_{1})}$",
-  "Eighth Law", "$y_{1}=\\frac{\\lambda_{2}+\\alpha_{1}-\\Omega_{1}}{2\\Omega_{2}}$", "$h_{1}=\\frac{\\Omega_{2}+\\alpha_{1}-\\lambda_{1}}{2\\lambda_{2}}$", "$n_{1}=\\frac{\\lambda_{2}+\\Omega_{1}-\\alpha_{1}}{2\\alpha_{2}}$",
-  "Ninth Law", "$\\alpha_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{1}$", "$\\alpha_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{1}$", "$\\Omega_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{1}$",
-  "Tenth Law", "$\\alpha_{1}=\\Omega_{1}(x_{1}-x_{2})+\\lambda_{2}$", "$\\alpha_{1}=\\lambda_{1}(g_{1}-g_{2})+\\Omega_{2}$", "$\\Omega_{1}=\\alpha_{1}(m_{1}-m_{2})+\\lambda_{2}$",
-  "Eleventh Law", "$\\alpha_{1}=\\Omega_{2}(y_{1}-y_{2})+\\lambda_{1}$", "$\\alpha_{1}=\\lambda_{2}(h_{1}-h_{2})+\\Omega_{1}$", "$\\Omega_{1}=\\alpha_{2}(n_{1}-n_{2})+\\lambda_{1}$",
-  "Twelfth Law", "$\\alpha_{1}=\\frac{x_{1}(y_{2}-y_{1})-\\lambda_{1}(x_{1}-y_{1})}{y_{2}-x_{1}}$", "$\\alpha_{1}=\\frac{g_{1}(h_{2}-h_{1})-\\Omega_{1}(g_{1}-h_{1})}{h_{2}-g_{1}}$", "$\\Omega_{1}=\\frac{m_{1}(n_{2}-n_{1})-\\lambda_{1}(m_{1}-n_{1})}{n_{2}-m_{1}}$",
-  "Thirteenth Law", "$\\lambda_{1}=x_{1}\\Omega_{1}+\\Omega_{2}y_{2}$", "$\\Omega_{1}=g_{1}\\lambda_{1}+\\lambda_{2}h_{2}$", "$\\lambda_{1}=m_{1}\\alpha_{1}+\\alpha_{2}n_{2}$",
-  "Fourteenth Law", "$\\lambda_{1}=\\Omega_{1}(x_{1}-x_{2})+\\alpha_{2}$", "$\\Omega_{1}=\\lambda_{1}(g_{1}-g_{2})+\\alpha_{2}$", "$\\lambda_{1}=\\alpha_{1}(m_{1}-m_{2})+\\Omega_{2}$",
-  "Fifteenth Law", "$\\lambda_{1}=\\frac{\\alpha_{1}(x_{1}-y_{2})-x_{1}(y_{1}-y_{2})}{x_{1}-y_{1}}$", "$\\Omega_{1}=\\frac{\\alpha_{1}(g_{1}-h_{2})-g_{1}(h_{1}-h_{2})}{g_{1}-h_{1}}$", "$\\lambda_{1}=\\frac{\\Omega_{1}(m_{1}-n_{2})-m_{1}(n_{1}-n_{2})}{m_{1}-n_{1}}$",
-  "Sixteenth Law", "$\\lambda_{1}=\\Omega_{2}(y_{2}-y_{1})+\\alpha_{1}$", "$\\Omega_{1}=\\lambda_{2}(h_{2}-h_{1})+\\alpha_{1}$", "$\\lambda_{1}=\\alpha_{2}(n_{2}-n_{1})+\\Omega_{1}$",
-  "Seventeenth Law", "$\\zeta=\\frac{x_{1}-\\alpha_{1}}{\\alpha_{1}-y_{1}};\\Omega_{1}=\\frac{y_{1}-\\alpha_{1}}{y_{1}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\alpha_{1}}{\\alpha_{1}-h_{1}};\\lambda_{1}=\\frac{h_{1}-\\alpha_{1}}{h_{1}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\Omega_{1}}{\\Omega_{1}-n_{1}};\\alpha_{1}=\\frac{n_{1}-\\Omega_{1}}{n_{1}-m_{1}}$",
-  "Eighteenth Law", "$\\Omega_{1}=\\frac{\\lambda_{2}-\\alpha_{1}}{x_{2}-x_{1}}=\\frac{\\alpha_{2}-\\lambda_{1}}{x_{2}-x_{1}}$", "$\\gamma_{1}=\\frac{\\Omega_{2}-\\alpha_{1}}{g_{2}-g_{1}}=\\frac{\\alpha_{2}-\\Omega_{1}}{g_{2}-g_{1}}$", "$\\alpha_{1}=\\frac{\\lambda_{2}-\\Omega_{1}}{m_{2}-m_{1}}=\\frac{\\Omega_{2}-\\lambda_{1}}{m_{2}-m_{1}}$",
-  "Nineteenth Law", "$\\zeta=\\frac{x_{1}-\\lambda_{1}}{\\lambda_{1}-y_{2}}; \\Omega_{1}=\\frac{y_{2}-\\lambda_{1}}{y_{2}-x_{1}}$", "$\\gamma=\\frac{g_{1}-\\Omega_{1}}{\\Omega_{1}-h_{2}}; \\lambda_{1}=\\frac{h_{2}-\\Omega_{1}}{h_{2}-g_{1}}$", "$\\xi=\\frac{m_{1}-\\lambda_{1}}{\\lambda_{1}-n_{2}}; \\alpha_{1}=\\frac{n_{2}-\\lambda_{1}}{n_{2}-m_{1}}$",
-  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
-)
-# Display the data.frame
-kable(laws_df, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+::: {.callout-note collapse="true"}
+```{r}
+kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
+
 ```
-
 :::
@@
 
-::: {.callout-caution collapse="true"}
-## Proportions
+### 20 laws
 
-```{r, echo=F}
-library(kableExtra)
-library(tibble)
-new_tbl <- data.frame(
-  V1 = c("North Ratio", "West Ratio", "Northwest Ratio", "Diagonal Aggregate", "Diagonal Complement", "West Aggregate", "East Aggregate", "North Aggregate", "South Aggregate"),
-  V2 = c("South Ratio", "East Ratio", "Northeast Ratio", "Diagonal Proportion", "Diagonal Inverse", "East to West Proportion", "West to East Proportion", "South to North Proportion", "North to South Proportion"),
-  V3 = c("North Complement", "West Complement", "Southeast Ratio", "1st Alpha Identity", "2nd Alpha Identity", "1st Lambda Identity", "2nd Lambda Identity", "1st Omega Identity", "2nd Omega Identity"),
-  V4 = c("South Complement", "East Complement", "Southwest Ratio", "Xi Identity", "Inverse Xi Identity", "Gamma Identity", "Inverse Gamma Identity", "Zeta Identity", "Inverse Zeta Identity"),
-  Equation1 = c("$x_{1} = \\frac{s}{s+t}$", "$g_{1} = \\frac{s}{s+v}$", "$m_{1} = \\frac{s}{s+u}$", "$\\alpha_{1} = \\frac{s+u}{(s+u)+(t+v)}$", "$\\alpha_{2} = \\frac{t+v}{(s+u)+(t+v)}$", "$\\lambda_{1} = \\frac{s+v}{(s+v)+(u+t)}$", "$\\lambda_{2} = \\frac{u+t}{(s+v)+(u+t)}$", "$\\Omega_{1} = \\frac{s+t}{(s+t)+(u+v)}$", "$\\Omega_{2} = \\frac{u+v}{(s+t)+(u+v)}$"),
-  Equation2 = c("$y_{1} = \\frac{u}{u+v}$", "$h_{1} = \\frac{u}{u+t}$", "$n_{1} = \\frac{t}{t+v}$", "$\\xi = \\frac{t+v}{s+u}$", "$\\xi^{-1} = \\frac{s+u}{t+v}$", "$\\gamma = \\frac{u+t}{s+v}$", "$\\gamma^{-1} = \\frac{s+v}{u+t}$", "$\\zeta = \\frac{u+v}{s+t}$", "$\\zeta^{-1} = \\frac{s+t}{u+v}$"),
-  Equation3 = c("$x_{2} = (1-x_{1}) = \\frac{t}{s+t}$", "$g_{2} = (1-g_{1}) = \\frac{v}{s+v}$", "$m_{2} = (1-m_{1}) = \\frac{u}{s+u}$", "$\\alpha_{1} = (\\xi+1)^{-1}$", "$\\alpha_{2} = (\\xi^{-1}+1)^{-1}$", "$\\lambda_{1} = (\\gamma+1)^{-1}$", "$\\lambda_{2} = (\\gamma^{-1}+1)^{-1}$", "$\\Omega_{1} = (\\zeta+1)^{-1}$", "$\\Omega_{2} = (\\zeta^{-1}+1)^{-1}$"),
-  Equation4 = c("$y_{2} = (1-y_{1}) = \\frac{v}{u+v}$", "$h_{2} = (1-h_{1}) = \\frac{t}{u+t}$", "$n_{2} = (1-n_{1}) = \\frac{v}{t+v}$", "$\\xi = \\frac{1-\\alpha_{1}}{\\alpha_{1}} = \\frac{\\alpha_{2}}{\\alpha_{1}}$", "$\\xi^{-1} = \\frac{1-\\alpha_{2}}{\\alpha_{2}} = \\frac{\\alpha_{1}}{\\alpha_{2}}$", "$\\gamma = \\frac{1-\\lambda_{1}}{\\lambda_{1}} = \\frac{\\lambda_{2}}{\\lambda_{1}}$", "$\\gamma^{-1} = \\frac{1-\\lambda_{2}}{\\lambda_{2}} = \\frac{\\lambda_{1}}{\\lambda_{2}}$", "$\\zeta = \\frac{1-\\Omega_{1}}{\\Omega_{1}} = \\frac{\\Omega_{2}}{\\Omega_{1}}$", "$\\zeta^{-1} = \\frac{1-\\Omega_{2}}{\\Omega_{2}} = \\frac{\\Omega_{1}}{\\Omega_{2}}$")
-)
+::: {.callout-note collapse="true"}
+```{r} 
+kable(laws2, format = "markdown", escape = FALSE)
 
-# Extract the columns
-V1 <- new_tbl$V1
-V2 <- new_tbl$V2
-V3 <- new_tbl$V3
-V4 <- new_tbl$V4
-Equation1 <- new_tbl$Equation1
-Equation2 <- new_tbl$Equation2
-Equation3 <- new_tbl$Equation3
-Equation4 <- new_tbl$Equation4
-
-# Combine the columns
-combined <- data.frame(
-  V1 = matrix(c(rbind(V1, Equation1)), ncol = 1),
-  V2 = matrix(c(rbind(V2, Equation2)), ncol = 1),
-  V3 = matrix(c(rbind(V3, Equation3)), ncol = 1),
-  V4 = matrix(c(rbind(V4, Equation4)), ncol = 1)
-)
-kable(combined, format = "markdown", escape = FALSE) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```
-
 :::
-
-## {{< var sec2.un3 >}}
-
-:::: {.columns}
-
-::: {.column width="50%"}
-
-*Standard form*
-
-Setting the first three parameters:
-
-- $x_i=\frac{s_i}{s_i+t_i}$
-- $y_i=\frac{u_i}{u_i+v_i}$
-- $\zeta_i=\frac{u_i+v_i}{s_i+t_i}$
-
-Backsolve for
-
-- $\alpha_i(x_,y_i,\zeta_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\lambda_i(x_i,y_i,\zeta_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::: {.column width="50%"}
-
-*Opposition form*
-
-Setting the first three parameters:
-
-- $g_i=\frac{s_i}{s_i+t_i}$
-- $h_i=\frac{u_i}{u_i+v_i}$
-- $\Gamma_i=\frac{u_i+d_i}{u_i+v_i}$
-
-Backsolve for
-
-- $\alpha_i(g_i,h_i,\Gamma_i)=\frac{x_i+\zeta_i\cdot y_i}{\zeta_i+1}$
-- $\Omega_i(g_i,h_i,\Gamma_i)=\frac{x_i\zeta_i\cdot(1-y_i)}{\zeta_i+1}$
-
-:::
-
-::::
-
-**Properties**:
-
-- 1<sup>st</sup> The total election outcome will be determined by *three* parameters: ( $x_i, y_i,\zeta_i$ ) under standard form and ( $g_i, h_i, \Gamma_i$ ) using hybrid form. 
-- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would in general have an impact on $\alpha_i$.
 
@@
 ::: {.column width="50%"}
-Non-rigged election using standard form
+Non-rigged election
 ```{r}
-#app_n_out[[4]] 
+appnf[[4]]
 ```
@@
 ```{r}
-#app_ex1_out[[4]] 
+appr1[[4]]
 ```
@@
   - b. Has no longer any causal impact on $\lambda_i$
+
+# {{< var sec3.nmn >}}
+
+## {{< var sec3.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- basc
+```
+{{< include tabpar.qmd >}}
+
+## {{< var sec3.un2 >}}
+
+### Normal form
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[1]]
+```
+{{< include tab.qmd >}}
+
+---
+
+### Hybrid
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[2]]
+```
+{{< include tab.qmd >}}
+
+---
+
+### Opposition
+```{r}
+#| echo: false
+#| output: false
+apps <- rigv[[3]]
+```
+{{< include tab.qmd >}}
+
+# {{< var sec5.nmn >}}
+
+![](images/ss.png){width=300}
+
+> Abstract: On August 15th, 2004, Venezuelans had the opportunity to vote in a Presidential Recall Referendum to decide whether or not President Hugo Chávez should be removed from office.
+The process was largely computerized using a touch-screen system.
+In general the ballots were not manually counted.
+The significance of the high linear correlation (0.99) between the number of requesting signatures for the recall petition and the number of opposition votes in computerized centers is analyzed.
+The same-day audit was found to be not only ineffective but a source of suspicion.
+Official results were compared with the 1998 presidential election and other electoral events and distortions were found.
+
+[Paper](https://projecteuclid.org/journals/statistical-science/volume-26/issue-4/Analysis-of-the-2004-Venezuela-Referendum--The-Official-Results/10.1214/08-STS263.full)
+
+---
+
+![](images/manifold.png){width=300}
+
+---
+
+{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
+
+# {{< var sec6.nmn >}}
+
+1. Check whether *trivial* Manifold occuranse related to (1) normal form, (2) hybrid form, or (3) opposition formare satisfied.
+1. If not, perform 3d Manifold analysis on all 10 different parameter combinations for all three forms of voting.
+1. For at least one of the suspicion cases, estimate the Manifold equation using (ordinary, complex or quaternionic) least squares estimation
+1. Check for normality of the estimated residual for the Manifold model.
+
+If we can walk through all of the **four** steps here, property 1<sup>st</sup> and 2<sup>nd</sup> that we have stated for a normal election are violated and we can conclude that the estimated Manifold equation is inserted - Manifold Destiny - to distort the outcome of normal election.
+
+## {{< var sec6.un1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app1
+```
+{{< include tabpar.qmd >}}
+
+## {{< var sec6.un2 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app2
+```
+{{< include tabpar.qmd >}}
+
+## {{< var sec6.un3 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app2
+```
+{{< include tabpar.qmd >}}
+## {{< var sec6.un4 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- app4
+```
+{{< include tabpar.qmd >}}
+
+# {{< var sec7.nmn >}}
+
+## {{< var sec7.un1 >}}
+
+# {{< var sec8.nmn >}}
+
+- At the heart of the difference between a fair and rigged election is the issue of causation
+  - Fair election: Aggregate Percentage of a Candidate **cannot** precede the Election Day and the Mail-in Percentages of that Candidate
+  - Rigged election: Aggregate Percentage of a Candidate **could** precede the Election Day and the Mail-in Percentages of that Candidate
+
+- If the conditions related to the the existance of a *trivial* Manifold occuranse to either normal form, hybrid form nor opposition form are not satisfied, this would imply
+	- 1<sup>st</sup> The total election outcome will be determined by *three* parameters (no manifold in 3d space). 
+	- 2<sup>nd</sup> Changes in $\Gamma_i$ and $\zeta_i$ would have an impact on $\alpha_i$.
+
+---
+
+- Condition on that $R^2$ falls within the critical region.
+	- Normal form
+	![](images/r2n.png){width=300}
+
+	- Hybrid form
+	![](images/r2h.png){width=300}
+
+---
+
+- Our four applications
+
+```{r, echo=F, warning=F, message=F}
+kableExtra::kbl(concl_appps) #%>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
+```
+
+# {{< var sec9.nmn >}}
+
+::: {#refs}
+:::

### 2024-07-13 presentation.qmd
abc
smallfix

@@
 #source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-appnf <- seloutput(selreport(basc))
-appr1 <- seloutput(selreport(rigv[[1]]))
-appr2 <- seloutput(selreport(rigv[[2]]))
-appr3 <- seloutput(selreport(rigv[[3]]))
+appnf <- seloutput(rppnf <- selreport(basc))
+appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
+appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
+appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
 #source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
 modlat <- eqpar$meql
-cx
+penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
+per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
+per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
+per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
 ```
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+f(x)_{0}^{1}=`r paste0(penf)`$
 \end{equation*}
@@
 ```{r, echo=F}
-#pri_int_ex1
-#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
-#mean(app_ex1_cou$rdfc$alpha)
+round(polynom::integral(penf,c(0,1)),3)
 ```
@@
 
-$f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pos_int_ex1)),3))`$
+$f(x)_{0}^{1}=`r paste0(per1)`$
 
@@
 ```{r, echo=F}
-#polynom::integral(round(polynom::polynomial(unname(pos_int_ex1))),c(0,1))
-#pos_int_ex1
+round(polynom::integral(per1,c(0,1)),3)
 ```
@@
 
-![](images/manifold.png){width=300}
+The video "Conexiones Peligrosas"
+
+{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
 
 ---
-
-{{< video https://www.youtube.com/watch?v=YQg1Cr3vRic&t=76s >}}
 

### 2024-07-13 script/R/simulations.R

@@ -36,11 +36,23 @@ rigv <- lapply(exs, function(x) {
   return(rasc)
 })
 ####################################################################################################################################################################
-appnf <- seloutput(selreport(basc))
-appr1 <- seloutput(selreport(rigv[[1]]))
-appr2 <- seloutput(selreport(rigv[[2]]))
-appr3 <- seloutput(selreport(rigv[[3]]))
-appr4 <- seloutput(selreport(rigv[[4]]))
+#appnf <- seloutput(abc <- selreport(basc))
+###appr1 <- seloutput(selreport(rigv[[1]]))
+###appr2 <- seloutput(selreport(rigv[[2]]))
+###appr3 <- seloutput(selreport(rigv[[3]]))
+###appr4 <- seloutput(selreport(rigv[[4]]))
+#polynom::polynomial(abc[[1]]$polyc)
+#
+#
+#unname(abc[[1]]$polyc)
+#2+2
+##f(x)_{0}^{1}=`r #paste0(round(polynom::polynomial(unname(pri_int_ex1)),3))`$
+#fc <- abc[[1]]
+#fc$polyc[[1]]
+##rppnf[[1]]
+#pri_int_ex1
+#polynom::integral(round(polynom::polynomial(unname(pri_int_ex1))),c(0,1))
+#mean(app_ex1_cou$rdfc$alpha)
 
 ####################################################################################################################################################################
 ######### Concluding Tabl

### 2024-07-13 presentation.qmd
publishloss

@@
 
+---
+
+## {{< var sec2.un1 >}}
+
+- Specify a loss function
+  - $\sum_{p=1}^{P}(\alpha_p-\overline{\alpha})^2$
+- $M(,)=$x+y$
+  - Use: Linear, quadratic, cubic or quartic (all have analytical solutions)
+  - Also: Euler rotation
+- System approach Demands mulitvariate Manifold Equations
+  - Univariate manifold Equation
+  - Multivariate Manifold Equations
+- Constrain on implementation
+  - Flipping votes on one mode
+  - Vote registration until upper limit
+
+---
+
+![](images/loss_5_conditions.png){width=300}
+
 # {{< var sec3.nmn >}}

### 2024-07-13 presentation.qmd
updpres

@@
 ManifoldDestiny::wasmconload()
-library(huxtable)
-library(kableExtra)
 library(ManifoldDestiny)
@@
 penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
+
+round(polynom::integral(penf,c(0,1)),3)
+
 per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r paste0(penf)`$
+f(x)_{0}^{1}=`r paste0(round(penf,3))`$
 \end{equation*}
@@
 Election outome 
-```{r, echo=F}
-round(polynom::integral(penf,c(0,1)),3)
-```
+  - Integral `r round(polynom::integral(penf,c(0,1)),3)`
+  - Counting `r round(rppnf[[1]]$desms[7,2],3)`
 
@@
 
-$f(x)_{0}^{1}=`r paste0(per1)`$
+\begin{equation*}
+f(x)_{0}^{1}=`r paste0(round(per1,3))`$
+\end{equation*}
 
@@
 
+- Venezuela referendum to recall President Hugo Chávez (2004)
+	- Mode 1: Computerized Voting Centers
+	- Mode 2: Manuel Voting Centers
+
+> HYPOTHESIS: **In computerized centers**, official **results were forced to follow a linear relationship** with respect to the number of signatures.
+
+![](images/manifold.png){width=300}
+
+---
+
 The video "Conexiones Peligrosas"

### 2024-07-13 presentation.qmd
upd

@@
 ManifoldDestiny::wasmconload()
+modlat <- eqpar$meql
 library(ManifoldDestiny)
@@
 laws_df2 <- ManifoldDestiny::eqdef$meqs
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
 appnf <- seloutput(rppnf <- selreport(basc))
@@
 appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
-modlat <- eqpar$meql
 penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
-
-round(polynom::integral(penf,c(0,1)),3)
-
 per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
@@
 per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
+#round(polynom::integral(penf,c(0,1)),3)
 ```
@@
 \end{equation*}
-
 ---

### 2024-07-13 R/wasmconverting.R

@@ -632,6 +632,7 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
 
   ## Variables
   lof <- function(kvec=NULL,prn=T){
+#	  browser()
     kvnr <- c(3,6,10,17)[mansysl$plnr]
     kvea <- rep(0,kvnr); names(kvea) <- paste0("k",0:(length(kvea)-1))
     kvea[1:length(kvec)] <- kvec
@@ -639,6 +640,8 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
     abcv <- setNames(as.vector(lapply(enf[[3]][[3]], as.character)),c(paste0(rep(letters[1:3], each=3), rep(1:3, times=3))))
     mv <- c(m1=cos(rad[1]),m2=cos(rad[2]),m3=cos(rad[3]))
     nv <- c(n1=sin(rad[1]),n2=sin(rad[2]),n3=sin(rad[3]))
+    #head(loss_df)
+    #browser()
     loss_df <<- rdfci %>%
       dplyr::select(P,R,S,T,U,V,Z,all_of(allvec)) %>%
       data.table::setnames(allvec,altvec) %>%
@@ -668,7 +671,8 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
       dplyr::mutate(!!allvec[4]:=pareq(se[[endp[1]]][2],c(as.list(.[,])))) %>%
       dplyr::mutate(!!allvec[5]:=pareq(se[[endp[2]]][2],c(as.list(.[,])))) %>%
       dplyr::mutate(!!allvec[6]:=pareq(se[[endp[3]]][2],c(as.list(.[,])))) %>%
-      dplyr::mutate(LSV:=pareq(mansysl$lf,c(as.list(.[,])))) %>%
+      dplyr::mutate(LSV=0) %>%
+      #dplyr::mutate(LSV:=pareq(mansysl$lf,c(as.list(.[,])))) 
       ##### Backsolving for ballots
       ## Observatinal values
       dplyr::mutate(!!paste0(stuv[1],'_m'):=pareq(se[[paste0(stuv[1],sho)]][2],as.list(.[])))  %>%
@@ -691,13 +695,13 @@ Countingprocess$methods(manimp=function(init_par=NULL,wn=c(0,0),
     #print(clvl)
   }
   # Init
+  #browser()
[…]

### 2024-07-13 addendum/Addendum_az.qmd
abcdef

@@
 ---
-title: "Addendum"
-subtitle: "Arizona General Election 2022"
-#format:
-#  revealjs: 
-#    smaller: true
-#    toc-depth: 1
-#    toc: true 
-webr: 
-  show-startup-message: true    # Disable displaying status of webR initialization
-  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
-filters:
-- webr 
+title: "{{< var addns >}}"
+subtitle: "{{< var addnl >}}"
+format:
+  revealjs: 
+    smaller: true
+    toc-depth: 1
+    toc: true 
+execute: 
+  cache: false
 footer: <https://lotariohw26.github.io/ManifoldDestiny/>
+output: 
+  html_document:
+    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
+nocite: |
+  @*
 ---
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-07-13 addendum/Addendum_ne.qmd
abcdef

@@
 ---
-title: "Addendum"
-subtitle: "Nevada General Election 2022"
-#format:
-#  revealjs: 
-#    smaller: true
-#    toc-depth: 1
-#    toc: true 
-webr: 
-  show-startup-message: true    # Disable displaying status of webR initialization
-  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
-filters:
-- webr 
+title: "{{< var addas >}}"
+subtitle: "{{< var addal >}}"
+format:
+  revealjs: 
+    smaller: true
+    toc-depth: 1
+    toc: true 
+execute: 
+  cache: false
 footer: <https://lotariohw26.github.io/ManifoldDestiny/>
+output: 
+  html_document:
+    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
+nocite: |
+  @*
 ---

### 2024-07-13 presentation.qmd
abcdef

@@
 
+```{r}
+knitr::knit_exit()
+```
+
 ```{r, echo=F, message=F, warning=F, results='hide'}
@@
 modlat <- eqpar$meql
-library(ManifoldDestiny)
 laws_df1 <- ManifoldDestiny::eqdef$meql
@@
 per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
-#round(polynom::integral(penf,c(0,1)),3)
+```
+
+```{r}
+knitr::knit_exit()
 ```

### 2024-07-13 prerendr.R

@@ -123,4 +123,15 @@ suppressMessages(ManifoldDestiny::wasmconload())
 #usethis::use_data(concl_appps, overwrite = TRUE)
 #
 
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+usethis::use_data(basc, overwrite = TRUE)
+usethis::use_data(rigv, overwrite = TRUE)
+appnf <- seloutput(rppnf <- selreport(basc))
+appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
+appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
+appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
+penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
+per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
+per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
+per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
 

### 2024-07-13 analyzer.qmd
sommore

@@
 
-## Install
-
 ```{webr-r}
@@
 library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
 ls(package:ManifoldDestinyWASMP)
 data(package='ManifoldDestinyWASMD')
-```
-
-## Select case
-
-```{webr-r}
 dfl <- ManifoldDestinyWASMD::yout
@@
 
-## Counting
-
 ```{webr-r}
-Countingprocess(dfl)
+apps <- basc
+adat <- apps[[1]]
+amet <- apps[[2]]
+cogr <- Countinggraphs(apps[[1]])
+#selo <- seloutput(selreport(apps))
+#copl <- cogr$polyc[[1]][[1]]
+cogr$sdfc
 ```
-
-## Estimation

### 2024-07-13 rigging.qmd
sommore

--- 2024-07-09 rigging.qmd
@@
 ---
+
+```{webr-r}
+#| echo: fenced
+#| eval: true
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+ls(package:ManifoldDestinyWASMP)
+data(package='ManifoldDestinyWASMD')
+dfl <- ManifoldDestinyWASMD::yout
+```
+
+```{webr-r}
+###### Normal 
+# Simulation
+perv <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
+prow <- c(m=0.51,s=0.10)
+proa <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
+prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
+ztec <- c(0,1)	
+basc <- list(df=ballcastsim(perv,prow,proa,prob,ztec),list(fr=1,eq="alpha=k0+k1*x+k2*y",va='y',prg=list(cnd=1)))
+# Rigged election
+cogr <- Countinggraphs(basc[[1]])
+copl <- cogr$polyc[[1]][[1]]
+plfc <- c(0.20,0.20,0.20)
+ex1s <- list(frm=1, pre=c("alpha","x","y"), end=c("zeta","Omega","lamda"),
+	     stuv=c("S","T","U","V"),
+	     plnr=1,rot=list(fr=c(1,10),sr=c(4,0),tr=c(2,0)),
+	     ls="(alpha-alpha_s)^2"
+)
+ex2s <- list(frm=1, pre=c("alpha","x","y"), end=c("zeta","Omega","lamda"),
+	     stuv=c("S","T","U","V"),
+	     plnr=1,rot=list(fr=c(1,10),sr=c(4,0),tr=c(2,0)),
+	     ls="(alpha-alpha_s)^2"
+)
+ex3s <- list(frm=1, pre=c("alpha","x","y"), end=c("zeta","Omega","lamda"),
+	     stuv=c("S","T","U","V"),
+	     plnr=1,rot=list(fr=c(1,10),sr=c(4,0),tr=c(2,0)),
+	     ls="(alpha-alpha_s)^2"
+)
+exs <- list(ex1s,ex2s,ex3s)
+rigv <- lapply(1:3, function(x) { 
+  cogr$mansys(sygen=exs[[x]])
+  cogr$polyc[[x]]
+  cogr$setres(NULL,1)
+  cogr$setres(plfc[x],1)
+  cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
+  exs[[1]]$frm
+  rasc <- list(cogr$rdfc,list(fr=1,eq="alpha=k0+k1*x+k2*y",va='y',prg=list(cnd=1)))
+})
+###################################################################################################################################################################
+```
+
+```{webr-r}
+appnf <- seloutput(rppnf <- selreport(basc))
+appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
+appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
+appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
+penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
+per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
+per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
+per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
+```
+
+```{webr-r}
+appnf[[1]]
+```

### 2024-07-13 simulations.qmd
python
sommore

@@
 data(package='ManifoldDestinyWASMD')
-library(ggplot2)
-library(combinat)
-library(plotly)
-library(htmltools)
-library(broom)
-set.seed(1)
-dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
-probw <- c(m=0.51,s=0.10)
-probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztech <- c(0,1)	
-mdn <- list(frn=1,eq="alpha=k0+k1*x+k2*y")
-app_bal <- list(df=ballcastsim(dfm,probw,probva,probvb,ztech),list(fr=1,eq="alpha=k0+k1*x+k2*y"))
-app_bal[1]
+dfl <- ManifoldDestinyWASMD::yout
 ```
@@
 ```{webr-r}
+perv <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
+prow <- c(m=0.51,s=0.10)
+proa <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
+prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
+ztec <- c(0,1)	
+basc <- list(df=ballcastsim(perv,prow,proa,prob,ztec),list(fr=1,eq="alpha=k0+k1*x+k2*y",va='y',prg=list(cnd=1)))
+cogr <- Countinggraphs(basc[[1]])
+```
+
+```{webr-r}
+cogr$rdfci
 ```

### 2024-07-17 tabset.qmd
abc
befdel

@@
 
+```{r}
+knitr::knit_exit()
+```
+
 ::: {.callout-caution collapse="true"}
 ## {{< var tabh.h0 >}}
-```{r, echo=FALSE, results='asis',warning=F}
+```{r}
+#| echo: false
+#| output: false
 apps <- basc
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
+{{< include tab.qmd >}}
 :::
@@
 ## {{< var tabh.h1 >}}
-```{r, echo=FALSE, results='asis',warning=F}
+```{r}
+#| echo: false
+#| output: false
 apps <- rigv[[1]]
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
+{{< include tab.qmd >}}
 :::
@@
 ## {{< var tabh.h2 >}}
-```{r, echo=FALSE, results='asis',warning=F}
+```{r}
+#| echo: false
+#| output: false
 apps <- rigv[[2]]
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
+{{< include tab.qmd >}}
 :::
@@
 ## {{< var tabh.h3 >}}
-```{r, echo=FALSE, results='asis',warning=F}
+```{r}
+#| echo: false
+#| output: false
 apps <- rigv[[3]]
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
+{{< include tab.qmd >}}
 :::
@@
 ## {{< var sec6.un1 >}}
-```{r, echo=FALSE, results='asis',warning=F}
+```{r}
+#| echo: false
+#| output: false
 apps <- app1
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
+{{< include tab.qmd >}}
 :::
@@
 ## {{< var sec6.un2 >}}
-```{r, echo=FALSE, results='asis',warning=F}
+```{r}
+#| echo: false
+#| output: false
 apps <- app2
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
+{{< include tab.qmd >}}
 :::
@@
 ## {{< var sec6.un3 >}}
-```{r, echo=FALSE, results='asis',warning=F}
-apps <- app3
-app_a_out <- basc
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
+```{r}
+#| echo: false
+#| output: false
+apps <- app2
 ```
+{{< include tab.qmd >}}
 :::
@@
 ## {{< var sec6.un4 >}}
-```{r, echo=FALSE, results='asis',warning=F}
+```{r}
+#| echo: false
+#| output: false
 apps <- app4
-app1_fil <- paste0(rprojroot::find_rstudio_root_file(), '/tab.qmd')
-text <- readLines(app1_fil)
-cat(knitr::knit_child(text = paste(text[50:length(text)], collapse = "\n"), quiet = TRUE))
 ```
+{{< include tab.qmd >}}
 :::

### 2024-07-17 R/wasmconverting.R

@@ -197,8 +197,12 @@ ballcastsim <- function(dfm=(function(x){data.frame(P=seq(1,x),RV=as.integer(rno
 selreport <- function(
 		      baldata=NULL
 		      ){
+
+  browser()
   da <- baldata[[1]]
   md <- baldata[[2]]
+  if (is.null(md)) md <- list( mtd = list( nmn = "Default"), spr = list(), sol = list( fr = "1", eq = "alpha=k0+k1*x+k2*y", va = "y"), prg = list( cnd = 0, z = 0, stuv = c(0,0,0,0), blup = c(0,1), eqp = "alpha=k0+k1*g+k2*h"), bib = list()) 
+
   frm <- as.numeric(md$sol$fr)
   co <- Countinggraphs(da)
   if (md$prg$cnd==1) co$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp)
@@ -886,6 +890,7 @@ Estimation <- setRefClass("Estimation", fields=list(
 						kvec='vector',
 						param='vector',
 						syequ='list',
+						metad='list',
 						roto='vector',
 						comdesc='data.frame',
 						radpar='vector',
@@ -898,6 +903,7 @@ Estimation$methods(initialize=function(rdfcinp=NULL,form=1){
   param <<- stickers[['parameters']][[fnr]]
   syequ <<- eqpar$meqs
   #radpar <<- c(theta=0,phi=0,rho=0)
+  metad <<- list( mtd = list( nmn = "Default"), spr = list(), sol = list( fr = "1", eq = "alpha=k0+k1*x+k2*y", va = "y"), prg = list( cnd = 0, z = 0, stuv = c(0,0,0,0), blup = c(0,1), eqp = "alpha=k0+k1*g+k2*h"), bib = list())
   lpku <<- list(
     S = list(
       x = c(Sd = 'x*(Z-U-V)', Td = '(1-x)*(Z-U-V)', Ud = 'U', Vd = 'V'),'S~S_hat',

### 2024-07-17 R/wasmnonverting.R

@@ -14,6 +14,12 @@ recoudatr <- function(mda=NULL,prn=1){
   do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
   return(mda$nid)
 }
+recousiml <- function(mda=NULL,prn=1){
+
+}
+recousiml()
+
+
 ##' @export recoudatr
 #recoudatr <- function(mda=NULL,prn=1){
 #  gsh <- googlesheets4::read_sheet(mda$spr$url,sheet=mda$spr$pgn,range=mda$spr$rng) %>%

### 2024-07-17 shinyapps/empapp/app.R

@@ -1,10 +1,9 @@
-options(digits=2)
-
 ManifoldDestiny::wasmconload()
 abc <- data(package = "ManifoldDestiny")[[3]][,3]
 abr <- abc[grepl("app", abc)][3]
 # [1] "app0"        "app0nr"      "app1"        "app2"        "app3"        "app4"        "concl_appps"
 apps <- get(abr)
+options(digits=2)
 ###############################################################################################################################################################
 ui <- fluidPage(
   titlePanel("Election results analyzer"),
@@ -62,29 +61,25 @@ server <- function(input, output, session) {
   })  
   cformo <- reactive({
     # Manual
-    #isla <- input$app_select
     seld <- apps
     seld[[1]]
     seld[[2]]
     #mds <- md[[sna]]
     ##### Purge
-    #mds$mtd$prg$cnd <- c(0)
-    #mds$mtd$prg$stuv <- c(0,0,0,0)
-    #mds$mtd$prg$blup[1] <- 0
-    #mds$mtd$prg$blup[2] <- 1
+    #seld[[2]]$prg$cnd <- c(0)
+    #seld[[2]]$prg$cnd <- c(0)
+    #seld[[2]]$prg$stuv <- c(0,0,0,0)
+    #seld[[2]]$prg$blup[1] <- 0
+    #seld[[2]]$prg$blup[2] <- 1
     ##### Solution
-    #mds$sgs$fr <- as.numeric(input$form)
-    #mds$sgs$eq <- as.numeric(input$meqf)
-    #mds$sgs$va <- as.numeric(input$solvf)
+    #seld[[2]]$sgs$fr <- as.numeric(input$form)
+    #seld[[2]]$sgs$eq <- as.numeric(input$meqf)
+    #seld[[2]]$sgs$va <- as.numeric(input$solvf)
     ##### Rotation
     #mds$mtd$sgs$ro[1] <- input$theta*pi/180
     #mds$mtd$sgs$ro[2] <- input$phi*pi/180
     #mds$mtd$sgs$ro[3] <- input$rho*pi/180
     #### Selreport
-    selr <- selreport(seld)
-    #selr[[2]]$comdesc
-    #selr[[1]]$pl_3d_mani[[1]]
-    #selr[[1]]$all_pl_3d_mani[[1]]
     return(selreport(seld))
   })
   observe(print(cformo()[[1]]$desms))
[…]

### 2024-07-19 presentation.qmd
manfe

@@
 laws_df2 <- ManifoldDestiny::eqdef$meqs
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-appnf <- seloutput(rppnf <- selreport(basc))
-appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
-appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
-appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
-penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
-per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
-per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
-per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
+source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
 ```

### 2024-07-19 tabset.qmd
manfe

@@
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
-source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
-```
-
-```{r}
-knitr::knit_exit()
 ```
@@
 #| output: false
-apps <- basc
+apps <- appsn
 ```
@@
 #| output: false
-apps <- rigv[[1]]
+apps <- apprn
 ```
@@
 #| output: false
-apps <- rigv[[2]]
+apps <- apprh
 ```
@@
 #| output: false
-apps <- rigv[[3]]
+apps <- appro
 ```

### 2024-07-19 data-raw/record_static.R

@@ -7,10 +7,10 @@ qenvar <- yaml::yaml.load_file(paste0(rprojroot::find_rstudio_root_file(),"/_app
 googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
 #######################################################################################################################################################
 # Applications
-recoudatr(qenvar$app1)
-recoudatr(qenvar$app2)
-recoudatr(qenvar$app3)
-recoudatr(qenvar$app4)
+recoudatr(qenvar$appn1)
+recoudatr(qenvar$appn2)
+recoudatr(qenvar$appn3)
+recoudatr(qenvar$appn4)
 #######################################################################################################################################################
 # Simulation
 ## Normal 
@@ -20,7 +20,7 @@ proa <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
 prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
 ztec <- c(0,1)	
 gsh <- ballcastsim(perv,prow,proa,prob,ztec)
-mda <- qenvar$appsd
+mda <- qenvar$appsn
 assign(mda$nid,list(gsh,mda))
 do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
 ## Rigged election
@@ -45,3 +45,9 @@ rigv <- lapply(1:3, function(x) {
   do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
 })
 #######################################################################################################################################################
+#apps <- ManifoldDestiny::appsn
+#adat <- apps[[1]]
+#amet <- apps[[2]]
+#cogr <- Countinggraphs(apps[[1]])
+#selo <- seloutput(selreport(apps))
+

### 2024-07-19 presentation.qmd
sommorepres
abc

@@
 
-```{r}
-knitr::knit_exit()
-```
-
 ```{r, echo=F, message=F, warning=F, results='hide'}
@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-```
-
-```{r}
-knitr::knit_exit()
+# abc <- seloutput(selreport(appsn))
+# abc <- seloutput(selreport(apprn))
 ```
@@
 ```{r}
-appnf[[4]]
+#appsn[[4]]
 ```
@@
 ```{r}
-appr1[[4]]
+#apprs[[4]]
 ```
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r paste0(round(penf,3))`$
+f(x)_{0}^{1}=`r #paste0(round(penf,3))`$
 \end{equation*}
@@
 Election outome 
-  - Integral `r round(polynom::integral(penf,c(0,1)),3)`
-  - Counting `r round(rppnf[[1]]$desms[7,2],3)`
+  - Integral `r #round(polynom::integral(penf,c(0,1)),3)`
+  - Counting `r #round(rppnf[[1]]$desms[7,2],3)`
 
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r paste0(round(per1,3))`$
+f(x)_{0}^{1}=`r #paste0(round(per1,3))`$
 \end{equation*}
@@
 ```{r, echo=F}
-round(polynom::integral(per1,c(0,1)),3)
+#round(polynom::integral(per1,c(0,1)),3)
 ```

### 2024-07-19 presentation.qmd
befrem

@@
 ManifoldDestiny::wasmconload()
+library(polynom)
 modlat <- eqpar$meql
@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-# abc <- seloutput(selreport(appsn))
-# abc <- seloutput(selreport(apprn))
+ssr <- selreport(ManifoldDestiny::appsn)
+rsr  <- selreport(ManifoldDestiny::apprn)
 ```
@@
 ```{r}
-#appsn[[4]]
+ssr[[1]]$pl_2dsort
 ```
@@
 ```{r}
-#apprs[[4]]
+rsr[[1]]$pl_2dsort
 ```
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r #paste0(round(penf,3))`$
+f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`
 \end{equation*}
@@
 Election outome 
-  - Integral `r #round(polynom::integral(penf,c(0,1)),3)`
-  - Counting `r #round(rppnf[[1]]$desms[7,2],3)`
+  - Integral `r round(polynom::integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients)),c(0,1),3),3)`
+  - Counting `r round(ssr[[1]]$desms[7,2],3)`
+
+```{r}
+knitr::knit_exit()
+```
 
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r #paste0(round(per1,3))`$
+$f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`$
 \end{equation*}
@@
 ```{r, echo=F}
-#round(polynom::integral(per1,c(0,1)),3)
+round(polynom::integral(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)),c(0,1),3),3)
 ```

### 2024-07-19 presentation.qmd
break

@@
 rsr  <- selreport(ManifoldDestiny::apprn)
+round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
 ```
@@
 \begin{equation*}
-f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`
+f(x)_{0}^{1}=`r round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))`
 \end{equation*}
 
-Election outome 
+Election outome:
+
 - Integral `r round(polynom::integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients)),c(0,1),3),3)`
 - Counting `r round(ssr[[1]]$desms[7,2],3)`
-
-```{r}
-knitr::knit_exit()
-```
 
@@
 \begin{equation*}
-$f(x)_{0}^{1}=`r round(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients)))`$
+f(x)_{0}^{1}=`r round(integral(polynomial(unname(rsr[[1]]$polyc[[1]]$coefficients))))`
 \end{equation*}

### 2024-07-20 addendum/Addendum_ne.qmd
nevada

@@
 ---
-title: "{{< var addas >}}"
-subtitle: "{{< var addal >}}"
+title: "{{< var addnl >}}"
 format: 
-  revealjs: 
-    smaller: true
-    toc-depth: 1
+  html:
     toc: true
-execute: 
-  cache: false
-footer: <https://lotariohw26.github.io/ManifoldDestiny/>
-output: 
-  html_document:
-    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
-nocite: |
-  @*
+    toc-depth: 3
+    number-sections: false
 ---
@@
 ```{r}
+#| echo: false
+#| output: false
+#| message: false
+#| warning: false
+options(digits=2)
+ManifoldDestiny::wasmconload()
+apps <- appn1
+adat <- apps[[1]]
+amet <- apps[[2]]
+cogr <- Countinggraphs(apps[[1]])
+selo <- seloutput(selreport(apps))
+copl <- cogr$polyc[[1]][[1]]
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+```
+
+### Without purge
+
+::: {.panel-tabset}
+
+### {{< var tabs.h1 >}}
+
+```{r, echo=F}
+kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+```
+### {{< var tabs.h2 >}}
+```{r, echo=F, out.width="60%"}
+selo[['corxy']]
+```
+### {{< var tabs.h3 >}}
+```{r, echo=F, out.width="60%"}
+selo[['qunt']]
+```
+### {{< var tabs.h4 >}}
+```{r, echo=F}
+selo[['ro3d']]
+```
+### {{< var tabs.h5 >}}
+```{r, echo=F, out.width="60%"}
+selo[['regr']]
+```
+### {{< var tabs.h6 >}}
+```{r, echo=F, out.width="60%"}
+selo[['cmp']]
+```
+### {{< var tabs.h7 >}}
+```{r, echo=F, out.width="60%"}
+selo[['resp']]
+```
+:::
+
+### With purge
+
+```{r}
+#| echo: false
+#| output: false
+#| message: false
+#| warning: false
+options(digits=2)
+ManifoldDestiny::wasmconload()
+apps <- appn1
+adat <- apps[[1]]
+amet <- apps[[2]]
+amet$prg$z <- 0
+cogr <- Countinggraphs(apps[[1]])
+selo <- seloutput(selreport(apps))
+copl <- cogr$polyc[[1]][[1]]
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+```
+
+::: {.panel-tabset}
+
+### {{< var tabs.h1 >}}
+
+```{r, echo=F}
+kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+```
+### {{< var tabs.h2 >}}
+```{r, echo=F, out.width="60%"}
+selo[['corxy']]
+```
+### {{< var tabs.h3 >}}
+```{r, echo=F, out.width="60%"}
+selo[['qunt']]
+```
+### {{< var tabs.h4 >}}
+```{r, echo=F}
+selo[['ro3d']]
+```
+### {{< var tabs.h5 >}}
+```{r, echo=F, out.width="60%"}
+selo[['regr']]
+```
+### {{< var tabs.h6 >}}
+```{r, echo=F, out.width="60%"}
+selo[['cmp']]
+```
+### {{< var tabs.h7 >}}
+```{r, echo=F, out.width="60%"}
+selo[['resp']]
+```
+:::
+
+[Spreadsheet calculation (Solomon)](https://docs.google.com/spreadsheets/d/1gkf41sJRAQ6bwKmlAAcb7hAQ6v4zIXG2wDYl67LrJ4k/edit?gid=59123130#gid=59123130)
+
+```{r, echo=F}
 knitr::knit_exit()
 ```
-
-```{r, echo=F, warning=F, message=F}
-library(ManifoldDestiny)
-library(RefManageR)
-library(huxtable)
-library(plotly)
-xaringanExtra::use_editable(expires = 1)
-xaringanExtra::use_tile_view()
-xaringanExtra::use_share_again()
-xaringanExtra::use_scribble()
-xaringanExtra::use_webcam()
-xaringanExtra::use_panelset()
-modlat <- eqpar$meql
-labs <- stickers[['parameters']]
-abs_p <- rprojroot::find_rstudio_root_file()
-#source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_az.R'))
-```
-
-```{r, eval=F, echo=F, message=F, warning=F}
-pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/inst/www/addendum/Addendum_ne.Rmd')
-xaringan::inf_mr(pre_fil)
-#rmarkdown::render(pre_fil) 
-```
-
-```{r}
-knitr::knit_exit()
-```
-
----
-title: "Nevada"
-output:
-  bookdown::html_document2: default
-# https://docs.google.com/document/d/13u3lL_emHyLpog-rFrm7-zk7lKM_AmQd28CJlJ5odFE/edit#
----
-
-```{r}
-source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_ne.R'))
-```
-
-# Introduction
-
-![](pngs/necawa.png)
-
-[$50,000 Reward!](https://operationsunlight.com/2022/11/26/50000-reward/)
-
-```{r}
-plotly::plot_ly(bindf, x = ~g, y = ~h, z = ~alpha, color = ~tpg,
-        type = "scatter3d", mode = "markers")
-```
-
-# Main results
-
-# Sideeffects
-
-## Sideeffect #1
-
-```{r}
-abc <- allreport(fir$sdfc)
-abc[[1]][[2]][[4]]
-```
-
-```{r}
-abc <- allreport(sec$sdfc)
-abc[[1]][[2]][[4]]
-```
-## Sideeffect #2
-## Sideeffect #3
-## Sideeffect #4

### 2024-07-20 paper.qmd
nevada

@@
 
+```{r, echo=F}
+ManifoldDestiny::wasmconload()
+#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+```
+
 ```{r}
-ManifoldDestiny::wasmconload()
-library(ManifoldDestiny)
-library(huxtable)
-library(kableExtra)
-#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
+#| echo: false
+#| output: false
+apps <- appn1
+```
+{{< include tabpar.qmd >}}
+
+```{r}
+knitr::knit_exit()
 ```
@@
 #| output: false
-apps <- basc
+apps <- appsn
 ```
 {{< include tabpar.qmd >}}
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-07-20 tab.qmd
nevada

@@
 ```{r, echo=F, out.width="60%"}
+selo[['cmp']]
+```
+### {{< var tabs.h7 >}}
+```{r, echo=F, out.width="60%"}
 selo[['resp']]

### 2024-07-20 R/wasmconverting.R

@@ -247,7 +247,7 @@ seloutput <- function(selreport=NULL){
   l3 <- selreport[[2]]$resplots[[1]][[3]]
   l4 <- selreport[[2]]$resplots[[1]][[4]]
   tab8 <- cowplot::plot_grid(plotlist=list(l1,l2,l3,l4))
-  tab9 <- selreport[[2]]$comdesc
+  tab9 <- dplyr::select(selreport[[2]]$comdesc,1,3)
   tab10 <- selreport[[4]]
   tab11 <- selreport[[5]]$pl_2dsort
   tab12 <- selreport[[6]]
@@ -996,6 +996,17 @@ Estimation$methods(hat_predict=function(svf='y'){
   regsum[[2]] <<- lm(as.formula(paste0(svf[1],"~", svf[1],'_hat')),data=pred_df_pol)
 })
 Estimation$methods(hat_intcomp=function(){
+  txvnc <- c("Mean votes",
+	     "Number of precincts",
+	     "Full match",
+	     "Percentage",
+	     "Mean",
+	     "Standard deviation",
+	     "Max",
+	     "Miss +/-1" ,
+	     "Miss +/-2" ,
+	     "Miss +/-3",
+             "Full match or +/-1,2,3")
   svf <- as.character(summary(regsum[[2]])[[2]][[2]])
   lpkus <- lpku[[fnr]][[svf]]
   BLM <- c('S','T','U','V','Z')
@@ -1031,6 +1042,6 @@ Estimation$methods(hat_intcomp=function(){
     match_2=sum(compare[[comps]]==2|compare[[comps]]==-2),
     match_3=sum(compare[[comps]]==3|compare[[comps]]==-3),
     prc0123=100*sum(abs(compare[[comps]] - 0) <= 3)/length(compare[[comps]]))
-  comdesc <<- data.frame(stats=names(vnd),values=vnd)
+  comdesc <<- data.frame(fname=txvnc,stats=names(vnd),values=vnd)
 })
 

### 2024-07-20 script/R/applications.R

@@ -1,25 +1,7 @@
-library(ManifoldDestiny)
-library(ggplot2)
-library(dplyr)
-library(ManifoldDestiny)
-library(htmltools)
+ManifoldDestiny::wasmconload()
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 #######################################################################################################################################################
-set.seed(1)
-#######################################################################################################################################################
-P  <- c(1,2,3,4,5,6)
-S  <- c(60,60,60,60,60,60)
-T  <- c(40,40,40,40,40,40)
-U  <- c(40,40*2,40*3,40*4,40*5,40*6)
-V  <- c(60,60*2,60*3,40*4,40*5,40*6)
-Up <- c(40,40*2-5,40*3-15,40*4,40*5,40*6)
-Vp <- c(60,60*2+5,60*3+15,40*4,40*5,40*6)
-R  <- c(200,200*2,200*3,200*4,200*5,200*6)
-pro_rec_ex1 <- data.frame(P=c(1,2,3),S=S,T=T,U=U,V=V,R=R) 
-pro_rec_ex2 <- data.frame(P=c(1,2,3),S=S,T=T,U=Up,V=Vp,R=R) 
-pro_elc_ex1 <- Countinggraphs(pro_rec_ex1,polyn=1)
-pro_elc_ex2 <- Countinggraphs(pro_rec_ex2,polyn=1)
 ########################################################################################################################################################
 app0_rp <- selreport(app0)
 app_0_out <- seloutput(app0_rp)

### 2024-07-20 script/R/simulations.R

@@ -1,60 +1,60 @@
-library(ggplot2)
-library(dplyr)
-library(ManifoldDestiny)
-library(htmltools)
-##########################################################################################################################################################
-set.seed(1)
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
-##########################################################################################################################################################
-###### Normal 
-# Simulation
-perv <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,100,30)))})(100)
-prow <- c(m=0.51,s=0.10)
-proa <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
-prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
-ztec <- c(0,1)	
-basc <- list(df=ballcastsim(perv,prow,proa,prob,ztec),NULL)
-
-# Rigged election
-cogr <- Countinggraphs(basc[[1]])
-copl <- cogr$polyc[[1]][[1]]
-plfc <- c(0.20,0.20,0.20)
-ex1s <- list(frm=1, pre=c("alpha","x","y"), end=c("zeta","Omega","lamda"),
-	     stuv=c("S","T","U","V"),
-	     plnr=1,rot=list(fr=c(1,10),sr=c(4,0),tr=c(2,0)),
-	     ls="(alpha-alpha_s)^2"
-)
-ex2s <- list(frm=1, pre=c("alpha","x","y"), end=c("zeta","Omega","lamda"),
-	     stuv=c("S","T","U","V"),
-	     plnr=1,rot=list(fr=c(1,10),sr=c(4,0),tr=c(2,0)),
-	     ls="(alpha-alpha_s)^2"
-)
-ex3s <- list(frm=1, pre=c("alpha","x","y"), end=c("zeta","Omega","lamda"),
-	     stuv=c("S","T","U","V"),
-	     plnr=1,rot=list(fr=c(1,10),sr=c(4,0),tr=c(2,0)),
-	     ls="(alpha-alpha_s)^2"
-)
-exs <- list(ex1s,ex2s,ex3s)
-rigv <- lapply(1:3, function(x) { 
-  cogr$mansys(sygen=exs[[x]])
-  cogr$polyc[[x]]
-  cogr$setres(NULL,1)
-  cogr$setres(plfc[x],1)
[…]

### 2024-07-20 script/R/testing.R

@@ -2,9 +2,11 @@ ManifoldDestiny::wasmconload()
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 ###########################################################################################################
-appt <- app0
+# Applications
+appt <- app1
 # Report
-repot <- seloutput(selreport(appt))
+rept <- seloutput(selreport(appt))
+rept[[10]]
 # Componenta
 ## Counting
 sum(dplyr::select(appt[[1]],S,T,U,V))

### 2024-07-20 addendum/Addendum_ne.qmd
again

@@
 ManifoldDestiny::wasmconload()
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 apps <- appn1
@@
 copl <- cogr$polyc[[1]][[1]]
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 ```
@@
 ManifoldDestiny::wasmconload()
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+appn1[[2]]$prg$cnd  <- 1
+appn1[[2]]$prg$z  <- 200
 apps <- appn1
@@
 amet <- apps[[2]]
-amet$prg$z <- 0
 cogr <- Countinggraphs(apps[[1]])
 selo <- seloutput(selreport(apps))
+selo[[2]]
 copl <- cogr$polyc[[1]][[1]]
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 ```

### 2024-07-20 R/wasmconverting.R

@@ -202,7 +202,6 @@ selreport <- function(
 
   da <- baldata[[1]]
   md <- baldata[[2]]
-
   frm <- as.numeric(md$sol$fr)
   co <- Countinggraphs(da)
   if (md$prg$cnd==1) co$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp)
@@ -557,7 +556,7 @@ Countingprocess$methods(plext=function(){
 Countingprocess$methods(purging=function(z=0,stuv=c(0,0,0,0),blup=c(0,1),eqp=c("alpha=k0+k1*x+k2*y"),rnk=0,pres=NULL,pri=0){
   rdfv <- rdfci %>%
     dplyr::arrange(P) %>%
-    dplyr::filter(Z>=stuv[1]) %>%
+    dplyr::filter(Z>=z) %>%
     dplyr::filter(S>=stuv[1]) %>%
     dplyr::filter(T>=stuv[2]) %>%
     dplyr::filter(U>=stuv[3]) %>%
@@ -1032,7 +1031,7 @@ Estimation$methods(hat_intcomp=function(){
   regsum[[3]] <<- lm(as.formula(lpkus[[5]]),data=compare)
   vnd <- c(
     meantotvote=mean(compare$Z),
-    nmbpre=length(compare[[comps]] == 0),
+    nmbpre=as.integer(length(compare[[comps]] == 0)),
     match_0=sum(compare[[comps]] == 0),
     prc=100*sum(compare[[comps]] == 0)/length(compare[[comps]] == 0),
     mean=mean(compare[[comps]]),

### 2024-07-20 addendum/Addendum_ne.qmd
abcdef

@@
 
-[Spreadsheet calculation (Solomon)](https://docs.google.com/spreadsheets/d/1gkf41sJRAQ6bwKmlAAcb7hAQ6v4zIXG2wDYl67LrJ4k/edit?gid=59123130#gid=59123130)
+[Independent spreadsheet calculations (Solomon)](https://docs.google.com/spreadsheets/d/1gkf41sJRAQ6bwKmlAAcb7hAQ6v4zIXG2wDYl67LrJ4k/edit?gid=59123130#gid=59123130)
 

### 2024-07-20 addendum/Addendum_ne.qmd
abc

@@
 #| warning: false
-options(digits=2)
+options(scipen = 999)
 ManifoldDestiny::wasmconload()
@@
 
-::: {.panel-tabset}
-
-### {{< var tabs.h1 >}}
-
-```{r, echo=F}
-kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-### {{< var tabs.h2 >}}
-```{r, echo=F, out.width="60%"}
-selo[['corxy']]
-```
-### {{< var tabs.h3 >}}
-```{r, echo=F, out.width="60%"}
-selo[['qunt']]
-```
-### {{< var tabs.h4 >}}
-```{r, echo=F}
-selo[['ro3d']]
-```
-### {{< var tabs.h5 >}}
-```{r, echo=F, out.width="60%"}
-selo[['regr']]
-```
-### {{< var tabs.h6 >}}
-```{r, echo=F, out.width="60%"}
-selo[['cmp']]
-```
-### {{< var tabs.h7 >}}
-```{r, echo=F, out.width="60%"}
-selo[['resp']]
-```
-:::
+{{< include ../tab.qmd >}}
 
@@
 
-::: {.panel-tabset}
-
-### {{< var tabs.h1 >}}
-
-```{r, echo=F}
-kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
-```
-### {{< var tabs.h2 >}}
-```{r, echo=F, out.width="60%"}
-selo[['corxy']]
-```
-### {{< var tabs.h3 >}}
-```{r, echo=F, out.width="60%"}
-selo[['qunt']]
-```
-### {{< var tabs.h4 >}}
-```{r, echo=F}
-selo[['ro3d']]
-```
-### {{< var tabs.h5 >}}
-```{r, echo=F, out.width="60%"}
-selo[['regr']]
-```
-### {{< var tabs.h6 >}}
-```{r, echo=F, out.width="60%"}
-selo[['cmp']]
-```
-### {{< var tabs.h7 >}}
-```{r, echo=F, out.width="60%"}
-selo[['resp']]
-```
-:::
+{{< include ../tab.qmd >}}
 
 [Independent spreadsheet calculations (Solomon)](https://docs.google.com/spreadsheets/d/1gkf41sJRAQ6bwKmlAAcb7hAQ6v4zIXG2wDYl67LrJ4k/edit?gid=59123130#gid=59123130)
-
-```{r, echo=F}
-knitr::knit_exit()
-```

### 2024-07-20 tab.qmd
abc

--- 2024-07-11 tab.qmd
@@
 ::: {.panel-tabset}
-
+### {{< var tabs.h0 >}} 
+```{r, echo=F}
+paste0(amet$mtd$nmn,amet$mtd$yea,amet$mtd$std,amet$mtd$cou)
+```
 ### {{< var tabs.h1 >}} 
-
 ```{r, echo=F}

### 2024-07-20 tabset.qmd
abc

@@
 ManifoldDestiny::wasmconload()
-library(ManifoldDestiny)
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))

### 2024-07-20 addendum/Addendum_ne.qmd
publish

@@
 #| warning: false
-options(scipen = 999)
 ManifoldDestiny::wasmconload()
@@
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+```
+
+```{r}
+#| echo: false
+#| output: false
+#| message: false
+#| warning: false
 apps <- appn1
@@
 #| warning: false
-options(digits=2)
-ManifoldDestiny::wasmconload()
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
-source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 appn1[[2]]$prg$cnd  <- 1

### 2024-07-20 tab.qmd
publish

--- 2024-07-11 tab.qmd
@@
 copl <- cogr$polyc[[1]][[1]]
+options(digits = 2)                                                                                               
 ```
@@
 ```{r, echo=F, out.width="60%"}
+kableExtra::kbl(selo[['cmp']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+```
+### {{< var tabs.h7 >}}
+```{r, echo=F, out.width="60%"}
 selo[['resp']]

### 2024-07-21 tab.qmd
befrev

@@
 ```
+### {{< var tabs.h8 >}}
+```{r, echo=F, out.width="60%"}
+selo[['bs']]
+```
 :::

### 2024-07-21 R/wasmconverting.R
abcdef

@@ -585,7 +585,6 @@ Countingprocess$methods(sortpre=function(form=1,
 					 sortby='alpha'
 					 ){
 
-	browser()
   frmsel <- list(c(1,2,3,4,5,6),c(7,8,9,10,11,12),c(13,14,15,16,17,18),c(19,20,21,22,23,24))[[form]]
   # [1] "alpha" "x"     "y"     "zeta"  "lamda" "Omega" "alpha" "g"     "h"     "Gamma" "Omega" "lamda" "alpha"
   #[14] "m"     "n"     "xi"    "lamda" "Omega" "alpha" "x"     "y"     "Omega" "m"     "n"    

### 2024-07-21 R/wasmnonverting.R

@@ -1,5 +1,6 @@
 #' @export recoudatr
 recoudatr <- function(mda=NULL,prn=1){
+#	browser()
   gsh <- googlesheets4::read_sheet(mda$spr$url,sheet=mda$spr$pgn,range=mda$spr$rng) %>%
     data.table::setnames(new=mda$spr$cln) %>%
     dplyr::mutate(P=row_number(PN)) %>%

### 2024-07-21 data-raw/record_static.R

@@ -7,10 +7,10 @@ qenvar <- yaml::yaml.load_file(paste0(rprojroot::find_rstudio_root_file(),"/_app
 googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
 #######################################################################################################################################################
 # Applications
-recoudatr(qenvar$appn1)
-recoudatr(qenvar$appn2)
+#recoudatr(qenvar$appn1)
+#recoudatr(qenvar$appn2)
 recoudatr(qenvar$appn3)
-recoudatr(qenvar$appn4)
+#recoudatr(qenvar$appn4)
 #######################################################################################################################################################
 # Simulation
 ## Normal 

### 2024-07-21 presentation.qmd
abcdef
all

@@
 
----
-
 # {{< var sec6.nmn >}}
@@
 #| output: false
-apps <- app1
+apps <- appn1
 ```
@@
 #| output: false
-apps <- app2
+apps <- appn2
 ```
@@
 #| output: false
-apps <- app4
+apps <- appn4
 ```

### 2024-07-21 tab.qmd
abcdef
all

--- 2024-07-20 tab.qmd
@@
 #| warning: false
+#ManifoldDestiny::wasmconload()
+#source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+#source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+#apps <- appsn
 adat <- apps[[1]]
@@
 selo[['regr']]
+selo[['regi']]
 ```
@@
 ```{r, echo=F, out.width="60%"}
-selo[['cmp']]
+kableExtra::kbl(selo[['cmp']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```

### 2024-07-21 tabset.qmd
publish
abc
all

@@
 ```
-
-::: {.callout-caution collapse="true"}
-## {{< var tabh.h0 >}}
-```{r}
-#| echo: false
-#| output: false
-apps <- appsn
-```
-{{< include tab.qmd >}}
-:::
 
@@
 #| output: false
-apps <- app2
+apps <- appn3
 ```

### 2024-07-21 R/wasmconverting.R

@@ -198,12 +198,11 @@ ballcastsim <- function(dfm=(function(x){data.frame(P=seq(1,x),RV=as.integer(rno
 selreport <- function(
 		      baldata=NULL
 		      ){
-
   da <- baldata[[1]]
   md <- baldata[[2]]
   frm <- as.numeric(md$sol$fr)
   co <- Countinggraphs(da)
-  if (md$prg$cnd==1) co$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp)
+  if (md$prg$cnd==1) {co$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp)}
   co$sortpre(frm)
   co$descriptive(frm)
   co$r2siminput(frm)
@@ -222,11 +221,13 @@ selreport <- function(
   ges$hat_intcomp()
   ### Identify
   ies <- Estimation(co$rdfc,frm)
+  md$sol$eq
   ies$regression(md$sol$eq[2])
   ies$diagnostics()
   ## Identify
   ### Bowplot
   cob <- Countinggraphs(da,selvar=names(da))
+  if (md$prg$cnd==1) {cob$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp)}
   cob$sortpre(4,3)
   cob$plot2d(4,labs=list(title=NULL,x="precinct (normalized)",y="percentage",caption=NULL,alpha=0.4,size=0.5),
   selv=2)
@@ -248,8 +249,9 @@ seloutput <- function(selreport=NULL){
   tab8 <- cowplot::plot_grid(plotlist=list(l1,l2,l3,l4))
   tab9 <- dplyr::select(selreport[[2]]$comdesc,1,3)
   tab10 <- selreport[[4]]$pl_2dsort
-  tab11 <- selreport[[5]]
-  list(rdfc=tab1,decs=tab2,corxy=tab3,qunt=tab4,ro3d=tab5,r2li=tab6,regr=tab7,resp=tab8,cmp=tab9,bs=tab10,md=tab11)
+  tab11 <- list(summary(selreport[[3]]$regsum[[1]]))
+  tab12 <- selreport[[5]]
[…]

### 2024-07-21 R/wasmnonverting.R

@@ -1,7 +1,7 @@
 #' @export recoudatr
 recoudatr <- function(mda=NULL,prn=1){
-#	browser()
-  gsh <- googlesheets4::read_sheet(mda$spr$url,sheet=mda$spr$pgn,range=mda$spr$rng) %>%
+  gsh <- googlesheets4::read_sheet(mda$spr$url,sheet=mda$spr$pgn,range=mda$spr$rng) %>% 
+    dplyr::mutate(across(where(is.list), ~ as.character(.x))) %>%
     data.table::setnames(new=mda$spr$cln) %>%
     dplyr::mutate(P=row_number(PN)) %>%
     dplyr::mutate(

### 2024-07-21 script/R/testing.R

@@ -3,12 +3,11 @@ source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 ###########################################################################################################
 ###########################################################################################################
-apps <- appn1
+apps <- appn3
 adat <- apps[[1]]
 amet <- apps[[2]]
 rept <- seloutput(selreport(apps))
-rept[[1]]
-
+rept[[7]]
 
 ###########################################################################################################
 apps <- appn3
@@ -19,15 +18,10 @@ cob$sortpre(4,3)
 cob$plot2d(4,labs=list(title=NULL,x="precinct (normalized)",y="percentage",caption=NULL,alpha=0.4,size=0.5))
 summary(selreport(apps)[[3]]$regsum[[1]])
 rept <- seloutput(selreport(apps))
-rept[[10]]
+ggplot2::geom_point(data=filter(longdf,name%in%psel),ggplot2::aes(x=pri,y=value, color=name),size=labs$size,alpha=labs$alpha) +
+ggplot2::geom_line(data=filter(longdf,name%in%paste0(psel,'_pred')),ggplot2::aes(x=pri,y=value, color=name)) 
 
-bm()
-
-
-    ggplot2::geom_point(data=filter(longdf,name%in%psel),ggplot2::aes(x=pri,y=value, color=name),size=labs$size,alpha=labs$alpha) +
-    ggplot2::geom_line(data=filter(longdf,name%in%paste0(psel,'_pred')),ggplot2::aes(x=pri,y=value, color=name)) 
-
-  pselv <- list(psel,psel[c(1,2,3)])[[1]]
+pselv <- list(psel,psel[c(1,2,3)])[[1]]
 
 
 

### 2024-08-01 abc.qmd
abc

@@
 ---
-title: ""
+title: "{{< var titll >}}"
+subtitle: "Based upon the ideas developed by Edward K. Solomon"
+format:
+  revealjs:
+    drop:
+      engine: webr
       webr:
-  show-startup-message: true      # Display status of webR initialization
-  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['dplyr','data.table','readr','ggplotly']             # Pre-install dependencies
-  cell-options:
-    autorun: true
-filters:
-  - panelize
-  - pyodide
-  - webr
+        packages:
+          - ggplot2
+          - dplyr
+execute: 
+  cache: false
+footer: <https://lotariohw26.github.io/ManifoldDestiny/>
+output: 
+  html_document:
+    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
+nocite: |
+  @*
 ---
 
-## Web-R
+# Abc
 
-:::{.to-webr}
-```{r}
-1 + 1
-```
-:::
-
-## Pyodide
-
-:::{.to-pyodide}
-```{python}
-x = [1, 2]
-print(x)
-```
-:::
+2+2

### 2024-08-01 shinyapps/manimp/app.R

@@ -1,53 +1,55 @@
 ManifoldDestiny::wasmconload()
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 # Shiny
 ui <- fluidPage(
   titlePanel("Election simulator for the rigging of a natural election"),
   sidebarLayout(
     sidebarPanel(
-      h4("Simulation settings:"),
-      textInput("prec",  "Numer of precinct", value='30, 50, 3'),
-      textInput("probw",  "Prob of assigning to R:", value='0.51, 0.01'),
-      textInput("prob_rv", "Prob of R voting:", value='0.7, 0.01'),
-      textInput("prob_rm", "Prob of voting by mail if voting by R:", value='0.4, 0.01'),
-      textInput("prob_dv", "Prob of D voting:", value='0.5, 0.01'),
-      textInput("prob_dm", "Prob of voting by mail if voting by D:", value='0.6, 0.01'),
-      selectInput("form", "Rigged:",
-                  choices = c("Normal Form" = "1",
-                              "Hybrid Form" = "2",
-                              "Opposition Form" = "3"), selected = "1"),
-      selectizeInput("prevar","Predermined variables",choices=c("alpha","x","y","zeta","omega"),multiple =TRUE,options=list(maxItems=3),
-      selected = c("alpha", "x", "y")),
-      selectizeInput("endvar","Endogenous variables",choices=c("alpha","x","y","zeta","lamda"),multiple =TRUE,options=list(maxItems=2), selected=c("zeta","lamda")),
-      textInput("pn", "Polynomial", value='0.23'),
-      selectInput("linear", "Polynomial:",
-                  choices = c("Linear" = "1",
-                              "Quadratic" = "2",
-                              "Cubic" = "3",
-                              "Quartic" = "4"), selected = "1"),
-      textInput("wn", "White noise", value='0.0, 0.0'),
-      textInput("kvec", "parameters", value='0,0.5,0.5'),
[…]

### 2024-08-02 script/R/testing.R
updrot

@@ -2,6 +2,29 @@ ManifoldDestiny::wasmconload()
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 ###########################################################################################################
+apps <- apprn
+adat <- apps[[1]]
+amet <- apps[[2]]
+rept <- seloutput(selreport(apps))
+rept[[7]]
+
+###########################################################################################################
+googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
+url <- "https://docs.google.com/spreadsheets/d/1IYZEi4WnbyZ5PhOZPFV1h6wO3w2e59qL5l7JJZ3Illw/edit?gid=0#gid=0"
+gsh <- googlesheets4::read_sheet(url,sheet=1,range="B1:D609") %>% dplyr::mutate(P=row_number())
+abc <- erotation(dfe=gsh,c("A","H","G"),amean=T)
+
+
+View(abc)
+
+
+
+
+
+
+
+
+
 ###########################################################################################################
 apps <- appn7
 adat <- apps[[1]]
@@ -15,14 +38,6 @@ cob$rotation()
 def <- Estimation(cob$rdfc)
 def$regression("alpha=k0+k1*h+k2*g")
 
-###########################################################################################################
-apps <- apprn
-adat <- apps[[1]]
-amet <- apps[[2]]
-rept <- seloutput(selreport(apps))
-rept[[7]]
-
-###########################################################################################################
 apps <- appsn
 adat <- apps[[1]]
 amet <- apps[[2]]

### 2024-08-15 tab.qmd
man0

--- 2024-07-20 tab.qmd
@@
 #| warning: false
+#ManifoldDestiny::wasmconload()
+#source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+#source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+#apps <- appn1
+#
 adat <- apps[[1]]
@@
 cogr <- Countinggraphs(apps[[1]])
-selo <- seloutput(selreport(apps))
-copl <- cogr$polyc[[1]][[1]]
-options(digits = 2)                                                                                               
+#selo <- seloutput(selreport(apps))
+#options(digits = 2)                                                                                               
+```
+
+```{r}
+paste0(amet$mtd$nmn,amet$mtd$yea,amet$mtd$std,amet$mtd$cou)
+```
+
+```{r}
+knitr::knit_exit()
 ```
@@
 ```{r, echo=F}
-paste0(amet$mtd$nmn,amet$mtd$yea,amet$mtd$std,amet$mtd$cou)
+#paste0(amet$mtd$nmn,amet$mtd$yea,amet$mtd$std,amet$mtd$cou)
 ```
@@
 ```{r, echo=F}
-kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+#kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```
@@
 ```{r, echo=F, out.width="60%"}
-selo[['corxy']]
+#selo[['corxy']]
 ```
@@
 ```{r, echo=F, out.width="60%"}
-selo[['qunt']]
+#selo[['qunt']]
 ```
@@
 ```{r, echo=F}
-selo[['ro3d']]
+#selo[['ro3d']]
 ```
@@
 ```{r, echo=F, out.width="60%"}
-selo[['regr']]
+#selo[['regr']]
+#selo[['regi']]
 ```
@@
 ```{r, echo=F, out.width="60%"}
-kableExtra::kbl(selo[['cmp']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+#kableExtra::kbl(selo[['cmp']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```
@@
 ```{r, echo=F, out.width="60%"}
-selo[['resp']]
+#selo[['resp']]
+```
+### {{< var tabs.h8 >}}
+```{r, echo=F, out.width="60%"}
+#selo[['bs']]
 ```

### 2024-08-15 tabset.qmd
abc
updrot
man0

@@
 ```
+::: {.callout-caution collapse="true"}
+## {{< var tabh.h1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- appsn
+```
+:::
+{{< include tab.qmd >}}
+```{r}
+knitr::knit_exit()
+```
 
@@
 ```
-{{< include tab.qmd >}}
 :::

### 2024-08-15 script/R/testing.R

@@ -1,9 +1,71 @@
 ManifoldDestiny::wasmconload()
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+#
+apps <- appn0
+adat <- apps[[1]]
+amet <- apps[[2]]
+cob <- Countinggraphs(adat,selvar=names(adat))
+cob$purging() 
+cob$
+def <- Estimation(cob$rdfc)
+def$regression("alpha=k0+k1*h+k2*g")
+summary(def$regsum[[1]])
+
+apps <- appn0
+adat <- apps[[1]]
+amet <- apps[[2]]
+selo <- seloutput(selreport(apps))
+View(selo[[1]])
+
+fopl <- cogr$polyc[[1]][[1]]
+options(digits = 2)                                                                                               
+
+
+View(co$rdfc)
+#ifelse(Sys.info()[['sysname']]==
+#
+#
+#if(Sys.info()[['sysname']]=="Emscripten")
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+ManifoldDestiny::wasmconload()
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 ###########################################################################################################
 ###########################################################################################################
-apps <- appsn
+apps <- app1
 adat <- apps[[1]]
 amet <- apps[[2]]
 rept <- seloutput(selreport(apps))

### 2024-08-16 tab.qmd
upd

--- 2024-07-21 tab.qmd
@@
 #| warning: false
+ManifoldDestiny::wasmconload()
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+apps <- appn1
+#
 adat <- apps[[1]]
@@
 selo <- seloutput(selreport(apps))
-copl <- cogr$polyc[[1]][[1]]
 options(digits = 2)                                                                                               
@@
 ```{r, echo=F}
-paste0(amet$mtd$nmn,amet$mtd$yea,amet$mtd$std,amet$mtd$cou)
+kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
 ```
@@
 ```{r, echo=F}
-kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
+paste0(amet$mtd$nmn,amet$mtd$yea,amet$mtd$std,amet$mtd$cou)
 ```

### 2024-08-16 tabset.qmd
upd

--- 2024-07-21 tabset.qmd
@@
 ```
+::: {.callout-caution collapse="true"}
+## {{< var tabh.h1 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- appsn
+```
+:::
+{{< include tab.qmd >}}
 
@@
 ```
+:::
 {{< include tab.qmd >}}
-:::
 
@@
 ```
+:::
 {{< include tab.qmd >}}
-:::

### 2024-08-17 index.qmd
abc
abcdef
sommore
manfe
sommorepres
late

@@
   cache: false
-webr:
-  show-startup-message: true      # Display status of webR initialization
-  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
-  cell-options:
-    autorun: true
-filters:
-  - panelize
-  - webr
+#webr:
+#  show-startup-message: true      # Display status of webR initialization
+#  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
+#  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
+#  cell-options:
+#    autorun: true
+#filters:
+#  - panelize
+#  - webr
 ---
@@
 
-# Testing (latest from Ed's Youtube stream)
+```{r, echo=F}
+suppressMessages(ManifoldDestiny::wasmconload()) 
+apps <- appn0
+adat <- apps[[1]]
+amet <- apps[[2]]
+cob <- Countinggraphs(adat,selvar=names(adat))
+sum(dplyr::select(cob$rdfci,S,T,U,V))
+cob$purging(z=amet$prg$z,pri=1) 
+cob$plext(2)
+sum(dplyr::select(cob$rdfce,S,T,U,V))
+def <- Estimation(cob$rdfce)
+def$regression("alpha=k0 + k1*g + k2*h")
+summary(def$regsum[[1]])
+```
 
-## Installling packages
+```{r}
+def$regression("alpha=k0 + k1*g + k2*h")
+summary(def$regsum[[1]])
+```
+
+```{r}
+def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
+summary(def$regsum[[1]])
+```
+
+```{r, echo=F}
+knitr::knit_exit()
+```
 
@@
 dfl <- ManifoldDestinyWASMD::yout
+```
+
+```{r, echo=F}
+knitr::knit_exit()
 ```
@@
 **Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
-
-```{r, echo=F}
-knitr::knit_exit()
-```

### 2024-08-17 tabset.qmd
tabsets

--- 2024-07-21 tabset.qmd
@@
 ```
-
 ::: {.callout-caution collapse="true"}
@@
 #| output: false
-apps <- apprn
+apps <- appsn
 ```

### 2024-08-17 index.qmd
break

--- 2024-07-09 index.qmd
@@
 
-# Testing (latest from Ed's Youtube stream)
+```{webr-r}
+#| echo: fenced
+#| eval: true
+webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
+webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
+library(ManifoldDestinyWASMP)
+library(ManifoldDestinyWASMD)
+ls(package:ManifoldDestinyWASMP)
+data(package='ManifoldDestinyWASMD')
+```
 
-## Installling packages
+```{r, echo=F}
+knitr::knit_exit()
+```
+
+```{r, echo=F}
+suppressMessages(ManifoldDestiny::wasmconload()) 
+apps <- appn0
+adat <- apps[[1]]
+amet <- apps[[2]]
+cob <- Countinggraphs(adat,selvar=names(adat))
+sum(dplyr::select(cob$rdfci,S,T,U,V))
+cob$purging(z=amet$prg$z,pri=1) 
+cob$plext(2)
+sum(dplyr::select(cob$rdfce,S,T,U,V))
+def <- Estimation(cob$rdfce)
+def$regression("alpha=k0 + k1*g + k2*h")
+summary(def$regsum[[1]])
+```
+
+```{r}
+def$regression("alpha=k0 + k1*g + k2*h")
+summary(def$regsum[[1]])
+```
+
+```{r}
+def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
+summary(def$regsum[[1]])
+```
+
+```{r, echo=F}
+knitr::knit_exit()
+```
 

### 2024-08-17 index.qmd
alapha

@@
 library(ManifoldDestinyWASMD)
-ls(package:ManifoldDestinyWASMP)
-data(package='ManifoldDestinyWASMD')
+#ls(package:ManifoldDestinyWASMP)
+#data(package='ManifoldDestinyWASMD')
+apps <- appn0
+```
+
+```{webr-r}
+adat <- apps[[1]]
+amet <- apps[[2]]
+cob <- Countinggraphs(adat)
+cob$purging(z=0) 
+def <- Estimation(cob$rdfce)
+```
+
+```{webr-r}
+def$regression("alpha=k0 + k1*g + k2*h")
+summary(def$regsum[[1]])
+```
+
+```{webr-r}
+def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
+summary(def$regsum[[1]])
 ```

### 2024-08-17 analyzer.qmd
all

--- 2024-07-09 analyzer.qmd
@@
 library(ManifoldDestinyWASMP)
-ls(package:ManifoldDestinyWASMP)
-data(package='ManifoldDestinyWASMD')
+library(ManifoldDestinyWASMD)
+#ls(package:ManifoldDestinyWASMP)
+#data(package='ManifoldDestinyWASMD')
+apps <- appn0
 ```
 
-## Select case
+```{webr-r}
+adat <- apps[[1]]
+amet <- apps[[2]]
+cob <- Countinggraphs(adat)
+cob$purging(z=0) 
+def <- Estimation(cob$rdfce)
+```
 
 ```{webr-r}
-dfl <- ManifoldDestinyWASMD::yout
+def$regression("alpha=k0 + k1*g + k2*h")
+summary(def$regsum[[1]])
 ```
 
-## Counting
-
 ```{webr-r}
-Countingprocess(dfl)
+def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
+summary(def$regsum[[1]])
 ```
-
-## Estimation

### 2024-08-17 index.qmd
all

--- 2024-08-17 index.qmd
@@
 
-```{webr-r}
-#| echo: fenced
-#| eval: true
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-ls(package:ManifoldDestinyWASMP)
-data(package='ManifoldDestinyWASMD')
-```
-
-```{r, echo=F}
-knitr::knit_exit()
-```
-
-```{r, echo=F}
-suppressMessages(ManifoldDestiny::wasmconload()) 
-apps <- appn0
-adat <- apps[[1]]
-amet <- apps[[2]]
-cob <- Countinggraphs(adat,selvar=names(adat))
-sum(dplyr::select(cob$rdfci,S,T,U,V))
-cob$purging(z=amet$prg$z,pri=1) 
-cob$plext(2)
-sum(dplyr::select(cob$rdfce,S,T,U,V))
-def <- Estimation(cob$rdfce)
-def$regression("alpha=k0 + k1*g + k2*h")
-summary(def$regsum[[1]])
-```
-
-```{r}
-def$regression("alpha=k0 + k1*g + k2*h")
-summary(def$regsum[[1]])
-```
-
-```{r}
-def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
-summary(def$regsum[[1]])
-```
-
-```{r, echo=F}
-knitr::knit_exit()
-```
-
-```{webr-r}
-#| echo: fenced
-#| eval: true
-webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
-webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
-library(ManifoldDestinyWASMP)
-library(ManifoldDestinyWASMD)
-ls(package:ManifoldDestinyWASMP)
-data(package='ManifoldDestinyWASMD')
-dfl <- ManifoldDestinyWASMD::yout
-```
-
-```{r, echo=F}
-knitr::knit_exit()
-```
-
-```{webr-r}
-coi <- Countingprocess(dfl[[1]])
-ges <- Estimation(coi$rdfc,2)
-ges$regression("alpha=k0+k1*g+k2*h")
-ges$diagnostics()
-broom::tidy(ges$regsum[[1]])
-broom::glance(ges$regsum[[1]])
-```
-
-[Nevada](https://docs.google.com/spreadsheets/d/1gCfmuK44sUeb0Hb0plAc8VllPSjtUiEHWlJjeHq3xXY/edit?gid=0#gid=0)
-
 **Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

### 2024-08-17 tabset.qmd
set

@@
 ::: {.callout-caution collapse="true"}
+## {{< var tabh.h0 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- appsn
+```
+{{< include tab.qmd >}}
+:::
+::: {.callout-caution collapse="true"}
 ## {{< var tabh.h1 >}}
@@
 #| output: false
-apps <- appsn
+apps <- apprn
 ```

### 2024-08-18 randpython.qmd
abc

@@
 
-def genpolycoeff(plr=1,parm=["alpha", "x", "y"],solvd='alpha',eur=[0, 0, 0]):
+def genpolycoeff(equn="alpha=k0+k1*g+k2*h",solv='y',grd=0,parm=["alpha", "x", "y"],plr=1,eur=[1, 4, 2]):
     x, y, z = sympy.symbols('x y z')
     k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
-    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
+    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
     expr = [Eq(z,k0+k1*x+k2*y),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3)][plr-1]
-    sum_eur = sum(eur)
     # Without rotation
-    if sum_eur == 0:
-        exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
-        polys = poly(exprc, sympify(solvd)).all_coeffs()
+    if grd == 0:
+        #exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
+        ls, rs = equn.split('=')
+        eqs = Eq(sympify(ls), sympify(rs))
+        polys = poly(eqs.rhs - eqs.lhs, sympify(solv)).all_coeffs()
         abc = []
@@
         ABCDE[:len(polys)] = polys
-        return ABCDE 
+        return ABCDE, 0, 0
     # With rotation
@@
                 dic = [dic1,dic2][0]
-                nrs = dxyz[solvd]-1
+                nrs = dxyz[solv]-1
         ABCDE = [0, 0, 0, 0, 0]
@@
         return ABCDE, matarch, abc
-
 ```
@@
 ```{pyodide-python}
-genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y') 
-genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y',eur=[1, 4, 2])[0]
+#genpolycoeff(equn="alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2",solv="y")
+#genpolycoeff(plr=1,parm=["alpha", "x", "y"], solv='y',grd=1,eur=[1, 4, 2])[0]
 ```

### 2024-08-18 randpython.qmd
newupd

@@
 ```{pyodide-python}
-#genpolycoeff(equn="alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2",solv="y")
+#genpolycoeff(equn="alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2",solv="y")[0]
 #genpolycoeff(plr=1,parm=["alpha", "x", "y"], solv='y',grd=1,eur=[1, 4, 2])[0]

### 2024-09-08 randpython.qmd
df2

--- 2024-07-09 randpython.qmd
@@
 
-def genpolycoeff(plr=1,parm=["alpha", "x", "y"],solvd='alpha',eur=[0, 0, 0]):
+def genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g'):
+    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
     x, y, z = sympy.symbols('x y z')
+    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
     k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
-    sympy.var('alpha x y g h n m zeta Gamma lamda ui')
-    expr = [Eq(z,k0+k1*x+k2*y),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3)][plr-1]
-    sum_eur = sum(eur)
-    # Without rotation
-    if sum_eur == 0:
-        exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
-        polys = poly(exprc, sympify(solvd)).all_coeffs()
-        abc = []
+    parm = elem[2-1][:5]
+    ls, rs = expr.split('=')
+    expr = Eq(sympify(ls), sympify(rs))
+    plr = int(sympy.total_degree(expr))-1
+    polys = poly(expr.rhs - expr.lhs, sympify(solv)).all_coeffs()
+    abc = [1,0,0,0,1,0,0,0,1]
     uvw = []
@@
     ABCDE[:len(polys)] = polys
-        return ABCDE 
-    # With rotation
-    else:
+    matarch = 0
+    return ABCDE, abc, matarch, plr
+
+#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
+
+def genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4]):
+    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
+    x, y, z = sympy.symbols('x y z')
+    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
+    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
+    parm = elem[form-1][:5]
+    pamm = [element + "_m" for element in parm]
+    ls, rs = expr.split('=')
+    expr = Eq(sympify(ls), sympify(rs))
+    plr = int(sympy.total_degree(expr))-1
     dxyz = {'x': 1, 'y': 2, 'z': 3}
+    nrs = parm.index(solv)
     # Defining
@@
     Ew = Eq(z, c1 * u0 + c2 * v0 + c3 * w0)
-        # Start with non-rotated
     exprf = solve(expr,z)[0]-z
@@
         nrfs = len(varn.free_symbols)
+        #varn.free_symbols
         matarch.loc[i, 'var'] = str(varn)
@@
             dic = [dic1,dic2][0]
-                nrs = dxyz[solvd]-1
     ABCDE = [0, 0, 0, 0, 0]
@@
         A[2] += dic['d_300']
-            B[0] +=  dic['d_320']*u0+dic['d_321']*w0
-            B[1] +=  dic['d_302']*u0+dic['d_312']*v0
-            B[2] +=  dic['d_301']*w0+dic['d_310']*v0
-            C[0] +=  dic['d_310']*u0**2+dic['d_311']*u0*w0+dic['d_312']*w0**2+dic['d_110']
-            C[1] +=  dic['d_301']*u0**2+dic['d_311']*u0*v0+dic['d_321']*v0**2+dic['d_101']
-            C[2] +=  dic['d_302']*w0**2+dic['d_311']*w0*v0+dic['d_320']*w0**2+dic['d_201']*v0+dic['d_210']*w0+dic['d_110']
-            D[0] += dic['d_300']*u0**3+dic['d_301']*w0*u0**2+dic['d_302']*w0**2*u0+dic['d_303']*w0**3
-            D[1] += dic['d_300']*u0**3+dic['d_310']*u0*v0**2+dic['d_320']*v0**2*u0+dic['d_330']*v0**3
-            D[2] += dic['d_303']*v0**3+dic['d_312']*w0*v0**2+dic['d_321']*w0**2*v0+dic['d_330']*v0**3
+        B[0] += dic['d_320']*z + dic['d_321']*y
+        B[1] += dic['d_302']*z + dic['d_312']*x
+        B[2] += dic['d_301']*y + dic['d_310']*x
+        C[0] += dic['d_310']*z**2 + dic['d_311']*y*z + dic['d_312']*y**2
+        C[1] += dic['d_301']*z**2 + dic['d_311']*x*z + dic['d_321']*x**2
+        C[2] += dic['d_302']*y**2 + dic['d_311']*x*y + dic['d_320']*x**2
+        D[0] += dic['d_300']*y**3 + dic['d_301']*y*z**2 + dic['d_302']*y**2*y+dic['d_303']*z**3
+        D[1] += dic['d_300']*x**3 + dic['d_310']*x*y**2 + dic['d_320']*y**2*x+dic['d_330']*y**3
+        D[2] += dic['d_303']*y**3 + dic['d_312']*z*y**2 + dic['d_321']*z**2*y + dic['d_330']*y**3
     if plr in [2,3]:
@@
         B[2] += dic['d_200']
-            C[0] += dic['d_210']*u0+dic['d_211']*w0
-            C[1] += dic['d_201']*u0+dic['d_211']*v0
-            C[2] += dic['d_201']*v0+dic['d_210']*w0
-            D[0] += dic['d_200']*u0**2+dic['d_201']*w0*u0+dic['d_202']*w0**2
-            D[1] += dic['d_200']*u0**2+dic['d_210']*v0*u0+dic['d_220']*v0**2
-            D[2] += dic['d_202']*v0**2+dic['d_211']*v0*w0+dic['d_220']*w0**2
+        C[0] += dic['d_210']*z + dic['d_211']*y
+        C[1] += dic['d_201']*z + dic['d_211']*x
+        C[2] += dic['d_201']*y + dic['d_210']*x
+        D[0] += dic['d_200']*z**2 + dic['d_201']*y*z + dic['d_202']*y**2
+        D[1] += dic['d_200']*z**2 + dic['d_210']*x*z + dic['d_220']*x**2
+        D[2] += dic['d_202']*y**2 + dic['d_211']*x*y + dic['d_220']*x**2
     if plr in [1,2,3]:
@@
         C[1] += dic['d_101']
-            C[2] += dic['d_110']
-            D[0] += dic['d_100']*u0+dic['d_101']*w0+dic['d_000']
-            D[1] += dic['d_100']*u0+dic['d_110']*v0+dic['d_000']
-            D[2] += dic['d_101']*v0+dic['d_110']*w0+dic['d_000']
-        ABCDE[0] = A[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
-        ABCDE[1] = B[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
-        ABCDE[2] = C[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
-        ABCDE[3] = D[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
+        C[2] += dic['d_100']
+        D[0] += dic['d_100']*z + dic['d_101']*y+dic['d_000']
+        D[1] += dic['d_100']*z + dic['d_110']*x+dic['d_000']
+        D[2] += dic['d_101']*y + dic['d_110']*x+dic['d_000']
+    ABCDE[0] = A[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
+    ABCDE[1] = B[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
+    ABCDE[2] = C[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
+    ABCDE[3] = D[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
     ABCDE[4] = E[nrs]
@@
     matarch[msl]=matarch[msl].astype(str)
-        return ABCDE, matarch, abc
+    return ABCDE, abc, matarch, plr
 
@@
 ```{pyodide-python}
-genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y') 
-genpolycoeff(plr=1,parm=["alpha", "x", "y"], solvd='y',eur=[1, 4, 2])[0]
+#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
+#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='alpha',eur=[1, 2, 4])
+#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='x',eur=[1, 2, 4])[0]
+#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4])[0]
+#genpolycoeffr(form=2,expr="z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",solv='alpha',eur=[1, 2, 4])
 ```

### 2024-09-23 randpython.qmd
abc

--- 2024-08-18 randpython.qmd
@@
 from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
-def rall(sel=[0, 0, 0]):
-    n, m = symbols('n m')
-
-    rxy = Matrix([[m, -n, 0], 
-                  [n, m, 0],
-                  [0, 0, 1]])
-
-    rxz = Matrix([[m, 0, -n], 
-                  [0, 1, 0],
-                  [n, 0, m]])
-
-    ryx = Matrix([[m, n, 0], 
-                  [-n, m, 0],
-                  [0, 0, 1]])
-
-    ryz = Matrix([[1, 0, 0], 
-                  [0, m, -n],
-                  [0, n, m]])
-
-    rzx = Matrix([[m, 0, n], 
-                  [0, 1, 0],
-                  [-n, 0, m]])
-
-    rzy = Matrix([[1, 0, 0], 
-                  [0, m, n],
-                  [0, -n, m]])
-
-    ps = [0, rxy, rxz, ryx, ryz, rzx, rzy]
-
-    allrot = [ps[i] for i in sel]
-    return allrot
-
-def genpolycoeff(equn="alpha=k0+k1*g+k2*h",solv='y',grd=0,parm=["alpha", "x", "y"],plr=1,eur=[1, 4, 2]):
-    x, y, z = sympy.symbols('x y z')
-    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
-    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
-    expr = [Eq(z,k0+k1*x+k2*y),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2),Eq(z,k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3)][plr-1]
-    # Without rotation
-    if grd == 0:
-        #exprc = expr.subs([(z,parm[0]),(x,parm[1]),(y,parm[2])])
-        ls, rs = equn.split('=')
-        eqs = Eq(sympify(ls), sympify(rs))
-        polys = poly(eqs.rhs - eqs.lhs, sympify(solv)).all_coeffs()
-        abc = []
-        uvw = []
-        ABCDE = [0, 0, 0, 0, 0]
-        ABCDE[:len(polys)] = polys
-        return ABCDE, 0, 0
-    # With rotation
-    else:
-        dxyz = {'x': 1, 'y': 2, 'z': 3}
-        # Defining
-        x,  y,  z  = sympy.symbols('x y z')
-        ui, vi, wi = sympy.symbols('ui vi wi')
-        u0, v0, w0 = sympy.symbols('u0 v0 w0')
-        u1, v1, w1 = sympy.symbols('u1 v1 w1')
-        u2, v2, w2 = sympy.symbols('u2 v2 w2')
-        a1, a2, a3 = sympy.symbols('a1 a2 a3')
-        b1, b2, b3 = sympy.symbols('b1 b2 b3')
-        c1, c2, c3 = sympy.symbols('c1 c2 c3')
-        m1, m2, m3 = sympy.symbols('m1 m2 m3')
-        n1, n2, n3 = sympy.symbols('n1 n2 n3')
-        mu, mv, mw = sympy.symbols('mu mv mw')
-        # Replace
-        PS = rall(sel=eur)
-        r0 = Matrix([u0, v0, w0])
-        r1 = PS[0].subs([(n, n1), (m, m1)]) * r0
-        r2 = PS[1].subs([(n, n2), (m, m2)]) * r1
-        RR = PS[2].subs([(n, n3), (m, m3)]) * r2
-        sympy.expand(RR.row(0)[0])
-        sympy.expand(RR.row(1)[0])
-        sympy.expand(RR.row(2)[0])
-        av = sympy.collect(sympy.expand(RR.row(0)[0]), (u0, v0, w0))
-        bv = sympy.collect(sympy.expand(RR.row(1)[0]), (u0, v0, w0))
-        cv = sympy.collect(sympy.expand(RR.row(2)[0]), (u0, v0, w0))
-        a1s = av.coeff(u0)
-        a2s = av.coeff(v0)
-        a3s = av.coeff(w0)
-        b1s = bv.coeff(u0)
-        b2s = bv.coeff(v0)
-        b3s = bv.coeff(w0)
-        c1s = cv.coeff(u0)
-        c2s = cv.coeff(v0)
-        c3s = cv.coeff(w0)
-        Eu = Eq(x, a1s * u0 + a2s * v0 + a3s * w0)
-        Ev = Eq(y, b1s * u0 + b2s * v0 + b3s * w0)
-        Ew = Eq(z, c1s * u0 + c2s * v0 + c3s * w0)
-        abc = [a1s, a2s, a3s, b1s, b2s, b3s, c1s, c2s, c3s]
-        # Manual
-        pvar = [w0, v0, u0, w0**2, v0*w0, v0**2, u0*w0, u0*v0, u0**2, w0**3, v0*w0**2, v0**2*w0, v0**2*w0, v0**3, u0*w0**2, u0*v0*w0, u0*v0**2, u0**2*w0, u0**2*v0, u0**3]
-        # Connect to rotmat
-        Eu = Eq(x, a1 * u0 + a2 * v0 + a3 * w0)
-        Ev = Eq(y, b1 * u0 + b2 * v0 + b3 * w0)
-        Ew = Eq(z, c1 * u0 + c2 * v0 + c3 * w0)
-        # Start with non-rotated
-        exprf = solve(expr,z)[0]-z
-        exprc = exprf.subs([(x, solve(Eu, x)[0]), (y, solve(Ev, y)[0]), (z, solve(Ew, z)[0])])
-        # Reorganize
-        exprr = collect(expand(exprc), pvar)
-        xr = [] 
-        yr = []
-        zr = []
-        clma = ['u0','v0','w0','d','var','expr','expr2']
-        eqsn = len(exprr.args)
-        data = [["0"] * 7 for _ in range(eqsn)]
-        matarch = pandas.DataFrame(data, columns=clma)
-        matarch.loc[0, ['expr','expr2']]=exprr.args[0]
-        matarch.loc[0, ['d']]='d_000'
-        for i in range(1, eqsn):
-            expt = exprr.args[i]
-            expr = expt.args[-1]
-            varn = expt / expr
-            nrfs = len(varn.free_symbols)
-            matarch.loc[i, 'var'] = str(varn)
-            for j in range(0,nrfs):
-                varn = expt.args[j].as_base_exp()[0]
-                pown = expt.args[j].as_base_exp()[1]
-                matarch.loc[i, str(varn)] = pown
-                subd = {a1: a1s, a2: a2s, a3: a3s,b1: b1s, b2: b2s, b3: b3s,c1: c1s, c2: c2s, c3: c3s}
-                matarch.loc[i, 'expr'] = expr
-                matarch.loc[i, 'expr2'] = expr.subs(subd) 
-                cmbx = int(matarch.loc[i, 'u0'])
-                cmby = int(matarch.loc[i, 'v0'])
-                cmbz = int(matarch.loc[i, 'w0'])
-                dr = sum([cmbx, cmby, cmbz])
-                matarch.loc[i,'d']='d_'+"".join([str(dr),str(cmbx),str(cmby)])
-                dic1 = matarch.set_index('d')['expr'].to_dict()
-                dic2 = matarch.set_index('d')['expr2'].to_dict()
-                dic = [dic1,dic2][0]
-                nrs = dxyz[solv]-1
-        ABCDE = [0, 0, 0, 0, 0]
-        A=Matrix([0,0,0])
-        B=Matrix([0,0,0])
-        C=Matrix([0,0,0])
-        D=Matrix([0,0,0])
-        E=Matrix([0,0,0])
-        if plr in [3]:
-            A[0] +=  dic['d_330']
-            A[1] +=  dic['d_303']
-            A[2] +=  dic['d_300']
-            B[0] +=  dic['d_320']*u0+dic['d_321']*w0
-            B[1] +=  dic['d_302']*u0+dic['d_312']*v0
-            B[2] +=  dic['d_301']*w0+dic['d_310']*v0
-            C[0] +=  dic['d_310']*u0**2+dic['d_311']*u0*w0+dic['d_312']*w0**2+dic['d_110']
-            C[1] +=  dic['d_301']*u0**2+dic['d_311']*u0*v0+dic['d_321']*v0**2+dic['d_101']
-            C[2] +=  dic['d_302']*w0**2+dic['d_311']*w0*v0+dic['d_320']*w0**2+dic['d_201']*v0+dic['d_210']*w0+dic['d_110']
-            D[0] += dic['d_300']*u0**3+dic['d_301']*w0*u0**2+dic['d_302']*w0**2*u0+dic['d_303']*w0**3
-            D[1] += dic['d_300']*u0**3+dic['d_310']*u0*v0**2+dic['d_320']*v0**2*u0+dic['d_330']*v0**3
-            D[2] += dic['d_303']*v0**3+dic['d_312']*w0*v0**2+dic['d_321']*w0**2*v0+dic['d_330']*v0**3
-        if plr in [2,3]:
-            B[0] += dic['d_220']
-            B[1] += dic['d_202']
-            B[2] += dic['d_200']
-            C[0] += dic['d_210']*u0+dic['d_211']*w0
-            C[1] += dic['d_201']*u0+dic['d_211']*v0
-            C[2] += dic['d_201']*v0+dic['d_210']*w0
-            D[0] += dic['d_200']*u0**2+dic['d_201']*w0*u0+dic['d_202']*w0**2
-            D[1] += dic['d_200']*u0**2+dic['d_210']*v0*u0+dic['d_220']*v0**2
-            D[2] += dic['d_202']*v0**2+dic['d_211']*v0*w0+dic['d_220']*w0**2
-        if plr in [1,2,3]:
-            C[0] += dic['d_110']
-            C[1] += dic['d_101']
-            C[2] += dic['d_110']
-            D[0] += dic['d_100']*u0+dic['d_101']*w0+dic['d_000']
-            D[1] += dic['d_100']*u0+dic['d_110']*v0+dic['d_000']
-            D[2] += dic['d_101']*v0+dic['d_110']*w0+dic['d_000']
-        ABCDE[0] = A[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
-        ABCDE[1] = B[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
-        ABCDE[2] = C[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
-        ABCDE[3] = D[nrs].subs([(u0,parm[0]),(v0,parm[1]),(w0,parm[2])])
-        ABCDE[4] = E[nrs]
-        indpr = [[2,3,4,0,1],[1,2,3,4,0],[0,1,2,3,4]]
-        ABCDE = [ABCDE[i] for i in indpr[plr-1]]
-        msl = ['u0','v0','w0','expr','expr2']
-        matarch[msl]=matarch[msl].astype(str)
-        return ABCDE, matarch, abc
+abc=123
 ```
@@
 ```{pyodide-python}
-#genpolycoeff(equn="alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2",solv="y")
-#genpolycoeff(plr=1,parm=["alpha", "x", "y"], solv='y',grd=1,eur=[1, 4, 2])[0]
+abc
 ```
@@
 ```{pyodide-python}
-def pareq(ste='(x + y*zeta)/(zeta + 1)', **kwargs):
-    return eval(ste, kwargs)
+abc*2
 ```
 
-```{pyodide-python}
-pareq(ste='(x + y*zeta)/(zeta + 1)', x=0.75, y=0.25, zeta=1)
-pareq(ste='(x + y*zeta)/(zeta + 1)', y=0.25, zeta=1,x=2.75)
+```{r, echo=F, eval=T}
+knitr::knit_exit()
 ```

### 2024-09-23 R/abc.R

@@ -1,55 +1,35 @@
-##' @export abc
-abc <- function(){
-}
-##' @export def
-def <- function(){
-}
-
-##' @export manobj
-#manobj <- function(enfl=NULL,dfa=NULL,svar='y'){
-#  polyc <- setNames(as.vector(lapply(enfl[[1]], as.character)),LETTERS[1:5])
-#  la_e <- unlist(polyc[c(LETTERS[1:5])])
-#  pnr <- sum(la_e!="0")
-#  rootdf <- dfa  %>%
-#    dplyr::mutate(A=pareq(la_e[1],c(as.list(.[,])))) %>%
-#    dplyr::mutate(B=pareq(la_e[2],c(as.list(.[,])))) %>%
-#    dplyr::mutate(C=pareq(la_e[3],c(as.list(.[,])))) %>%
-#    dplyr::mutate(D=pareq(la_e[3],c(as.list(.[,])))) %>%
-#    dplyr::mutate(E=pareq(la_e[3],c(as.list(.[,])))) %>%
-#    dplyr::group_by(P) %>%
-#    #dplyr::mutate(polsolv=py_polysolverW(pnr-1,c(A,B,C,D,E)[1:pnr])) %>%
-#    dplyr::mutate(polsolv=py_polysolver(pnr-1,c(A,B,C,D,E)[1:pnr])) %>%
-#    dplyr::mutate(!!paste0(svar):=Re(polsolv[1])) %>%
-#    dplyr::ungroup()
-#  rootdf[[svar]]
-#}
+##########################################################################################################
 #' @export comdat
-
-comdat <- function(dr=goext,zv=c('alpha','NULL'),xv=c('lamda','Psi_s'),yv=c('lamda','Psi_t')){
+comdat <- function(dr=goext,plr=1,zv=c('NULL','NULL'),xv=c('NULL','NULL'),yv=c('NULL','NULL')){
   P <- dr['P']
   le <- dim(P)[1]
   dr <- dplyr::arrange(dr,P)
   ### Data
-  if (is.null(zv[2])) zv[[2]]<- rep(0,le)
-  z0 <- complex(real=dr[[zv[1]]],imaginary=dr[[zv[2]]])
+  #if (is.null(zv[1]) {zv[[1]]<- rep(0,le)}
+  #if (is.null(zv[2]) {zv[[2]]<- rep(0,le)}
[…]

### 2024-09-23 randpython.qmd
autorun

--- 2024-09-08 randpython.qmd
@@
     return allrot
+```
 
-def genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g'):
+```{pyodide-python}
+def genpolycoeffn(form,expr,solv):
     elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
@@
 
-#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
+```
 
-def genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4]):
-    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
+```{pyodide-python}
+def genpolycoeffr(elem,expr,solv,eur):
+    #elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
     x, y, z = sympy.symbols('x y z')
@@
     k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
-    parm = elem[form-1][:5]
+    parm = elem #elem[form-1][:5]
     pamm = [element + "_m" for element in parm]
@@
         C[2] += dic['d_302']*y**2 + dic['d_311']*x*y + dic['d_320']*x**2
-        D[0] += dic['d_300']*y**3 + dic['d_301']*y*z**2 + dic['d_302']*y**2*y+dic['d_303']*z**3
-        D[1] += dic['d_300']*x**3 + dic['d_310']*x*y**2 + dic['d_320']*y**2*x+dic['d_330']*y**3
+        D[0] += dic['d_300']*y**3 + dic['d_301']*y*z**2 + dic['d_302']*y**2*y + dic['d_303']*z**3
+        D[1] += dic['d_300']*x**3 + dic['d_310']*x*y**2 + dic['d_320']*y**2*x + dic['d_330']*y**3
         D[2] += dic['d_303']*y**3 + dic['d_312']*z*y**2 + dic['d_321']*z**2*y + dic['d_330']*y**3
@@
         C[2] += dic['d_100']
-        D[0] += dic['d_100']*z + dic['d_101']*y+dic['d_000']
-        D[1] += dic['d_100']*z + dic['d_110']*x+dic['d_000']
-        D[2] += dic['d_101']*y + dic['d_110']*x+dic['d_000']
+        D[0] += dic['d_100']*z + dic['d_101']*y + dic['d_000']
+        D[1] += dic['d_100']*z + dic['d_110']*x + dic['d_000']
+        D[2] += dic['d_101']*y + dic['d_110']*x + dic['d_000']
     ABCDE[0] = A[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
@@
     return ABCDE, abc, matarch, plr
-
 ```
@@
 ```{pyodide-python}
-#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
-#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='alpha',eur=[1, 2, 4])
-#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='x',eur=[1, 2, 4])[0]
-#genpolycoeffr(form=1,expr="z=k0+k1*x+k2*y",solv='y',eur=[1, 2, 4])[0]
-#genpolycoeffr(form=2,expr="z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",solv='alpha',eur=[1, 2, 4])
+testn = genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
 ```
@@
 ```{pyodide-python}
-def pareq(ste='(x + y*zeta)/(zeta + 1)', **kwargs):
-    return eval(ste, kwargs)
+testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha')
 ```
 
-```{pyodide-python}
-pareq(ste='(x + y*zeta)/(zeta + 1)', x=0.75, y=0.25, zeta=1)
-pareq(ste='(x + y*zeta)/(zeta + 1)', y=0.25, zeta=1,x=2.75)
+```{r, echo=F, eval=T}
+knitr::knit_exit()
 ```

### 2024-09-23 R/wasmconverting.R

@@ -254,6 +254,7 @@ ballcastsim <- function(dfm=(function(x){data.frame(P=seq(1,x),RV=as.integer(rno
 selreport <- function(
 		      baldata=NULL
 		      ){
+  browser()
   WS <- Sys.info()[['sysname']]=="Emscripten"
   da <- baldata[[1]]
   md <- baldata[[2]]

### 2024-09-23 script/R/testing.R

@@ -15,9 +15,27 @@ aps <- apn3n
 adat <- aps[[1]]
 amet <- aps[[2]]
 ##########################################################################################################
-#slr <- selreport(aps)
+slr <- selreport(aps)
 #slo <- seloutput(slr)
 ##########################################################################################################
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
 vmat <- c(1,2,4)
 plnr <- 1
 googlesheets4::gs4_auth(email="lotariohw26@gmail.com")

### 2024-09-23 addendum/Addendum_az.qmd
closed

@@
 subtitle: "{{< var addnl >}}"
-format:
-  revealjs: 
-    smaller: true
-    toc-depth: 1
-    toc: true 
-execute: 
-  cache: false
-footer: <https://lotariohw26.github.io/ManifoldDestiny/>
-output: 
-  html_document:
-    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
-nocite: |
-  @*
+# format:
+#   revealjs: 
+#     smaller: true
+#     toc-depth: 1
+#     toc: true 
+# execute: 
+#   cache: false
+# footer: <https://lotariohw26.github.io/ManifoldDestiny/>
+# output: 
+#   html_document:
+#     mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
+# nocite: |
+#   @*
 ---
-
-```{r}
-knitr::knit_exit()
-```
 
@@
 ```{r, echo=FALSE, out.width="80%", fig.cap=""}
-pa <- paste0(rprojroot::find_rstudio_root_file(),'/inst/addendum/pngs/ALEXANDER_chart-of-Rs-voting-for-Hobbs.jpg')
+#pa <- paste0(rprojroot::find_rstudio_root_file(),'/inst/addendum/pngs/ALEXANDER_chart-of-Rs-voting-for-Hobbs.jpg')
 knitr::include_graphics(c(pa))

### 2024-09-23 randpython.qmd
testindex

@@
   cache: false
-webr:
-  show-startup-message: false      # Display status of webR initialization
-  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['dplyr','data.table','ggplot2','combinat','plotly','htmltools','broom'] # Pre-install dependencies
-  cell-options:
-    autorun: true
 filters:
@@
 ```
-
-# Python
-
-<head>
-  <script src="https://cdn.jsdelivr.net/pyodide/v0.24.1/full/pyodide.js"></script>
-</head>
-
-<body>
-  <p>
-    You can execute any Python code. Just enter something in the box below and
-    click the button.
-  </p>
-  <input id="code" value="sum([1, 2, 3, 4, 5])" />
-  <button onclick="evaluatePython()">Run</button>
-  <br />
-  <br />
-  <div>Output:</div>
-  <textarea id="output" style="width: 100%;" rows="6" disabled></textarea>
-
-  <script>
-    const output = document.getElementById("output");
-    const code = document.getElementById("code");
-
-    function addToOutput(s) {
-      output.value += ">>>" + code.value + "\n" + s + "\n";
-    }
-
-    output.value = "Initializing...\n";
-    // init Pyodide
-    async function main() {
-      let pyodide = await loadPyodide();
-      output.value += "Ready!\n";
-      return pyodide;
-    }
-    let pyodideReadyPromise = main();
-
-    async function evaluatePython() {
-      let pyodide = await pyodideReadyPromise;
-      try {
-        let output = pyodide.runPython(code.value);
-        addToOutput(output);
-      } catch (err) {
-        addToOutput(err);
-      }
-    }
-  </script>
-</body>
-
-# R
-
-<div>
-  <pre><code id="out">Loading webR, please wait...</code></pre>
-  <input spellcheck="false" autocomplete="off" id="input" type="text">
-  <button onclick="globalThis.sendInput()" id="run">Run</button>
-</div>
-
-<script type="module">
-  /* Create a webR console using the Console helper class */
-  import { Console } from 'https://webr.r-wasm.org/latest/webr.mjs';
-  const webRConsole = new Console({
-    stdout: line => document.getElementById('out').append(line + '\n'),
-    stderr: line => document.getElementById('out').append(line + '\n'),
-    prompt: p => document.getElementById('out').append(p),
-  });
-  webRConsole.run();
-
-  /* Write to the webR console using the ``stdin()`` method */
-  let input = document.getElementById('input');
-  globalThis.sendInput = () => {
-    webRConsole.stdin(input.value);
-    document.getElementById('out').append(input.value + '\n');
-    input.value = "";
-  }
-
-  /* Send input on Enter key */
-  input.addEventListener(
-    "keydown",
-    (evt) => {if(evt.keyCode === 13) globalThis.sendInput()}
-  );
-</script>
-
-**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**
-
-```{r, echo=F}
-knitr::knit_exit()
-```

### 2024-09-23 index.qmd
closed
pyodide

@@
   - panelize
+  - pyodide
   - webr
@@
 # script/R/simulations.R
+# ![](pngs/md.png)
 ```
@@
 **Based upon the ideas developed by Edward K. Solomon**
-![](pngs/md.png)
+
+```{pyodide-python}
+import sympy, pandas, numpy
+from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
+def rall(sel=[0, 0, 0]):
+    n, m = symbols('n m')
+
+    rxy = Matrix([[m, -n, 0], 
+                  [n, m, 0],
+                  [0, 0, 1]])
+
+    rxz = Matrix([[m, 0, -n], 
+                  [0, 1, 0],
+                  [n, 0, m]])
+
+    ryx = Matrix([[m, n, 0], 
+                  [-n, m, 0],
+                  [0, 0, 1]])
+
+    ryz = Matrix([[1, 0, 0], 
+                  [0, m, -n],
+                  [0, n, m]])
+
+    rzx = Matrix([[m, 0, n], 
+                  [0, 1, 0],
+                  [-n, 0, m]])
+
+    rzy = Matrix([[1, 0, 0], 
+                  [0, m, n],
+                  [0, -n, m]])
+
+    ps = [0, rxy, rxz, ryx, ryz, rzx, rzy]
+
+    allrot = [ps[i] for i in sel]
+    return allrot
+```
+
+```{pyodide-python}
+def genpolycoeffn(form,expr,solv):
+    elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
+    x, y, z = sympy.symbols('x y z')
+    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
+    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
+    parm = elem[2-1][:5]
+    ls, rs = expr.split('=')
+    expr = Eq(sympify(ls), sympify(rs))
+    plr = int(sympy.total_degree(expr))-1
+    polys = poly(expr.rhs - expr.lhs, sympify(solv)).all_coeffs()
+    abc = [1,0,0,0,1,0,0,0,1]
+    uvw = []
+    ABCDE = [0, 0, 0, 0, 0]
+    ABCDE[:len(polys)] = polys
+    matarch = 0
+    return ABCDE, abc, matarch, plr
+
+```
+
+```{pyodide-python}
+def genpolycoeffr(elem,expr,solv,eur):
+    #elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
+    x, y, z = sympy.symbols('x y z')
+    alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')
+    k0, k1, k2, k3, k4, k5, k6, k7, k8, k9, k10 = symbols('k0:11')
+    parm = elem #elem[form-1][:5]
+    pamm = [element + "_m" for element in parm]
+    ls, rs = expr.split('=')
+    expr = Eq(sympify(ls), sympify(rs))
+    plr = int(sympy.total_degree(expr))-1
+    dxyz = {'x': 1, 'y': 2, 'z': 3}
+    nrs = parm.index(solv)
+    # Defining
+    x,  y,  z  = sympy.symbols('x y z')
+    ui, vi, wi = sympy.symbols('ui vi wi')
+    u0, v0, w0 = sympy.symbols('u0 v0 w0')
+    u1, v1, w1 = sympy.symbols('u1 v1 w1')
+    u2, v2, w2 = sympy.symbols('u2 v2 w2')
+    a1, a2, a3 = sympy.symbols('a1 a2 a3')
+    b1, b2, b3 = sympy.symbols('b1 b2 b3')
+    c1, c2, c3 = sympy.symbols('c1 c2 c3')
+    m1, m2, m3 = sympy.symbols('m1 m2 m3')
+    n1, n2, n3 = sympy.symbols('n1 n2 n3')
+    mu, mv, mw = sympy.symbols('mu mv mw')
+    # Replace
+    PS = rall(sel=eur)
+    r0 = Matrix([u0, v0, w0])
+    r1 = PS[0].subs([(n, n1), (m, m1)]) * r0
+    r2 = PS[1].subs([(n, n2), (m, m2)]) * r1
+    RR = PS[2].subs([(n, n3), (m, m3)]) * r2
+    sympy.expand(RR.row(0)[0])
+    sympy.expand(RR.row(1)[0])
+    sympy.expand(RR.row(2)[0])
+    av = sympy.collect(sympy.expand(RR.row(0)[0]), (u0, v0, w0))
+    bv = sympy.collect(sympy.expand(RR.row(1)[0]), (u0, v0, w0))
+    cv = sympy.collect(sympy.expand(RR.row(2)[0]), (u0, v0, w0))
+    a1s = av.coeff(u0)
+    a2s = av.coeff(v0)
+    a3s = av.coeff(w0)
+    b1s = bv.coeff(u0)
+    b2s = bv.coeff(v0)
+    b3s = bv.coeff(w0)
+    c1s = cv.coeff(u0)
+    c2s = cv.coeff(v0)
+    c3s = cv.coeff(w0)
+    Eu = Eq(x, a1s * u0 + a2s * v0 + a3s * w0)
+    Ev = Eq(y, b1s * u0 + b2s * v0 + b3s * w0)
+    Ew = Eq(z, c1s * u0 + c2s * v0 + c3s * w0)
+    abc = [a1s, a2s, a3s, b1s, b2s, b3s, c1s, c2s, c3s]
+    # Manual
+    pvar = [w0, v0, u0, w0**2, v0*w0, v0**2, u0*w0, u0*v0, u0**2, w0**3, v0*w0**2, v0**2*w0, v0**2*w0, v0**3, u0*w0**2, u0*v0*w0, u0*v0**2, u0**2*w0, u0**2*v0, u0**3]
+    # Connect to rotmat
+    Eu = Eq(x, a1 * u0 + a2 * v0 + a3 * w0)
+    Ev = Eq(y, b1 * u0 + b2 * v0 + b3 * w0)
+    Ew = Eq(z, c1 * u0 + c2 * v0 + c3 * w0)
+    exprf = solve(expr,z)[0]-z
+    exprc = exprf.subs([(x, solve(Eu, x)[0]), (y, solve(Ev, y)[0]), (z, solve(Ew, z)[0])])
+    # Reorganize
+    exprr = collect(expand(exprc), pvar)
+    xr = [] 
+    yr = []
+    zr = []
+    clma = ['u0','v0','w0','d','var','expr','expr2']
+    eqsn = len(exprr.args)
+    data = [["0"] * 7 for _ in range(eqsn)]
+    matarch = pandas.DataFrame(data, columns=clma)
+    matarch.loc[0, ['expr','expr2']]=exprr.args[0]
+    matarch.loc[0, ['d']]='d_000'
+    for i in range(1, eqsn):
+        expt = exprr.args[i]
+        expr = expt.args[-1]
+        varn = expt / expr
+        nrfs = len(varn.free_symbols)
+        #varn.free_symbols
+        matarch.loc[i, 'var'] = str(varn)
+        for j in range(0,nrfs):
+            varn = expt.args[j].as_base_exp()[0]
+            pown = expt.args[j].as_base_exp()[1]
+            matarch.loc[i, str(varn)] = pown
+            subd = {a1: a1s, a2: a2s, a3: a3s,b1: b1s, b2: b2s, b3: b3s,c1: c1s, c2: c2s, c3: c3s}
+            matarch.loc[i, 'expr'] = expr
+            matarch.loc[i, 'expr2'] = expr.subs(subd) 
+            cmbx = int(matarch.loc[i, 'u0'])
+            cmby = int(matarch.loc[i, 'v0'])
+            cmbz = int(matarch.loc[i, 'w0'])
+            dr = sum([cmbx, cmby, cmbz])
+            matarch.loc[i,'d']='d_'+"".join([str(dr),str(cmbx),str(cmby)])
+            dic1 = matarch.set_index('d')['expr'].to_dict()
+            dic2 = matarch.set_index('d')['expr2'].to_dict()
+            dic = [dic1,dic2][0]
+    ABCDE = [0, 0, 0, 0, 0]
+    A=Matrix([0,0,0])
+    B=Matrix([0,0,0])
+    C=Matrix([0,0,0])
+    D=Matrix([0,0,0])
+    E=Matrix([0,0,0])
+    if plr in [3]:
+        A[0] += dic['d_330']
+        A[1] += dic['d_303']
+        A[2] += dic['d_300']
+        B[0] += dic['d_320']*z + dic['d_321']*y
+        B[1] += dic['d_302']*z + dic['d_312']*x
+        B[2] += dic['d_301']*y + dic['d_310']*x
+        C[0] += dic['d_310']*z**2 + dic['d_311']*y*z + dic['d_312']*y**2
+        C[1] += dic['d_301']*z**2 + dic['d_311']*x*z + dic['d_321']*x**2
+        C[2] += dic['d_302']*y**2 + dic['d_311']*x*y + dic['d_320']*x**2
+        D[0] += dic['d_300']*y**3 + dic['d_301']*y*z**2 + dic['d_302']*y**2*y + dic['d_303']*z**3
+        D[1] += dic['d_300']*x**3 + dic['d_310']*x*y**2 + dic['d_320']*y**2*x + dic['d_330']*y**3
+        D[2] += dic['d_303']*y**3 + dic['d_312']*z*y**2 + dic['d_321']*z**2*y + dic['d_330']*y**3
+    if plr in [2,3]:
+        B[0] += dic['d_220']
+        B[1] += dic['d_202']
+        B[2] += dic['d_200']
+        C[0] += dic['d_210']*z + dic['d_211']*y
+        C[1] += dic['d_201']*z + dic['d_211']*x
+        C[2] += dic['d_201']*y + dic['d_210']*x
+        D[0] += dic['d_200']*z**2 + dic['d_201']*y*z + dic['d_202']*y**2
+        D[1] += dic['d_200']*z**2 + dic['d_210']*x*z + dic['d_220']*x**2
+        D[2] += dic['d_202']*y**2 + dic['d_211']*x*y + dic['d_220']*x**2
+    if plr in [1,2,3]:
+        C[0] += dic['d_110']
+        C[1] += dic['d_101']
+        C[2] += dic['d_100']
+        D[0] += dic['d_100']*z + dic['d_101']*y + dic['d_000']
+        D[1] += dic['d_100']*z + dic['d_110']*x + dic['d_000']
+        D[2] += dic['d_101']*y + dic['d_110']*x + dic['d_000']
+    ABCDE[0] = A[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
+    ABCDE[1] = B[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
+    ABCDE[2] = C[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
+    ABCDE[3] = D[nrs].subs([(x,pamm[0]),(y,pamm[1]),(z,pamm[2])])
+    ABCDE[4] = E[nrs]
+    indpr = [[2,3,4,0,1],[1,2,3,4,0],[0,1,2,3,4]]
+    ABCDE = [ABCDE[i] for i in indpr[plr-1]]
+    msl = ['u0','v0','w0','expr','expr2']
+    matarch[msl]=matarch[msl].astype(str)
+    return ABCDE, abc, matarch, plr
+```
+
+```{pyodide-python}
+testn = genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
+```
+
+```{pyodide-python}
+testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha')
+```
 

### 2024-09-23 index.qmd
abc

@@
 ```{pyodide-python}
-testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha')
+testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',[1,2,4])
 ```

### 2024-09-23 script/R/testing.R

@@ -19,10 +19,8 @@ slr <- selreport(aps)
 ##########################################################################################################
 adat
 amet
-2+2
 
 
-alpha *
 
 
 

### 2024-09-23 script/python/polysolver.py

@@ -33,6 +33,7 @@ def rall(sel=[0, 0, 0]):
     return allrot
 
 def genpolycoeffn(form,expr,solv):
+    forp = {'N': 1, 'H': 2, 'O': 3}
     elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
     x, y, z = sympy.symbols('x y z')
     alpha, g, h, n, m, zeta, Gamma, lamda, ui = symbols('alpha g h n m zeta Gamma lamda ui')

### 2024-09-23 index.qmd
eur

--- 2024-09-23 index.qmd
@@
 ```{pyodide-python}
-testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha')
+testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',eur=[1,2,4])
 ```

### 2024-09-23 index.qmd
abc

@@
   cache: false
-webr:
-  show-startup-message: true      # Display status of webR initialization
-  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
-  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
-  cell-options:
-    autorun: true
+#webr:
+#  show-startup-message: true      # Display status of webR initialization
+#  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
+#  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
+#  cell-options:
+#    autorun: true
 filters:
@@
   - pyodide
-  - webr
 ---
@@
 **Based upon the ideas developed by Edward K. Solomon**
+
+```{r}
+knitr::knit_exit()
+```
 

### 2024-09-28 tab.qmd
abc

@@
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
-apps <- appn1
+apps <- apn1n
 #
@@
 selo <- seloutput(selreport(apps))
-options(digits = 2)                                                                                               
+#options(digits = 2)                                                                                               
 ```

### 2024-09-28 tabset.qmd
abc

--- 2024-08-17 tabset.qmd
@@
 ```
+
+::: {.callout-caution collapse="true"}
+## {{< var tabh.h0 >}}
+```{r}
+#| echo: false
+#| output: false
+apps <- appsn
+```
+{{< include tab.qmd >}}
+:::
 ::: {.callout-caution collapse="true"}
@@
 :::
-
 ::: {.callout-caution collapse="true"}
@@
 #| output: false
-apps <- appn1
+apps <- apn1n
 ```
@@
 :::
-
+```{r}
+knitr::knit_exit()
+```
 ::: {.callout-caution collapse="true"}

### 2024-09-29 docs/calculator.qmd
outlined

---
title: ""
execute: 
  cache: false
webr:
  show-startup-message: false      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['complexlm','dplyr','data.table','ggplot2','combinat','plotly','htmltools','broom'] # Pre-install dependencies
  cell-options:
    autorun: false
filters:
  - panelize
  - webr
  - pyodide
---

```{webr-r}
#| echo: fenced
#| eval: true
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
#ls(package:ManifoldDestinyWASMP)
#data(package='ManifoldDestinyWASMD')
dfl <- appn3
```

```{webr-r}
df1[[1]]
```

**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

```{r, echo=F}
knitr::knit_exit()
```

### 2024-09-29 script/R/testing.R

@@ -1,34 +1,27 @@
 library(ggplot2)
 library(complexlm)
 library(dplyr)
-ManifoldDestiny::wasmconload()
 library(ManifoldDestiny)
+ManifoldDestiny::wasmconload()
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/abc.R"))
 ls(package:ManifoldDestiny)
-aps <- apn1n
+#aps <- apn1n
 #aps <- apn2n
-#aps <- apn3n
+aps <- apn3r
 #aps <- apn4n
 adat <- aps[[1]]
 amet <- aps[[2]]
 ##########################################################################################################
 slr <- selreport(aps)
-slo <- seloutput(slr)
+
+#slo <- seloutput(slr)
 ##########################################################################################################
+md$prg$eqp
+amet$pm$prg$eqp
 
-
-
-
-
-
-
-
-
-
-
-
+amet$mtd
 
 vmat <- c(1,2,4)
 plnr <- 1
@@ -805,4 +798,5 @@ abc <- distinct(dplyr::select(re$tdf,a1,a2,a3,b1,b2,b3,c1,c2,c3,k1,k2,k3,k4,k5,k
 
 # 
 abc$k9*6*abc$b1*abc$b2*abc$b3+abc$k6*6*abc$a1*abc$a2*abc$a3
+
 

### 2024-09-29 randpython.qmd
python

@@
 import sympy, pandas, numpy
-from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
+```
+
+```{pyodide-python}
 def rall(sel=[0, 0, 0]):
@@
 def genpolycoeffn(form,expr,solv):
+    forp = {'N': 1, 'H': 2, 'O': 3}
     elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
@@
 
+```{pyodide-python}
+pareq(ste="(a + b)*c", a=2, b=4, c=3)
+```
+
 ```{r, echo=F, eval=T}

### 2024-09-29 script/R/testing.R

@@ -9,20 +9,14 @@ source(paste0(rprojroot::find_rstudio_root_file(),"/R/abc.R"))
 ls(package:ManifoldDestiny)
 #aps <- apn1n
 #aps <- apn2n
-aps <- apn3r
-#aps <- apn4n
-adat <- aps[[1]]
-amet <- aps[[2]]
+#aps <- apn3r
+##aps <- apn4n
+#adat <- aps[[1]]
+#amet <- aps[[2]]
+###########################################################################################################
+#slr <- selreport(aps)
+##slo <- seloutput(slr)
 ##########################################################################################################
-slr <- selreport(aps)
-
-#slo <- seloutput(slr)
-##########################################################################################################
-md$prg$eqp
-amet$pm$prg$eqp
-
-amet$mtd
-
 vmat <- c(1,2,4)
 plnr <- 1
 googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
@@ -30,21 +24,13 @@ url <- "https://docs.google.com/spreadsheets/d/1Qf51QlYkCmd8h72R5JrFUt9VYCgpq8U_
 crot <- googlesheets4::read_sheet(url, range="G3:R228") %>% dplyr::mutate(P = dplyr::row_number(.[[1]]))
 names(crot) <- c("PW","PN","g","h","alpha","Data#","u[0]","v[0]","w[0]","x","y","z","P") 
 rotuvw <- erotation(crot,c("g","h","alpha","P"),rs=c(1,2,4),gra=c(-44.9573,7.001545,-19.9677)) 
-re <- Estimation(rotuvw,2)
-#re$regression("z=k0+k1*y+k2*x+k3*y2+k4*yx+k5*x2+k6*y3+k7*y2x+k8*yx2+k9*x3")
+re <- Estimation(rotuvw,"H")
 re$regression("z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3")
-broom::tidy(re$regsum[[1]])$estimate
-#  [1]  0.001643394  1.075717880 -0.731335532  0.064912642  0.064007760 -0.785443920
[…]

### 2024-10-06 randpython.qmd
test

--- 2024-09-23 randpython.qmd
@@
 ---
+
+```{pyodide-python}
+import sympy, pandas, numpy, math
+```
 
@@
     return allrot
-```
 
-```{pyodide-python}
 def genpolycoeffn(form,expr,solv):
+    forp = {'N': 1, 'H': 2, 'O': 3}
     elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
@@
 
-```
+#genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
 
-```{pyodide-python}
 def genpolycoeffr(elem,expr,solv,eur):
     #elem = [["alpha","x","y","zeta","lamda","Omega"], ["alpha","g","h","Gamma","Omega","lamda"], ["alpha","m","n","xi","lamda","Omega"]]
+    #breakpoint()
     x, y, z = sympy.symbols('x y z')
@@
     return ABCDE, abc, matarch, plr
+
+genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',[1,2,4])[2]
+
+def pareq(ste='(x + y*zeta)/(zeta + 1)', **kwargs):
+    return eval(ste, kwargs)
+
+prv = ["g","h","alpha"]
+rve = [1, 2, 4]
+gra = [-44.9573,7.001545,-19.9677]
+eqs = ["z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3","alpha=k0+k1*g+k2*h+k3*Gamma"][0]
+sfo = ['g','h','alpha'][2]
+test = genpolycoeffr(elem=prv,expr=eqs,solv=sfo,eur=rve)
+m1v = math.cos(math.radians(gra[0]))
+m2v = math.cos(math.radians(gra[1]))
+m3v = math.cos(math.radians(gra[2]))
+n1v = math.sin(math.radians(gra[0]))
+n2v = math.sin(math.radians(gra[1]))
+n3v = math.sin(math.radians(gra[2]))
+m1v, m2v, m3v, n1v, n2v, n3v
+k0=0.001643394  
+k1=1.075717880 
+k2=-0.731335532
+k3=0.064912642  
+k4=0.064007760 
+k5=-0.785443920
+k6=0.092375583 
+k7=-1.271709722  
+k8=3.038048882
+k9=0.923841730
+
+# I
+a1 = pareq(ste=str(test[1][0]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+a2 = pareq(ste=str(test[1][1]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+a3 = pareq(ste=str(test[1][2]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+b1 = pareq(ste=str(test[1][3]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+b2 = pareq(ste=str(test[1][4]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+b3 = pareq(ste=str(test[1][5]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+c1 = pareq(ste=str(test[1][6]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+c2 = pareq(ste=str(test[1][7]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+c3 = pareq(ste=str(test[1][8]),m1=m1v,m2=m2v,m3=m3v,n1=n1v,n2=n2v,n3=n3v)
+
+results = []
+for nr in range(20):  # Example: looping from 0 to 19, you can change the range as needed
+    lhs = test[2]['d'][nr]
+    rhs = test[2]['expr'][nr]
+    pareq_result = plsv.pareq(
+        str(rhs),
+        a1=a1, a2=a2, a3=a3,
+        b1=b1, b2=b2, b3=b3,
+        c1=c1, c2=c2, c3=c3,
+        k0=k0, k1=k1, k2=k2, k3=k3, k4=k4, k5=k5, k6=k6, k7=k7, k8=k8, k9=k9
+    )
+    # Append the result dictionary directly to the list
+    results.append({
+        'lhs': lhs,
+        'rhs': rhs,
+        'pareq_result': pareq_result
+    })
+
+df_results = pd.DataFrame(results)
 ```
@@
 ```{pyodide-python}
-testn = genpolycoeffn(form=2,expr="alpha=k0+k1*g+k2*h",solv='g')
+a1, a2, a3, b1, b2, b3, c1, c2, c3
 ```
@@
 ```{pyodide-python}
-testr = genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha')
+# https://docs.google.com/spreadsheets/d/1Qf51QlYkCmd8h72R5JrFUt9VYCgpq8U_RyQTLzOoiFc/edit?gid=499474525#gid=499474525
+df_results 
 ```
-
-```{r, echo=F, eval=T}
-knitr::knit_exit()
-```

### 2024-10-06 inst/shinyapps/r2rsim/app.R

@@ -1,18 +1,18 @@
-library(plotly)
-library(dplyr)
-library(shiny)
-library(combinat)
-library(htmltools)
-library(ggplot2)
-library(gridExtra)
-library(broom)
-library(tidyr)
-library(combinat)
-library(AlgebraicHaploPackage)
-library(huxtable)
-library(kableExtra)
-library(polynom)
-#ManifoldDestiny::wasmconload()
+#library(plotly)
+#library(dplyr)
+#library(shiny)
+#library(combinat)
+#library(htmltools)
+#library(ggplot2)
+#library(gridExtra)
+#library(broom)
+#library(tidyr)
+#library(combinat)
+#library(AlgebraicHaploPackage)
+#library(huxtable)
+#library(kableExtra)
+#library(polynom)
+ManifoldDestiny::wasmconload()
 #Shiny
 ui <- fluidPage(
   titlePanel("R2 Simulator"),

### 2024-10-06 randpython.qmd
trystackframe

@@
 import sympy, pandas, numpy, math
-```
-
-```{pyodide-python}
-import sympy, pandas, numpy
 from sympy import solve, Eq, symbols, latex, simplify, diff, poly, sympify, Matrix, pprint, collect, expand, Poly, Symbol, Pow
@@
 
-genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',[1,2,4])[2]
+# genpolycoeffr(["g","h","alpha"],"z=k0+k1*x+k2*y+k3*x**2+k4*x*y+k5*y**2+k6*x**3+k7*x**2*y+k8*y**2*x+k9*y**3",'alpha',[1,2,4])[2]
 
@@
     rhs = test[2]['expr'][nr]
-    pareq_result = plsv.pareq(
+    pareq_result = pareq(
         str(rhs),
@@
 
-df_results = pd.DataFrame(results)
+df_results = pandas.DataFrame(results)
+
 ```
 
+# Output
 ```{pyodide-python}
@@
 ```{pyodide-python}
-# https://docs.google.com/spreadsheets/d/1Qf51QlYkCmd8h72R5JrFUt9VYCgpq8U_RyQTLzOoiFc/edit?gid=499474525#gid=499474525
 df_results

### 2024-10-20 abc.qmd
cont

@@
----
-title: "{{< var titll >}}"
-subtitle: "Based upon the ideas developed by Edward K. Solomon"
-format:
-  revealjs:
-    drop:
-      engine: webr
-      webr:
-        packages:
-          - ggplot2
-          - dplyr
-execute: 
-  cache: false
-footer: <https://lotariohw26.github.io/ManifoldDestiny/>
-output: 
-  html_document:
-    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
-nocite: |
-  @*
----
-
 # Abc
 
-2+2
+[abc](https://www.arapahoevotes.gov/sites/default/files/2023-12/REDACTED_CVR_Export_20231128_0.xls)

### 2024-10-20 R/wasmnonverting.R

@@ -10,8 +10,7 @@ recoudatr <- function(mda=NULL,prn=1){
         U = !!rlang::parse_expr(mda$spr$stuv[3]),
         V = !!rlang::parse_expr(mda$spr$stuv[4])
       ) %>%
-  #!
-  mutate(R = dplyr::if_else(!is.na(R), R, S + T + U + V)) 
+ { if ("R" %in% .[]) . else mutate(., R = S + T + U + V)}  
   assign(mda$nid,list(as.data.frame(gsh),mda))
   do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
   return(mda$nid)

### 2024-10-20 abc.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+echo 'abc'
+

### 2024-10-20 inst/shinyapps/r2rsim/app.R

@@ -1,17 +1,17 @@
-#library(plotly)
-#library(dplyr)
-#library(shiny)
-#library(combinat)
-#library(htmltools)
-#library(ggplot2)
-#library(gridExtra)
-#library(broom)
-#library(tidyr)
-#library(combinat)
-#library(AlgebraicHaploPackage)
-#library(huxtable)
-#library(kableExtra)
-#library(polynom)
+library(plotly)
+library(dplyr)
+library(shiny)
+library(combinat)
+library(htmltools)
+library(ggplot2)
+library(gridExtra)
+library(broom)
+library(tidyr)
+library(combinat)
+library(AlgebraicHaploPackage)
+library(huxtable)
+library(kableExtra)
+library(polynom)
 ManifoldDestiny::wasmconload()
 #Shiny
 ui <- fluidPage(

### 2024-10-26 presentation.qmd
abc
presupd
set

@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-ssr <- selreport(ManifoldDestiny::appsn)
-rsr  <- selreport(ManifoldDestiny::apprn)
-round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
+#ssr <- selreport(ManifoldDestiny::appsn)
+#rsr <- selreport(ManifoldDestiny::apprn)
+#round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
 ```
 
-# {{< var sec1.nmn >}}
+# {{< var sec1.1 >}}
+
 Ed. Solomon
@@
 
-## {{< var sec1.un1 >}}
+## {{< var sec1.2.1 >}}
+
 - Two candidates: A, B
@@
 
-## {{< var sec1.un2 >}}
+## {{< var sec1.2.2 >}}
+
 ```{r, echo=F}
@@
 
-## {{< var sec1.un3 >}}
+## {{< var sec1.2.3 >}}
+
 ```{r, echo=F}
@@
 
-## {{< var sec1.un4 >}}
+## {{< var sec1.2.4 >}}
+
 ```{r, echo=F}
@@
 
-## {{< var sec1.un5 >}}
+## {{< var sec1.2.6 >}}
 
@@
 
-## {{< var sec1.un6 >}}
+## {{< var sec1.2.6 >}}
 
@@
 
-## {{< var sec1.un7 >}}
+## {{< var sec1.2.7 >}}
 
@@
 
-# {{< var sec2.nmn >}}
+# {{< var sec2.1 >}}
+
+# {{< var sec9.1 >}}
+
+::: {#refs}
+:::
+
+```{r}
+knitr::knit_exit()
+```
+
 ## {{< var sec2.un1 >}}

### 2024-10-26 prerendr.R

@@ -1,26 +1,36 @@
-##############################################################################################################
-# Settings
+############################################################################################################## Settings
 apps <- F # Oppdater plot
+eqma <- F # Oppdater plot
 ##############################################################################################################
-# Packages
 suppressMessages(ManifoldDestiny::wasmconload())
 ###############################################################################################################
 ManifoldDestiny::bm()
 ###############################################################################################################
 if(isTRUE(apps)) {
-x <- 1
-appl <- list(c("abc","ManifoldDestiny"), c("manimp","ManifoldDestiny"),c("empapp","ManifoldDestiny"), c("restor","ManifoldDestiny"))
-  lapply(1:1, function(x) {
-		 x <- 1
-     system.file("shinyapps",appl[x][[1]][1], package=appl[x][[1]][2]) %>%
-     fs::dir_copy(paste0("inst/shinyapps/",appl[x][[1]][1]), overwrite = TRUE)
-     dp <- paste0("inst/shinyapps/",appl[[x]][1])
-     tp <- paste0("docs/",appl[[x]][1])
-     shinylive::export(dp,tp)
-  })
+  appl <- list(c("abc","ManifoldDestiny"), c("manimp","ManifoldDestiny"),c("empapp","ManifoldDestiny"), c("restor","ManifoldDestiny"))
+    lapply(1:1, function(x) {
+  		 x <- 1
+       system.file("shinyapps",appl[x][[1]][1], package=appl[x][[1]][2]) %>%
[…]

### 2024-10-26 presentation.qmd
abc

@@
 laws_df1 <- ManifoldDestiny::eqdef$meql
+laws1 <- laws_df1 
 laws_df2 <- ManifoldDestiny::eqdef$meqs
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-#ssr <- selreport(ManifoldDestiny::appsn)
-#rsr <- selreport(ManifoldDestiny::apprn)
-#round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
+ssr <- selreport(ManifoldDestiny::appsn)
+rsr <- selreport(ManifoldDestiny::apprn)
+round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))
 ```
@@
 
-# {{< var sec9.1 >}}
-
-::: {#refs}
-:::
-
-```{r}
-knitr::knit_exit()
-```
-
-## {{< var sec2.un1 >}}
+## {{< var sec2.2.1 >}}
 - We have identified three ways of counting
@@
 ```{r}
-kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
-
+#kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
 ```
@@
 ```{r} 
-kable(laws2, format = "markdown", escape = FALSE)
+#kable(laws2, format = "markdown", escape = FALSE)
 
@@
 
-## {{< var sec2.un4 >}}
+## {{< var sec2.2.2 >}}
 
@@
 
-## {{< var sec2.un1 >}}
+## {{< var sec2.2.5 >}}
 
@@
 
-# {{< var sec3.nmn >}}
+# {{< var sec3.1 >}}
+
+```{r}
+knitr::knit_exit()
+```
 
@@
 :::
+
+# {{< var sec9.1 >}}
+
+::: {#refs}
+:::

### 2024-10-26 script/R/stylized.R

@@ -59,3 +59,5 @@ clambda <- round(c1df$sdfc$lamda,2)
 cg <- round(c1df$sdfc$g,2)
 ch <- round(c1df$sdfc$y,2)
 cGamma <- round(c1df$sdfc$Gamma,2)
+
+

### 2024-10-28 presentation.qmd
mda

@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-ssr <- selreport(ManifoldDestiny::appsn)
-rsr <- selreport(ManifoldDestiny::apprn)
+#ssr <- selreport(ManifoldDestiny::apsnn)
+#rsr <- selreport(ManifoldDestiny::aprhn)
 round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))

### 2024-10-28 R/wasmconverting.R

@@ -305,10 +305,10 @@ selreport <- function(
   ies$regression(md$sol$eq[2])
   ies$diagnostics()
   ## Identify
-  ### Bowplot
+  ## Bowplot
   cob <- Countinggraphs(da,selvar=names(da))
   if (md$prg$cnd==1) {cob$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp,prma=md$prg$prma)}
-  cob$sortpre(4,3)
+  cob$sortpre("S",polyn=6)
   cob$plot2d(4,labs=list(title=NULL,x="precinct (normalized)",y="percentage",caption=NULL,alpha=0.4,size=0.5),
   selv=2)
   return(list(co=co,
@@ -611,11 +611,11 @@ Countingprocess$methods(initialize=function(sdfinp=NULL,
   pdata <- rdfci  %>% dplyr::arrange(alpha) 
   pnset <- min(length(rdfci$pri)-1,polyn)
   ### Init values standard form
-  polyc[[1]] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
+  polyc[['S']] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
   ### Init valuesstats:: hybrid form
-  polyc[[2]] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
+  polyc[['H']] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
   ##### Init valustats::es opposition form
-  polyc[[3]] <<- stats::lm(rdfci$lamda ~ poly(rdfci$pri, pnset, raw=TRUE))
+  polyc[['O']] <<- stats::lm(rdfci$lamda ~ poly(rdfci$pri, pnset, raw=TRUE))
 
 })
 
@@ -714,11 +714,10 @@ Countingprocess$methods(purging=function(z=0,stuv=c(0,0,0,0),blup=c(0,1),eqp=c("
     dplyr::arrange(P)
   if (pri==1) {print(dim(rdfci)[1]); print(dim(rdfc)[1])}
 })
-Countingprocess$methods(sortpre=function(form="N",
+Countingprocess$methods(sortpre=function(form="S",
 					 polyn=6,
 					 sortby='alpha'
 					 ){
-
[…]

### 2024-10-28 data-raw/record_static.R

@@ -24,33 +24,35 @@ proa <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
 prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
 ztec <- c(0,1)	
 gsh <- ballcastsim(perv,prow,proa,prob,ztec)
-mda <- qenvas$apsnn
-assign(mda$nid,list(gsh,mda))
+assign(names(qenvas)[1],list(gsh,mda))
 do.call("use_data", list(as.name(mda$nid), overwrite = TRUE))
 ## Rigged election
 set.seed(1)
 cogr <- Countinggraphs(gsh)
 copl <- cogr$polyc[[1]][[1]]
 plfc <- c(0.21,0.21,0.21,0.21)
-exn <- c("aprnn","aprhn","apron","aprnr")[1:3]
+exn <- names(qenvas)[-1]
 rigv <- lapply(1:3, function(x) { 
-  mda <- qenvas[[exn[x]]]
-  exs <- list(
-	    frm=mda$sol$fr,
-  	    pre=mda$sol$pr,
-  	    end=mda$sol$de,
-  	    eq=mda$sol$eq[1],
-  	    va=mda$sol$va,
-            rot=mda$sol$ro
-  	  )
-  cogr$mansys(sygen=exs)
-  cogr$polyc[[1]]
-  #cogr$setres(NULL,1)
-  cogr$setres(plfc[x],1)
-  cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
-  assign(mda$nid,list(cogr$rdfc,mda))
-  do.call("use_data", list(as.name(mda$nid), overwrite = T))
+ x <- 1
+ mda <- qenvas[[exn[x]]]
+ exs <- list(
+           frm=mda$sol$fr,
+ 	    pre=mda$sol$pr,
+ 	    end=mda$sol$de,
+ 	    eq=mda$sol$eq[1],
+ 	    va=mda$sol$va,
+           rot=mda$sol$ro
+ 	  )
+ cogr$mansys(sygen=exs)
+ cogr$polyc[[1]]
+ #cogr$setres(NULL,1)
+ cogr$setres(plfc[x],1)
+ cogr$manimp(init_par=c(k0=0,k1=0.60,k2=0.40),wn=c(0,0),man=T)
+ assign(mda$nid,list(cogr$rdfc,mda))
[…]

### 2024-10-28 prerendr.R

@@ -30,12 +30,23 @@ if(isTRUE(eqma)) {
   usethis::use_data(eqpar, overwrite = TRUE)
 }
 ###############################################################################################################
-form <- list(N=c(1),H=c(2),O=c(3))
-form[['N']]
+form <- list(S=c(1),H=c(2),O=c(3))
+form[['S']]
 usethis::use_data(form, overwrite = TRUE)
 ManifoldDestiny::bm()
 ManifoldDestiny::form
-2+2
+stick <-
+  list(parm=list(
+  S=c("alpha","x","y","zeta","lamda","Omega"),
+  H=c("alpha","g","h","Gamma","Omega","lamda"),
+  O=c("alpha","m","n","xi","lamda","Omega"),
+  B=c("alpha","x","y","Omega","m","n")
+  ),
+  forms=list('_s','o_h','h_o')) 
+usethis::use_data(stick, overwrite = TRUE)
+frmsel <- list(c(1,2,3,4,5,6),c(7,8,9,10,11,12),c(13,14,15,16,17,18),c(19,20,21,22,23,24))
+usethis::use_data(frmsel, overwrite = TRUE)
+bm()
 ###############################################################################################################
 #lpku <<- list(
 #  S = list(
@@ -92,18 +103,6 @@ ManifoldDestiny::form
 #  "Twentieth Law", "$\\zeta=\\frac{\\lambda_{1}-\\alpha_{1}}{(y_{2}-y_{1})+(\\alpha_{1}-\\lambda_{1})}$", "$\\gamma=\\frac{\\Omega_{1}-\\alpha_{1}}{(h_{2}-h_{1})+(\\alpha_{1}-\\Omega_{1})}$", "$\\xi=\\frac{\\lambda_{1}-\\Omega_{1}}{(n_{2}-n_{1})+(\\Omega_{1}-\\lambda_{1})}$"
 #)
 ################################################################################################################
-#stick <-
-#  list(parm=list(
-#  S=c("alpha","x","y","zeta","lamda","Omega"),
-#  H=c("alpha","g","h","Gamma","Omega","lamda"),
-#  O=c("alpha","m","n","xi","lamda","Omega"),
-#  B=c("alpha","x","y","Omega","m","n")
-#  ),
-#  forms=list('_s','o_h','h_o')) 
-#usethis::use_data(stick, overwrite = TRUE)
-#  
[…]

### 2024-10-29 presentation.qmd
abc

--- 2024-10-26 presentation.qmd
@@
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
-ssr <- selreport(ManifoldDestiny::appsn)
-rsr <- selreport(ManifoldDestiny::apprn)
+ssr <- selreport(ManifoldDestiny::apsnn)
+rsr <- selreport(ManifoldDestiny::aprhn)
 round(integral(polynomial(unname(ssr[[1]]$polyc[[1]]$coefficients))))

### 2024-10-29 tabset.qmd
abc

@@
 #| output: false
-apps <- appsn
+apps <- apsnn
 ```
@@
 #| output: false
-apps <- apprn
+apps <- aprnn
 ```
@@
 #| output: false
-apps <- apprh
+apps <- aprnn
 ```
@@
 #| output: false
-apps <- appro
+apps <- aprnn
 ```
@@
 #| output: false
-apps <- appn2
+apps <- apn1n
 ```

### 2024-10-29 script/R/testing.R

@@ -7,23 +7,23 @@ source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/abc.R"))
 ls(package:ManifoldDestiny)
-#aps <- appsn
-#aps <- apn5an
-#aps <- apn5bn
 aps <- apn1n
 aps <- apn2n
 #aps <- apn3r
-##aps <- apn4n
+#aps <- apn4n
+aps <- apsnn
+aps <- aprnn
+#aps <- apn5an
+#aps <- apn5bn
 adat <- aps[[1]]
 amet <- aps[[2]]
 ############################################################################################################
 slr <- selreport(aps)
-#slo <- seloutput(slr)
+slo <- seloutput(slr)
 ###########################################################################################################
 frm <- 1
 co <- Countinggraphs(adat,selvar=c('PN','P','R','S','T','U','V'))
 co$purging(prma=c(59,191,206,214,299,300,215,217,317,318),pri=1)
-bm()
 co$sortpre(frm)
 
 co$descriptive(frm)

### 2024-10-31 presentation.qmd
settingpres
abc

@@
 laws_df2 <- ManifoldDestiny::eqdef$meqs
+laws2 <- laws_df2
 source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
@@
 
+```{r}
+knitr::knit_exit()
+```
+
 ### 40 isometris
@@
 ```{r}
+#laws1
 #kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
@@
 
-# {{< var sec3.1 >}}
-
 ```{r}
@@
 ```
+
+# {{< var sec3.1 >}}
 
@@
 
+```{r}
+knitr::knit_exit()
+```
+
 ## {{< var sec6.un1 >}}
@@
 
+```{r}
+knitr::knit_exit()
+```
+
 - Our four applications

### 2024-10-31 tab.qmd
abc

--- 2024-08-16 tab.qmd
@@
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
-apps <- appn1
+apps <- apsnn
 #

### 2024-11-01 presentation.qmd
abc

--- 2024-10-29 presentation.qmd
@@
 library(polynom)
+library(ManifoldDestiny)
 modlat <- eqpar$meql
 laws_df1 <- ManifoldDestiny::eqdef$meql
-laws1 <- laws_df1 
 laws_df2 <- ManifoldDestiny::eqdef$meqs
@@
 ```{r}
-#kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
+kable(laws1[,c(5,6,7,8)], format = "markdown", escape = FALSE) # %>% kableExtra::kable_styling(font_size=8)
 ```
@@
 ```{r} 
-#kable(laws2, format = "markdown", escape = FALSE)
+kable(laws2, format = "markdown", escape = FALSE)
 

### 2024-11-01 prerendr.R

@@ -1,178 +1,84 @@
+library(tibble)
 ############################################################################################################## Settings
 apps <- F # Oppdater plot
 eqma <- F # Oppdater plot
 ##############################################################################################################
-suppressMessages(ManifoldDestiny::wasmconload())
-###############################################################################################################
-ManifoldDestiny::bm()
-###############################################################################################################
-if(isTRUE(apps)) {
-  appl <- list(c("abc","ManifoldDestiny"), c("manimp","ManifoldDestiny"),c("empapp","ManifoldDestiny"), c("restor","ManifoldDestiny"))
-    lapply(1:1, function(x) {
-  		 x <- 1
-       system.file("shinyapps",appl[x][[1]][1], package=appl[x][[1]][2]) %>%
-       fs::dir_copy(paste0("inst/shinyapps/",appl[x][[1]][1]), overwrite = TRUE)
-       dp <- paste0("inst/shinyapps/",appl[[x]][1])
-       tp <- paste0("docs/",appl[[x]][1])
-       shinylive::export(dp,tp)
-    })
-}
-#runStaticServer("docs/r2rsim")
-###############################################################################################################
-fdm <- paste0(rprojroot::find_rstudio_root_file(),'/script/python/20_laws_40_isos.py')
-reticulate::source_python(fdm)
-eqdef <- list(meql=reticulate::py$dfl,meqs=reticulate::py$dfs)
-usethis::use_data(eqdef, overwrite = TRUE)
-if(isTRUE(eqma)) {
[…]

### 2024-11-01 tab.qmd
upd

--- 2024-08-16 tab.qmd
@@
 source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
-apps <- appn1
-#
+apps <- apsnn
 adat <- apps[[1]]

### 2024-11-01 tabset.qmd
abc

@@
 ::: {.callout-caution collapse="true"}
-## {{< var sec6.un1 >}}
+## {{< var sec6.2.1 >}}
 ```{r}
@@
 ::: {.callout-caution collapse="true"}
-## {{< var sec6.un2 >}}
+## {{< var sec6.2.2 >}}
 ```{r}
@@
 ::: {.callout-caution collapse="true"}
-## {{< var sec6.un3 >}}
+## {{< var sec6.2.3 >}}
 ```{r}
@@
 ::: {.callout-caution collapse="true"}
-## {{< var sec6.un4 >}}
+## {{< var sec6.2.4 >}}
 ```{r}

### 2024-11-10 tab.qmd
more

@@
 apps <- apsnn
+#apps <- aprnn
+#apps <- aprhn
+#apps <- apron
+#apps <- apn1n
+#apps <- apn2n
+#apps <- apn3r
+#apps <- apn4n
+#apps <- apn5an
+#apps <- apn5bn
 adat <- apps[[1]]

### 2024-11-10 tabset.qmd
fixed
more

@@
 #| output: false
-apps <- aprnn
+apps <- aprhn
 ```

### 2024-11-10 R/wasmconverting.R

@@ -280,9 +280,11 @@ selreport <- function(
   co <- Countinggraphs(da)
   if (md$prg$cnd==1) {co$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp,frm=md$prg$frp,prma=md$prg$prma)}
   co$sortpre(frm)
+  co$plot2d(selv=c(1:3,6))
+  #browser()
+  #co$pl_2dsort
   co$descriptive(frm)
   co$r2siminput(frm)
-  co$plot2d()
   co$plotxy(frm)
   co$resplot(frm)
   co$plotly3d(partition=frm)
@@ -308,10 +310,10 @@ selreport <- function(
   # Bowplot
   cob <- Countinggraphs(da,selvar=names(da))
   if (md$prg$cnd==1) {cob$purging(z=md$prg$z,stuv=md$prg$stuv,blup=md$prg$blup,eqp=md$prg$eqp,prma=md$prg$prma)}
-  cob$sortpre("S",polyn=6)
+  cob$sortpre("B",polyn=6)
   cob$plot2d(labs=list(title=NULL,x="precinct (normalized)",y="percentage",caption=NULL,alpha=0.4,size=0.5),
-  selv=c(1:3,6))
-  #cob$pl_2dsort[[1]]
+  selv=c(1:6))
+  cob$pl_2dsort[[1]]
   return(list(co=co,
               ges=ges,
               ies=ies,
@@ -613,6 +615,7 @@ Countingprocess$methods(initialize=function(sdfinp=NULL,
   pnset <- min(length(rdfci$pri)-1,polyn)
   ### Init values standard form
   polyc[['S']] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
+  polyc[['B']] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
   ### Init valuesstats:: hybrid form
   polyc[['H']] <<- stats::lm(rdfci$alpha ~ poly(rdfci$pri, pnset, raw=TRUE))
   ##### Init valustats::es opposition form
@@ -717,12 +720,13 @@ Countingprocess$methods(purging=function(z=0,stuv=c(0,0,0,0),blup=c(0,1),eqp=c("
 })
 Countingprocess$methods(sortpre=function(form="S",
 					 polyn=6,
-					 sortby='alpha'
[…]

### 2024-11-10 data-raw/pdf/abc.R

@@ -1,23 +1,0 @@
-library(googlesheets4)                                                                                        
-library(tidyverse)                                                                                            
-library(readxl)                                                                                          
-ls(package:readxl)
-
-
-pp <- paste0(rprojroot::find_rstudio_root_file(),"/data-raw/pdf/BaltimorePrecincts.xlsx")
-sh <- excel_sheets(pp)                                                             
-#length(sh)
-lbal <- lapply(1:length(), function(x) dim(read_excel(pp, sheet=x)))
-
-dplyr::bind_rows(lbal[[1]],lbal[[2]])
-
-View(lbal[[1]])
-
-abc <- cbind(lbal[[1]],lbal[[2]])
-
-
-usethis::use_data(lbal, overwrite=T)
-
-
-
-

### 2024-11-14 docs/presentation.qmd
setup

--- 2024-11-01 presentation.qmd
@@
 
-```{r}
-knitr::knit_exit()
-```
-
-## {{< var sec3.un1 >}}
+## {{< var sec3.2.1 >}}
 ```{r}
@@
 
-## {{< var sec3.un2 >}}
+## {{< var sec3.2.2 >}}
 
@@
 
-# {{< var sec5.nmn >}}
+# {{< var sec5.1 >}}
 
@@
 
-# {{< var sec6.nmn >}}
+# {{< var sec6.1 >}}
 
@@
 
-```{r}
-knitr::knit_exit()
-```
-
-## {{< var sec6.un1 >}}
+## {{< var sec6.2.1 >}}
 ```{r}
@@
 
-## {{< var sec6.un2 >}}
+## {{< var sec6.2.2 >}}
 ```{r}
@@
 
-## {{< var sec6.un3 >}}
+## {{< var sec6.2.3 >}}
 ```{r}
@@
 #| output: false
-apps <- appn2
+apps <- apn1n
 ```
 {{< include tabpar.qmd >}}
-## {{< var sec6.un4 >}}
+## {{< var sec6.2.3 >}}
 ```{r}
@@
 #| output: false
-apps <- appn4
+apps <- apn1n
 ```
@@
 
-# {{< var sec7.nmn >}}
-
-## {{< var sec7.un1 >}}
-
-# {{< var sec8.nmn >}}
+# {{< var sec8.1 >}}
 
@@
 
-```{r}
-knitr::knit_exit()
-```
-
 - Our four applications
@@
 
-# {{< var sec9.nmn >}}
+# {{< var sec9.1 >}}
 
@@
 
-# {{< var sec9.1 >}}
-
-::: {#refs}
-:::
+```{r}
+knitr::knit_exit()
+```

### 2024-11-15 docs/analyzer.qmd
rec

--- 2024-08-17 analyzer.qmd
@@
 library(ManifoldDestinyWASMD)
-#ls(package:ManifoldDestinyWASMP)
-#data(package='ManifoldDestinyWASMD')
-apps <- appn0
+ls(package:ManifoldDestinyWASMP)
+data(package='ManifoldDestinyWASMD')
 ```
@@
 ```{webr-r}
-adat <- apps[[1]]
-amet <- apps[[2]]
-cob <- Countinggraphs(adat)
-cob$purging(z=0) 
-def <- Estimation(cob$rdfce)
+#apps <- appn0
+#adat <- apps[[1]]
+#amet <- apps[[2]]
+#cob <- Countinggraphs(adat)
+#cob$purging(z=0) 
+#def <- Estimation(cob$rdfce)
 ```

### 2024-11-15 data-raw/datatraf.R

@@ -1,3 +1,4 @@
+# Arizona
 library(ManifoldDestiny)
 library(dplyr)
 stodfl <- dyntabulation()

### 2024-11-15 prerendr.R

@@ -1,8 +1,73 @@
 library(tibble)
+ManifoldDestiny::wasmconload()
+library(usethis)
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+qrel2022 <- yaml::yaml.load_file(paste0(rprojroot::find_rstudio_root_file(),"/_apps_rel_2022.yml"))
+qrel2024 <- yaml::yaml.load_file(paste0(rprojroot::find_rstudio_root_file(),"/_apps_rel_2024.yml"))
+qrelhis <- yaml::yaml.load_file(paste0(rprojroot::find_rstudio_root_file(),"/_apps_his.yml"))
+qrelsim <- yaml::yaml.load_file(paste0(rprojroot::find_rstudio_root_file(),"/_apps_sim.yml"))
+googlesheets4::gs4_auth(email="lotariohw26@gmail.com")
 ############################################################################################################## Settings
+reqa <- F # Oppdater plot
+reqs <- F # Oppdater plot
 apps <- F # Oppdater plot
 eqma <- F # Oppdater plot
 ##############################################################################################################
+# 2024
+recoudatr(qrel2024$pma24)
+# Applications
+
+#recoudatr(qenvae$apn2n)
+#recoudatr(qenvae$apn3r)
+#recoudatr(qenvae$apn4n)
+#recoudatr(qenvae$apn5an)
+#recoudatr(qenvae$apn5bn)
+#ManifoldDestiny::bm()
+
+
+
+######################################################################################################################################################
+# Simulation
+## Normal 
+set.seed(1)
+perv <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(100)
+prow <- c(m=0.51,s=0.10)
+proa <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
+prob <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
+ztec <- c(0,1)	
+gsh <- ballcastsim(perv,prow,proa,prob,ztec)
+assign(names(qenvas)[1],list(gsh,qenvas[[1]]))
+do.call("use_data", list(as.name(qenvas[[1]]$nid), overwrite = TRUE))
+
+## Rigged election
+cogr <- Countinggraphs(gsh)
[…]

### 2024-11-15 analyzer.qmd
addedata

@@
 ```{webr-r}
+apps <- pma24[[1]]
 adat <- apps[[1]]
 amet <- apps[[2]]
-cob <- Countinggraphs(adat)
-cob$purging(z=0) 
-def <- Estimation(cob$rdfce)
+```
+
+```{r}
+knitr::knit_exit()
+```
+
+```{webr-r}
+#apps <- appn0
+#adat <- apps[[1]]
+#amet <- apps[[2]]
+#cob <- Countinggraphs(adat)
+#cob$purging(z=0) 
+#def <- Estimation(cob$rdfce)
 ```

### 2024-11-15 script/R/testing2024.R

@@ -1,0 +1,14 @@
+library(ggplot2)
+library(complexlm)
+library(dplyr)
+library(ManifoldDestiny)
+ManifoldDestiny::wasmconload()
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
+source(paste0(rprojroot::find_rstudio_root_file(),"/R/abc.R"))
+ls(package:ManifoldDestiny)
+aps <- apn1n
+
+co <- Countinggraphs(aps,selvar=c('P','R','S','T','U','V'))
+
+View(pma24[[1]])

### 2025-04-10 index.qmd
abc
cont

@@
----
+si---
 title: "{{< var titll >}}"
@@
 **Based upon the ideas developed by Edward K. Solomon**
+
+**Last time updated: {{< now timestamp >}}**
 

### 2025-04-27 presentation.qmd
upd

@@
 ---
+
+# {{< var sec1.1 >}}
+
+```{r}
+knitr::knit_exit()
+```
 
